### 2017-03-01 mnras_template.tex
Update on Overleaf.

% mnras_template.tex 
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{natbib}
\usepackage{xcolor}
\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[SL Challenge]{Strong Gravitational Finding Lensing Challenge}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1}$\thanks{E-mail: robertbenton.metcalf@unibo.it}
A. N. Other,$$
Third Author$$
and Fourth Author$$
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}

\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}

\section{The Challenge}

\section{the simulations}

\section{lens finding methods}

\subsection{GAHEC IRAP}

Arcfinder (Alard, 2006, Cabanac et al. 2007, More et al., 2012) is a fast linear method that computes a pixelwise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images. Arcfinder then extract contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness. A final thresholding is set to maximize purity over completeness on a few typical arcs of the dataset.
For the current SL challenge, arcfinder was tunned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.  A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code as a linux line command. Arcfinder took a couple of hours to run on the entire dataset with some overheads due to the dataset format. The code is publicly available at https://github.com/rcabanac/arcfinder.

optional fig included:
From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties.
\section{results}

\section{Conclusions \& discussion}

\section*{Acknowledgements}

The Acknowledgements section is not numbered. Here you can thank helpful
colleagues, acknowledge funding agencies, telescopes and facilities used etc.
Try to keep it short.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

%\bibliographystyle{mnras}
%\bibliography{example} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Author}{2012}]{Author2012}
Author A.~N., 2013, Journal of Improbable Astronomy, 1, 1
\bibitem[\protect\citeauthoryear{Others}{2013}]{Others2013}
Others S., 2012, Journal of Interesting Stuff, 17, 198
\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2017-03-01 paper.tex
edit

\documentclass[useAMS,usenatbib]{mn2e}

% A Monthly Notices of the Royal Astronomical Society sample TeX file.
% The teX file has had all publication information removed and been left intentionally blank
% Created by: Martyn Bristow, M.Bristow@2007.ljmu.ac.uk, http://martynbristow.co.uk
% Edit this file to suit your needs, but be careful not to remove something important
% I have added sample images, tables and equations to help you if your don't know how to write them in LaTeX and to make your life easier.

\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage{natbib}
\usepackage{xcolor}

\def\aap{Astronomy \& Astrophysics}
\def\apj{The Astrophysical Journal}
\def\mnras{Monthly Notices of the Royal Astronomical Society}

\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\newcommand{\red}[1]{{\color{red} #1}}

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

\title[SL Challenge]{Strong Gravitational  Lensing Finding Challenge}

\author[R. B. Metcalf {\it et al.}]{
R. Benton Metcalf,$^{1}$\thanks{E-mail: robertbenton.metcalf@unibo.it} R\'emi Cabanac,$^2$ 
A. N. Other,$^3$ \\
% List of institutions
$^{1}$Department of Physics and Astronomy, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
$^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
}

\begin{document}

\date{Accepted . Received ; in original form }

\maketitle

\label{firstpage}

% Abstract of the paper
\begin{abstract}

\end{abstract}

\begin{keywords}
gravitational lensing -- cosmology 
\end{keywords}

\section{Introduction}

some numbers about future surveys

\section{The Challenge}

\section{the simulations}

\section{lens finding methods}

This section contains short descriptions of the lens finding methods that were used in 
the challenge.  Each subsection refers to a team which gave a separate entry.

\subsection{GAHEC IRAP}

\begin{figure}
 \includegraphics[width=\columnwidth]{Cabanac/arcmethod.pdf}
 \caption{\footnotesize  GAHEC IRAP) From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties. 
}
 \label{fig:Cabanac}
\end{figure}

Arcfinder \citep{2006astro.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} is a fast linear method that computes a pixelwise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images. Arcfinder then extract contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness. A final thresholding is set to maximize purity over completeness on a few typical arcs of the dataset.
For the current SL challenge, arcfinder was tunned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.  A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code as a linux line command. Arcfinder took a couple of hours to run on the entire dataset with some overheads due to the dataset format. The code is publicly available at https://github.com/rcabanac/arcfinder.

\red{Referenc to figure \ref{fig:Cabanac}?}
\section{results}

\section{Conclusions \& discussion}

It is clear that the robustness of lens finders against falsely classifying unusual galaxies as lenses was not adequitely tested in this challenge.  Some of the methods which appear overly conservative in this test might be better at avoiding false positives in real data.  This can be seen as a form of overfitting to the test set.
In future challenges we wish to concentrate on this aspect of the problem.

\section*{Acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

\bibliographystyle{mn2e}
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

\appendix

\label{lastpage}
\end{document}

### 2017-03-02 paper.tex
Edit.

@@
  \includegraphics[width=\columnwidth]{Cabanac/arcmethod.pdf}
- \caption{\footnotesize  GAHEC IRAP) From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties.
+ \caption{ (GAHEC IRAP) From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties.
 }
@@
 
-\red{Referenc to figure \ref{fig:Cabanac}?}
+\red{Reference to figure \ref{fig:Cabanac}?}
 \section{results}
@@
 In future challenges we wish to concentrate on this aspect of the problem.
+
+Human inspection was the only method to find the jackpot lens
 

### 2017-03-06 paper.tex
Edit.

@@
 \usepackage{ae,aecompl}
+\usepackage{hyperref}
 
@@
 
-\title[SL Challenge]{Strong Gravitational  Lensing Finding Challenge}
+\title[SL Challenge]{The Strong Gravitational  Lens Finding Challenge}
 
 \author[R. B. Metcalf {\it et al.}]{
-R. Benton Metcalf,$^{1}$\thanks{E-mail: robertbenton.metcalf@unibo.it} R\'emi Cabanac,$^2$ 
-A. N. Other,$^3$ \\
+R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} M. Meneghetti,$^4$ R\'emi Cabanac,$^2$ Emmanuel Bertin,$^3$ 
+and  \\
 % List of institutions
-$^{1}$Department of Physics and Astronomy, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
+$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
 $^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
+$^{3}$ Sorbonne Universités, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014, Paris \\
+$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
 }
@@
 
-\subsection{GAHEC IRAP}
+\subsection{GAHEC IRAP (Remi Cabanac)}
 
@@
 \red{Reference to figure \ref{fig:Cabanac}?}
+
+\subsection{AstrOmatic (Emmanuel Bertin)}
+
+The lens detector is based on a convolutional neural network (CNN), trained with the provided training datasets.
+The CNN is implemented in Python, using the TensorFlow framework\footnote{http://www.tensorflow.org/}.
+Both ground multichannel and space monochannel image classifiers have the exact same CNN architecture.
+
+The network itself consists of three convolutional layers ($11\times 11\times 32$, $5\times 5 \times 64$ and $3\times 3\times 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer.
+The first five layers use the ELU (Exponential Linear Unit) activation function \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
+Dropout regularization \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
+
+Prior to entering the first convolutional layer, input image data are rescaled and dynamic-range compressed with function $f(x) =
+\mathrm{arcsinh} (10^{11} x)$, and bad pixels are simply set to 0.
+Data augmentation is performed in the form of random up-down and left-right image flipping, plus $k\pi/2$ rotations, where $k$ is a random integer in the $[0,3]$ range.
+Additionally, a small rotation with random angle $\theta$ is applied, involving bicubic image resampling.
+$\theta$ follows a Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma_{\theta}=5^{\circ}$.
+No attempt was made to generate and randomize bad pixel masks in the data augmentation process.
+
+The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$.
+The network is trained on a Titan-X ``Pascal'' nVidia GPU using the Adam gradient-based optimizer \citep{2014arXiv1412.6980K} during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
+Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.
+
 \section{results}
@@
 \section*{Acknowledgements}
+
+EB thanks Raphael Gavazzi for proposing him to participate to the challenge.
 

### 2017-03-07 paper.tex
Edit.

--- 2017-03-02 paper.tex
@@
 R. Benton Metcalf,$^{1}$\thanks{E-mail: robertbenton.metcalf@unibo.it} R\'emi Cabanac,$^2$ 
-A. N. Other,$^3$ \\
+Alessandro Sonnenfeld,$^5$ \\
 % List of institutions
@@
 $^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
+$^{5}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
 }
@@
 \red{Reference to figure \ref{fig:Cabanac}?}
+
+\subsection{YattaLens Lite (Alessandro Sonnenfeld)}
+YattaLensLite is a simpler version of the algorithm YattaLens (Sonnenfeld et al. in prep.), modified to meet the time constraints of the challenge.
+YattaLensLite subtracts a model surface brightness profile describing the lens galaxy from the $g$-band image, then runs SExtractor to detect tangentially elongated or ring-shaped objects, which are interpreted as lensed images.
+In the ground-based challenge, the model lens surface brightness profile is obtained by taking a rescaled version of the $i$-band image.
+The difference in color between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
+However in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
+at the smallest radius between the position where the surface brightness is comparable to the sky background level or the position of a positive radial gradient in surface brightness, if detected.
+
+In the space-based challenge it is not possible to separate lens and source based on color, because only data in one band is provided.
+The lens light model then is produced by taking a centrally-inverted image and then using the same truncation prescription used with ground-based data.
+The central inversion step is taken to reduce the chances of subtracting flux from lensed images, which are in general not centrally symmetric as opposed to typical lens galaxies.
+
+In the full version of YattaLens, a lens modeling step is performed to improve the purity of the sample. However, such a procedure is too time consuming and was not performed in this challenge.
+
 \section{results}
@@
 \section*{Acknowledgements}
+
+AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.
+RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349.
 

### 2017-03-08 paper.tex
Edit.

@@
 
+\subsection{figures of merit}
+
+In deriving a good figure of merit for evaluating lens finding algorithms one needs to take into account the particular nature of this problem.
+The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or {\bf ROC} curve.
+This a plot of the true positive rate (TPR) and the false positive rate (FPR).
+In this case these are defined as
+\begin{align}
+{\rm TPR} &= \frac{\textrm{ number of true lenses classified as lenses}}{\textrm{ total number of true lenses}} \\
+{\rm FPR} &= \frac{\textrm{number of non-lenses classified as lenses}}{\textrm{ total number of non-lenses}}
+\end{align}
+The classifier generally gives a probability of a case being a lens, $p$ in which case a threshold is set and everything with $p$ greater is classified as a lens and everything smaller classified as not a lens.
+The TPR and FPR are then plotted as a curve parametrised by this threshold.
+At $p=1$ all of the cases are classified as non-lenses and so TPR=FPR=1 and at $p=0$ all of the cases are classified as lenses so TPR=FPR=0.
+These points are always added to the ROC curve.
+If the classifier made random guesses then the ratio of lenses to non-lenses would be the same as the ratio of the number of cases classified as lens to the number of cases classified as non-lenses and so TPR=FPR.
+The better a classifier is the smaller the FPR and the larger the TPR so the further away from this diagonal line it will be.
+When a classifier provides only a binary classification or a discrete ranking the ROC connects the endpoints to the discrete points found be using each rank as a threshold.
+
+A common figure of merit for a classifier is the area under the ROC ({\bf AUROC}).
+This evaluates the overall ability of a classifier to distinguish between cases.
+This was the criterion on which the challenge participants were told to optimize.
+However, in the case of gravitational lensing this is not the only thing, and not the most important thing, to consider.
+Gravitational lenses are rare events, but to improve the discrimination and training of the classifies the fraction lenses in the boosted to something around half.
+In these circumstances it is important to consider the absolute number of cases that will be missclassified when the fraction of true cases is closer to what is expected in the data.
+
+If the rates of false positives and false negatives remain the same in real data  the contamination of the sample will be
+\begin{align}
+\frac{\rm FP}{\rm TP} \simeq \frac{\rm FPR}{\rm TPR} \left(\frac{\textrm{number of non-lenses in sample}}{\textrm{number of lenses is sample}} \right)
+\end{align}
+Since only about one in a thousand objects will be lenses (perhaps somewhat more depending on pre-selection) the contamination will be high unless the FPR is much less than the TPR.
+For this reason we consider some additional figures of merit.
+
+The {\bf TPR0} will be defined as the highest TPR reached, as a function of $p$ threshold, before a single false positive occurs in the test set of 100,000 images.
+This is the point were the ROC meets the FPR = 0 axis.
+This quantity highly penalizes classifiers with discrete ranking which often get TPR0 = 0 because their highest classification level is not conservative enough to eliminate all false positives.
+We also define {\bf TPR10} which is the TPR at the point were less than ten false positives are made.
+If the TP
+rate is boosted from the FPR by a factor of 1,000 in a realistic data set with would correspond to about a 10\% contamination.
+
+In addition to these considerations, the performance of a classifier is a function of many characteristics of the lens system.
+It might be that one classifier is good at finding systems with large Einstein radii and incomplete arcs, but not as good at finding small complete Einstein rings that are blended with the light of the lens galaxy.
+Also lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test data set.
+We want to include these objects because we want to test the limits of the classifiers.
+As we will see, if you restrict your objectives to detecting only lensed images with surface brightness above threshold, for example, the "best" algorithm might change and the TPR will change.
+For this reason we plot the AUROC, TPR0 and TPR10 as a function of several variables for all the entries.
+This is done by removing all the lenses that do not exceed the threshold and then recalculating the these quantities, the number of non-lenses remains the same.
+
+***
+\subsection{plots}
+
 \section{Conclusions \& discussion}
 
-It is clear that the robustness of lens finders against falsely classifying unusual galaxies as lenses was not adequitely tested in this challenge.
+It is clear that the robustness of lens finders against falsely classifying unusual galaxies as lenses was not adequately tested in this challenge.
 Some of the methods which appear overly conservative in this test might be better at avoiding false positives in real data.
-This can be seen as a form of overfitting to the test set.
+This can be seen as a form of over fitting to the test set.
 In future challenges we wish to concentrate on this aspect of the problem.

### 2017-03-08 paper.tex
Edit.

@@
 \subsection{YattaLens Lite (Alessandro Sonnenfeld)}
-YattaLensLite is a simpler version of the algorithm YattaLens (Sonnenfeld et al. in prep.), modified to meet the time constraints of the challenge.
+YattaLensLite is a simpler version of the algorithm YattaLens \citep{Sonnenfeld17}, modified to meet the time constraints of the challenge.
 YattaLensLite subtracts a model surface brightness profile describing the lens galaxy from the $g$-band image, then runs SExtractor to detect tangentially elongated or ring-shaped objects, which are interpreted as lensed images.

### 2017-03-09 paper.tex

@@
 \documentclass[useAMS,usenatbib]{mn2e}
-
-% A Monthly Notices of the Royal Astronomical Society sample TeX file.
-% The teX file has had all publication information removed and been left intentionally blank
-% Created by: Martyn Bristow, M.Bristow@2007.ljmu.ac.uk, http://martynbristow.co.uk
-% Edit this file to suit your needs, but be careful not to remove something important
-% I have added sample images, tables and equations to help you if your don't know how to write them in LaTeX and to make your life easier.
 
@@
 
-\title[SL Challenge]{Strong Gravitational  Lensing Finding Challenge}
+\title[SL Challenge]{The Strong Gravitational  Lens Finding Challenge}
 
 \author[R. B. Metcalf {\it et al.}]{
-R. Benton Metcalf,$^{1}$\thanks{E-mail: robertbenton.metcalf@unibo.it} R\'emi Cabanac,$^2$ 
-Alessandro Sonnenfeld,$^5$ \\
+R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} M. Meneghetti,$^4$ R\'emi Cabanac,$^2$ Emmanuel Bertin,$^3$ Alessandro Sonnenfeld,$^5$ and \\
 % List of institutions
-$^{1}$Department of Physics and Astronomy, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
+$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
 $^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
+$^{3}$ Sorbonne Universités, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014, Paris \\
+$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
 $^{5}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
@@
 \red{Reference to figure \ref{fig:Cabanac}?}
+
+\subsection{AstrOmatic (Emmanuel Bertin)}
+
+The lens detector is based on a convolutional neural network (CNN), trained with the provided training datasets.
+The CNN is implemented in Python, using the TensorFlow framework\footnote{http://www.tensorflow.org/}.
+Both ground multichannel and space monochannel image classifiers have the exact same CNN architecture.
+
+The network itself consists of three convolutional layers ($11\times 11\times 32$, $5\times 5 \times 64$ and $3\times 3\times 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer.
+The first five layers use the ELU (Exponential Linear Unit) activation function \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
+Dropout regularization \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
+
+Prior to entering the first convolutional layer, input image data are rescaled and dynamic-range compressed with function $f(x) =
+\mathrm{arcsinh} (10^{11} x)$, and bad pixels are simply set to 0.
+Data augmentation is performed in the form of random up-down and left-right image flipping, plus $k\pi/2$ rotations, where $k$ is a random integer in the $[0,3]$ range.
+Additionally, a small rotation with random angle $\theta$ is applied, involving bicubic image resampling.
+$\theta$ follows a Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma_{\theta}=5^{\circ}$.
+No attempt was made to generate and randomize bad pixel masks in the data augmentation process.
+
+The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$.
+The network is trained on a Titan-X ``Pascal'' nVidia GPU using the Adam gradient-based optimizer \citep{2014arXiv1412.6980K} during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
+Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.
 
@@
 
+EB thanks Raphael Gavazzi for proposing him to participate to the challenge.
 AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.

### 2017-04-04 paper.tex
Added Philippa.

@@
 \usepackage{xcolor}
+\usepackage{import}
 
@@
 \def\mnras{Monthly Notices of the Royal Astronomical Society}
+\def\aj{Astronomical Journal}
+\def\aaps{AAPS}
 
@@
 \author[R. B. Metcalf {\it et al.}]{
-R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} M. Meneghetti,$^4$ R\'emi Cabanac,$^2$ Emmanuel Bertin,$^3$ Alessandro Sonnenfeld,$^5$ and \\
+R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
+M. Meneghetti,$^4$ 
+Fabio Bellagamba,$^1$
+Emmanuel Bertin,$^3$ 
+\newauthor
+R\'emi Cabanac,$^2$ 
+Remi Flamary,$^8$
+Mario Geiger,$^6$ 
+Philippa Hartley,$^7$
+Neal Jackson,$^7$ 
+\newauthor
+Jean-Paul Kneib,$^6$
+Christoph Sch\"{a}fer,$^6$ 
+Alessandro Sonnenfeld,$^5$ 
+Amit Tagore,$^7$
+\newauthor
+and ?\\
 % List of institutions
@@
 $^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
-$^{3}$ Sorbonne Universités, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014, Paris \\
+$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014,\\ Paris France.\\
 $^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
-$^{5}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+$^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
+$^{6}$ EPFL\\
+$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of Manchester, Oxford Rd, Manchester M13 9PL, UK \\
+$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique, Observatoire de la C\^{o}te d'Azur, \\ Parc Valrose, 06108 Nice, France \\
 }
@@
 \begin{abstract}
-
+The present the results of an open gravitational lens finding challenge.
+Participants were asked to classify 100,000 candidate objects as to whether they were gravitational lenses or not with the goal of developing better automated methods for finding lenses in large data sets.
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:introduction}
 
@@
 
+some background of passed methods
+
+The paper is organized as follows.
+The form of the challenge and its rules are described in the next section.
+The methods used to simulate mock images of galaxies and gravitational lenses are described in section~\ref{sec:simulation}.
+In section~\ref{sec:entries} each of the methods that were used to solve the challenge are briefly described.
+We discuss the metrics used to evaluate entries in section~\ref{sec:figure_of_merit}.
+The performance of each of the methods broken down in different ways is presented in section~\ref{sec:performance}.
+Finally,  in section~\ref{sec:conclusion}, we conclude with a discussion of what was learned and how methods can be improved in the future.
+
 \section{The Challenge}
+\label{sec:challenge}
+
+The challenge was in fact two independent challenges that could be entered independently.
+One was designed to mimic a single band of a future imaging data set from a satellite survey such as Euclid\footnote{https://www.euclid-ec.org/} \citep{***}.
+The other was designed to mimic ground based data with multiple bands, roughly modeled on the Kilo-Degree Survey (KiDS)\footnote{http://kids.strw.leidenuniv.nl/} \citep{***} .
+In neither case were the simulated images meant to precisely mock these surveys, but only used them as general guide as to set noise levels, pixel sizes, sensitivities and other parameters.
+
+In each case a training set of 20,000 images in each band was provided for download at any time along with a key giving some properties of the object including whether it was a gravitational lens.
+Each image was $101\times101$ pixels.
+The researchers were free to download these sets and train their algorithms on them.
+To enter the contest the participants needed to register with a team name at which point they would be given a unique key and the address of a test data set.
+These data sets contained 100,000 candidates.
+In the case of the multi-band ground-based set this was 400,000 images.
+The participant had 48 hours to upload a classification of all candidates consisting of a score between 0 and 1 -- 0 signifying the lowest confidence that it is a lens and 1 signifying the highest confidence that it is a lens.
+This ranking could have been a simple binary (0 or 1) classification  or it could have been a continuous range of numbers representing the probability of being a lens or it could have been a finite number of confidence levels.
+
+The challenge was opened on November 25, 2016 and closed on February 5, 2017.
 
 \section{the simulations}
+\label{sec:simulation}
+
+Creating the mock images starts with a cosmological nbody simulation.  In this case it was the Millennium simulation \citep{***}.   A catalog of dark matter halos within a light-cone is 
+constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
+Using the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} we identify and map out all the caustics within the light-cone for *** source planes.
+For every caustic that corresponded to a critical curve with an Einstein radius larger than **** arcseconds, we identify the main object causing lensing by finding the largest ****.
+The Einstein radius is estimated here and in all that follows as $R_{\rm ein}=\sqrt{A_{\rm ein}/\pi}$ where $A_{\rm ein}$ is the angular area within the critical curve.
+All the halos within *** Mpc of this main lens are extracted and used as a lens.
+This collection of halos is rotated to produce more random lenses.
+A **** light-cone gives rise to **** such lenses.
+
+For lensed sources we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.  This is the same set of images as used 
+in ***.
+The source is placed within **** of the center of the lenses caustic as found in the initial ray tracing.
+This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the proccess  inefficiently because most of the sources are too far away from the caustic to produce clear lenses.
+If the source positions where taken completely at random the fraction of clear lenses would be very low.
+
+ \red{How the redshifts are picked}
+
+{\bf Lens Galaxies}
+
+There are not enough large galaxies in the UDF to make enough mock lens galaxies.
+The Millennium Observatory provides parameters for the galaxies that inhabit the dark matter halos using the semi-analytic galaxy formation models of ****.
+To model the surface brightness of these galaxies we use the models ****
+
+{\bf mass rendering}
+
+To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
+The surface brightness map in converted into a mass map by assuming a uniform mass-to-light ratio of **** in the **** band.
+This mass map is added to the lens before the ray tracing is done.
+
+Every time the lens is reoriented a new realization of the lens galaxies is made and a new source position is found.
+
+{\bf size of cones}
+
+{\bf products - images output}
+
+For the training sets all these products were provided, but for the test sets only the final images were provided to participants although all the information was stored for analysing the entries.
+
+\subsection{space-based}
+
+For the space-based data sets a simple Gaussian PSF was applied with a ***** of **** arcsec.  
+The band used was SDSS K.  The noise was a Gaussian random realization ****.
+
+{\bf fractions}
+
+\subsection{ground-based}
+
+For the ground-based images four bands where *****.  
+ The KiDS survey provided a representative PSF map, **** image stamps of their targets and the weights maps for those images.
+Some of these images had masked regions to remove stars, cosmic rays and bad pixels.
+The PSF had a FWHM of *** and was applied to all the images.
+Noise was simulated by adding normally distributed numbers with the variance given by the weight maps.
+The weight maps where also randomly rotated and flipped.
+This resulted in many of the images having large masked regions in them ($\sim$ ***** \%).
+
+In the test image set some actual KiDS images were used also.
+Here a random mass distribution and source was used to produce a lensed source that was added directly to the KiDS image after aplying the PSF.
+No additional noise was added.
+
+{\bf fractions}
+
+By chance one of the original KiDS images appears to have been a lens.  When an additional lensed source was added this made a double lens or "jockpot" lens.
+
+\section{the entries}
+\label{sec:entries}
+
+There were 24 valid entries into the challenge.
+They are listed in table~\ref{table:entries}.
+There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries form people outside of the field.
+
+\begin{table*}
+\centering
+\begin{tabular}{rlll}
+  \hline
+ & Name & type & authors \\ 
+  \hline
+  1 & AstrOmatic & Space-Based & Bertin   \\ 
+  2 & GAHEC IRAP & Space-Based & Cabanac  \\ 
+  3 & CAS Swinburne Melb & Ground-Based & Jacobs   \\ 
+  4 & ALL-star & Ground-Based & Avestruz, N.Li \& Lightman  \\ 
+  5 & Manchester1 & Space-Based & Jackson, Hartley \& Tagore  \\ 
+  6 & CMU-DeepLens-Resnet-Voting & Space-Based & Ma, Lanusse \& C. Li  \\ 
+  7 & Manchester SVM & Ground-Based & Hartley   \\ 
+  8 & CMU-DeepLens-ResNet & Space-Based & Francois Lanusse, Ma, C. Li \& Ravanbakhsh \\ 
+  9 & CMU-DeepLens-Resnet-Voting & Ground-Based & Ma, Lanusse \& C. Li   \\ 
+  10 & YattaLensLite & Space-Based &  Sonnenfeld  \\ 
+  11 & NeuralNet2 & Space-Based &  Davies  \\ 
+  12 & CAST & Ground-Based &  Roque De Bom, Valent\"{\i}n \&  Makler  \\ 
+  13 & CMU-DeepLens-ResNet-ground3 & Ground-Based &  Lanusse, Ma, Ravanbakhsh \& C. Li \\ 
+  14 & GAMOCLASS & Space-Based & Marc Huertas-Company, Tuccillo, Velasco-Forero \& Decenci\~{a}re \\ 
+  15 & LASTRO EPFL (CNN) & Space-Based & Geiger, Sch\"{a}fer \& Kneib \\ 
+  16 & Manchester SVM & Space-Based &  Hartley  \\ 
+  17 & CMU-DeepLens-ResNet-aug & Space-Based & Ma,  Lanusse, Ravanbakhsh \& C. Li \\ 
+  18 & LASTRO EPFL & Ground-Based & Geiger, Sch\"{a}fer \& Kneib   \\ 
+  19 & CAST & Space-Based & Roque De Bom, Valent\"{\i}n \& Makler  \\ 
+  20 & AstrOmatic & Ground-Based & Bertin  \\ 
+  21 & All-now & Space-Based & Avestruz, N. Li \& Lightman   \\ 
+  22 & Manchester-NA2 & Ground-Based & Jackson \& Tagore  \\ 
+  23 & YattaLensLite & Ground-Based & Sonnenfeld   \\ 
+  24 & Kapteyn & Space-Based & Petrillo, Koopmans, Kleijn, Tortora \& Vernardos \\ 
+   \hline
+\end{tabular}
+\caption{Entries to the challenges.}
+\label{table:entries}
+\end{table*}
 
 \section{lens finding methods}
+\label{sec:methods}
 
@@
 \begin{figure}
- \includegraphics[width=\columnwidth]{Cabanac/arcmethod.pdf}
+ \includegraphics[width=\columnwidth]{figures/arcmethod.pdf}
  \caption{ (GAHEC IRAP) From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties.
@@
 
+\subsection{LASTRO EPFL (Geiger, Sch\"{a}fer)}
+
+We used a convolutional neural network \citep{Fukushima1980,Lecun1998} with a simple architecture of 12 layers (inspired by \citep{symmetry}), see table \ref{tab:architecture}.
+To avoid the problem of the data flow distribution getting out of the comfort zone of the activation functions (Internal Covariate Shift), we used a mix of normalization propagation \citep{norm_prop} (without the constraint on the weights but a proper initialization) and batch normalization \citep{batch_norm} (slowly disabled over the iterations).
+As activation function, we used a scaled and shifted ReLU (Rectifier Linear Unit), 
+\begin{equation} \label{eq:relu}
+    \frac{1}{\sqrt{\pi-1}} (\sqrt{2 \pi} \max(0,x) - 1),
+\end{equation}
+to satisfy the properties required by the normalization propagation.
+In our implementation of batch normalization, instead of using only the moments computed over the current batch, we used a low-pass filter ($\bar\mu_i \longleftarrow (1-\eta) \; \bar\mu_{i-1} + \eta \; \mu_i(\text{batch})$, $\eta$ set to $1$ at the beginning and decay with the iterations).
+For the training, the 20k provided images were split into two sets, 17k for training and 3k for validation.
+Each iteration of the gradient descent (more precisely ADAM \citep{adam}) minimizes the cross entropy, 
+\begin{equation} \label{eq:xent}
+    \left\{
+    \begin{array}{ll}
+        - \log(p)   & \text{if the image is a true lens} \\
+        - \log(1-p) & \text{if the image is a nonlens}
+    \end{array}
+    \right.,
+\end{equation}
+where $p$ is the output of the neural network, computed over a batch of 30 images, 15 lenses and 15 nonlenses, picked from the training set.
+Making batches of 30 images adds noise to the gradient makes the iterations faster.
+
+To augment the training set, each image of the batch is transformed with a random transformation of the dihedral group (rotations of 90 degrees and mirrors), its pixel values multiplied by a factor picked between $0.8$ and $1.2$ and shifted by a random value between $-0.1$ and $0.1$.
+To prevent the overfitting, we used some dropout \citep{dropout} (with a keeping probability decreasing with the iterations).
+The masked region of the ground based images are handled by simply setting them to zero.
+Each final prediction is made of the product of the predictions of the 8 transformations of the image by the dihedral group.
+The architecture is implemented in Tensorflow\footnote{\url{http://tensorflow.org/}}.
+Our code is accessible on github\footnote{\url{https://github.com/antigol/lensfinder-euclid}}.
+
+\begin{table*}
+    \centering
+    \begin{tabular}{|l|l|l|l|}
+        \hline
+        Layer type & shape & activation & \# parameters \\ \hline \hline
+
+        \textbf{convolutional 4x4} & $101\!\times\! 101\!\times\!1/4 \to 98\!\times\!98\!\times\!16$ & rectifier & 256/1'024 + 16 \\ \hline
+        \textbf{convolutional 3x3} & $98\times98\times16 \to 96\times96\times16$ & rectifier & 2'304 + 16 \\ \hline
+        max pool /2 & $96\times96\times16 \to 48\times48\times16$ & - & - \\ \hline
+        batch normalization & $48\times48\times16$ & - & 16 + 16 \\ \hline
+
+        \textbf{convolutional 3x3} & $48\times48\times16 \to 46\times46\times32$ & rectifier & 4'608 + 32 \\ \hline
+        \textbf{convolutional 3x3} & $46\times46\times32 \to 44\times44\times32$ & rectifier & 9'216 + 32 \\ \hline
+        max pool /2 & $44\times44\times32 \to 22\times22\times32$ & - & - \\ \hline
+        batch normalization & $22\times22\times32$ & - & 32 + 32 \\ \hline
+
+        \textbf{convolutional 3x3} & $22\times22\times32 \to 20\times20\times64$ & rectifier & 18'432 + 64 \\ \hline
+        \textbf{convolutional 3x3} & $20\times20\times64 \to 18\times18\times64$ & rectifier & 36'864 + 64 \\ \hline
+        max pool /2 & $18\times18\times64 \to 9\times9\times64$ & - & - \\ \hline
+        batch normalization & $9\times9\times64$ & - & 64 + 64 \\ \hline
+        dropout & $9\times9\times64$ & - & - \\ \hline
+
+        \textbf{convolutional 3x3} & $9\times9\times64 \to 7\times7\times128$ & rectifier & 73'728 + 128 \\ \hline
+        dropout & $7\times7\times128$ & - & - \\ \hline
+        \textbf{convolutional 3x3} & $7\times7\times128 \to 5\times5\times128$ & rectifier & 147'456 + 128 \\ \hline
+        batch normalization & $5\times5\times128$ & - & 128 + 128 \\ \hline
+        dropout & $5\times5\times128$ & - & - \\ \hline
+
+        \textbf{fully-connected} & $5\times5\times128 \to 1024$ & rectifier & 3'276'800 + 1'024 \\ \hline
+        dropout & $1024$ & - & - \\ \hline
+        \textbf{fully-connected} & $1024 \to 1024$ & rectifier & 1'048'576 + 1'024 \\ \hline
+        dropout & $1024$ & - & - \\ \hline
+        \textbf{fully-connected} & $1024 \to 1024$ & rectifier & 1'048'576 + 1'024 \\ \hline
+        batch normalization & $1024$ & - & 1'024 + 1'024 \\ \hline
+        \textbf{fully-connected} & $1024 \to 1$ & sigmoid & 1'024 + 1 \\ \hline \hline
+        Total & - & - & $\approx$ 5'674'000 \\ \hline
+    \end{tabular}
+    \caption{LASTRO EPFL architecture}
+    \label{tab:architecture}
+\end{table*}
+
+\subsection{Manchester/Manchester1 (Jackson, Tagore)}
+
+All images (a total of 100000) were examined for each of the space- and
+ground-based datasets. This was done by two observers; AT examined 30000
+images in each case and NJ examined 70000. Observation was carried out
+over a 48-hour period, at the rate of 5000/hr (NJ) and 2500/hr (AT). 
+The overall results, in terms of ROC curves, were very similar for 
+both observers. The space-based challenge produced areas of 0.800 and 
+0.812 for NJ and AT respectively, and the ground-based challenge yielded 
+0.891 and 0.884.
+
+The Python scripts used for manual examination of multiple images are available
+on https://github.com/nealjackson/bigeye and are described in more detail
+in Hartley et al. (2016, in preparation). For one-colour data such as
+the space-based training set, the images are individually colour-scaled using
+square-root scaling. The bright limit of the colour-scale is determined
+from the pixel values in a rectangle comprising the inner ninth of the
+image area, with the limit being chosen as the $n$th centile of the pixel
+values in this area. Values between $n=95$ and $n=98$ give optimum results,
+judging by experiments on the training set. The number of images in each
+grid was also optimised using the training set, with 16$\times$8 or 
+8$\times$4 giving good results on one-colour data. For three-colour data,
+such as the ground-based challenge data, the individual bands for each 
+object are colour-scaled and then combined into an RGB image. In this case
+8$\times$4 grids were used for examination, due to the generally lower 
+resolution of the images. The script also allows the user to adjust the
+colour-scale in real time when examining and marking images, and records
+the image name corresponding to the image within which the cursor resides
+at the time any key is pressed, together with the key.
+
+Images were classified by both observers into 5 categories, ranging from
+0 (no evidence of any lensed objects in the image) to 4 (certain lenses).
+For both observers, the rate of false positives in the ``certain'' lenses
+was between 0.1\% and 0.3\%. The exception was the ground-based imaging 
+for one observer, where a 4.6\% rate resulted mainly from a
+single decision to allow a false-positive ``double lens'' which occurred
+repeatedly throughout the data at different orientations. The false-negative
+rate among the class-0 identifications was similar for both observers, at
+around 25\% for the space-based images and 20\% for the ground-based.
+
+\subsection{Gabor-SVM (Hartley,Flamary)}
+
+A Support Vector Machine (SVM) is a supervised machine learning method which uses labelled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
+A preprocessing stage first extracts a set of useful features from input samples, before projecting each sample as a vector in multidimensional space.
+The model then separates classes of data by maximising the margin between a defining hyperplane and a set of so-called support-vectors at the inner edge of each class.
+The process of classification is computationally inexpensive since optimisation depends only on the dot products of the support vector subset.
+Feature extraction, however,  requires both an extensive exploration of the feature space during the development of a model, and potentially intensive computer resources in order to transform the original samples.
+Our full method is described in detail in Hartley et.
+al., in prep., and was developed using the Python scikit-learn and scikit-image packages \citep{scikit-learn,scikit-image}.
+
+During our development of an SVM classifier for lens finding, feature extraction initially involved the decomposition of each image into a set of objects, using SExtractor \citep{1996A&AS..117..393B} and GALFIT \citep{2002AJ....124..266P} to recover and subtract objects iteratively.
+This method had previously been used in a static algorithm approach which assigned points according to the morphological properties of each image \citep[see][]{2014A&A...566A..63J}.
+Lensed-like objects displaying, for example, greater ellipticity and tangentiality were awarded more points.
+Since the SVM operates in a fixed dimensional space,  properties of individual objects were collapsed into a fixed set describing the mean and variance of morphological properties of all the objects within an image.
+After training an SVM using these features we recorded a modest separation of lens and non-lens classes.
+
+An alternative approach was to design a set of Gabor filters to be applied to each sample.
+The Gabor kernel is described by a sinusoidal function multiplied by a Gaussian envelope.
+We discard the imaginary part of the function to leave, in two-dimensional space:
+
+\begin{equation}
+G_c[i,j]=Be^{-\frac{(i^2+j^2)}{2\sigma^2}} \mathrm{cos}\left(\frac{2\pi}{\lambda} (i\, \mathrm{cos} \, \theta + j\, \mathrm{sin} \,\theta)\right),
+\end{equation}
+
+where harmonic wavelength $\lambda$, Gaussian spread  $\sigma$ and orientation $\theta$ define the operation performed on each point $i,j$ in an image.
+Such a kernel is a popular image processing choice for edge detection and texture classification \citep[e.g.][]{Feichtinger98a,Springer-verlag97computationalmodels} and is thought to mimic some image processing functions of the mammalian brain \citep{Jones1233}.
+
+\begin{figure}
+  \centering
+      \includegraphics[width=1\columnwidth]{figures/polarfilter.pdf} 
+  \caption{Example of our feature extraction procedure used to transform a ring.
+The image on the right shows the response of a set of Gabor filters after convolution with a polar transformed image of an Einstein ring.
+The strongest response is seen in the orientation perpendicular to the radial direction and at the frequency most closely matching that of the ring.}
+ \label{gaborring}
+
+\end{figure}
+
+Our final feature extraction procedure first applied a polar transform to each image in order to exploit the edge detection of the Gabor filter, picking out tangential components typical of galaxy-galaxy lensing.
+Each image was then convolved with several Gabor filters of varying frequency and rotation (see Fig.~\ref{gaborring}).
+Stability selection methods were used to investigate the classification performance using different combinations of filters.
+The responses for each Gabor filter when applied to each image were measured by calculating statistical moments for each filtered image.
+These moments formed  our final input data on which the SVM could be trained and applied.
+We used brute-force optimisation methods to select a non-linear SVM containing radial basis function (RBF) kernel and tuned a small set of regularisation hyperparameters to achieve good generalisation performance.
+During training and testing, our final and best scores achieved when testing on the lens finding challenge training data were an AUC of 0.88 for the space set and 0.95 for the ground set.
+Classification was performed using a modest desktop PC.
+
 \section{results}
+\label{sec:results}
+
+In this section we summarize some of our analysis of the submissions.
+In section~\ref{sec:figure_of_merit} we discuss how to judge a classifier in this particular case and define some metrics of success.
 
 \subsection{figures of merit}
+\label{sec:figure_of_merit}
 
@@
 
-The {\bf TPR0} will be defined as the highest TPR reached, as a function of $p$ threshold, before a single false positive occurs in the test set of 100,000 images.
+The {\bf TPR$_0$} will be defined as the highest TPR reached, as a function of $p$ threshold, before a single false positive occurs in the test set of 100,000 images.
 This is the point were the ROC meets the FPR = 0 axis.
-This quantity highly penalizes classifiers with discrete ranking which often get TPR0 = 0 because their highest classification level is not conservative enough to eliminate all false positives.
-We also define {\bf TPR10} which is the TPR at the point were less than ten false positives are made.
+This quantity highly penalizes classifiers with discrete ranking which often get TPR$_0$ = 0 because their highest classification level is not conservative enough to eliminate all false positives.
+We also define {\bf TPR$_{10}$} which is the TPR at the point were less than ten false positives are made.
 If the TP
@@
 As we will see, if you restrict your objectives to detecting only lensed images with surface brightness above threshold, for example, the "best" algorithm might change and the TPR will change.
-For this reason we plot the AUROC, TPR0 and TPR10 as a function of several variables for all the entries.
+For this reason we plot the AUROC, TPR$_0$ and TPR$_{10}$ as a function of several variables for all the entries.
 This is done by removing all the lenses that do not exceed the threshold and then recalculating the these quantities, the number of non-lenses remains the same.
@@
 ***
-\subsection{plots}
+
+\subsection{Performance of methods}
+\label{sec:performance}
+
+\begin{table*}
+\centering
+\begin{tabular}{llrrrl}
+  \hline
+  Name & type & AUROC & TPR$_0$ & TPR$_{10}$ & short description \\ 
+  \hline
+ CMU-DeepLens-ResNet-ground3 & Ground-Based & 0.98 & 0.09 & 0.45 & CNN \\ 
+  CMU-DeepLens-Resnet-Voting & Ground-Based & 0.98 & 0.02 & 0.10 & CNN \\ 
+  LASTRO EPFL & Ground-Based & 0.97 & 0.07 & 0.11 & CNN \\ 
+  CAS Swinburne Melb & Ground-Based & 0.96 & 0.02 & 0.08 & CNN \\ 
+  AstrOmatic & Ground-Based & 0.96 & 0.00 & 0.01 & CNN \\ 
+  Manchester SVM & Ground-Based & 0.93 & 0.22 & 0.35 & SVM / Gabor \\ 
+  Manchester-NA2 & Ground-Based & 0.89 & 0.00 & 0.01 & Human Inspection \\ 
+   ALL-star & Ground-Based & 0.84 & 0.01 & 0.02 & edges/gradiants and Logistic Reg. \\ 
+   CAST & Ground-Based & 0.83 & 0.00 & 0.00 & CNN / SVM \\ 
+   YattaLensLite & Ground-Based & 0.82 & 0.00 & 0.00 & SExtractor \\ 
+   LASTRO EPFL (CNN) & Space-Based & 0.93 & 0.00 & 0.08 & CNN \\ 
+  CMU-DeepLens-ResNet & Space-Based & 0.92 & 0.22 & 0.29 & CNN \\ 
+   GAMOCLASS & Space-Based & 0.92 & 0.07 & 0.36 & CNN \\ 
+  CMU-DeepLens-Resnet-Voting & Space-Based & 0.91 & 0.00 & 0.01 & CNN \\ 
+  AstrOmatic & Space-Based & 0.91 & 0.00 & 0.01 & CNN \\ 
+   CMU-DeepLens-ResNet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 
+   Kapteyn & Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
+   CAST & Space-Based & 0.81 & 0.07 & 0.12 & CNN \\ 
+  Manchester1 & Space-Based & 0.81 & 0.01 & 0.17 & Human Inspection \\ 
+   Manchester SVM & Space-Based & 0.81 & 0.03 & 0.08 & SVM / Gabor \\ 
+   NeuralNet2 & Space-Based & 0.76 & 0.00 & 0.00 & CNN / wavelets \\ 
+   YattaLensLite & Space-Based & 0.76 & 0.00 & 0.00 & Arcs / SExtractor \\ 
+   All-now & Space-Based & 0.73 & 0.05 & 0.07 & edges/gradiants and Logistic Reg. \\ 
+  GAHEC IRAP & Space-Based & 0.66 & 0.00 & 0.01 & arc finder \\ 
+   \hline
+\end{tabular}
+\caption{The AUROC, TPR$_0$ and TPR$_{10}$ for the entries in order of AUROC.}
+\label{table:AUROC}
+\end{table*}
+
+\begin{table*}
+\centering
+\begin{tabular}{llrrrl}
+  \hline
+  Name & type & AUROC & TPR$_0$ & TPR$_{10}$ & short description \\ 
+  \hline
+ Manchester SVM & Ground-Based & 0.93 & 0.22 & 0.35 & SVM / Gabor \\ 
+  CMU-DeepLens-ResNet-ground3 & Ground-Based & 0.98 & 0.09 & 0.45 & CNN \\ 
+  LASTRO EPFL & Ground-Based & 0.97 & 0.07 & 0.11 & CNN \\ 
+   CMU-DeepLens-Resnet-Voting & Ground-Based & 0.98 & 0.02 & 0.10 & CNN \\ 
+   CAS Swinburne Melb & Ground-Based & 0.96 & 0.02 & 0.08 & CNN \\ 
+   ALL-star & Ground-Based & 0.84 & 0.01 & 0.02 & edges/gradiants and Logistic Reg. \\ 
+   Manchester-NA2 & Ground-Based & 0.89 & 0.00 & 0.01 & Human Inspection \\ 
+   YattaLensLite & Ground-Based & 0.82 & 0.00 & 0.00 & SExtractor \\ 
+   CAST & Ground-Based & 0.83 & 0.00 & 0.00 & CNN / SVM \\ 
+   AstrOmatic & Ground-Based & 0.96 & 0.00 & 0.01 & CNN \\ 
+   CMU-DeepLens-ResNet & Space-Based & 0.92 & 0.22 & 0.29 & CNN \\ 
+   GAMOCLASS & Space-Based & 0.92 & 0.07 & 0.36 & CNN \\ 
+   CAST & Space-Based & 0.81 & 0.07 & 0.12 & CNN \\ 
+   All-now & Space-Based & 0.73 & 0.05 & 0.07 & edges/gradiants and Logistic Reg. \\ 
+   Manchester SVM & Space-Based & 0.80 & 0.03 & 0.07 & SVM / Gabor \\ 
+   Manchester1 & Space-Based & 0.81 & 0.01 & 0.17 & Human Inspection \\ 
+   LASTRO EPFL (CNN) & Space-Based & 0.93 & 0.00 & 0.08 & CNN \\ 
+   GAHEC IRAP & Space-Based & 0.66 & 0.00 & 0.01 & arc finder \\ 
+   AstrOmatic & Space-Based & 0.91 & 0.00 & 0.01 & CNN \\ 
+   Kapteyn & Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
+   CMU-DeepLens-ResNet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 
+   CMU-DeepLens-Resnet-Voting & Space-Based & 0.91 & 0.00 & 0.01 & CNN \\ 
+   NeuralNet2 & Space-Based & 0.76 & 0.00 & 0.00 & CNN / wavelets \\ 
+   YattaLensLite & Space-Based & 0.76 & 0.00 & 0.00 & Arcs / SExtractor \\ 
+   \hline
+\end{tabular}
+\caption{The AUROC, TPR$_0$ and TPR$_{10}$ for the entries in order of TPR$_0$.  }
+\label{table:TPR0}
+\end{table*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/roc_space.pdf}
+ \caption{The ROC curves for the space-based entries.}
+ \label{fig:roc_space}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/roc_ground.pdf}
+ \caption{The ROC curves for the ground-based entries.
+Notice that these are are generally better than in figure~\ref{fig:einstein_space} indicating that colour information is an important discriminant.
+}
+ \label{fig:roc_ground}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/roc_kids.pdf}
+ \caption{The ROC curves for the ground-based entries including only the cases with authentic images taken from the KiDS survey.
+It can be seen that in all cases these are lower than in figure~\ref{fig:roc_ground}.}
+ \label{fig:roc_kids}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/einstein_space.pdf}
+ \caption{The AUROC, TPR$_0$, TPR$_{10}$ and the fraction of lenses in the test sample after discarding the lenses with Einstein radii larger than the number indicated on the x-axis. }
+ \label{fig:einstein_space}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/einstein_ground.pdf}
+ \caption{Same as figure~\ref{fig:einstein_space}, but for space-based entries.}
+ \label{fig:einstein_ground}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/flux_space.pdf}
+ \caption{}
+ \label{fig:flux_space}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/flux_ground.pdf}
+ \caption{}
+ \label{fig:flux_ground}
+\end{figure*}
+
+\begin{figure*}
+\includegraphics[width=2\columnwidth]{figures/npixel_space.pdf}
+ \caption{}
+ \label{fig:npixel_space}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/npixel_ground.pdf}
+ \caption{}
+ \label{fig:npixel_ground}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/flux_contrast_space.pdf}
+ \caption{}
+ \label{fig:flux_contrast_space}
+\end{figure*}
+
+\begin{figure*}
+ \includegraphics[width=2\columnwidth]{figures/flux_contrast_ground.pdf}
+ \caption{}
+ \label{fig:flux_contrast_ground}
+\end{figure*}
+
+\red{surface brightness contrast}
+
+\red{breakups Manchester between Neil and Amit}
 
 \section{Conclusions \& discussion}
+\label{sec:conclusion}
 
@@
 RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349.
+AT acknowledges receipt of an STFC postdoctoral research
+assistantship.
+\red{We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}}
 

### 2017-04-05 paper.tex
Edit

@@
 % List of institutions
-$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, viale Berti Pichat 6/2, 40127 Bologna, Italy \\
+$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
 $^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
@@
 
-some background of passed methods
+some background on past methods
 
@@
 The Einstein radius is estimated here and in all that follows as $R_{\rm ein}=\sqrt{A_{\rm ein}/\pi}$ where $A_{\rm ein}$ is the angular area within the critical curve.
+A **** square degree light-cone gives rise to **** such lenses.
 All the halos within *** Mpc of this main lens are extracted and used as a lens.
 This collection of halos is rotated to produce more random lenses.
-A **** light-cone gives rise to **** such lenses.
+In this way the lenses contain the all the subhalos and near by companion halos.
 
@@
 \subsection{space-based}
+\label{sec:sim-space-based}
 
@@
 \subsection{ground-based}
+\label{sec:sim-ground-based}
 
@@
    YattaLensLite & Ground-Based & 0.82 & 0.00 & 0.00 & SExtractor \\ 
-   LASTRO EPFL (CNN) & Space-Based & 0.93 & 0.00 & 0.08 & CNN \\ 
+   LASTRO EPFL & Space-Based & 0.93 & 0.00 & 0.08 & CNN \\ 
   CMU-DeepLens-ResNet & Space-Based & 0.92 & 0.22 & 0.29 & CNN \\ 
@@
 \end{table*}
+
+Table~\ref{table:AUROC} shows the AUROC, TPR$_0$ and TPR$_{10}$ for the entries in order of AUROC and data set type.
+It can be seen that CMU-DeepLens-ResNet-ground3 had the best AUROC for the ground-based set and LASTRO EPFL the best for the space-based set.
+The order is different if TPR$_0$ is used to rank the entries as seen in table~\ref{table:TPR0}.
+Here Manchester SVM and
+CMU-DeepLens-ResNet get the best scores.
 
@@
    Manchester1 & Space-Based & 0.81 & 0.01 & 0.17 & Human Inspection \\ 
-   LASTRO EPFL (CNN) & Space-Based & 0.93 & 0.00 & 0.08 & CNN \\ 
+   LASTRO EPFL & Space-Based & 0.93 & 0.00 & 0.08 & CNN \\ 
    GAHEC IRAP & Space-Based & 0.66 & 0.00 & 0.01 & arc finder \\ 
@@
 
+Figures~\ref{fig:roc_space} and \ref{fig:roc_space} show the ROC curves for all the entries.
+In addition figure~\ref{fig:roc_kids} shows the ROC curves for only the ground-based images where an actual KiDS image was used (see section~\ref{sec:sim-ground-based}).
+It can be seen that the classifiers do uniformly less well on this subset.
+This indicates that the simulated galaxy images are different from the real ones and that the classifiers are not able to distinguish fake foreground galaxies from lenses more easily.
+This is perhaps not unexpected, but does show that the simulated lenses need to be improved before the raw numbers can be directly used to evaluate the performance of a classifier on real data.
+
 \begin{figure*}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_space.pdf}
- \caption{}
+ \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the flux within the pixels that are above 1 $\sigma$ in the lensed source only image.}
  \label{fig:flux_space}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_ground.pdf}
- \caption{}
+ \caption{Same as figure~\ref{fig:flux_space}, but for space-based entries.}
  \label{fig:flux_ground}
@@
 \includegraphics[width=2\columnwidth]{figures/npixel_space.pdf}
- \caption{}
+ \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the number of pixels that are above 1 $\sigma$ in the lensed source only image.
+This is an indication of the lensed arcs' size.}
  \label{fig:npixel_space}
@@
  \includegraphics[width=2\columnwidth]{figures/npixel_ground.pdf}
- \caption{}
+ \caption{Same as figure~\ref{fig:npixel_space}, but for space-based entries.}
  \label{fig:npixel_ground}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_contrast_space.pdf}
- \caption{}
+  \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the ratio of the flux coming from the lensed source to the total flux in the image.  (\red{ check this.  Band?})}
  \label{fig:flux_contrast_space}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_contrast_ground.pdf}
- \caption{}
+ \caption{Same as figure~\ref{fig:flux_contrast_space}, but for space-based entries.}
  \label{fig:flux_contrast_ground}

### 2017-04-19 paper.tex
Edit.

@@
 
-***
-
 \subsection{Performance of methods}
@@
 
+Figures~\ref{fig:einstein_space} and \ref{fig:einstein_ground} shows the AUROC, TPR$_0$, TPR$_{10}$ and fraction of lenses as a function of a lower cutoff on the Einstein radius (area).
+There is also a vertical dotted line that indicates where no more than 100 lenses in the test sample had Einstein radii larger than this mark.
+Beyond this point one should be suspicius of small number statistics.
+When deriving the distribution of Einstein radii from data these curves would need to be used to correct for detection bias.
+It can be seen the CMU-DeepLens-ResNet, Manchester1, Manchester SVM and GAMOCLASS obtain significantly higher TPR$_0$ and  TPR$_{10}$ for larger Einstein radii.
+Manchester1 is the human inspection method.
+In some cases these are above 50\% of the lenses that meet the criterion.
+Remember that many of the so called lenses are very dim or there is no significant arc because of the source position is well outside the caustic.
+If an additional require was placed on the definition of a lens, such as the brightness of the arc being above a threshold, the TPRs would go up.
+
+Figures~\ref{fig:flux_space} and \ref{fig:flux_ground} are the same except that the flux in the lensed image is used as the threshold.
+We count only the flux in pixels with flux over one $\sigma$ of the background.
+In some cases one can see an abrupt rise in the TPRs at some flux threshold.
+CMU-DeepLens-ResNet in particular reaches a TPR$_0$ above 75\% for the bightest $\sim$ 10\% of the lenses.
+
+A lensed image can be bright without being visibly distorted as in the case of a unresolved image.
+Figures~\ref{fig:npixel_space} and \ref{fig:npixel_ground} use the number of pixels in the lensed image(s) that are over  one $\sigma$ of the background.
+In this case also some classifiers show an abrupt improvement when the image is required to be larger than some threshold.
+Interestingly in some cases the TPRs go down with lensed image size after reaching a peak.
+This could be because they are not differentiating the arcs from companion galaxies as well in this regime.
+
+Figures~\ref{fig:flux_contrast_space} and \ref{fig:flux_contrast_ground} investigate how the flux contrast between the foreground objects and the lensed source affects the classifiers.
+Interestingly some method's TPRs go up with this quantity and some go down.
+
 \red{surface brightness contrast}

### 2017-05-03 paper.tex
Edit.

@@
 \begin{abstract}
-The present the results of an open gravitational lens finding challenge.
+We present a description and results of an open gravitational lens finding challenge.
 Participants were asked to classify 100,000 candidate objects as to whether they were gravitational lenses or not with the goal of developing better automated methods for finding lenses in large data sets.
@@
 
-Creating the mock images starts with a cosmological nbody simulation.  In this case it was the Millennium simulation \citep{***}.   A catalog of dark matter halos within a light-cone is 
-constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
-Using the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} we identify and map out all the caustics within the light-cone for *** source planes.
-For every caustic that corresponded to a critical curve with an Einstein radius larger than **** arcseconds, we identify the main object causing lensing by finding the largest ****.
+Creating the mock images starts with a cosmological nbody simulation.
+In this case it was the Millennium simulation \citep{2009MNRAS.398.1150B}.
+A catalog of dark matter halos within a light-cone is constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O} down to a mass of ****.
+These halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
+This code projects the halos onto lens planes, in this case 20, and finds the deflection angle on each plane by a hybrid tree method.
+In this way the halos have the mass, concentration and clustering properties from the nbody simulation, but within each strong lens the mass resolution is not limited by the original simulation, but follows the analytic mass profile.
+
+With GLAMER we identify and map out all the caustics within the light-cone for 33 source planes -- z=1 to 3 in intervals of 0.1 and 3 to 6 in intervals of 0.25.
+We take every caustic that corresponded to a critical curve with an Einstein radius larger than 1.5 times the resolution.
 The Einstein radius is estimated here and in all that follows as $R_{\rm ein}=\sqrt{A_{\rm ein}/\pi}$ where $A_{\rm ein}$ is the angular area within the critical curve.
-A **** square degree light-cone gives rise to **** such lenses.
-All the halos within *** Mpc of this main lens are extracted and used as a lens.
-This collection of halos is rotated to produce more random lenses.
-In this way the lenses contain the all the subhalos and near by companion halos.
+
+ A **** square degree light-cone gives rise to **** such caustics, but these over count the number of lenses since most will have caustics on multiple source planes.
+These lenses could be used as is, but we want to produce a much larger number with more randomness.
+For each caustic we identify the lens plane with the highest convergence and identify all the halos within a three dimensional distance of 0.5 Mpc from the center of the critical curve and on this and its neighboring lens planes.
+This collection of halos is then used as the lens and rotated to produce more random lenses.
+It  contains all the subhalos and near by companion halos, but not the large scale structure surrounding it.
 
@@
 There are not enough large galaxies in the UDF to make enough mock lens galaxies.
-The Millennium Observatory provides parameters for the galaxies that inhabit the dark matter halos using the semi-analytic galaxy formation models of ****.
+The Millennium Observatory provides parameters for the galaxies that inhabit the dark matter halos using the semi-analytic galaxy formation models of \citet{2011MNRAS.413..101G}.
 To model the surface brightness of these galaxies we use the models ****
@@
 Interestingly some method's TPRs go up with this quantity and some go down.
+\red{explaination?}
 

### 2017-05-03 paper.tex
Edit

@@
 
+Arcfinder\citep{2007A&A...472..341S}
+
+\citet{2006astro.ph..6757A} arc finder used in the CFHT \citep{2007A&A...461..813C,2012ApJ...749...38M}
+
+Some finders compare each image with a lens model \citep{2009ApJ...694..924M,2010A&A...517A..25S}.
+
+\citep{2014A&A...566A..63J,2016A&A...592A..75P}
+
 some numbers about future surveys
@@
 One was designed to mimic a single band of a future imaging data set from a satellite survey such as Euclid\footnote{https://www.euclid-ec.org/} \citep{***}.
-The other was designed to mimic ground based data with multiple bands, roughly modeled on the Kilo-Degree Survey (KiDS)\footnote{http://kids.strw.leidenuniv.nl/} \citep{***} .
+The other was designed to mimic ground based data with multiple bands, roughly modeled on the Kilo-Degree Survey (KiDS)\footnote{http://kids.strw.leidenuniv.nl/} \citep{2013ExA....35...25D} .
 In neither case were the simulated images meant to precisely mock these surveys, but only used them as general guide as to set noise levels, pixel sizes, sensitivities and other parameters.
@@
 For lensed sources we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.  This is the same set of images as used 
-in ***.
+in ****.
 The source is placed within **** of the center of the lenses caustic as found in the initial ray tracing.
-This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the proccess  inefficiently because most of the sources are too far away from the caustic to produce clear lenses.
+This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the process  inefficiently because most of the sources are too far away from the caustic to produce clear lenses.
 If the source positions where taken completely at random the fraction of clear lenses would be very low.
@@
 
-For the training sets all these products were provided, but for the test sets only the final images were provided to participants although all the information was stored for analysing the entries.
+For the training sets all these products were provided, but for the test sets only the final images were provided to participants although all the information was stored for analyzing the entries.
 
@@
 In the test image set some actual KiDS images were used also.
-Here a random mass distribution and source was used to produce a lensed source that was added directly to the KiDS image after aplying the PSF.
+Here a random mass distribution and source was used to produce a lensed source that was added directly to the KiDS image after applying the PSF.
 No additional noise was added.
@@
 
-By chance one of the original KiDS images appears to have been a lens.  When an additional lensed source was added this made a double lens or "jockpot" lens.
+By chance one of the original KiDS images appears to have been a lens.  When an additional lensed source was added this made a double lens or "jackpot" lens.
 
@@
  \includegraphics[width=\columnwidth]{figures/arcmethod.pdf}
- \caption{ (GAHEC IRAP) From top-left to botton right, 1) a simulated arc extracted from SL challenge in which an tunned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixelwise elongation is computed, 3) the resulting elongated pixels after thresholding, 4) the set of pixels selected for the computation of arc candidate properties.
+ \caption{ (GAHEC IRAP) From top-left to bottom right, 1) a simulated arc extracted from SL challenge in which an tuned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixel wise elongation is computed, 3) the resulting elongated pixels after threshold, 4) the set of pixels selected for the computation of arc candidate properties.
 }
@@
 
-Arcfinder \citep{2006astro.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} is a fast linear method that computes a pixelwise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
+Arcfinder \citep{astronaut.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
 Arcfinder then extract contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness.
-A final thresholding is set to maximize purity over completeness on a few typical arcs of the dataset.
-For the current SL challenge, arcfinder was tunned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.
+A final thresholding is set to maximize purity over completeness on a few typical arcs of the data set.
+For the current SL challenge, arcfinder was tuned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.
 A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code as a linux line command.
-Arcfinder took a couple of hours to run on the entire dataset with some overheads due to the dataset format.
+Arcfinder took a couple of hours to run on the entire data set with some overheads due to the data set format.
 The code is publicly available at https://github.com/rcabanac/arcfinder.
@@
 
-The lens detector is based on a convolutional neural network (CNN), trained with the provided training datasets.
+The lens detector is based on a convolutional neural network (CNN), trained with the provided training data sets.
 The CNN is implemented in Python, using the TensorFlow framework\footnote{http://www.tensorflow.org/}.
@@
 
-A Support Vector Machine (SVM) is a supervised machine learning method which uses labelled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
+A Support Vector Machine (SVM) is a supervised machine learning method which uses labeled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
 A preprocessing stage first extracts a set of useful features from input samples, before projecting each sample as a vector in multidimensional space.
@@
 There is also a vertical dotted line that indicates where no more than 100 lenses in the test sample had Einstein radii larger than this mark.
-Beyond this point one should be suspicius of small number statistics.
+Beyond this point one should be suspicious of small number statistics.
 When deriving the distribution of Einstein radii from data these curves would need to be used to correct for detection bias.
@@
 In some cases one can see an abrupt rise in the TPRs at some flux threshold.
-CMU-DeepLens-ResNet in particular reaches a TPR$_0$ above 75\% for the bightest $\sim$ 10\% of the lenses.
+CMU-DeepLens-ResNet in particular reaches a TPR$_0$ above 75\% for the brightest $\sim$ 10\% of the lenses.
 
@@
 Interestingly some method's TPRs go up with this quantity and some go down.
-\red{explaination?}
+\red{explanation?}
 

### 2017-05-03 paper.tex
Edit

@@
 \newcommand{\red}[1]{{\color{red} #1}}
-
+\newcommand{\degree}{^{\circ}}
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
@@
 A catalog of dark matter halos within a light-cone is constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O} down to a mass of ****.
-These halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
+The challenge sets were based on a 1.6 sq.deg.
+light cone extending out to redshift 6.
+The halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
 This code projects the halos onto lens planes, in this case 20, and finds the deflection angle on each plane by a hybrid tree method.
@@
 For lensed sources we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.  This is the same set of images as used 
-in ****.
-The source is placed within **** of the center of the lenses caustic as found in the initial ray tracing.
+in  \red{*** Massimo: Can you put a citation in for this?}.   There are 9,350 such sources with redshifts and separate coefficients in 10 bands.
+
+To construct a mock lens, first a caustic on the highest redshift source plane is selected.
+This is done in order of Einstein area, but all the critical curves are used more than once.
+Since every lens with a caustic at a lower redshift will have a caustic at the highest redshift this is a selection from all of the caustics in the light-cone.
+The lens is extracted as explained above and rotated randomly in three dimensions.
+A source is selected at random from the shapelet catalog subject to a magnitude limit in a target band.
+The redshift of the UDF source is used as the source redshift.
+If the source is at a lower redshift than the lens or within $\Delta z = 0.4$ another source is selected.
+
+The furthest point in the caustic is found from its own center and the source is placed randomly within 3 times this distance.
 This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the process  inefficiently because most of the sources are too far away from the caustic to produce clear lenses.
@@
 
- \red{How the redshifts are picked}
+The visible galaxies associated with the lens must also be simulated.
+There were not enough large galaxies in the UDF catalog to make enough mock lens galaxies for this purpose.
+Instead, for most of the lenses, we used an analytic model for the surface brightness of these galaxies.
+The Millennium Observatory provides parameters for the galaxies that inhabit the dark matter halos using the semi-analytic galaxy formation models of \citet{2011MNRAS.413..101G}.
+The parameters used here were the total magnitude, the bulge-to-disk ratio, the disk scale height and the bulge effective radius.
+The magnitude and bulge-to-disk ratio are a function of the pass band.
+Each galaxy is given a random orientation and inclination angle.between 0 and $80\degree$.
+The disk is exponential with no vertical height which is why the inclination is limited to $80\degree$.
+The bulge is represented by a S\'{e}rsic profile with a axis ratio randomly sampled between 0.5 and 1.
+The S\'{e}rsic index, $n_s$, is by
+\begin{align}
+\log( n_s )= 0.4 \log\left[ {\rm max}\left(\frac{B}{T},0.03\right)\right] + 0.1 x 
+\end{align}
+where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.  This approximately reproduces the observed correlation between these quantities.
 
-{\bf Lens Galaxies}
+In addition to the basic disk and bulge models we introduce some spiral arms.  The surface brightness of 
+the disks are given by
+\begin{align}
+S(\theta,r) = e^{-r/R_h} \left( 1 + A \cos(N_a\theta + \phi_r \right) ~, \\
+\phi_r = \alpha\log(2 r/ R_h) + \phi_d \nonumber
+\end{align}
+where $R_h$ is the scale height of the disk.
+The phase angle of the arms, $\phi_d$, is chosen at random.
+The parameters $A$, $\alpha$ and $N_a$ are chosen from distributions that are judged by eye to produce realistic
+galaxies.
+The bulge is also perturbed from a perfect S\'{e}rsic profile by multiplying the surface brightness by
+\begin{align}
+1+\sum_{n=1}^6 a_n \cos\left( n \theta  + \phi_n \right)
+\end{align}
+where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002.
 
-There are not enough large galaxies in the UDF to make enough mock lens galaxies.
-The Millennium Observatory provides parameters for the galaxies that inhabit the dark matter halos using the semi-analytic galaxy formation models of \citet{2011MNRAS.413..101G}.
-To model the surface brightness of these galaxies we use the models ****
+These foreground galaxies are rotated in three dimensions with the halos of the lens each time a random lens is produced so that they remain in the same same positions relative to the mass.
+All the random parameters are also reassigned with every realization of the lens.
 
-{\bf mass rendering}
+These images of the of foreground galaxies are not intended to reproduce the true population of galaxies, but only to be sufficiently irregular to make them difficult to fit to a simple analytic model that might make them very easy to distinguish from a foreground plus a lensed image.
+As will be discussed later, more realistic models will be needed in the future and are a subject of current investigation.
 
 To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
-The surface brightness map in converted into a mass map by assuming a uniform mass-to-light ratio of **** in the **** band.
+The surface brightness map in converted into a mass map by assuming a uniform mass-to-light ratio of 1.5 solar in the target band.
 This mass map is added to the lens before the ray tracing is done.
 
-Every time the lens is reoriented a new realization of the lens galaxies is made and a new source position is found.
-
-{\bf size of cones}
-
-{\bf products - images output}
-
-For the training sets all these products were provided, but for the test sets only the final images were provided to participants although all the information was stored for analyzing the entries.
+The code is able to produce any combination of foreground galaxies, lensed image and noise that is desired.
+For the training set we provided an image of the total lens with noise, an image of the foreground galaxies with noise and and image of the lensed background source without noise.
+For the test sets only the final images were provided to participants although all the information was stored for analyzing the entries.
 
@@
 
-For the space-based data sets a simple Gaussian PSF was applied with a ***** of **** arcsec.  
+For the space-based datasets a simple Gaussian PSF was applied with a ***** of **** arcsec.  
 The band used was SDSS K.  The noise was a Gaussian random realization ****.
@@
 Arcfinder then extract contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness.
-A final thresholding is set to maximize purity over completeness on a few typical arcs of the data set.
+A final thresholding is set to maximize purity over completeness on a few typical arcs of the dataset.
 For the current SL challenge, arcfinder was tuned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.
 A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code as a linux line command.
-Arcfinder took a couple of hours to run on the entire data set with some overheads due to the data set format.
+Arcfinder took a couple of hours to run on the entire dataset with some overheads due to the dataset format.
 The code is publicly available at https://github.com/rcabanac/arcfinder.
@@
 
-The lens detector is based on a convolutional neural network (CNN), trained with the provided training data sets.
+The lens detector is based on a convolutional neural network (CNN), trained with the provided training datasets.
 The CNN is implemented in Python, using the TensorFlow framework\footnote{http://www.tensorflow.org/}.
@@
 If the TP
-rate is boosted from the FPR by a factor of 1,000 in a realistic data set with would correspond to about a 10\% contamination.
+rate is boosted from the FPR by a factor of 1,000 in a realistic dataset with would correspond to about a 10\% contamination.
 
@@
 It might be that one classifier is good at finding systems with large Einstein radii and incomplete arcs, but not as good at finding small complete Einstein rings that are blended with the light of the lens galaxy.
-Also lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test data set.
+Also lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test dataset.
 We want to include these objects because we want to test the limits of the classifiers.
@@
 
-Table~\ref{table:AUROC} shows the AUROC, TPR$_0$ and TPR$_{10}$ for the entries in order of AUROC and data set type.
+Table~\ref{table:AUROC} shows the AUROC, TPR$_0$ and TPR$_{10}$ for the entries in order of AUROC and dataset type.
 It can be seen that CMU-DeepLens-ResNet-ground3 had the best AUROC for the ground-based set and LASTRO EPFL the best for the space-based set.

### 2017-05-05 paper.tex
Edit Add GAMOCLASS

@@
 \newauthor
+Diego Tuccillo,$^{9,10}$
+Marc Huertas-Company,$^9$
+Santiago Velasco-Forero,$^10$
+Etienne Decenci\`ere,$^10$
 and ?\\
@@
 $^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique, Observatoire de la C\^{o}te d'Azur, \\ Parc Valrose, 06108 Nice, France \\
+$^{9}$ LERMA, Observatoire de Paris, CNRS, Université Paris Diderot, 61, Avenue de l’Observatoire F-75014, Paris, France \\
+$^{10}$ Centre for mathematical morphology, Mathematics and Systems department, MINES ParisTech, 35 rue Saint-Honore, Fontainebleau, France \\
 }
@@
 
-For the space-based datasets a simple Gaussian PSF was applied with a ***** of **** arcsec.  
-The band used was SDSS K.  The noise was a Gaussian random realization ****.
+For the space-based datasets the pixel size was set to 0.1 arcsec and 
+a simple Gaussian PSF was applied with a FWHM of 0.18 arcsec.  
+The reference band was SDSS K.
+The noise is based on a 1,800 second exposure, a transmission of 0.3, a telescope diameter of 119~cm, a readout noise of 5 electrons per pixel and a sky background of 22.8 magnitudes per sq.arcsec.
+We use a simple Gaussian random realization of the noise uncorrelated between pixels.
 
-{\bf fractions}
+ In the challenge set the limiting magnitude for background sources to 28 in K.   60\% of the cases had no background source and were thus labeled as non-lenses.
 
@@
 
-For the ground-based images four bands where *****.  
- The KiDS survey provided a representative PSF map, **** image stamps of their targets and the weights maps for those images.
-Some of these images had masked regions to remove stars, cosmic rays and bad pixels.
-The PSF had a FWHM of *** and was applied to all the images.
-Noise was simulated by adding normally distributed numbers with the variance given by the weight maps.
+For the ground-based images four bands where I, G, U and R.
+The reference band was R.
+For the challenge set 85\% images where made with purely simulated images as outlines above and the other 15\% used actual images taken from a preliminary sample of bright galaxies directly from the KiDS survey.
+Lensed source images where added to these real images at the same rate as for the mock images,  in this case 50\%.
+No attempt was made to match the halo masses to the observed galaxies in these cases.
+These real images where added for more realism and so that, by comparing the results for real and mock images, we can evaluate how realistic our simulations are in this context.
+
+number of stamps
+
+The KiDS survey provided a representative PSF map in each band that was applied to all mock images.   The pixel size 
+in this case was 0.2~arcsec. 
+Weight maps for the KiDS images were also provided some of which have masked masked regions from remove stars, cosmic rays and bad pixels.
+For the mock images the noise was simulated by adding normally distributed numbers with the variance given by the weight maps taken.
 The weight maps where also randomly rotated and flipped.
 This resulted in many of the images having large masked regions in them ($\sim$ ***** \%).
-
-In the test image set some actual KiDS images were used also.
-Here a random mass distribution and source was used to produce a lensed source that was added directly to the KiDS image after applying the PSF.
-No additional noise was added.
-
-{\bf fractions}
 
@@
  \label{gaborring}
-
 \end{figure}
@@
 Classification was performed using a modest desktop PC.
+
+\subsection{GAMOCLASS (Tuccillo, Huertas-Company, Velasco-Forero, Decenci\`ere)}
+
+Our algorithm for classification of strong lensed galaxies was developed as a convolutional neural network (CNN) used for binary classification task.
+Our code was trained and tested on the space-based dataset (dataset 0) provided for the Strong lensing challenge, comprising 20,000 stamps of single band simulated galaxies.
+We used the full dataset in the proportion of 4/5 for training and 1/5 for validation.
+The training images were labelled with 1 if showing strong lensing and 0 otherwise.
+Our CNN gives as output a probability [0,1] of the input image being a strongly lensed system.
+The final architecture of our model is illustrated in Fig.
+\ref{Fig1_gamoclass}.
+The input image (101x101 pixels) is first processed by a 2D convolution layer with a 3x3 filter size, then subsampled by a 3x3 max pooling layer.
+Other two identical units follow, with a growing dimensionality of the output space (depth, i.e.output number of filters) in the convolution, for a total of 3 convolutional layers and 3 max pooling layers.
+Each of these convolutional layers is followed by a rectified linear unit (ReLU) step.
+The output of these units is then processed through a single fully-connected layer follower by a dropout layer, and, finally, by a one-neuron fully connected layer with sigmoid activation function.
+For the classification problem we used the binary cross-entropy cost function and for weights updates we used an adaptive moment estimation (ADAM, \citealt{Kingma_2014}) optimization method.
+The use of the ADAM optimizer improves the learning rate, and previous tests with stochastic gradient descent (SGD) lead to worse results on the classification of the validation sample.
+In order to increase the size of the training set and make the model invariant to specific transformations, we perform several data augmentation steps:
+\begin{itemize}
+\item Random rotation of the image in the range [0, 180$\degree$], using a reflection fill mode to keep constant the size of the images.
+\item The images were randomly shifted of 0.02 times the total width of the image.
+\item Random horizontal and vertical flips of the images
+\end{itemize}
+During the training we initialize the weights of our model with random normal values and we warm up the training \citet{Huang_2016} of the CNN for 25 epochs, using an exponential decay rate (1e-6) and a staring learning rate of α = 0.001.
+Then the network is trained using an early stopping method, and for a maximum number of 300 epochs.
+The early stopping method is an effective method to prevent overfitting and consists in stopping the training if a monitored quantity does not improve for a fixed number (called \textit{patience}) of training epochs.
+The quantity that we monitored was the \textit{accuracy} of the classification of the validation sample.
+The best architecture was trained over 220 epochs with a parameter of patience equal to 20.
+We implemented our code the Keras framework \citet{Chollet_2015} on top of Theano \citet{Bastien_2012}.
+Our architecture converges with a classification accuracy of 91\% on the validation sample.
+We further evaluated the performance of our classifier calculating the ROC curve of the classifier, i.e.
+the True Positive Rate (TPR) against the False Positive Rate.
+As shown in Fig.
+\ref{Fig2_gamoclass}, we reach a TPR higher than the 90\% with a FPR < 8\%.
+
+\begin{figure}
+  \centering
+      \includegraphics[width=1\columnwidth]{figures/Fig1_gamoclass.pdf} 
+  \caption{GAMOCLASS}
+ \label{Fig1_gamoclass}
+\end{figure}
+
+\begin{figure}
+  \centering
+      \includegraphics[width=1\columnwidth]{figures/Fig2_gamoclass.pdf} 
+  \caption{GAMOCLASS ROC on training data.}
+ \label{Fig2_gamoclass}
+\end{figure}
 

### 2017-05-08 paper.tex
Update on Overleaf.
Added GAMOCLASS

@@
 R\'emi Cabanac,$^2$ 
+Etienne Decenci\`ere,$^{10}$
 Remi Flamary,$^8$
 Mario Geiger,$^6$ 
+\newauthor
 Philippa Hartley,$^7$
+Marc Huertas-Company,$^9$
 Neal Jackson,$^7$ 
+Jean-Paul Kneib,$^6$
 \newauthor
-Jean-Paul Kneib,$^6$
 Christoph Sch\"{a}fer,$^6$ 
@@
 Amit Tagore,$^7$
+Diego Tuccillo,$^{9,10}$
 \newauthor
-Diego Tuccillo,$^{9,10}$
-Marc Huertas-Company,$^9$
-Santiago Velasco-Forero,$^10$
-Etienne Decenci\`ere,$^10$
+Santiago Velasco-Forero,$^{10}$
 and ?\\
@@
 $^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{6}$ EPFL\\
+$^{6}$ \red{EPFL}\\
 $^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of Manchester, Oxford Rd, Manchester M13 9PL, UK \\
 $^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique, Observatoire de la C\^{o}te d'Azur, \\ Parc Valrose, 06108 Nice, France \\
-$^{9}$ LERMA, Observatoire de Paris, CNRS, Université Paris Diderot, 61, Avenue de l’Observatoire F-75014, Paris, France \\
+$^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
 $^{10}$ Centre for mathematical morphology, Mathematics and Systems department, MINES ParisTech, 35 rue Saint-Honore, Fontainebleau, France \\
@@
 
-\subsection{GAHEC IRAP (Remi Cabanac)}
+\subsection{GAHEC IRAP (Cabanac)}
 
@@
 
-\subsection{AstrOmatic (Emmanuel Bertin)}
+\subsection{AstrOmatic (Bertin)}
 
@@
 
-\subsection{YattaLens Lite (Alessandro Sonnenfeld)}
+\subsection{YattaLens Lite (Sonnenfeld)}
 YattaLensLite is a simpler version of the algorithm YattaLens \citep{Sonnenfeld17}, modified to meet the time constraints of the challenge.
@@
 
-\subsection{Manchester/Manchester1 (Jackson, Tagore)}
+\subsection{Manchester/Manchester1 (Jackson,Tagore)}
 
@@
 
+\begin{figure}
+  \centering
+      \includegraphics[width=1\columnwidth]{figures/Fig1_gamoclass.pdf} 
+  \caption{GAMOCLASS schematic}
+ \label{Fig1_gamoclass}
+\end{figure}
+
 Our algorithm for classification of strong lensed galaxies was developed as a convolutional neural network (CNN) used for binary classification task.
@@
 \ref{Fig2_gamoclass}, we reach a TPR higher than the 90\% with a FPR < 8\%.
-
-\begin{figure}
-  \centering
-      \includegraphics[width=1\columnwidth]{figures/Fig1_gamoclass.pdf} 
-  \caption{GAMOCLASS}
- \label{Fig1_gamoclass}
-\end{figure}
 

### 2017-05-08 paper.tex
Edit.

@@
-\documentclass[useAMS,usenatbib]{mn2e}
+\documentclass[useAMS,usenatbib]{mnras}
 
@@
 These real images where added for more realism and so that, by comparing the results for real and mock images, we can evaluate how realistic our simulations are in this context.
+There were about number 160,000 of these stamps from KiDS.
 
-number of stamps
-
-The KiDS survey provided a representative PSF map in each band that was applied to all mock images.   The pixel size 
-in this case was 0.2~arcsec. 
-Weight maps for the KiDS images were also provided some of which have masked masked regions from remove stars, cosmic rays and bad pixels.
+The KiDS survey provided a representative PSF map in each band that was applied to all mock images.   The pixel size in this case was 0.2~arcsec. 
+Weight maps for the KiDS images were also provided some of which have masked regions from remove stars, cosmic rays and bad pixels.
 For the mock images the noise was simulated by adding normally distributed numbers with the variance given by the weight maps taken.
 The weight maps where also randomly rotated and flipped.
-This resulted in many of the images having large masked regions in them ($\sim$ ***** \%).
+This resulted in many of the images having large masked regions in them.
 

### 2017-05-15 paper.tex
Added “All” method section.

@@
 Santiago Velasco-Forero,$^{10}$
+Camille Avestruz,$^{11-13,\dagger}$
+Nan Li,$^{12-14}$
+Matthew Lightman,$^{15}$
+\newauthor
 and ?\\
@@
 $^{10}$ Centre for mathematical morphology, Mathematics and Systems department, MINES ParisTech, 35 rue Saint-Honore, Fontainebleau, France \\
+$^{11}${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
+$^{12}${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
+$^{13}${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
+$^{14}${High Energy Physics Division, Argonne National Laboratory, Lemont, IL 60439}\\
+$^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
+$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
 }
@@
 
+%-------------------------------------------------%
+\subsection{ALL Methodology (Avestruz, Li, Lightman}
+%-------------------------------------------------%
+
+We detail the ALL team methodology in \citet{avestruz_etal17}. The
+pipeline was originally developed to automatically classify strong
+lenses in mock Hubble Space Telescope and Large Synoptic Sky Telescope
+data generated with code described in \citet{li_etal16} and
+\citet{collett_15}.  We apply the same exact steps for the single-band
+data for Euclid, but modify the feature extraction step for the
+four-band KIDS data.  We summarize the steps below.
+
+We use tools from {\em Scikit-learn} \citep{pedregosa_etal12} and
+perform minimal image preprocessing. First, we replace masked pixels
+with the average of surrounding pixels, then enhance contrast in the
+image by taking the normalized log of pixel values.  The next step of
+our pipeline consists of a feature extraction stage, where our feature
+vector is a {\em histogram of oriented gradients} (HOG)
+\citep{dalalandtriggs_05} that quantifies edges in the image.  HOG has
+three main parameters that determine the binning and resolution of
+edges captured by the features.  The result is a one dimensional
+feature vector corresponding to the magnitude of oriented gradients
+across the image.  With the KIDS data, we extract a feature vector for
+each of the four bands and concatenate the vectors to create a final
+feature vector for each object that we use to train a model
+classifier.
+
+We use {\em Logistic Regression} (LR), a machine learning algorithm,
+to train a classifier model.  LR requires a parameter search over the
+regression coefficient, $C_{LogReg}$.  The parameters from both the
+feature extrator, HOG, and the linear classifier, LR, contain
+parameters that we optimize for peak model performance.  We use {\em
+  GridSearchCV} from {\em Scikit-learn} to select cross-validated
+parameters for HOG parameters and a subset of $C_{LogReg}$ values with
+20\% of the test images provided.  We then run a finer parameter
+search over $C_{LogReg}$, splitting the test images into 80\% training
+and and 20\% test to avoid overfitting the data.  We use the best
+parameters to then train the entire dataset for the final model
+classifier that we used to evaluate the competition data.
+
 \section{results}
@@
 \red{We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}}
+CA acknowledges support from the Enrico Fermi
+Institute at the University of Chicago, and the University of Chicago
+Provost's Office. NL would like to thank the funding support from
+NSFC, grant no.11503064, and Shanghai Natural Science Foundation,
+grant no. 15ZR1446700. This work was also supported in part by the
+Kavli Institute for Cosmological Physics at the University of Chicago
+through grant NSF PHY-1125897 and an endowment from the Kavli
+Foundation and its founder Fred Kavli.
 

### 2017-06-13 paper.tex
Added ‘ALL’ submission.
Filled in some introduction.

@@
 \def\aaps{AAPS}
+\def\nat{Nature}
 
@@
 \newcommand{\degree}{^{\circ}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{etoolbox}
+\makeatletter
+\newcount\c@additionalboxlevel
+\setcounter{additionalboxlevel}{0}
+\newcount\c@maxboxlevel
+\setcounter{maxboxlevel}{1}
+\patchcmd\@combinedblfloats{\box\@outputbox}{%
+  \stepcounter{additionalboxlevel}%
+  \box\@outputbox
+}{}{\errmessage{\noexpand\@combinedblfloats could not be patched}}
+
+\AtBeginShipout{%
+  \ifnum\value{additionalboxlevel}>\value{maxboxlevel}%
+    \typeout{Warning: maxboxlevel might be too small, increase to %
+      \the\value{additionalboxlevel}%
+    }%
+  \fi 
+  \@whilenum\value{additionalboxlevel}<\value{maxboxlevel}\do{%
+    \typeout{* Additional boxing of page `\thepage'}%
+    \setbox\AtBeginShipoutBox=\hbox{\copy\AtBeginShipoutBox}%
+    \stepcounter{additionalboxlevel}%
+  }%
+  \setcounter{additionalboxlevel}{0}%
+}
+\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
@@
 Remi Flamary,$^8$
+Raphael Gavazzi,$^{17}$ 
+\newauthor
 Mario Geiger,$^6$ 
-\newauthor
 Philippa Hartley,$^7$
@@
 Neal Jackson,$^7$ 
+\newauthor
+Eric Jullo,$^{16}$
 Jean-Paul Kneib,$^6$
-\newauthor
 Christoph Sch\"{a}fer,$^6$ 
 Alessandro Sonnenfeld,$^5$ 
+\newauthor
 Amit Tagore,$^7$
 Diego Tuccillo,$^{9,10}$
+Santiago Velasco-Forero,$^{10}$
+Camille Avestruz,$^{11,12,13,\dagger}$
 \newauthor
-Santiago Velasco-Forero,$^{10}$
-Camille Avestruz,$^{11-13,\dagger}$
-Nan Li,$^{12-14}$
+Nan Li,$^{12,13,14}$
 Matthew Lightman,$^{15}$
-\newauthor
 and ?\\
@@
 $^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
+$^{16}$\red{LAM} \\
+$^{17}$\red{IAP} \\
 $^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
@@
 
-Arcfinder\citep{2007A&A...472..341S}
+Strong gravitational lenses are rare cases where a distant galaxy or quasar is aligned so closely with a foreground galaxy or cluster of galaxies  that the gravitational field of the foreground object creates multiple, highly distorted images of the background object.
+These take the form of multiple images of a quasar and Einstein rings surrounding a galaxy and of highly distorted arcs seen through galaxy groups and clusters.
+The first strong lens was discovered in 1979 \citep{1979Natur.279..381W} and since then many valuable scientific uses have been found for them.
+They have been used to study the mass distribution in galaxies and substructure in dark matter.
+They have been used to measure the Hubble constant and other cosmological parameters.
+Their magnification has been used as a natural telescope to observe otherwise undetectable objects.
+They have put limits on the self interaction of dark matter and on the theory of gravitation.
+Through microlensing they have been used to study the structure of quasars.
+To access this wealth of information the first step is to find the lenses.
+\red{Could use some citations in this paragraph.}
 
-\citet{2006astro.ph..6757A} arc finder used in the CFHT \citep{2007A&A...461..813C,2012ApJ...749...38M}
+The Square Kilometer Array (SKA)\footnote{http://skatelescope.org/}, the Large Synoptic Survey Telescope (LSST)\footnote{https://www.lsst.org/} and the Euclid space telescope\footnote{https://www.euclid-ec.org/} are expected to increase the number of potential lenses by orders of magnitude \citep{collett_15,euclidSLWGwhitepaper,2015aska.confE..84M,2010MNRAS.405.2579O}.
+For example it is estimated that there will be approximately 200,000 observable galaxy-galaxy lenses in the Euclid data set among \red{tens of billions (better number??)} of potential objects .
+So far, less than a thousand lenses have been found in total across many heterogeneous data sets.
+These surveys will bring a new era for strong lensing where large relatively well defined samples of lenses will be possible.
+It will also require handling much larger quantities of data than has been customary in this field.
 
-Some finders compare each image with a lens model \citep{2009ApJ...694..924M,2010A&A...517A..25S}.
+Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of a samples candidates that have been selected on the bases of luminosity and/or color.
+This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F} \red{(Maybe there are some others to cite here?)}.
+A related method pioneered by the SPACE WARPS project \citep{2016MNRAS.455.1171M,2016MNRAS.455.1191M} has been to crowd source the visual inspection through an online platform.
+These efforts have proved very fruitful, but they deal with orders of magnitude fewer candidates and lenses than will be necessary in the future.
+Dealing with such large quantities of data will not be practical for any visual inspection approach.
+In addition, the efficiency and detection bias of human inspection methods are difficult to rigorously quantify.
 
-\citep{2014A&A...566A..63J,2016A&A...592A..75P}
+Galaxy scale lenses have also been searched for spectroscopicly by looking for high redshift stellar lines in the spectra of lower redshift large galaxies.
+Notably this was done in the Sloan Lens ACS (SLACS) survey to producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006ApJ...638..703B}.
+However, spectroscopy is telescope-time consuming and for the foreseeable future we are not likely to have spectroscopic surveys that cover anywhere near the number of objects as the planned imaging surveys.
 
-some numbers about future surveys
+Some automated algorithms have been developed in the past to detect lenses in images.
+These have been designed to detect arc-like features \citep{2006astro.ph..6757A,2007A&A...472..341S} and rings \citep{2014ApJ...785..144G,2014A&A...566A..63J}.
+They have been applied to survey data and found of order 200 lenses \citep{2007A&A...461..813C,2012ApJ...749...38M,2016A&A...592A..75P}.
+Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2010A&A...517A..25S}.
 
-some background on past methods
+More recently machine learning techniques that have become widely used in the fields computer image processing and artificial intelegence 
+have been applied to this problem and others in astronomy, in particular, artificial neural networks (ANNs) and support vector machines (SVM).
+These algorithms do not pick out particular predefined features, but learn from a training set which features are most important for distinguishing categories of objects.
+These have been used widely for such tasks as handwriting and facial recognition.
+In astronomy they are beginning to be used for catagorizing galaxies morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017arXiv170207675P,2017MNRAS.465.4325O}.
+
+Given the future of this field with large amounts of data coming soon and many new ideas emerging we thought it would be a good time to stage a series of challenges to stimulate new work, determine what can realistically be done in lens finding and get a better idea of the strengths and weaknesses to different methods.
+The long term goal is to get a set of algorithms that can handle Euclid, LSST or SKA data sets and produce high purity and high completeness lens samples with well defined efficiency or selection.
+We anticipate further challenges in the future were the realism of the data simulations will become progressively more realistic.
+Here we have chosen to concentrate on galaxy/small group scale lenses where the background source is a galaxy because we feel that this is were the most progress can be made and the scientific return is the highest, but QSO lenses and cluster/group lenses challenges may follow.
 
@@
 The code is able to produce any combination of foreground galaxies, lensed image and noise that is desired.
-For the training set we provided an image of the total lens with noise, an image of the foreground galaxies with noise and and image of the lensed background source without noise.
+For the training set we provided an image of the total lens with noise, an image of the foreground galaxies with noise and image of the lensed background source without noise.
 For the test sets only the final images were provided to participants although all the information was stored for analyzing the entries.

### 2017-06-14 paper.tex
Edit

@@
 
-The challenge was in fact two independent challenges that could be entered independently.
-One was designed to mimic a single band of a future imaging data set from a satellite survey such as Euclid\footnote{https://www.euclid-ec.org/} \citep{***}.
+The challenge was in fact two separate challenges that could be entered independently.
+One was designed to mimic a single band of a future imaging data set from a satellite survey such as Euclid \citep{***} \red{(the latest description)}.
 The other was designed to mimic ground based data with multiple bands, roughly modeled on the Kilo-Degree Survey (KiDS)\footnote{http://kids.strw.leidenuniv.nl/} \citep{2013ExA....35...25D} .
-In neither case were the simulated images meant to precisely mock these surveys, but only used them as general guide as to set noise levels, pixel sizes, sensitivities and other parameters.
+In neither case were the simulated images meant to precisely mock these surveys, but the surveys were used as guides to set noise levels, pixel sizes, sensitivities and other parameters.
 
-In each case a training set of 20,000 images in each band was provided for download at any time along with a key giving some properties of the object including whether it was a gravitational lens.
+In each case, a training set of 20,000 images in each band was provided for download at any time along with a key giving some properties of the object including whether it was a gravitational lens.
 Each image was $101\times101$ pixels.
@@
 In this case it was the Millennium simulation \citep{2009MNRAS.398.1150B}.
-A catalog of dark matter halos within a light-cone is constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O} down to a mass of ****.
+A catalog of dark matter halos within a light-cone is constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
 The challenge sets were based on a 1.6 sq.deg.
@@
 With GLAMER we identify and map out all the caustics within the light-cone for 33 source planes -- z=1 to 3 in intervals of 0.1 and 3 to 6 in intervals of 0.25.
-We take every caustic that corresponded to a critical curve with an Einstein radius larger than 1.5 times the resolution.
+We take every caustic that corresponded to a critical curve with an Einstein radius larger than 1.5 times the resolution of the final images.
 The Einstein radius is estimated here and in all that follows as $R_{\rm ein}=\sqrt{A_{\rm ein}/\pi}$ where $A_{\rm ein}$ is the angular area within the critical curve.
@@
  A **** square degree light-cone gives rise to **** such caustics, but these over count the number of lenses since most will have caustics on multiple source planes.
-These lenses could be used as is, but we want to produce a much larger number with more randomness.
+These lenses could be used as is, but we wanted to produce a much larger number with more randomness.
 For each caustic we identify the lens plane with the highest convergence and identify all the halos within a three dimensional distance of 0.5 Mpc from the center of the critical curve and on this and its neighboring lens planes.
 This collection of halos is then used as the lens and rotated to produce more random lenses.
-It  contains all the subhalos and near by companion halos, but not the large scale structure surrounding it.
+It  contains all the subhalos and nearby companion halos, but not the large scale structure surrounding it.
 

### 2017-06-15 paper.tex
Edit.

@@
 For lensed sources we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.  This is the same set of images as used 
-in  \red{*** Massimo: Can you put a citation in for this?}.   There are 9,350 such sources with redshifts and separate coefficients in 10 bands.
+in  \red{*** Massimo: Can you put a citation in for this?}.   There are 9,350 such sources with redshifts and separate shapelet coefficients in 10 bands. \red{(verify)}
 
@@
 The lens is extracted as explained above and rotated randomly in three dimensions.
-A source is selected at random from the shapelet catalog subject to a magnitude limit in a target band.
+A source is selected at random from the shapelet catalog subject to a magnitude limit in a reference band.
 The redshift of the UDF source is used as the source redshift.
-If the source is at a lower redshift than the lens or within $\Delta z = 0.4$ another source is selected.
+If the source is at a lower redshift than the lens or within $\Delta z = 0.4$ another random source is selected.
 
 The furthest point in the caustic is found from its own center and the source is placed randomly within 3 times this distance.
-This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the process  inefficiently because most of the sources are too far away from the caustic to produce clear lenses.
+This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the process  inefficient because most of the sources are too far away from the caustic to produce clear lenses.
 If the source positions where taken completely at random the fraction of clear lenses would be very low.
@@
 The bulge is represented by a S\'{e}rsic profile with a axis ratio randomly sampled between 0.5 and 1.
-The S\'{e}rsic index, $n_s$, is by
+The S\'{e}rsic index, $n_s$, is given by
 \begin{align}
@@
 \end{align}
-where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.  This approximately reproduces the observed correlation between these quantities.
+\red{(reference)} where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.
+This approximately reproduces the observed correlation between these quantities.
 
@@
 \end{align}
-where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002.
+where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002. \red{(reference)}
 
@@
 To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
-The surface brightness map in converted into a mass map by assuming a uniform mass-to-light ratio of 1.5 solar in the target band.
+The surface brightness map in converted into a mass map by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
 This mass map is added to the lens before the ray tracing is done.
@@
 
-For the ground-based images four bands where I, G, U and R.
+For the ground-based images four bands (I, G, U and R) where simulated.
 The reference band was R.
@@
 These real images where added for more realism and so that, by comparing the results for real and mock images, we can evaluate how realistic our simulations are in this context.
-There were about number 160,000 of these stamps from KiDS.
+There were about 160,000 of these stamps from KiDS.
 
 The KiDS survey provided a representative PSF map in each band that was applied to all mock images.   The pixel size in this case was 0.2~arcsec. 
-Weight maps for the KiDS images were also provided some of which have masked regions from remove stars, cosmic rays and bad pixels.
-For the mock images the noise was simulated by adding normally distributed numbers with the variance given by the weight maps taken.
+Weight maps for the KiDS images were also provided.
+Some of these had masked regions from remove stars, cosmic rays and bad pixels.
+For the mock images the noise was simulated by adding normally distributed numbers with the variance given by the weight maps.
 The weight maps where also randomly rotated and flipped.
@@
 They are listed in table~\ref{table:entries}.
-There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries form people outside of the field.
+There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries from people outside of the field.
 
@@
 
-Arcfinder \citep{astronaut.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
-Arcfinder then extract contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness.
+Arcfinder \citep{astronaut.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} \red{(seems to have lost this first reference)} is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
+Arcfinder then extracts contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness.
 A final thresholding is set to maximize purity over completeness on a few typical arcs of the dataset.
@@
 The Python scripts used for manual examination of multiple images are available
-on https://github.com/nealjackson/bigeye and are described in more detail
+onGitHub\footnote{https://github.com/nealjackson/bigeye} and are described in more detail
 in Hartley et al. (2016, in preparation). For one-colour data such as
@@
 The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or {\bf ROC} curve.
-This a plot of the true positive rate (TPR) and the false positive rate (FPR).
+This is a plot of the true positive rate (TPR) and the false positive rate (FPR).
 In this case these are defined as
@@
 \end{align}
-The classifier generally gives a probability of a case being a lens, $p$ in which case a threshold is set and everything with $p$ greater is classified as a lens and everything smaller classified as not a lens.
+The classifier generally gives a probability of a case being a lens, $p$ in which case a threshold is set and everything with $p$ greater is classified as a lens and everything smaller is classified as not a lens.
 The TPR and FPR are then plotted as a curve parametrised by this threshold.
@@
 The better a classifier is the smaller the FPR and the larger the TPR so the further away from this diagonal line it will be.
-When a classifier provides only a binary classification or a discrete ranking the ROC connects the endpoints to the discrete points found be using each rank as a threshold.
+When a classifier provides only a binary classification or a discrete ranking, the ROC connects the endpoints to the discrete points found be using each rank as a threshold.
 
@@
 However, in the case of gravitational lensing this is not the only thing, and not the most important thing, to consider.
-Gravitational lenses are rare events, but to improve the discrimination and training of the classifies the fraction lenses in the boosted to something around half.
+Gravitational lenses are rare events, but to improve the discrimination and training of the classifiers the fraction lenses in test and training sets are boosted to something around half.
 In these circumstances it is important to consider the absolute number of cases that will be missclassified when the fraction of true cases is closer to what is expected in the data.
@@
 
-The {\bf TPR$_0$} will be defined as the highest TPR reached, as a function of $p$ threshold, before a single false positive occurs in the test set of 100,000 images.
+The {\bf TPR$_0$} will be defined as the highest TPR reached, as a function of $p$ threshold, before a single false positive occurs in the test set of 100,000 cases.
 This is the point were the ROC meets the FPR = 0 axis.
@@
 We also define {\bf TPR$_{10}$} which is the TPR at the point were less than ten false positives are made.
-If the TP
-rate is boosted from the FPR by a factor of 1,000 in a realistic dataset with would correspond to about a 10\% contamination.
+If the TP rate is boosted from the FPR by a factor of 1,000 in a realistic data set this would correspond to about a 10\% contamination.
 
@@
 
-Figures~\ref{fig:roc_space} and \ref{fig:roc_space} show the ROC curves for all the entries.
-In addition figure~\ref{fig:roc_kids} shows the ROC curves for only the ground-based images where an actual KiDS image was used (see section~\ref{sec:sim-ground-based}).
+Figures~\ref{fig:roc_space} and \ref{fig:roc_ground} show the ROC curves for all the entries.
+In addition, figure~\ref{fig:roc_kids} shows the ROC curves for only the ground-based images where an actual KiDS image was used (see section~\ref{sec:sim-ground-based}).
 It can be seen that the classifiers do uniformly less well on this subset.
-This indicates that the simulated galaxy images are different from the real ones and that the classifiers are not able to distinguish fake foreground galaxies from lenses more easily.
+This indicates that the simulated galaxy images are different from the real ones and that the classifiers are able to distinguish fake foreground galaxies from lenses more easily than from real galaxies.
 This is perhaps not unexpected, but does show that the simulated lenses need to be improved before the raw numbers can be directly used to evaluate the performance of a classifier on real data.
@@
 Manchester1 is the human inspection method.
-In some cases these are above 50\% of the lenses that meet the criterion.
+In some cases the TPR$_0$'s are above 50\% of the lenses that meet this criterion.
 Remember that many of the so called lenses are very dim or there is no significant arc because of the source position is well outside the caustic.
@@
 
-A lensed image can be bright without being visibly distorted as in the case of a unresolved image.
+A lensed image can be bright without being visibly distorted as in the case of a unresolved images.
 Figures~\ref{fig:npixel_space} and \ref{fig:npixel_ground} use the number of pixels in the lensed image(s) that are over  one $\sigma$ of the background.
@@
 This could be because they are not differentiating the arcs from companion galaxies as well in this regime.
+There were also cases where the arc intersects with the borders of the image that might cause them to be missed.
 

### 2017-06-18 paper.tex
Update on Overleaf.
Edit.

@@
 a simple Gaussian PSF was applied with a FWHM of 0.18 arcsec.  
-The reference band was SDSS K.
+The reference band was SDSS I.
 The noise is based on a 1,800 second exposure, a transmission of 0.3, a telescope diameter of 119~cm, a readout noise of 5 electrons per pixel and a sky background of 22.8 magnitudes per sq.arcsec.
@@
 
-It is clear that the robustness of lens finders against falsely classifying unusual galaxies as lenses was not adequately tested in this challenge.
-Some of the methods which appear overly conservative in this test might be better at avoiding false positives in real data.
-This can be seen as a form of over fitting to the test set.
-In future challenges we wish to concentrate on this aspect of the problem.
+A large variety of lens finding methods were tested on simulated images that were developed separately.
+We found that some methods could recover more than 50\% of the lenses above a lens image brightness or size threshold without a single false positive.
+If the data closely resembled the simulations we would already have reasonably good methods whose efficiency and biases can be quantitatively characterized.
 
-Human inspection was the only method to find the jackpot lens
+We have done a fairly good jobs of determining that lenses can be identified in a population of fairly "normal" galaxies.
+It is the rare "abnormal" objects that pose the greatest challenge.
+When real KiDS data was used in the simulations the classifiers were all less accurate and it was only human inspection that found the one jackpot lens in the data.
+Things like ring galaxies, tidal tails in merging galaxies and irregular galaxies can be mistaken for lenses and were not well represented in the simulated data.
+Accurately reproducing these objects will be an objective of future work.
+
+It was surprising to some of the authors how well CNN and SVM methods did relative to human inspection.
+These methods find differences in the classes of images that are not obvious to a human and can classify things as lenses with high confidence where a human would have doubt.
+This ability comes with some danger of over fitting to the training set however.
+The distinguishing characteristics might only be a property of simulated data and not of real data.
+The confidence one will have in these methods is really the confidence one has in the realism of the simulations.
+
+When initiating this project we had a concern that current methods would be too slow or require too much human intervention to handle large data sets.
+Happily this seems not to be a problem with most of the automatic methods.
+The CNN and SVM codes take some time to train, but once trained they are very fast in classifying objects.
+Billions of objects can be easily handled.
+
+Another lesson is that color information is very important.
+Even with lower noise levels, higher resolution, a simpler PSF and no masking the lenses in the space-based set were harder to find than the lenses in the ground-based set.
+Having multiple bands clearly makes a big difference.
+Euclid will have several infrared bands with lower resolution than the visible images that were not included in the challenge.
+Even rather low resolution information from another instrument or telescope when combined with higher resolution data in one band might significantly improve the detection rates.
 

### 2017-06-19 paper.tex
Update on Overleaf.

@@
 The first strong lens was discovered in 1979 \citep{1979Natur.279..381W} and since then many valuable scientific uses have been found for them.
-They have been used to study the mass distribution in galaxies and substructure in dark matter.
-They have been used to measure the Hubble constant and other cosmological parameters.
-Their magnification has been used as a natural telescope to observe otherwise undetectable objects.
+They have been used to study how dark matter is distributed in galaxies and clusters \citep[e.g.][]{1991ApJ...373..354K,2001ApJ...554.1216C,2002ApJ...568L...5K,2003ApJ...587..143R,2003ApJ...583..606K,2005MNRAS.360.1333W,2005ApJ...623...31D,2009MNRAS.392..945V,2016MNRAS.463.3115T}.
+They have been used to measure the Hubble constant and other cosmological parameters \citep[e.g.][]{1964MNRAS.128..307R,1992ARA&A..30..311B,2000ApJ...544...98W,2013ApJ...766...70S,2016A&ARv..24...11T}.
+Their magnification has been used as a natural telescope to observe otherwise undetectable objects \citep[e.g][]{2007ApJ...671.1196M,2017MNRAS.464.4823B,2016ApJ...833..264S}.
 They have put limits on the self interaction of dark matter and on the theory of gravitation.
@@
 
-More recently machine learning techniques that have become widely used in the fields computer image processing and artificial intelegence 
+More recently machine learning techniques that have become widely used in the fields computer image processing and artificial intelligence 
 have been applied to this problem and others in astronomy, in particular, artificial neural networks (ANNs) and support vector machines (SVM).
@@
 
-Given the future of this field with large amounts of data coming soon and many new ideas emerging we thought it would be a good time to stage a series of challenges to stimulate new work, determine what can realistically be done in lens finding and get a better idea of the strengths and weaknesses to different methods.
+Given the future of this field with large amounts of data coming soon and many new ideas emerging, it is timely to stage a series of challenges to stimulate new work, determine what can realistically be done in lens finding and get a better idea of the strengths and weaknesses to different methods.
 The long term goal is to get a set of algorithms that can handle Euclid, LSST or SKA data sets and produce high purity and high completeness lens samples with well defined efficiency or selection.
-We anticipate further challenges in the future were the realism of the data simulations will become progressively more realistic.
-Here we have chosen to concentrate on galaxy/small group scale lenses where the background source is a galaxy because we feel that this is were the most progress can be made and the scientific return is the highest, but QSO lenses and cluster/group lenses challenges may follow.
+We anticipate further challenges in the future were the realism of the data simulations will become progressively larger.
+Here we have chosen to concentrate on galaxy/small group scale lenses where the background source is a galaxy because we feel that this is where the most progress can be made and the scientific return is the highest, but QSO lenses and cluster/group lenses challenges may follow.
 
@@
 One was designed to mimic a single band of a future imaging data set from a satellite survey such as Euclid \citep{***} \red{(the latest description)}.
-The other was designed to mimic ground based data with multiple bands, roughly modeled on the Kilo-Degree Survey (KiDS)\footnote{http://kids.strw.leidenuniv.nl/} \citep{2013ExA....35...25D} .
-In neither case were the simulated images meant to precisely mock these surveys, but the surveys were used as guides to set noise levels, pixel sizes, sensitivities and other parameters.
+The other was designed to mimic ground based data with multiple bands, roughly modeled on the Kilo-Degree Survey (KiDS)\footnote{http://kids.strw.leidenuniv.nl/} \citep{2013ExA....35...25D}.
+In neither case were the simulated images meant to precisely mock these surveys, but the surveys were used as guides to set noise levels, pixel sizes, sensitivities, and other parameters.
 
@@
 
-Creating the mock images starts with a cosmological nbody simulation.
+Creating the mock images starts with a cosmological N-body simulation.
 In this case it was the Millennium simulation \citep{2009MNRAS.398.1150B}.
@@
 The challenge sets were based on a 1.6 sq.deg.
-light cone extending out to redshift 6.
+light cone extending out to redshift $z=6$.
 The halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
 This code projects the halos onto lens planes, in this case 20, and finds the deflection angle on each plane by a hybrid tree method.
-In this way the halos have the mass, concentration and clustering properties from the nbody simulation, but within each strong lens the mass resolution is not limited by the original simulation, but follows the analytic mass profile.
+In this way the halos have the mass, concentration and clustering properties from the N-body simulation, but within each strong lens the mass resolution is not limited by the original simulation, but follows the analytic mass profile.
+{\color{red} MM: I am a bit confused: at this stage, how are the halos modeled?
+N-body or analytic?
+What is the shape of the halos?}
 
@@
 This collection of halos is then used as the lens and rotated to produce more random lenses.
-It  contains all the subhalos and nearby companion halos, but not the large scale structure surrounding it.
+It  contains all the sub-halos and nearby companion halos, but not the large scale structure surrounding it.
 
 For lensed sources we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.  This is the same set of images as used 
-in  \red{*** Massimo: Can you put a citation in for this?}.   There are 9,350 such sources with redshifts and separate shapelet coefficients in 10 bands. \red{(verify)}
+in  \citep{2008A&A...482..403M,2010A&A...514A..93M,2016arXiv160604548M}.   There are 9,350 such sources with redshifts and separate shapelet coefficients in 4 bands.
 
@@
 The visible galaxies associated with the lens must also be simulated.
-There were not enough large galaxies in the UDF catalog to make enough mock lens galaxies for this purpose.
+There  too few bright galaxies in the  in the UDF catalog to make enough mock lens galaxies for this purpose.
 Instead, for most of the lenses, we used an analytic model for the surface brightness of these galaxies.
@@
 This mass map is added to the lens before the ray tracing is done.
+{\color{red} MM: Again, I am confused with how the lenses are modeled in this stage of the simulation and during the search for caustics described in the beginning of this section.}
 
@@
 
-\subsection{space-based}
+\subsection{Space-based}
 \label{sec:sim-space-based}
@@
 a simple Gaussian PSF was applied with a FWHM of 0.18 arcsec.  
-The reference band was SDSS I.
+The reference band was SDSS $i$.
 The noise is based on a 1,800 second exposure, a transmission of 0.3, a telescope diameter of 119~cm, a readout noise of 5 electrons per pixel and a sky background of 22.8 magnitudes per sq.arcsec.
@@
 
-\subsection{ground-based}
+\subsection{Ground-based}
 \label{sec:sim-ground-based}
 
-For the ground-based images four bands (I, G, U and R) where simulated.
-The reference band was R.
+For the ground-based images four bands ($u,g,r$, and $i$) where simulated {\color{red} (these are SDSS filters too, right?)}.
+The reference band was $r$.
 For the challenge set 85\% images where made with purely simulated images as outlines above and the other 15\% used actual images taken from a preliminary sample of bright galaxies directly from the KiDS survey.
@@
 Weight maps for the KiDS images were also provided.
-Some of these had masked regions from remove stars, cosmic rays and bad pixels.
+Some of these had masked regions from removed stars, cosmic rays, and bad pixels.
 For the mock images the noise was simulated by adding normally distributed numbers with the variance given by the weight maps.
@@
 
-\section{the entries}
+\section{The Entries}
 \label{sec:entries}
@@
 
-The network itself consists of three convolutional layers ($11\times 11\times 32$, $5\times 5 \times 64$ and $3\times 3\times 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer.
+{\color{red} (MM: I think that the co-authors should provide a more detailed description of the algorithms.
+For example, they should quickly explain what is a CNN and what are its general components (i.e.
+what kind of layers, activation functions, etc.)}
+
+The network itself consists of three convolutional layers ($11\times 11\times 32$, $5\times 5 \times 64$ and $3\times 3\times 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer {\color{red} MM: the numbers make little sense without a description of what the mean -- see my previous comment}.
 The first five layers use the ELU (Exponential Linear Unit) activation function \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
@@
 Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.
+
+{\red MM: May be we could separate the methods into three categories: machine-learning, arc-finders, visual inspection and group them accordingly}
 
@@
 
-\bibliographystyle{mn2e}
+\bibliographystyle{mnras}
 \bibliography{references}

### 2017-06-21 paper.tex
Update on Overleaf.

@@
 
-For the space-based datasets the pixel size was set to 0.1 arcsec and 
-a simple Gaussian PSF was applied with a FWHM of 0.18 arcsec.  
-The reference band was SDSS $i$.
-The noise is based on a 1,800 second exposure, a transmission of 0.3, a telescope diameter of 119~cm, a readout noise of 5 electrons per pixel and a sky background of 22.8 magnitudes per sq.arcsec.
-We use a simple Gaussian random realization of the noise uncorrelated between pixels.
+The space-based datasets were meant to roughly mimic the data quality which is expected from observations by the Euclid telescope in the visible channel.
+To this end, the pixel size was set to 0.1 arcsec and a Gaussian PSF was applied with a FWHM of 0.18 arcsec.
+The Gaussian PSF is clearly a simplified model, but a realistic treatment of the PSF is outside the scope of this paper.
+The typical width of the blurring due to the PSF is anyway realistic.
+The reference band for background and foreground galaxies was SDSS $i$, which is overlapping with the broader Euclid VIS band.
+The realisation of the mock images followed the same procedure described in \citet{2004PASP..116..750G} and \citet{2008A&A...482..403M}.
+As a result, the noise follows a Gaussian distribution with a realistic width and is uncorrelated between pixels.
+Characteristics of the instrument, filter and exposure times were taken from the Euclid Red Book \citep{2011arXiv1110.3193L}.
 
- In the challenge set the limiting magnitude for background sources to 28 in K.   60\% of the cases had no background source and were thus labeled as non-lenses.
+ In the challenge set the limiting magnitude for background sources to 28 in $i$.   60\% of the cases had no background source and were thus labeled as non-lenses.
 

### 2017-08-04 paper.tex
Update on Overleaf.

@@
 Etienne Decenci\`ere,$^{10}$
-Remi Flamary,$^8$
+R\'emi Flamary,$^8$
 Raphael Gavazzi,$^{17}$ 
@@
 $^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
-$^{10}$ Centre for mathematical morphology, Mathematics and Systems department, MINES ParisTech, 35 rue Saint-Honore, Fontainebleau, France \\
+$^{10}$ MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue Saint-Honore, Fontainebleau, France \\
 $^{11}${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\

### 2017-08-07 paper.tex
Update on Overleaf.

@@
 \newauthor
-Nan Li,$^{12,13,14}$
+Nan Li,$^{14}$
 Matthew Lightman,$^{15}$
@@
 $^{13}${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
-$^{14}${High Energy Physics Division, Argonne National Laboratory, Lemont, IL 60439}\\
+$^{14}${School of Physics and Astronomy, Nottingham University, University Park, Nottingham, NG7 2RD, UK
+}\\
 $^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
@@
 They have been applied to survey data and found of order 200 lenses \citep{2007A&A...461..813C,2012ApJ...749...38M,2016A&A...592A..75P}.
-Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2010A&A...517A..25S}.
+Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2010A&A...517A..25S,2017arXiv170401585S}.
 
@@
 \subsection{YattaLens Lite (Sonnenfeld)}
-YattaLensLite is a simpler version of the algorithm YattaLens \citep{Sonnenfeld17}, modified to meet the time constraints of the challenge.
+YattaLensLite is a simpler version of the algorithm YattaLens \citep{2017arXiv170401585S}, modified to meet the time constraints of the challenge.
 YattaLensLite subtracts a model surface brightness profile describing the lens galaxy from the $g$-band image, then runs SExtractor to detect tangentially elongated or ring-shaped objects, which are interpreted as lensed images.
@@
 The difference in color between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
-However in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
-at the smallest radius between the position where the surface brightness is comparable to the sky background level or the position of a positive radial gradient in surface brightness, if detected.
+However, in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
+The model lens light is truncated at the smallest radius between the position where the surface brightness is comparable to the sky background level, or the position of a positive radial gradient in surface brightness, if detected.
 
-In the space-based challenge it is not possible to separate lens and source based on color, because only data in one band is provided.
+In the space-based challenge, it is not possible to separate lens and source based on color, because only data in one band is provided.
 The lens light model then is produced by taking a centrally-inverted image and then using the same truncation prescription used with ground-based data.

### 2017-08-08 paper.tex
Update on Overleaf.

@@
 
-\subsection{Gabor-SVM (Hartley,Flamary)}
+\subsection{Gabor-SVM (Hartley, Flamary)}
 
@@
 Feature extraction, however,  requires both an extensive exploration of the feature space during the development of a model, and potentially intensive computer resources in order to transform the original samples.
-Our full method is described in detail in Hartley et.
-al., in prep., and was developed using the Python scikit-learn and scikit-image packages \citep{scikit-learn,scikit-image}.
+Our full method is described in detail in \citet{hartley2017support}, and was developed using the Python scikit-learn and scikit-image packages \citep{scikit-learn,scikit-image}.
 

### 2017-08-09 paper.tex
Update on Overleaf.

@@
 Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of a samples candidates that have been selected on the bases of luminosity and/or color.
-This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F} \red{(Maybe there are some others to cite here?)}.
+This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2014MNRAS.439.3392P} \red{(Maybe there are some others to cite here?)}.
 A related method pioneered by the SPACE WARPS project \citep{2016MNRAS.455.1171M,2016MNRAS.455.1191M} has been to crowd source the visual inspection through an online platform.
@@
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy they are beginning to be used for catagorizing galaxies morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017arXiv170207675P,2017MNRAS.465.4325O}.
+In astronomy they are beginning to be used for catagorizing galaxies morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O}.
 

### 2017-08-09 paper.tex
Update on Overleaf.

@@
 $^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
-$^{2}$ IRAP, University of Toulouse, CNRS, UPS, France.\\
+$^{2}$ IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.\\
 $^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014,\\ Paris France.\\
@@
 
-Arcfinder \citep{astronaut.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} \red{(seems to have lost this first reference)} is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
+Arcfinder \citep{2006astro.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} illustrated Figure \ref{fig:Cabanac}, is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
 Arcfinder then extracts contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness.
@@
 The code is publicly available at https://github.com/rcabanac/arcfinder.
-
-\red{Reference to figure \ref{fig:Cabanac}?}
 

### 2017-08-16 paper.tex
Update on Overleaf.

@@
 They have put limits on the self interaction of dark matter and on the theory of gravitation.
-Through microlensing they have been used to study the structure of quasars.
+Through microlensing they have been used to study the structure of quasars \citep{2008ApJ...689..755M,2008ApJ...673...34P,2011ApJ...729...34B}.
 To access this wealth of information the first step is to find the lenses.
@@
 This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2014MNRAS.439.3392P} \red{(Maybe there are some others to cite here?)}.
-A related method pioneered by the SPACE WARPS project \citep{2016MNRAS.455.1171M,2016MNRAS.455.1191M} has been to crowd source the visual inspection through an online platform.
+A related method pioneered by the SPACE WARPS project \citep{2016MNRAS.455.1171M,2016MNRAS.455.1191M,2015MNRAS.452..502G} has been to crowd source the visual inspection through an online platform.
 These efforts have proved very fruitful, but they deal with orders of magnitude fewer candidates and lenses than will be necessary in the future.
@@
 
-Galaxy scale lenses have also been searched for spectroscopicly by looking for high redshift stellar lines in the spectra of lower redshift large galaxies.
-Notably this was done in the Sloan Lens ACS (SLACS) survey to producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006ApJ...638..703B}.
+Galaxy scale lenses have also been searched for spectroscopically by looking for high redshift stellar lines in the spectra of lower redshift large galaxies.
+Notably this was done in the Sloan Lens ACS (SLACS) survey, producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006ApJ...638..703B}.
 However, spectroscopy is telescope-time consuming and for the foreseeable future we are not likely to have spectroscopic surveys that cover anywhere near the number of objects as the planned imaging surveys.
@@
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy they are beginning to be used for catagorizing galaxies morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O}.
+In astronomy they are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O}.
 
@@
 The long term goal is to get a set of algorithms that can handle Euclid, LSST or SKA data sets and produce high purity and high completeness lens samples with well defined efficiency or selection.
-We anticipate further challenges in the future were the realism of the data simulations will become progressively larger.
+We anticipate further challenges in the future in which the realism of the data simulations will become progressively better.
 Here we have chosen to concentrate on galaxy/small group scale lenses where the background source is a galaxy because we feel that this is where the most progress can be made and the scientific return is the highest, but QSO lenses and cluster/group lenses challenges may follow.
@@
 
-These foreground galaxies are rotated in three dimensions with the halos of the lens each time a random lens is produced so that they remain in the same same positions relative to the mass.
+These foreground galaxies are rotated in three dimensions with the halos of the lens each time a random lens is produced so that they remain in the same positions relative to the mass.
 All the random parameters are also reassigned with every realization of the lens.
@@
 For the mock images the noise was simulated by adding normally distributed numbers with the variance given by the weight maps.
-The weight maps where also randomly rotated and flipped.
+The weight maps were also randomly rotated and flipped.
 This resulted in many of the images having large masked regions in them.
@@
 onGitHub\footnote{https://github.com/nealjackson/bigeye} and are described in more detail
-in Hartley et al. (2016, in preparation). For one-colour data such as
+in \citet{hartley2017support}. For one-colour data such as
 the space-based training set, the images are individually colour-scaled using

### 2017-08-19 paper.tex
Update on Overleaf.

@@
 Matthew Lightman,$^{15}$
+Cl\'ecio R. Bom,$^{18,19}$
+Manuel B. Valent\'in,$^{19}$
+Martin Makler,$^{19}$
+\newauthor
 and ?\\
@@
 $^{17}$\red{IAP} \\
+$^{18}${Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil}\\
+$^{19}${Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil}\\
 $^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
@@
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy they are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O}.
+In astronomy they are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017A&A...597A.135B}.
 
@@
   11 & NeuralNet2 & Space-Based &  Davies  \\ 
-  12 & CAST & Ground-Based &  Roque De Bom, Valent\"{\i}n \&  Makler  \\ 
+  12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  \\ 
   13 & CMU-DeepLens-ResNet-ground3 & Ground-Based &  Lanusse, Ma, Ravanbakhsh \& C. Li \\ 
@@
   18 & LASTRO EPFL & Ground-Based & Geiger, Sch\"{a}fer \& Kneib   \\ 
-  19 & CAST & Space-Based & Roque De Bom, Valent\"{\i}n \& Makler  \\ 
+  19 & CAST & Space-Based & Roque De Bom, Valent\'{\i}n \& Makler  \\ 
   20 & AstrOmatic & Ground-Based & Bertin  \\ 
@@
 classifier that we used to evaluate the competition data.
+
+%-------------------------------------------------%
+\subsection{CAST (Bom, Valent\'in, Makler)}
+%-------------------------------------------------%
+[Note: we are placing this section here, but we agree it is good to group the methods.
+Perhaps machine learning based methods could go on a separate section and a unified description can be given to CNN-based methods, as most follow under this category.]
+
+The CBPF Arc Search Team (CAST) tested several arcfinding schemes using as core a CNN.
+For both the space-based and ground-based samples we carried out a simple preprocessing phase to enhance the objects in the images in order to check if they improve the automated arc detection with CNN.
+We chose a contrast adjustment with $0.1\%$ pixel saturation and apply a low pass band Wiener filter \citep{wiener1964extrapolation} to reduce the effect of the noise.
+
+We used a native CNN from Matlab\footnote{\texttt{https://www.mathworks.com/products/matlab.html}, \texttt{https://www.mathworks.com/help/nnet/convolutional-neural-networks.html}}, which has Convolutional 2D layers with 20 5x5 filters.
+This CNN can work either with one or three input images, representing greyscale and colour images.
+Therefore, we employed different strategies for the two samples available for the challenge, which involve combinations of the available bands running in one or more CNN, using or not the preprocessing, and combining the output with the aid of other machine learning methods.
+In each case we used the simulations made available for the challenge both to train and to validate the results and we used the area under the ROC to determine which combination of methods gives the best result.
+We selected 
+%We evaluate the ROC curves for all configurations tested, selecting 
+$90\%$ of the images, chosen randomly, for the training and $10\%$ to validate.
+We repeated the process $10$ times to avoid bias due a specific choice of training/validation set and to define an uncertainty in our ROC.
+
+For the space-based data set we tested only two configurations: i) using the CNN straightforwardly for classification and ii) with the preprocessing described above. 
+We found that the results, accounting for the uncertainties,  
+were clearly superior for the area under the ROC in the case 
+including the preprocessing. Therefore, this is the configuration we have used for the challenge.
+
+As mentioned above, the CNN used can take 3 images as input.
+Thus, if we want to use the information on the $4$ available bands, we will have to either combine $2$ of the $4$ bands to end up with $3$ bands for a single RGB CNN (configuration I below) or we use multiple CNNs to use the information available (configuration II to VI below).
+To combine the outputs of several CNNs we use a Support Vector Machine \citep[hereafter SVM; see e.g., ][]{rebentrost2014quantum} also implemented in Matlab.
+The SVM is used to combine the outputs $p_i$ of the several CNN (configurations II, III, IV and VI).
+Instead of using only $p_i$ as inputs to the SVM we also tested providing the SVM with image features obtained by the CNN (feature maps, configuration V) as inputs.
+In all cases we tested with and without the preprocessing
+
+A more detailed description of each configuration tested is presented below:
+\begin{enumerate}
+\item Combination of bands r and i with the average between bands u and g. Use one CNN for classification.
+\item Creation of $1$ CNN for each band (total of $4$). The $4$ outputs are used as input to a SVM classifier which returns the final classification $p$. 
+\item Combination into 4 different combinations of bands:  RGB $\rightarrow$ (\textit{u,g,r}), (\textit{u,g,i}), (\textit{u,r,i}) and (\textit{g,r,i}).
+One CNN for each combination of bands and then use of the output score as input to an SVM classifier.
+%Mediatrix features used as input of an SVM classifier.
+%
+%IV) Use of wavelet decomposition for each band then use of these decomposed images in the same combinations of case III.
+\item  Average of bands in different combinations RGB $\rightarrow$ (\textit{ug,r,i}), (\textit{u,gr,i}) and (\textit{u,g,ri}). The outputs of these 3 CNNs are inputs to a SVM classifier.
+\item Use of CNN-activations (CNN feature maps) as inputs to a SVM classifier, using same combinations of bands of III. The output of each CNN is used as input to a SVM classifier.
+\item Use of wiener filter and contrast adjustment on each band, then using the resulting images in the same architecture as in (iii). 
+\end{enumerate}
+
+For the ground based cases three configurations with highest area under ROC were III,IV and VI.
+Although the areas are very similar between IV and VI the last one is superior in the low fake positives end.
+Thus, for the Strong Lensing Challenge in the ground base sample, we used configuration VI.
+This final scheme is ilustraded in figure \ref{colorCASTCNN}.
+
+The area under ROC, in both space based configurations were, in general, smaller than in the multi-band case, which suggests how the CNNs are sensitive to color information to find Strong Lensing.
+Particularly,  ground base configuration II used one CNN per band thus not considering color information and has the similar area under ROC as our best single band configuration.
+
+%In total we tested XX configurations for the ground based challenge.
+
+%Based on the ROC, we picked for the blind challenge XX, which is illustrated in figure \ref{colorCASTCNN}.
+
+\begin{figure}
+ \includegraphics[width=\columnwidth]{figures/SLchallengeCAST.png}
+ \caption{CAST Lens finder pipeline for the ground based sample. Illustration of the chosen architecture for the CAST search in the case of ground-based simulated images.}
+ \label{colorCASTCNN}
+\end{figure}
 

### 2017-08-21 paper.tex
Added section on CMU DeepLens

@@
 
+\newcommand{\fl}[1]{{\color{magenta}FL: #1}}
 \newcommand{\red}[1]{{\color{red} #1}}
@@
 \newauthor
+Fran\c{c}ois Lanusse,$^{20}$ Quanbin Ma,$^{21}$ Chun-Liang Li,$^{21}$
+\newauthor
 and ?\\
@@
 $^{19}${Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil}\\
+$^{20}${McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
+$^{21}${School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
 $^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
@@
 
+\subsection{CMU DeepLens (Lanusse, Ma, Li, Ravanbakhsh)}
+
+\subsubsection{Convolutional Neural Networks}
+\fl{I'm placing this section here but it's intended as a global introduction to CNNs.
+Feel free to move/modify/discard as you want.
+Also I tried to keep things concise but some concepts may still require a little bit explanations, let me know.}
+
+A Convolutional Neural Network (CNN) \citep{Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
+With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.
+
+The fundamental building block of a CNN is the \textit{convolutional layer}.
+This element applies a set of convolution filters on an input image to produce a series of so-called \textit{feature maps}.
+The coefficients of these filters are free parameters that are learned by the model.
+We will use the notation
+$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps \fl{As Massimo pointed out, I think it's useful to introduce this notation and harmonize its use}.
+In typical architectures, the size of these convolution filters is kept small (i.e.
+3x3 or 5x5 pixels) to limit the complexity of the model.
+To capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
+The most common downsampling schemes are the max-pooling and average pooling strategies, which downsample an input image by taking respectively the maximum or average values within a given region (e.g.
+2x2 patches for a downsampling of factor 2).
+
+A CNN architecture is therefore a stack of convolution layers and pooling layers, converting the input image into an increasing number of feature maps of progressively coarser resolution.
+The final feature maps can capture information on large scales and can reach a high-level of abstraction.
+To perform the classification itself from these feature maps, the CNN is typically topped by a fully-connected neural network outputting the class probability of the input image.
+
+For a binary classification problem such as the one involved in strong lens detection, the training is performed by optimizing the weights of the model as to minimize the \textit{binary cross-entropy} objective:
+\begin{equation}
+	- \sum_{n=1}^{N} y[n] \log \hat{y}[n] + (1 - y[n])\log(1 - \hat{y}[n]) \;,
+\end{equation}
+where $N$ is the number of training instances, $y \in \{0,1\}$ is the true class of the image and $\hat{y} \in [0,1]$ is the class probability predicted by the model.
+This optimization is performed by a Stochastic Gradient Descent (SGD) algorithm which updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
+All the CNN-based methods presented in this work rely on the ADAM \citep{Kingma_2014} algorithm, an accelerated variant of SGD algorithm.
+
+\fl{Things I still have to mention: activation function, dropout, batch normalisation}.
+
+% Francois: This is an attempt at comparing the different CNN-based methods, not sure it's really useful
+%\begin{table*}
+%\begin{tabular}{|c|c|c|c|c|c|c|}
+%\hline 
+%Method       & Depth & Activation & Optimizer & Regularisation &   Pre-processing &  learning rate\\ 
+%\hline 
+%AstrOmatic &  3 + 2 & ELU             & ADAM       &   Dropout            &   asinh                   &     0.001  +decay\\
+%LastroEPFL &   12    & ReLU           &  ADAM      &  Batch norm       & rotations and stuf  & 0.001 + decay\\
+%GLAMOCLASS & 3 + 1 & ReLU    &  ADAM      &   dropout last layer & rotations and stuff & 0.001 + decay \\
+%CMU DeepLens	& 47  & ELU 	    	 &  ADAM       &  batch norm     & rotations and stuff & 0.001 + decay drop \\
+%\hline 
+%\end{tabular} 
+%\caption{Comparison of CNN based methods}
+%\end{table*}
+
+\subsubsection{CMU DeepLens}
+
+\texttt{CMU DeepLens} is based on a residual network (or \textit{resnet}) architecture \citep{He2015a}, a modern variant of CNNs which can reach much greater depths (over 1000 layers) while still gaining accuracy.
+We provide a short overview of our model below but a full description of our architecture can be found in \citet{Lanusse2017}.
+
+Much like conventional CNNs, resnets are based on convolutional and pooling layers.
+However, resnet differ from CNNs by the introduction of so-called shortcut connections bypassing blocks of several convolutional layers.
+As a result, instead of learning the full mapping from their input to their output these residual blocks only have to learn the difference to the identity.
+In practice, this difference allows residual networks to be trained even for very deep models.
+For a more thorough description of this architecture, we refer the interested reader to Section~2.3 of \citet{Lanusse2017}.
+
+Our baseline model is composed of a first 7x7-32 convolutional layer which can accommodate either single-band or multi-band images.
+The rest of the model is composed of 5 successive blocks, each block being made of 3 resnet units (specifically, pre-activated bottleneck residual units \citep{He2016}).
+At each block, the signal is downsampled by a factor 2 and the number of feature maps is in turn multiplied by 2.
+The model is topped by an average-pooling layer followed by a single fully-connected sigmoid layer with a single output.
+Apart from the final layer, we use the ELU activation throughout.
+The weights of the model are initialized using random normal values, following the strategy advocated in \citet{He2015a}.
+
+Training was performed using the ADAM optimizer with mini-batches of size 128 over 120 epochs, with an initial learning rate of $\alpha=0.001$, subsequently decreased by a factor 10 every 40 epochs.
+This multi-step training procedure is important to progressively refine the model parameters of the model and achieve our final accuracy.
+
+We adopt a minimal pre-processing pre-processing strategy for the input images, removing the mean image and normalising by the noise standard deviation $\sigma$ in each band, these statistic being evaluated over the whole training set.
+In addition, we clip extreme values above $250 \sigma$ to limit the dynamic range of the input.
+Bad-pixels are simply set to 0 after this pre-processing step.
+
+Given the relatively small training set preventing overfitting is an important consideration.
+In our final model, we combine several data augmentation strategies: random rotations (in the range $[-90, \ 90^\circ]$), random mirroring along both axes, and random resizing (by a small factor in the range $[0.9, \ 1]$).
+
+The architecture presented above is the one that lead to our best results in both branches of the challenge, i.e.
+\texttt{CMU-DeepLens-Resnet} for space-based and \texttt{CMU-DeepLens-Resnet-ground3} for ground-based.
+We also submitted results for two variants of this baseline model, named \texttt{-aug} and \texttt{-Voting}.
+The first variant introduced several data-augmentation schemes, including the ones mentioned above and the addition of Gaussian noise to the input images.
+We found however that the introduction of noise was not necessary as the other methods were enough to prevent overfitting.
+The second variant was used to explore a voting strategy between three different models.
+These models differed by the type of residual blocks (bottleneck vs wide) and by their handling of missing pixels (setting to 0 or to the median value of the image).
+The predictions of the best 2 out of 3 models were then averaged to produce the final classification probability.
+
+Our model is implemented using the \texttt{Theano}\footnote{\url{http://deeplearning.net/software/theano/}} and \texttt{Lasagne}\footnote{\url{https://github.com/Lasagne/Lasagne}} libraries.
+On an Nvidia Titan Xp GPU, our full training procedure requires approximately 6 hours on the ground-based challenge, but classification of the whole testing set is performed in a couple of minutes.
+Finally, in the interest of reproducible research, our code is made publicly available at
+\begin{center}
+\url{https://github.com/McWilliamsCenter} 
+\end{center}
+This repository also contains a notebook detailing how to reproduce our challenge submission.
+
 \section{results}

### 2017-08-23 paper.tex
Update on Overleaf.

@@
 \title[SL Challenge]{The Strong Gravitational  Lens Finding Challenge}
-
+%C.~E.~Petrillo$^{1}$,  C.~Tortora$^{1}$, L.~V.~E.~Koopmans$^{1}$, \and G.~Verdoes~Kleijn$^{1}$
 \author[R. B. Metcalf {\it et al.}]{
@@
 Jean-Paul Kneib,$^6$
+Leon Koopmans,$^{11}$
+Carlo Enrico Petrillo,$^{11}$ 
 Christoph Sch\"{a}fer,$^6$ 
@@
 Amit Tagore,$^7$
+Crescenzo Tortora,$^{11}$
 Diego Tuccillo,$^{9,10}$
 Santiago Velasco-Forero,$^{10}$
+Gijs Verdoes Kleijn,$^{11}$ 
 Camille Avestruz,$^{11,12,13,\dagger}$
@@
 $^{21}${School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
+$^{22}${Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands}\\
 $^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
@@
 
+\subsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
+Our lens-finder is based on a Convolutional Neural Network (CNN), following the strategy adopted recently in our previous work \citep{petrillo2017}.
+
+We decide to treat the problem as a three-class classification problem where the classes are \textit{non-lenses}, \textit{clear lenses} and \textit{dubious lenses}.
+We define the \textit{dubious lenses} as the lenses with lensing features with less than 160 pixels and the \textit{clear lenses} those with more than 160 pixels belonging to the lensed source.
+This choice is motivated by the fact that specializing the network in recognizing different class could lead to a more robust classification.
+In addition, in a hypothetical application of the method to real data from a survey, this could be a way to select the most blatant lenses.
+
+Given the rules of the challenge, we had to submit a prediction for each source in the test-set as a single number: a number in the interval [0,1] or either a 0 or a 1.
+Unfortunately, to satisfy this requirement we had to collapse one of the class into another: we provided a 0 when the source is classified as a \textit{non-lens} and 1 if it is classified as a \textit{clear lenses} or as a \textit{dubious lenses}.
+Moreover, this did not allow to build a continuous ROC curve but only a binary one.
+\textbf{(We need to test if this was an improvement or not.
+I have the submission ready.)}
+
+Ihe final submission is made using the average values of the predictions from the same network trained three different times.
+
+\subsubsection{Implementation}
+The CNN is implemented in Python 2.7 using the open-source libraries \textsc{Lasagne}\footnote{\href{http://github.com/Lasagne/Lasagne/}{\tt http://github.com/Lasagne/Lasagne/}} 
+and \textsc{Theano}
+\footnote{\href{http://deeplearning.net/software/theano/}{\tt http://deeplearning.net/software/theano/}} \citep{theano}.  
+The training of the CNN is executed on a GeForce GTX 760 in parallel with the data augmentation performed on the CPU using the \textsc{scikit-image}\footnote{\href{http://scikit-image.org/}{\tt http://scikit-image.org/}} package \citep{van2014scikit}.
+
+\subsubsection{Architecture}
+We used the CNN architecture called ResNet described in \citep{he2015deep} with three stacks of residual blocks of 5 layers.
+
+The output layer is composed by three units. Each units gives in output a number between 0 and 1 that represents, respectively, the probability of being a non-lens, a small-lens, a big-lens.
+
+\subsubsection{Preprocessing}
+The training fits files are preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
+
+Due to memory limitations we down-sampled the images to 84 by 84 pixels. Most likely, this leads to a worse classification accuracy than using the original image resolution.
+
+We augmented the training images in the following way: i) random rotation of 90, 180 or 270 degrees; ii) random shift in both $x$ and $y$ direction between -2 and +2 pixels; iii) $50\%$ probability of horizontally flipping the image.
+
+Finally, the image border is cropped in order to have 80 by 80 pixel input images.
+
+\subsubsection{Training}
+The network is trained by minimizing the categorical cross-entropy loss function
+\begin{equation}
+L = -\sum_j t_{j}\log p_{j}
+\label{EQloss}
+\end{equation}
+where the $t_j$ and $p_j$ are respectively the label and the prediction for the class $j$. 
+The minimization is done via mini-batch stochastic gradient descent with \textit{ADAM} updates \citep{kingma2014adam}.
+We used a batch size of 56 and performed  46000 gradient updates.
+We started with a learning rate of $4 \times 10^{-4}$, decrease it to $4 \times 10^{-5}$ after 35000 updates and to $4 \times 10^{-6}$ after 43000 updates.
+The initial values of the biases are set to zero and the weights of each filter are initialized from a random normal distribution with variance ${2/n}$ where $n$ is the number of inputs of the unit (see \citep{he2015delving}).
+We use L2-norm regularization with $\lambda= 9 \times 10^{-3}$.
+
 \section{results}

### 2017-08-24 paper.tex
Update on Overleaf.

@@
 Jean-Paul Kneib,$^6$
-Leon Koopmans,$^{11}$
-Carlo Enrico Petrillo,$^{11}$ 
+Leon Koopmans,$^{22}$
+Carlo Enrico Petrillo,$^{22}$ 
 Christoph Sch\"{a}fer,$^6$ 
@@
 Amit Tagore,$^7$
-Crescenzo Tortora,$^{11}$
+Crescenzo Tortora,$^{22}$
 Diego Tuccillo,$^{9,10}$
 Santiago Velasco-Forero,$^{10}$
-Gijs Verdoes Kleijn,$^{11}$ 
+Gijs Verdoes Kleijn,$^{22}$ 
 Camille Avestruz,$^{11,12,13,\dagger}$
@@
   23 & YattaLensLite & Ground-Based & Sonnenfeld   \\ 
-  24 & Kapteyn & Space-Based & Petrillo, Koopmans, Kleijn, Tortora \& Vernardos \\ 
+  24 & Kapteyn Resnet & Space-Based & Petrillo, Koopmans, Kleijn, Tortora \& Vernardos \\ 
    \hline
@@
 The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$.
-The network is trained on a Titan-X ``Pascal'' nVidia GPU using the Adam gradient-based optimizer \citep{2014arXiv1412.6980K} during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
+The network is trained on a Titan-X ``Pascal'' nVidia GPU using the \textit{Adam} gradient-based optimizer \citep{2014arXiv1412.6980K} during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
 Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.
@@
 For the training, the 20k provided images were split into two sets, 17k for training and 3k for validation.
-Each iteration of the gradient descent (more precisely ADAM \citep{adam}) minimizes the cross entropy, 
+Each iteration of the gradient descent (more precisely \textit{Adam} \citep{adam}) minimizes the cross entropy, 
 \begin{equation} \label{eq:xent}
@@
 \subsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
-Our lens-finder is based on a Convolutional Neural Network (CNN), following the strategy adopted recently in our previous work \citep{petrillo2017}.
+Our lens-finder is based on a Convolutional Neural Network (CNN), following the strategy adopted recently in \citep{2017arXiv170207675P}.
 
@@
 where the $t_j$ and $p_j$ are respectively the label and the prediction for the class $j$. 
-The minimization is done via mini-batch stochastic gradient descent with \textit{ADAM} updates \citep{kingma2014adam}.
+The minimization is done via mini-batch stochastic gradient descent with \textit{Adam} updates \citep{Kingma_2014}.
 We used a batch size of 56 and performed  46000 gradient updates.
@@
    CMU-DeepLens-ResNet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 
-   Kapteyn & Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
+   Kapteyn Resnet & Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
    CAST & Space-Based & 0.81 & 0.07 & 0.12 & CNN \\ 
@@
    AstrOmatic & Space-Based & 0.91 & 0.00 & 0.01 & CNN \\ 
-   Kapteyn & Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
+   Kapteyn Resnet& Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
    CMU-DeepLens-ResNet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 

### 2017-08-26 paper.tex
Update on Overleaf.

@@
 Some automated algorithms have been developed in the past to detect lenses in images.
-These have been designed to detect arc-like features \citep{2006astro.ph..6757A,2007A&A...472..341S} and rings \citep{2014ApJ...785..144G,2014A&A...566A..63J}.
+These have been designed to detect arc-like features \citep{2006astro.ph..6757A,2007A&A...472..341S, 2017A&A...597A.135B} and rings \citep{2014ApJ...785..144G,2014A&A...566A..63J}.
 They have been applied to survey data and found of order 200 lenses \citep{2007A&A...461..813C,2012ApJ...749...38M,2016A&A...592A..75P}.
@@
   18 & LASTRO EPFL & Ground-Based & Geiger, Sch\"{a}fer \& Kneib   \\ 
-  19 & CAST & Space-Based & Roque De Bom, Valent\'{\i}n \& Makler  \\ 
+  19 & CAST & Space-Based & Bom, Valent\'{\i}n \& Makler  \\ 
   20 & AstrOmatic & Ground-Based & Bertin  \\ 

### 2017-08-29 paper.tex
Update on Overleaf.

@@
 have been applied to this problem and others in astronomy, in particular, artificial neural networks (ANNs) and support vector machines (SVM).
-These algorithms do not pick out particular predefined features, but learn from a training set which features are most important for distinguishing categories of objects.
+\red{PH: These algorithms require a set of predefined features from which a discriminating model can be learned.
+Convolutional neural networks (CNN), however,} do not require a pre-selected feature set, but instead learn from a training set which features are most important for distinguishing categories of objects.
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy they are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017A&A...597A.135B}.
+In astronomy these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017A&A...597A.135B,hartley2017support}.
 
@@
   4 & ALL-star & Ground-Based & Avestruz, N.Li \& Lightman  \\ 
-  5 & Manchester1 & Space-Based & Jackson, Hartley \& Tagore  \\ 
+  5 & Manchester1 & Space-Based & Jackson \& Tagore  \\ 
   6 & CMU-DeepLens-Resnet-Voting & Space-Based & Ma, Lanusse \& C. Li  \\ 
-  7 & Manchester SVM & Ground-Based & Hartley   \\ 
+  7 & Manchester SVM & Ground-Based & Hartley \& Flamary  \\ 
   8 & CMU-DeepLens-ResNet & Space-Based & Francois Lanusse, Ma, C. Li \& Ravanbakhsh \\ 
@@
   15 & LASTRO EPFL (CNN) & Space-Based & Geiger, Sch\"{a}fer \& Kneib \\ 
-  16 & Manchester SVM & Space-Based &  Hartley  \\ 
+  16 & Manchester SVM & Space-Based &  Hartley  \& Flamary\\ 
   17 & CMU-DeepLens-ResNet-aug & Space-Based & Ma,  Lanusse, Ravanbakhsh \& C. Li \\ 

### 2017-09-01 paper.tex
Reorganised some sections to group methods. Updated a few other things.

@@
 Carlo Enrico Petrillo,$^{22}$ 
+\newauthor
 Christoph Sch\"{a}fer,$^6$ 
 Alessandro Sonnenfeld,$^5$ 
-\newauthor
 Amit Tagore,$^7$
 Crescenzo Tortora,$^{22}$
+\newauthor
 Diego Tuccillo,$^{9,10}$
@@
 Gijs Verdoes Kleijn,$^{22}$ 
+\newauthor
 Camille Avestruz,$^{11,12,13,\dagger}$
-\newauthor
 Nan Li,$^{14}$
@@
 Cl\'ecio R. Bom,$^{18,19}$
+\newauthor
 Manuel B. Valent\'in,$^{19}$
 Martin Makler,$^{19}$
+Fran\c{c}ois Lanusse,$^{20}$ Quanbin Ma,$^{21}$ 
 \newauthor
-Fran\c{c}ois Lanusse,$^{20}$ Quanbin Ma,$^{21}$ Chun-Liang Li,$^{21}$
+Chun-Liang Li,$^{21}$
 \newauthor
@@
 $^{2}$ IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.\\
-$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  98bis Bd Arago, F-75014,\\ Paris France.\\
+$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  \\ 98bis Bd Arago, F-75014, Paris France.\\
 $^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
 $^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{6}$ \red{EPFL}\\
-$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of Manchester, Oxford Rd, Manchester M13 9PL, UK \\
-$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique, Observatoire de la C\^{o}te d'Azur, \\ Parc Valrose, 06108 Nice, France \\
+$^{6}$ \red{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)
+Observatoire de Sauverny CH - 1290 Versoix Switzerland} \\
+$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of \\ Manchester, Oxford Rd, Manchester M13 9PL, UK \\
+$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique,\\ Observatoire de la C\^{o}te d'Azur, Parc Valrose, 06108 Nice, France \\
 $^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
-$^{10}$ MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue Saint-Honore, Fontainebleau, France \\
+$^{10}$ MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue \\ Saint-Honore, Fontainebleau, France \\
 $^{11}${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
@@
 $^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
-$^{16}$\red{LAM} \\
-$^{17}$\red{IAP} \\
+$^{16}$\red{ LAM - Laboratory of Astrophysics of Marseille P\^ole de l'\'Etoile Website of Ch\^ateau-Gombert 
+38,} \\ \red{rue Fr\'ed\'eric Joliot-Curie 13388 Marseille cedex 13 FRANCE} \\
+$^{17}$\red{Institut d'Astrophysique de Paris (IAP)- 98 bis boulevard Arago - 75014 Paris } \\
 $^{18}${Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil}\\
@@
 have been applied to this problem and others in astronomy, in particular, artificial neural networks (ANNs) and support vector machines (SVM).
-\red{PH: These algorithms require a set of predefined features from which a discriminating model can be learned.
-Convolutional neural networks (CNN), however,} do not require a pre-selected feature set, but instead learn from a training set which features are most important for distinguishing categories of objects.
+These algorithms require a set of predefined features from which a discriminating model can be learned.
+Convolutional neural networks (CNN), however, do not require a pre-selected feature set, but instead learn from a training set which features are most important for distinguishing categories of objects.
 These have been used widely for such tasks as handwriting and facial recognition.
@@
 
-For the ground-based images four bands ($u,g,r$, and $i$) where simulated {\color{red} (these are SDSS filters too, right?)}.
+For the ground-based images four bands (SDSS $u,g,r$, and $i$) where simulated.
 The reference band was $r$.
@@
 
-\subsection{GAHEC IRAP (Cabanac)}
+{\color{red} MM: May be we could separate the methods into three categories: machine-learning, arc-finders, visual inspection and group them accordingly}
+
+\subsection{Visual Inspection}
+\subsubsection{Manchester/Manchester1 (Jackson,Tagore)}
+
+All images (a total of 100000) were examined for each of the space- and
+ground-based datasets. This was done by two observers; AT examined 30000
+images in each case and NJ examined 70000. Observation was carried out
+over a 48-hour period, at the rate of 5000/hr (NJ) and 2500/hr (AT). 
+The overall results, in terms of ROC curves, were very similar for 
+both observers. The space-based challenge produced areas of 0.800 and 
+0.812 for NJ and AT respectively, and the ground-based challenge yielded 
+0.891 and 0.884.
+
+The Python scripts used for manual examination of multiple images are available
+onGitHub\footnote{https://github.com/nealjackson/bigeye} and are described in more detail
+in \citet{hartley2017support}. For one-colour data such as
+the space-based training set, the images are individually colour-scaled using
+square-root scaling. The bright limit of the colour-scale is determined
+from the pixel values in a rectangle comprising the inner ninth of the
+image area, with the limit being chosen as the $n$th centile of the pixel
+values in this area. Values between $n=95$ and $n=98$ give optimum results,
+judging by experiments on the training set. The number of images in each
+grid was also optimised using the training set, with 16$\times$8 or 
+8$\times$4 giving good results on one-colour data. For three-colour data,
+such as the ground-based challenge data, the individual bands for each 
+object are colour-scaled and then combined into an RGB image. In this case
+8$\times$4 grids were used for examination, due to the generally lower 
+resolution of the images. The script also allows the user to adjust the
+colour-scale in real time when examining and marking images, and records
+the image name corresponding to the image within which the cursor resides
+at the time any key is pressed, together with the key.
+
+Images were classified by both observers into 5 categories, ranging from
+0 (no evidence of any lensed objects in the image) to 4 (certain lenses).
+For both observers, the rate of false positives in the ``certain'' lenses
+was between 0.1\% and 0.3\%. The exception was the ground-based imaging 
+for one observer, where a 4.6\% rate resulted mainly from a
+single decision to allow a false-positive ``double lens'' which occurred
+repeatedly throughout the data at different orientations. The false-negative
+rate among the class-0 identifications was similar for both observers, at
+around 25\% for the space-based images and 20\% for the ground-based.
+
+\subsection{Arc-Finders}
+\subsubsection{ IRAP (Cabanac)}
 
@@
 
-\subsection{AstrOmatic (Bertin)}
+\subsubsection{YattaLens Lite (Sonnenfeld)}
+
+YattaLensLite is a simpler version of the algorithm YattaLens \citep{2017arXiv170401585S}, modified to meet the time constraints of the challenge.
+YattaLensLite subtracts a model surface brightness profile describing the lens galaxy from the $g$-band image, then runs SExtractor to detect tangentially elongated or ring-shaped objects, which are interpreted as lensed images.
+In the ground-based challenge, the model lens surface brightness profile is obtained by taking a rescaled version of the $i$-band image.
+The difference in color between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
+However, in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
+The model lens light is truncated at the smallest radius between the position where the surface brightness is comparable to the sky background level, or the position of a positive radial gradient in surface brightness, if detected.
+
+In the space-based challenge, it is not possible to separate lens and source based on color, because only data in one band is provided.
+The lens light model then is produced by taking a centrally-inverted image and then using the same truncation prescription used with ground-based data.
+The central inversion step is taken to reduce the chances of subtracting flux from lensed images, which are in general not centrally symmetric as opposed to typical lens galaxies.
+
+In the full version of YattaLens, a lens modeling step is performed to improve the purity of the sample. However, such a procedure is too time consuming and was not performed in this challenge.
+
+\subsection{Trained Logistic Regression Methods}
+
+\subsubsection{Gabor-SVM (Hartley, Flamary)}
+
+A Support Vector Machine (SVM) is a supervised machine learning method which uses labeled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
+A preprocessing stage first extracts a set of useful features from input samples, before projecting each sample as a vector in multidimensional space.
+The model then separates classes of data by maximising the margin between a defining hyperplane and a set of so-called support-vectors at the inner edge of each class.
+The process of classification is computationally inexpensive since optimisation depends only on the dot products of the support vector subset.
+Feature extraction, however,  requires both an extensive exploration of the feature space during the development of a model, and potentially intensive computer resources in order to transform the original samples.
+Our full method is described in detail in \citet{hartley2017support}, and was developed using the Python scikit-learn and scikit-image packages \citep{scikit-learn,scikit-image}.
+
+During our development of an SVM classifier for lens finding, feature extraction initially involved the decomposition of each image into a set of objects, using SExtractor \citep{1996A&AS..117..393B} and GALFIT \citep{2002AJ....124..266P} to recover and subtract objects iteratively.
+This method had previously been used in a static algorithm approach which assigned points according to the morphological properties of each image \citep[see][]{2014A&A...566A..63J}.
+Lensed-like objects displaying, for example, greater ellipticity and tangentiality were awarded more points.
+Since the SVM operates in a fixed dimensional space,  properties of individual objects were collapsed into a fixed set describing the mean and variance of morphological properties of all the objects within an image.
+After training an SVM using these features we recorded a modest separation of lens and non-lens classes.
+
+An alternative approach was to design a set of Gabor filters to be applied to each sample.
+The Gabor kernel is described by a sinusoidal function multiplied by a Gaussian envelope.
+We discard the imaginary part of the function to leave, in two-dimensional space:
+
+\begin{equation}
+G_c[i,j]=Be^{-\frac{(i^2+j^2)}{2\sigma^2}} \mathrm{cos}\left(\frac{2\pi}{\lambda} (i\, \mathrm{cos} \, \theta + j\, \mathrm{sin} \,\theta)\right),
+\end{equation}
+
+where harmonic wavelength $\lambda$, Gaussian spread  $\sigma$ and orientation $\theta$ define the operation performed on each point $i,j$ in an image.
+Such a kernel is a popular image processing choice for edge detection and texture classification \citep[e.g.][]{Feichtinger98a,Springer-verlag97computationalmodels} and is thought to mimic some image processing functions of the mammalian brain \citep{Jones1233}.
+
+\begin{figure}
+  \centering
+      \includegraphics[width=1\columnwidth]{figures/polarfilter.pdf} 
+  \caption{Example of our feature extraction procedure used to transform a ring.
+The image on the right shows the response of a set of Gabor filters after convolution with a polar transformed image of an Einstein ring.
+The strongest response is seen in the orientation perpendicular to the radial direction and at the frequency most closely matching that of the ring.}
+ \label{gaborring}
+\end{figure}
+
+Our final feature extraction procedure first applied a polar transform to each image in order to exploit the edge detection of the Gabor filter, picking out tangential components typical of galaxy-galaxy lensing.
+Each image was then convolved with several Gabor filters of varying frequency and rotation (see Fig.~\ref{gaborring}).
+Stability selection methods were used to investigate the classification performance using different combinations of filters.
+The responses for each Gabor filter when applied to each image were measured by calculating statistical moments for each filtered image.
+These moments formed  our final input data on which the SVM could be trained and applied.
+We used brute-force optimisation methods to select a non-linear SVM containing radial basis function (RBF) kernel and tuned a small set of regularisation hyperparameters to achieve good generalisation performance.
+During training and testing, our final and best scores achieved when testing on the lens finding challenge training data were an AUC of 0.88 for the space set and 0.95 for the ground set.
+Classification was performed using a modest desktop PC.
+
+%-------------------------------------------------%
+\subsubsection{ALL Methodology (Avestruz, Li, Lightman}
+%-------------------------------------------------%
+
+We detail the ALL team methodology in \citet{avestruz_etal17}. The
+pipeline was originally developed to automatically classify strong
+lenses in mock Hubble Space Telescope and Large Synoptic Sky Telescope
+data generated with code described in \citet{li_etal16} and
+\citet{collett_15}.  We apply the same exact steps for the single-band
+data for Euclid, but modify the feature extraction step for the
+four-band KIDS data.  We summarize the steps below.
+
+We use tools from {\em Scikit-learn} \citep{pedregosa_etal12} and
+perform minimal image preprocessing. First, we replace masked pixels
+with the average of surrounding pixels, then enhance contrast in the
+image by taking the normalized log of pixel values.  The next step of
+our pipeline consists of a feature extraction stage, where our feature
+vector is a {\em histogram of oriented gradients} (HOG)
+\citep{dalalandtriggs_05} that quantifies edges in the image.  HOG has
+three main parameters that determine the binning and resolution of
+edges captured by the features.  The result is a one dimensional
+feature vector corresponding to the magnitude of oriented gradients
+across the image.  With the KIDS data, we extract a feature vector for
+each of the four bands and concatenate the vectors to create a final
+feature vector for each object that we use to train a model
+classifier.
+
+We use {\em Logistic Regression} (LR), a machine learning algorithm,
+to train a classifier model.  LR requires a parameter search over the
+regression coefficient, $C_{LogReg}$.  The parameters from both the
+feature extrator, HOG, and the linear classifier, LR, contain
+parameters that we optimize for peak model performance.  We use {\em
+  GridSearchCV} from {\em Scikit-learn} to select cross-validated
+parameters for HOG parameters and a subset of $C_{LogReg}$ values with
+20\% of the test images provided.  We then run a finer parameter
+search over $C_{LogReg}$, splitting the test images into 80\% training
+and and 20\% test to avoid overfitting the data.  We use the best
+parameters to then train the entire dataset for the final model
+classifier that we used to evaluate the competition data.
+
+\subsection{Convolutional Neural Networks ((Lanusse)}
+Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.
+A CNN \citep{Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
+With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.
+
+The fundamental building block of a CNN is the \textit{convolutional layer}.
+This element applies a set of convolution filters on an input image to produce a series of so-called \textit{feature maps}.
+The coefficients of these filters are free parameters that are learned by the model.
+We will use the notation
+$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps.
+In typical architectures, the size of these convolution filters is kept small (i.e.
+3x3 or 5x5 pixels) to limit the complexity of the model.
+To capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
+The most common downsampling schemes are the max-pooling and average pooling strategies, which downsample an input image by taking respectively the maximum or average values within a given region (e.g.
+2x2 patches for a downsampling of factor 2).
+
+A CNN architecture is therefore a stack of convolution layers and pooling layers, converting the input image into an increasing number of feature maps of progressively coarser resolution.
+The final feature maps can capture information on large scales and can reach a high-level of abstraction.
+To perform the classification itself from these feature maps, the CNN is typically topped by a fully-connected neural network outputting the class probability of the input image.
+
+For a binary classification problem such as the one involved in strong lens detection, the training is performed by optimizing the weights of the model as to minimize the \textit{binary cross-entropy} objective:
+\begin{equation}
+	- \sum_{n=1}^{N} y[n] \log \hat{y}[n] + (1 - y[n])\log(1 - \hat{y}[n]) \;,
+\end{equation}
+where $N$ is the number of training instances, $y \in \{0,1\}$ is the true class of the image and $\hat{y} \in [0,1]$ is the class probability predicted by the model.
+This optimization is performed by a Stochastic Gradient Descent (SGD) algorithm which updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
+All the CNN-based methods presented in this work rely on the ADAM \citep{Kingma_2014} algorithm, an accelerated variant of SGD algorithm.
+
+\fl{Things I still have to mention: activation function, dropout, batch normalisation}.
+
+\subsubsection{AstrOmatic (Bertin)}
 
@@
 what kind of layers, activation functions, etc.)}
+{\color{blue} RBM: I moved the general description of the CNN to the beginning of this section.}
 
@@
 
-{\red MM: May be we could separate the methods into three categories: machine-learning, arc-finders, visual inspection and group them accordingly}
-
-\subsection{YattaLens Lite (Sonnenfeld)}
-YattaLensLite is a simpler version of the algorithm YattaLens \citep{2017arXiv170401585S}, modified to meet the time constraints of the challenge.
-YattaLensLite subtracts a model surface brightness profile describing the lens galaxy from the $g$-band image, then runs SExtractor to detect tangentially elongated or ring-shaped objects, which are interpreted as lensed images.
-In the ground-based challenge, the model lens surface brightness profile is obtained by taking a rescaled version of the $i$-band image.
-The difference in color between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
-However, in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
-The model lens light is truncated at the smallest radius between the position where the surface brightness is comparable to the sky background level, or the position of a positive radial gradient in surface brightness, if detected.
-
-In the space-based challenge, it is not possible to separate lens and source based on color, because only data in one band is provided.
-The lens light model then is produced by taking a centrally-inverted image and then using the same truncation prescription used with ground-based data.
-The central inversion step is taken to reduce the chances of subtracting flux from lensed images, which are in general not centrally symmetric as opposed to typical lens galaxies.
-
-In the full version of YattaLens, a lens modeling step is performed to improve the purity of the sample. However, such a procedure is too time consuming and was not performed in this challenge.
-
-\subsection{LASTRO EPFL (Geiger, Sch\"{a}fer)}
+\subsubsection{LASTRO EPFL (Geiger, Sch\"{a}fer)}
 
@@
 
-\subsection{Manchester/Manchester1 (Jackson,Tagore)}
-
-All images (a total of 100000) were examined for each of the space- and
-ground-based datasets. This was done by two observers; AT examined 30000
-images in each case and NJ examined 70000. Observation was carried out
-over a 48-hour period, at the rate of 5000/hr (NJ) and 2500/hr (AT). 
-The overall results, in terms of ROC curves, were very similar for 
-both observers. The space-based challenge produced areas of 0.800 and 
-0.812 for NJ and AT respectively, and the ground-based challenge yielded 
-0.891 and 0.884.
-
-The Python scripts used for manual examination of multiple images are available
-onGitHub\footnote{https://github.com/nealjackson/bigeye} and are described in more detail
-in \citet{hartley2017support}. For one-colour data such as
-the space-based training set, the images are individually colour-scaled using
-square-root scaling. The bright limit of the colour-scale is determined
-from the pixel values in a rectangle comprising the inner ninth of the
-image area, with the limit being chosen as the $n$th centile of the pixel
-values in this area. Values between $n=95$ and $n=98$ give optimum results,
-judging by experiments on the training set. The number of images in each
-grid was also optimised using the training set, with 16$\times$8 or 
-8$\times$4 giving good results on one-colour data. For three-colour data,
-such as the ground-based challenge data, the individual bands for each 
-object are colour-scaled and then combined into an RGB image. In this case
-8$\times$4 grids were used for examination, due to the generally lower 
-resolution of the images. The script also allows the user to adjust the
-colour-scale in real time when examining and marking images, and records
-the image name corresponding to the image within which the cursor resides
-at the time any key is pressed, together with the key.
-
-Images were classified by both observers into 5 categories, ranging from
-0 (no evidence of any lensed objects in the image) to 4 (certain lenses).
-For both observers, the rate of false positives in the ``certain'' lenses
-was between 0.1\% and 0.3\%. The exception was the ground-based imaging 
-for one observer, where a 4.6\% rate resulted mainly from a
-single decision to allow a false-positive ``double lens'' which occurred
-repeatedly throughout the data at different orientations. The false-negative
-rate among the class-0 identifications was similar for both observers, at
-around 25\% for the space-based images and 20\% for the ground-based.
-
-\subsection{Gabor-SVM (Hartley, Flamary)}
-
-A Support Vector Machine (SVM) is a supervised machine learning method which uses labeled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
-A preprocessing stage first extracts a set of useful features from input samples, before projecting each sample as a vector in multidimensional space.
-The model then separates classes of data by maximising the margin between a defining hyperplane and a set of so-called support-vectors at the inner edge of each class.
-The process of classification is computationally inexpensive since optimisation depends only on the dot products of the support vector subset.
-Feature extraction, however,  requires both an extensive exploration of the feature space during the development of a model, and potentially intensive computer resources in order to transform the original samples.
-Our full method is described in detail in \citet{hartley2017support}, and was developed using the Python scikit-learn and scikit-image packages \citep{scikit-learn,scikit-image}.
-
-During our development of an SVM classifier for lens finding, feature extraction initially involved the decomposition of each image into a set of objects, using SExtractor \citep{1996A&AS..117..393B} and GALFIT \citep{2002AJ....124..266P} to recover and subtract objects iteratively.
-This method had previously been used in a static algorithm approach which assigned points according to the morphological properties of each image \citep[see][]{2014A&A...566A..63J}.
-Lensed-like objects displaying, for example, greater ellipticity and tangentiality were awarded more points.
-Since the SVM operates in a fixed dimensional space,  properties of individual objects were collapsed into a fixed set describing the mean and variance of morphological properties of all the objects within an image.
-After training an SVM using these features we recorded a modest separation of lens and non-lens classes.
-
-An alternative approach was to design a set of Gabor filters to be applied to each sample.
-The Gabor kernel is described by a sinusoidal function multiplied by a Gaussian envelope.
-We discard the imaginary part of the function to leave, in two-dimensional space:
-
-\begin{equation}
-G_c[i,j]=Be^{-\frac{(i^2+j^2)}{2\sigma^2}} \mathrm{cos}\left(\frac{2\pi}{\lambda} (i\, \mathrm{cos} \, \theta + j\, \mathrm{sin} \,\theta)\right),
-\end{equation}
-
-where harmonic wavelength $\lambda$, Gaussian spread  $\sigma$ and orientation $\theta$ define the operation performed on each point $i,j$ in an image.
-Such a kernel is a popular image processing choice for edge detection and texture classification \citep[e.g.][]{Feichtinger98a,Springer-verlag97computationalmodels} and is thought to mimic some image processing functions of the mammalian brain \citep{Jones1233}.
-
-\begin{figure}
-  \centering
-      \includegraphics[width=1\columnwidth]{figures/polarfilter.pdf} 
-  \caption{Example of our feature extraction procedure used to transform a ring.
-The image on the right shows the response of a set of Gabor filters after convolution with a polar transformed image of an Einstein ring.
-The strongest response is seen in the orientation perpendicular to the radial direction and at the frequency most closely matching that of the ring.}
- \label{gaborring}
-\end{figure}
-
-Our final feature extraction procedure first applied a polar transform to each image in order to exploit the edge detection of the Gabor filter, picking out tangential components typical of galaxy-galaxy lensing.
-Each image was then convolved with several Gabor filters of varying frequency and rotation (see Fig.~\ref{gaborring}).
-Stability selection methods were used to investigate the classification performance using different combinations of filters.
-The responses for each Gabor filter when applied to each image were measured by calculating statistical moments for each filtered image.
-These moments formed  our final input data on which the SVM could be trained and applied.
-We used brute-force optimisation methods to select a non-linear SVM containing radial basis function (RBF) kernel and tuned a small set of regularisation hyperparameters to achieve good generalisation performance.
-During training and testing, our final and best scores achieved when testing on the lens finding challenge training data were an AUC of 0.88 for the space set and 0.95 for the ground set.
-Classification was performed using a modest desktop PC.
-
-\subsection{GAMOCLASS (Tuccillo, Huertas-Company, Velasco-Forero, Decenci\`ere)}
+\subsubsection{GAMOCLASS (Tuccillo, Huertas-Company, Velasco-Forero, Decenci\`ere)}
 
@@
 %-------------------------------------------------%
-\subsection{ALL Methodology (Avestruz, Li, Lightman}
-%-------------------------------------------------%
-
-We detail the ALL team methodology in \citet{avestruz_etal17}. The
-pipeline was originally developed to automatically classify strong
-lenses in mock Hubble Space Telescope and Large Synoptic Sky Telescope
-data generated with code described in \citet{li_etal16} and
-\citet{collett_15}.  We apply the same exact steps for the single-band
-data for Euclid, but modify the feature extraction step for the
-four-band KIDS data.  We summarize the steps below.
-
-We use tools from {\em Scikit-learn} \citep{pedregosa_etal12} and
-perform minimal image preprocessing. First, we replace masked pixels
-with the average of surrounding pixels, then enhance contrast in the
-image by taking the normalized log of pixel values.  The next step of
-our pipeline consists of a feature extraction stage, where our feature
-vector is a {\em histogram of oriented gradients} (HOG)
-\citep{dalalandtriggs_05} that quantifies edges in the image.  HOG has
-three main parameters that determine the binning and resolution of
-edges captured by the features.  The result is a one dimensional
-feature vector corresponding to the magnitude of oriented gradients
-across the image.  With the KIDS data, we extract a feature vector for
-each of the four bands and concatenate the vectors to create a final
-feature vector for each object that we use to train a model
-classifier.
-
-We use {\em Logistic Regression} (LR), a machine learning algorithm,
-to train a classifier model.  LR requires a parameter search over the
-regression coefficient, $C_{LogReg}$.  The parameters from both the
-feature extrator, HOG, and the linear classifier, LR, contain
-parameters that we optimize for peak model performance.  We use {\em
-  GridSearchCV} from {\em Scikit-learn} to select cross-validated
-parameters for HOG parameters and a subset of $C_{LogReg}$ values with
-20\% of the test images provided.  We then run a finer parameter
-search over $C_{LogReg}$, splitting the test images into 80\% training
-and and 20\% test to avoid overfitting the data.  We use the best
-parameters to then train the entire dataset for the final model
-classifier that we used to evaluate the competition data.
-
-%-------------------------------------------------%
-\subsection{CAST (Bom, Valent\'in, Makler)}
+\subsubsection{CAST (Bom, Valent\'in, Makler)}
 %-------------------------------------------------%
@@
 
-\subsection{CMU DeepLens (Lanusse, Ma, Li, Ravanbakhsh)}
-
-\subsubsection{Convolutional Neural Networks}
-\fl{I'm placing this section here but it's intended as a global introduction to CNNs.
-Feel free to move/modify/discard as you want.
-Also I tried to keep things concise but some concepts may still require a little bit explanations, let me know.}
-
-A Convolutional Neural Network (CNN) \citep{Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
-With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.
-
-The fundamental building block of a CNN is the \textit{convolutional layer}.
-This element applies a set of convolution filters on an input image to produce a series of so-called \textit{feature maps}.
-The coefficients of these filters are free parameters that are learned by the model.
-We will use the notation
-$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps \fl{As Massimo pointed out, I think it's useful to introduce this notation and harmonize its use}.
-In typical architectures, the size of these convolution filters is kept small (i.e.
-3x3 or 5x5 pixels) to limit the complexity of the model.
-To capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
-The most common downsampling schemes are the max-pooling and average pooling strategies, which downsample an input image by taking respectively the maximum or average values within a given region (e.g.
-2x2 patches for a downsampling of factor 2).
-
-A CNN architecture is therefore a stack of convolution layers and pooling layers, converting the input image into an increasing number of feature maps of progressively coarser resolution.
-The final feature maps can capture information on large scales and can reach a high-level of abstraction.
-To perform the classification itself from these feature maps, the CNN is typically topped by a fully-connected neural network outputting the class probability of the input image.
-
-For a binary classification problem such as the one involved in strong lens detection, the training is performed by optimizing the weights of the model as to minimize the \textit{binary cross-entropy} objective:
-\begin{equation}
-	- \sum_{n=1}^{N} y[n] \log \hat{y}[n] + (1 - y[n])\log(1 - \hat{y}[n]) \;,
-\end{equation}
-where $N$ is the number of training instances, $y \in \{0,1\}$ is the true class of the image and $\hat{y} \in [0,1]$ is the class probability predicted by the model.
-This optimization is performed by a Stochastic Gradient Descent (SGD) algorithm which updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
-All the CNN-based methods presented in this work rely on the ADAM \citep{Kingma_2014} algorithm, an accelerated variant of SGD algorithm.
-
-\fl{Things I still have to mention: activation function, dropout, batch normalisation}.
+\subsubsection{CMU DeepLens (Lanusse, Ma, Li, Ravanbakhsh)}
 
@@
 
-\subsubsection{CMU DeepLens}
-
 \texttt{CMU DeepLens} is based on a residual network (or \textit{resnet}) architecture \citep{He2015a}, a modern variant of CNNs which can reach much greater depths (over 1000 layers) while still gaining accuracy.
@@
 
-\subsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
+\subsubsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
 Our lens-finder is based on a Convolutional Neural Network (CNN), following the strategy adopted recently in \citep{2017arXiv170207675P}.
@@
 
-\subsubsection{Implementation}
+{\bf Implementation}
 The CNN is implemented in Python 2.7 using the open-source libraries \textsc{Lasagne}\footnote{\href{http://github.com/Lasagne/Lasagne/}{\tt http://github.com/Lasagne/Lasagne/}} 
@@
 
-\subsubsection{Architecture}
+{\bf Architecture}
 We used the CNN architecture called ResNet described in \citep{he2015deep} with three stacks of residual blocks of 5 layers.
@@
 
-\subsubsection{Preprocessing}
+{\bf Preprocessing}
 The training fits files are preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
@@
 
-\subsubsection{Training}
+{\bf Training}
 The network is trained by minimizing the categorical cross-entropy loss function

### 2017-09-03 paper.tex
Edit.

@@
 M. Meneghetti,$^4$ 
+Camille Avestruz,$^{11,12,13,\dagger}$
+\newauthor
 Fabio Bellagamba,$^1$
+Cl\'ecio R. Bom,$^{18,19}$
 Emmanuel Bertin,$^3$ 
@@
 R\'emi Flamary,$^8$
+\newauthor
 Raphael Gavazzi,$^{17}$ 
-\newauthor
 Mario Geiger,$^6$ 
 Philippa Hartley,$^7$
+\newauthor
 Marc Huertas-Company,$^9$
 Neal Jackson,$^7$ 
+Eric Jullo,$^{16}$
 \newauthor
-Eric Jullo,$^{16}$
+Gijs Verdoes Kleijn,$^{22}$ 
 Jean-Paul Kneib,$^6$
 Leon Koopmans,$^{22}$
+\newauthor
+Fran\c{c}ois Lanusse,$^{20}$ 
+Chun-Liang Li,$^{21}$
+Quanbin Ma,$^{21}$ 
+\newauthor
+Martin Makler,$^{19}$
+Nan Li,$^{14}$
+Matthew Lightman,$^{15}$
+\newauthor
 Carlo Enrico Petrillo,$^{22}$
-\newauthor
 Christoph Sch\"{a}fer,$^6$ 
 Alessandro Sonnenfeld,$^5$ 
+\newauthor
 Amit Tagore,$^7$
 Crescenzo Tortora,$^{22}$
-\newauthor
 Diego Tuccillo,$^{9,10}$
-Santiago Velasco-Forero,$^{10}$
-Gijs Verdoes Kleijn,$^{22}$ 
-\newauthor
-Camille Avestruz,$^{11,12,13,\dagger}$
-Nan Li,$^{14}$
-Matthew Lightman,$^{15}$
-Cl\'ecio R. Bom,$^{18,19}$
 \newauthor
 Manuel B. Valent\'in,$^{19}$
-Martin Makler,$^{19}$
-Fran\c{c}ois Lanusse,$^{20}$ Quanbin Ma,$^{21}$ 
-\newauthor
-Chun-Liang Li,$^{21}$
-\newauthor
-and ?\\
+and Santiago Velasco-Forero,$^{10}$
+\\
 % List of institutions
@@
 \begin{abstract}
+\red{Preamble}
 We present a description and results of an open gravitational lens finding challenge.
 Participants were asked to classify 100,000 candidate objects as to whether they were gravitational lenses or not with the goal of developing better automated methods for finding lenses in large data sets.
+\red{Mehtods used.} \red{Conclusions}
 \end{abstract}
@@
 They have put limits on the self interaction of dark matter and on the theory of gravitation.
-Through microlensing they have been used to study the structure of quasars \citep{2008ApJ...689..755M,2008ApJ...673...34P,2011ApJ...729...34B}.
+\red{Citation?} Through microlensing they have been used to study the structure of quasars \citep{2008ApJ...689..755M,2008ApJ...673...34P,2011ApJ...729...34B}.
 To access this wealth of information the first step is to find the lenses.
-\red{Could use some citations in this paragraph.}
 
 The Square Kilometer Array (SKA)\footnote{http://skatelescope.org/}, the Large Synoptic Survey Telescope (LSST)\footnote{https://www.lsst.org/} and the Euclid space telescope\footnote{https://www.euclid-ec.org/} are expected to increase the number of potential lenses by orders of magnitude \citep{collett_15,euclidSLWGwhitepaper,2015aska.confE..84M,2010MNRAS.405.2579O}.
-For example it is estimated that there will be approximately 200,000 observable galaxy-galaxy lenses in the Euclid data set among \red{tens of billions (better number??)} of potential objects .
+For example it is estimated that there will be approximately 200,000 observable galaxy-galaxy lenses in the Euclid data set among tens of billions of potential objects .
 So far, less than a thousand lenses have been found in total across many heterogeneous data sets.
@@
 
-Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of a samples candidates that have been selected on the bases of luminosity and/or color.
+Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of candidates that have been selected on the bases of luminosity and/or color.
 This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2014MNRAS.439.3392P} \red{(Maybe there are some others to cite here?)}.
@@
 
-Galaxy scale lenses have also been searched for spectroscopically by looking for high redshift stellar lines in the spectra of lower redshift large galaxies.
+Spectroscopic searches for galaxy scale lenses have also been done by looking for high redshift stellar lines in the spectra of lower redshift large galaxies.
 Notably this was done in the Sloan Lens ACS (SLACS) survey, producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006ApJ...638..703B}.
@@
 
-More recently machine learning techniques that have become widely used in the fields computer image processing and artificial intelligence 
-have been applied to this problem and others in astronomy, in particular, artificial neural networks (ANNs) and support vector machines (SVM).
-These algorithms require a set of predefined features from which a discriminating model can be learned.
-Convolutional neural networks (CNN), however, do not require a pre-selected feature set, but instead learn from a training set which features are most important for distinguishing categories of objects.
+More recently, machine learning techniques that have become widely used in the fields of computer image processing and artificial intelligence have been applied to this problem and others in astronomy.
+In particular, artificial neural networks (ANNs) and support vector machines (SVM).
+SVMs and other logistic regression methods learn from a training set how to classify objects using predefined features which characterize each instance while ANNs (and a popular variant convolutional neural networks (CNNs) ) can learn directly from a training set which features are most important for distinguishing categories of objects.
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017A&A...597A.135B,hartley2017support}.
+In astronomy, these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017A&A...597A.135B,hartley2017support}.
 
@@
 The methods used to simulate mock images of galaxies and gravitational lenses are described in section~\ref{sec:simulation}.
-In section~\ref{sec:entries} each of the methods that were used to solve the challenge are briefly described.
+In section~\ref{sec:entries}, each of the methods that were used to solve the challenge are briefly described.
 We discuss the metrics used to evaluate entries in section~\ref{sec:figure_of_merit}.
@@
 The challenge was in fact two separate challenges that could be entered independently.
-One was designed to mimic a single band of a future imaging data set from a satellite survey such as Euclid \citep{***} \red{(the latest description)}.
+One was designed to mimic a single band of a future imaging data set from a satellite survey such as Euclid.
 The other was designed to mimic ground based data with multiple bands, roughly modeled on the Kilo-Degree Survey (KiDS)\footnote{http://kids.strw.leidenuniv.nl/} \citep{2013ExA....35...25D}.
@@
 Each image was $101\times101$ pixels.
-The researchers were free to download these sets and train their algorithms on them.
+The participants were free to download these sets and train their algorithms on them.
 To enter the contest the participants needed to register with a team name at which point they would be given a unique key and the address of a test data set.

### 2017-09-07 paper.tex
Update on Overleaf.
Edits

@@
 \newcommand{\red}[1]{{\color{red} #1}}
+\newcommand{\blue}[1]{{\color{blue} #1}}
 \newcommand{\degree}{^{\circ}}
@@
 
-Creating the mock images starts with a cosmological N-body simulation.
+Creating the mock images started with a cosmological N-body simulation.
 In this case it was the Millennium simulation \citep{2009MNRAS.398.1150B}.
@@
 light cone extending out to redshift $z=6$.
+The halos are found with a friends-of-friends algorithm and characterized by a total mass, size and half mass radius.
+They includes subhalos of larger halos.
 The halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
-This code projects the halos onto lens planes, in this case 20, and finds the deflection angle on each plane by a hybrid tree method.
+Within the code a Navarro, Frenk \& White (NFW) \citep{1996ApJ...462..563N} profile is fit to the three parameters given above.
+The halos are projected onto a series of lens planes, in this case 20,  and the deflection angle at any point in each plane can be calculated by summing the effects of all the halos with a hybrid tree method.
 In this way the halos have the mass, concentration and clustering properties from the N-body simulation, but within each strong lens the mass resolution is not limited by the original simulation, but follows the analytic mass profile.
-{\color{red} MM: I am a bit confused: at this stage, how are the halos modeled?
-N-body or analytic?
-What is the shape of the halos?}
+An additional mass component that will be discussed later is added to each halo to represent the stellar ans gas mass.
+
+{\color{blue} RBM: I added some explanation in the above.}
 
@@
 
- A **** square degree light-cone gives rise to **** such caustics, but these over count the number of lenses since most will have caustics on multiple source planes.
+ In the light cone there are many thousands of caustics for the higher source redshifts.
 These lenses could be used as is, but we wanted to produce a much larger number with more randomness.
@@
 
-For lensed sources we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.  This is the same set of images as used 
-in  \citep{2008A&A...482..403M,2010A&A...514A..93M,2016arXiv160604548M}.   There are 9,350 such sources with redshifts and separate shapelet coefficients in 4 bands.
+To model the background sources that are lensed we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.
+This is the same set of images as used in \citet{2008A&A...482..403M,2010A&A...514A..93M,2016arXiv160604548M}.
+There are 9,350 such sources with redshifts and separate shapelet coefficients in 4 bands.
 
@@
 The visible galaxies associated with the lens must also be simulated.
-There  too few bright galaxies in the  in the UDF catalog to make enough mock lens galaxies for this purpose.
+There  are too few bright galaxies in the UDF catalog  to make enough mock lens galaxies for this purpose.
 Instead, for most of the lenses, we used an analytic model for the surface brightness of these galaxies.
@@
 \end{align}
-\red{(reference)} where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.
-This approximately reproduces the observed correlation between these quantities.
+where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.  This approximately reproduces the observed correlation between these quantities.
 
@@
 
+{\color{blue}
 To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
-The surface brightness map in converted into a mass map by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
-This mass map is added to the lens before the ray tracing is done.
-{\color{red} MM: Again, I am confused with how the lenses are modeled in this stage of the simulation and during the search for caustics described in the beginning of this section.}
+The surface brightness map in converted into a mass map withing GLAMER by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
+These mass maps are added to the NFW dark matter halos discussed before to make the total lens mass distribution.
+The deflections caused by the mass maps are calculated by Fast Fourier Transform (FFT) and added to the halos'  deflections for the ray tracing is.}
 
@@
 The Gaussian PSF is clearly a simplified model, but a realistic treatment of the PSF is outside the scope of this paper.
-The typical width of the blurring due to the PSF is anyway realistic.
 The reference band for background and foreground galaxies was SDSS $i$, which is overlapping with the broader Euclid VIS band.
@@
 The reference band was $r$.
-For the challenge set 85\% images where made with purely simulated images as outlines above and the other 15\% used actual images taken from a preliminary sample of bright galaxies directly from the KiDS survey.
+For the challenge set 85\% of the images where made with purely simulated images as outlined above and the other 15\% used actual images taken from a preliminary sample of bright galaxies directly from the KiDS survey.
 Lensed source images where added to these real images at the same rate as for the mock images,  in this case 50\%.
@@
 
-\subsection{Trained Logistic Regression Methods}
+\subsection{Machine Learning Methods that use pre-selected features}
+
+These are methods that classify the objects by making linear or nonlinear boundaries in a feature space.
+The features are properties of the image and are typically chosen by the user with a combination of knowledge, intuition and trial-and-error.
+Using the training set, an optimal boundaries are found according to a criterion that depends on the method.
+The machine learns which combinations of features are best for distinguishing between lenses and non-lenses.
+
+\red{Philippa, what do you think of this? }
 

### 2017-09-07 paper.tex
Edit

@@
   2 & GAHEC IRAP & Space-Based & Cabanac  \\ 
-  3 & CAS Swinburne Melb & Ground-Based & Jacobs   \\ 
+  3 & \red{CAS Swinburne Melb} & Ground-Based & Jacobs   \\ 
   4 & ALL-star & Ground-Based & Avestruz, N.Li \& Lightman  \\ 
@@
   10 & YattaLensLite & Space-Based &  Sonnenfeld  \\ 
-  11 & NeuralNet2 & Space-Based &  Davies  \\ 
+  11 & \red{NeuralNet2} & Space-Based &  Davies  \\ 
   12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  \\ 
@@
 This section contains short descriptions of the lens finding methods that were used in 
-the challenge.  Each subsection refers to a team which gave a separate entry.
-
-{\color{red} MM: May be we could separate the methods into three categories: machine-learning, arc-finders, visual inspection and group them accordingly}
+the challenge.  Each subsection refers to a team which gave a separate entry.  We have grouped the 
+methods into four categories according to the type of method used.
 
@@
 All images (a total of 100000) were examined for each of the space- and
-ground-based datasets. This was done by two observers; AT examined 30000
-images in each case and NJ examined 70000. Observation was carried out
+ground-based datasets. This was done by two observers; AT (Amit Tagore) examined 30000
+images in each case and NJ (Neal Jackson) examined 70000. Observation was carried out
 over a 48-hour period, at the rate of 5000/hr (NJ) and 2500/hr (AT). 
@@
 The Python scripts used for manual examination of multiple images are available
-onGitHub\footnote{https://github.com/nealjackson/bigeye} and are described in more detail
+on GitHub\footnote{https://github.com/nealjackson/bigeye} and are described in more detail
 in \citet{hartley2017support}. For one-colour data such as
@@
 \subsection{Arc-Finders}
+
+These methods seek to identify gravitationally lensed arcs and differentiate between them and 
+other objects such as spiral arms and edge on spirals using their width, color, curvature and other pre-selected criterion.
+
 \subsubsection{ IRAP (Cabanac)}
@@
 
-Arcfinder \citep{2006astro.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} illustrated Figure \ref{fig:Cabanac}, is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
-Arcfinder then extracts contiguous pixels above a given background and computes the candidate arcs length, width, area, radius of curvature and peak surface brightness.
+Arcfinder \citep{2006astro.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} illustrated in Figure \ref{fig:Cabanac}, is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
+Arcfinder then extracts contiguous pixels above a given background and computes the candidate arc's length, width, area, radius of curvature and peak surface brightness.
 A final thresholding is set to maximize purity over completeness on a few typical arcs of the dataset.
@@
 We discard the imaginary part of the function to leave, in two-dimensional space:
-
 \begin{equation}
@@
 \end{equation}
-
 where harmonic wavelength $\lambda$, Gaussian spread  $\sigma$ and orientation $\theta$ define the operation performed on each point $i,j$ in an image.
@@
 %-------------------------------------------------%
-\subsubsection{ALL Methodology (Avestruz, Li, Lightman}
+\subsubsection{ALL (Avestruz, Li, Lightman)}
 %-------------------------------------------------%
@@
 \subsection{Convolutional Neural Networks ((Lanusse)}
+
 Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.
@@
 We will use the notation
-$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps.
-In typical architectures, the size of these convolution filters is kept small (i.e.
+$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps.\red{(Need to make everyone conform to this notation.)}  In typical architectures, the size of these convolution filters is kept small (i.e.
 3x3 or 5x5 pixels) to limit the complexity of the model.
@@
 where $N$ is the number of training instances, $y \in \{0,1\}$ is the true class of the image and $\hat{y} \in [0,1]$ is the class probability predicted by the model.
-This optimization is performed by a Stochastic Gradient Descent (SGD) algorithm which updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
+This optimization is usually performed by a Stochastic Gradient Descent (SGD) algorithm which updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
 All the CNN-based methods presented in this work rely on the ADAM \citep{Kingma_2014} algorithm, an accelerated variant of SGD algorithm.
+\red{True?}
 
@@
 
+\red{Blue terms in following need to be defined.}
+
 \subsubsection{AstrOmatic (Bertin)}
 
-The lens detector is based on a convolutional neural network (CNN), trained with the provided training datasets.
+The lens detector is based on a CNN, trained with the provided training datasets.
 The CNN is implemented in Python, using the TensorFlow framework\footnote{http://www.tensorflow.org/}.
@@
 
-{\color{red} (MM: I think that the co-authors should provide a more detailed description of the algorithms.
-For example, they should quickly explain what is a CNN and what are its general components (i.e.
-what kind of layers, activation functions, etc.)}
-{\color{blue} RBM: I moved the general description of the CNN to the beginning of this section.}
-
-The network itself consists of three convolutional layers ($11\times 11\times 32$, $5\times 5 \times 64$ and $3\times 3\times 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer {\color{red} MM: the numbers make little sense without a description of what the mean -- see my previous comment}.
-The first five layers use the ELU (Exponential Linear Unit) activation function \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
+The network itself consists of three convolutional layers ($11\times 11 - 32$, $5\times 5 - 64$ and $3\times 3 - 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output \blue{softmax layer}.
+The first five layers use the ELU (Exponential Linear Unit) \blue{activation function} \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
 Dropout regularization \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
@@
 \mathrm{arcsinh} (10^{11} x)$, and bad pixels are simply set to 0.
-Data augmentation is performed in the form of random up-down and left-right image flipping, plus $k\pi/2$ rotations, where $k$ is a random integer in the $[0,3]$ range.
+\blue{Data augmentation} is performed in the form of random up-down and left-right image flipping, plus $k\pi/2$ rotations, where $k$ is a random integer in the $[0,3]$ range.
 Additionally, a small rotation with random angle $\theta$ is applied, involving bicubic image resampling.
@@
 
-We used a convolutional neural network \citep{Fukushima1980,Lecun1998} with a simple architecture of 12 layers (inspired by \citep{symmetry}), see table \ref{tab:architecture}.
-To avoid the problem of the data flow distribution getting out of the comfort zone of the activation functions (Internal Covariate Shift), we used a mix of normalization propagation \citep{norm_prop} (without the constraint on the weights but a proper initialization) and batch normalization \citep{batch_norm} (slowly disabled over the iterations).
+We used a CNN \citep{Fukushima1980,Lecun1998} with a simple architecture of 12 layers (inspired by \citep{symmetry}), see table \ref{tab:architecture}.
+To avoid the problem of the data flow distribution getting out of the comfort zone of the activation functions (\blue{Internal Covariate Shift}), we used a mix of normalization propagation \citep{norm_prop} (without the constraint on the weights but a proper initialization) and batch normalization \citep{batch_norm} (slowly disabled over the iterations).
 As activation function, we used a scaled and shifted ReLU (Rectifier Linear Unit), 
@@
 where $p$ is the output of the neural network, computed over a batch of 30 images, 15 lenses and 15 nonlenses, picked from the training set.
-Making batches of 30 images adds noise to the gradient makes the iterations faster.
+Making batches of 30 images adds noise to the gradient \red{which?} makes the iterations faster.
 
@@
 
-Our algorithm for classification of strong lensed galaxies was developed as a convolutional neural network (CNN) used for binary classification task.
-Our code was trained and tested on the space-based dataset (dataset 0) provided for the Strong lensing challenge, comprising 20,000 stamps of single band simulated galaxies.
+Our algorithm for classification of strong lensed galaxies was developed as a CNN used for binary classification task.
+Our code was trained and tested on the space-based dataset (dataset 0) provided for the Ssrong lensing challenge, comprising 20,000 stamps of single band simulated galaxies.
 We used the full dataset in the proportion of 4/5 for training and 1/5 for validation.
@@
 The input image (101x101 pixels) is first processed by a 2D convolution layer with a 3x3 filter size, then subsampled by a 3x3 max pooling layer.
-Other two identical units follow, with a growing dimensionality of the output space (depth, i.e.output number of filters) in the convolution, for a total of 3 convolutional layers and 3 max pooling layers.
-Each of these convolutional layers is followed by a rectified linear unit (ReLU) step.
+Another two identical units follow, with a growing dimensionality of the output space (depth, i.e.output number of filters) in the convolution, for a total of 3 convolutional layers and 3 max pooling layers.
+Each of these convolutional layers is followed by a \blue{rectified linear unit (ReLU) step}.
 The output of these units is then processed through a single fully-connected layer follower by a dropout layer, and, finally, by a one-neuron fully connected layer with sigmoid activation function.
@@
 \begin{itemize}
-\item Random rotation of the image in the range [0, 180$\degree$], using a reflection fill mode to keep constant the size of the images.
+\item Random rotation of the image in the range [0, 180$\degree$], using a \blue{reflection fill mode} to keep constant the size of the images.
 \item The images were randomly shifted of 0.02 times the total width of the image.
@@
 \end{itemize}
-During the training we initialize the weights of our model with random normal values and we warm up the training \citet{Huang_2016} of the CNN for 25 epochs, using an exponential decay rate (1e-6) and a staring learning rate of α = 0.001.
+During the training we initialize the weights of our model with random normal values and we warm up the training \citet{Huang_2016} of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) and a staring learning rate of α = 0.001.
 Then the network is trained using an early stopping method, and for a maximum number of 300 epochs.
@@
 The best architecture was trained over 220 epochs with a parameter of patience equal to 20.
-We implemented our code the Keras framework \citet{Chollet_2015} on top of Theano \citet{Bastien_2012}.
+We implemented our code the Keras framework \citep{Chollet_2015} on top of Theano \citep{Bastien_2012}.
 Our architecture converges with a classification accuracy of 91\% on the validation sample.
@@
 %-------------------------------------------------%
-[Note: we are placing this section here, but we agree it is good to group the methods.
-Perhaps machine learning based methods could go on a separate section and a unified description can be given to CNN-based methods, as most follow under this category.]
 
@@
 
-As mentioned above, the CNN used can take 3 images as input.
+As mentioned above, the CNN used can take 3 color images as input.
 Thus, if we want to use the information on the $4$ available bands, we will have to either combine $2$ of the $4$ bands to end up with $3$ bands for a single RGB CNN (configuration I below) or we use multiple CNNs to use the information available (configuration II to VI below).
 To combine the outputs of several CNNs we use a Support Vector Machine \citep[hereafter SVM; see e.g., ][]{rebentrost2014quantum} also implemented in Matlab.
-The SVM is used to combine the outputs $p_i$ of the several CNN (configurations II, III, IV and VI).
+The SVM is used to combine the outputs $p_i$ of the several CNNs (configurations II, III, IV and VI).
 Instead of using only $p_i$ as inputs to the SVM we also tested providing the SVM with image features obtained by the CNN (feature maps, configuration V) as inputs.
@@
 However, resnet differ from CNNs by the introduction of so-called shortcut connections bypassing blocks of several convolutional layers.
-As a result, instead of learning the full mapping from their input to their output these residual blocks only have to learn the difference to the identity.
+As a result, instead of learning the full mapping from their input to their output these residual blocks only have to {\color{blue} learn the difference to the identity}\red{(I don't know what you mean by this)}.
 In practice, this difference allows residual networks to be trained even for very deep models.
@@
 The model is topped by an average-pooling layer followed by a single fully-connected sigmoid layer with a single output.
-Apart from the final layer, we use the ELU activation throughout.
+Apart from the final layer, we use the \blue{ELU} activation throughout.
 The weights of the model are initialized using random normal values, following the strategy advocated in \citet{He2015a}.
@@
 
-We adopt a minimal pre-processing pre-processing strategy for the input images, removing the mean image and normalising by the noise standard deviation $\sigma$ in each band, these statistic being evaluated over the whole training set.
-In addition, we clip extreme values above $250 \sigma$ to limit the dynamic range of the input.
+We adopt a minimal pre-processing strategy for the input images, removing the mean image and normalising by the noise standard deviation $\sigma$ in each band, these statistic being evaluated over the whole training set.
+In addition, we clip extreme values above $250 \,\sigma$ to limit the dynamic range of the input.
 Bad-pixels are simply set to 0 after this pre-processing step.
@@
 On an Nvidia Titan Xp GPU, our full training procedure requires approximately 6 hours on the ground-based challenge, but classification of the whole testing set is performed in a couple of minutes.
-Finally, in the interest of reproducible research, our code is made publicly available at
-\begin{center}
-\url{https://github.com/McWilliamsCenter} 
-\end{center}
+Finally, in the interest of reproducible research, our code is made publicly available on GitHub\footnote{\url{https://github.com/McWilliamsCenter} }.
 This repository also contains a notebook detailing how to reproduce our challenge submission.
@@
 \subsubsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
-Our lens-finder is based on a Convolutional Neural Network (CNN), following the strategy adopted recently in \citep{2017arXiv170207675P}.
+\red{This is a bit ragged and another submission needs to be analysed.}
+
+Our lens-finder is based on a CNN, following the strategy adopted recently in \citep{2017arXiv170207675P}.
 
@@
 \end{align}
-The classifier generally gives a probability of a case being a lens, $p$ in which case a threshold is set and everything with $p$ greater is classified as a lens and everything smaller is classified as not a lens.
+The classifier generally gives a probability of a case being a lens, $p$, in which case a threshold is set and everything with $p$ greater is classified as a lens and everything smaller is classified as not a lens.
 The TPR and FPR are then plotted as a curve parametrised by this threshold.
@@
 The better a classifier is the smaller the FPR and the larger the TPR so the further away from this diagonal line it will be.
-When a classifier provides only a binary classification or a discrete ranking, the ROC connects the endpoints to the discrete points found be using each rank as a threshold.
+When a classifier provides only a binary classification or a discrete ranking, the ROC connects the endpoints to the discrete points found by using each rank as a threshold.
 
@@
 
-\red{breakups Manchester between Neil and Amit}
+\red{breakups Manchester between Neal and Amit}
 

### 2017-09-08 paper.tex
Update on Overleaf.

--- 2017-09-07 paper.tex
@@
 
-\subsection{Convolutional Neural Networks ((Lanusse)}
+\subsection{Convolutional Neural Networks}
 Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.

### 2017-09-08 paper.tex
Added description of activation functions

@@
 Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.
-A CNN \citep{Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
+A CNN \citep{Fukushima1980,Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
 With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.
@@
 3x3 or 5x5 pixels) to limit the complexity of the model.
-To capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
+
+Similarly to conventional fully-connected neural networks, convolution layers are typically followed  by an element-wise activation function which allows for the modeling of complex functional forms  by introducing non-linearities in the model.
+Classical choices  for  activation functions  include the sigmoid-shaped logistic  function (or just sigmoid) $f(x) = 1/ (1  + \exp(-x))$ or the hyperbolic tangent function $f(x) = \tanh(x)$.
+However, much of the success of Deep Learning is due to the  introduction of activation functions that do not saturate, allowing for the  efficient training  of very deep architectures.
+The most common choice in modern deep learning models  is the simple ReLU activation (for rectified linear unit) \citep{Nair2010} defined as $f(x) = \max(x, 0 )$.
+A closely related  common alternative is the ELU activation (for Exponential Linear Unit) \citep{2015arXiv151107289C} defined as
+\begin{equation}
+	f(x ) = \begin{cases}
+    x & \text{if } x\geq 0\\
+    e^{x } - 1,              & \text{otherwise}
+\end{cases}\;,
+\end{equation}
+which often leads to better results in practice.
+
+Because the filters used in convolution layers are  typically  just a few pixels in size, to capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
 The most common downsampling schemes are the max-pooling and average pooling strategies, which downsample an input image by taking respectively the maximum or average values within a given region (e.g.
@@
 
-\fl{Things I still have to mention: activation function, dropout, batch normalisation}.
+\fl{Missing components:
+\begin{itemize}
+	\item dropout \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} 
+	\item batch norm \citep{batch_norm}
+\end{itemize}}
 
@@
 
-The network itself consists of three convolutional layers ($11\times 11\times 32$, $5\times 5 \times 64$ and $3\times 3\times 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer {\color{red} MM: the numbers make little sense without a description of what the mean -- see my previous comment}.
+%The network itself consists of three convolutional layers (11x11-32, 5x5-64 and 3x3-64), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer .
 The first five layers use the ELU (Exponential Linear Unit) activation function \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
 Dropout regularization \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
+The network itself consists of three convolutional layers (11x11-32, 5x5-64 and 3x3-64), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer .
+The first five layers use the ELU activation function, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
+Dropout regularization is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
 
@@
 
+%The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$.
+The network is trained on a Titan-X ``Pascal'' nVidia GPU using the \textit{Adam} gradient-based optimizer \citep{2014arXiv1412.6980K} during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
+Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.
 The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$.
-The network is trained on a Titan-X ``Pascal'' nVidia GPU using the \textit{Adam} gradient-based optimizer \citep{2014arXiv1412.6980K} during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
+The network is trained on a Titan-X ``Pascal'' nVidia GPU using the \textit{Adam} gradient-based optimizer during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
 Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.

### 2017-09-08 paper.tex

--- 2017-09-07 paper.tex
@@
 
-\subsection{Convolutional Neural Networks ((Lanusse)}
+\subsection{Convolutional Neural Networks}
 
 Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.
-A CNN \citep{Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
+A CNN \citep{Fukushima1980,Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
 With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.
@@
 We will use the notation
-$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps.\red{(Need to make everyone conform to this notation.)}  In typical architectures, the size of these convolution filters is kept small (i.e.
+$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps.
+In typical architectures, the size of these convolution filters is kept small (i.e.
 3x3 or 5x5 pixels) to limit the complexity of the model.
-To capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
+
+Similarly to conventional fully-connected neural networks, convolution layers are typically followed  by an element-wise activation function which allows for the modeling of complex functional forms  by introducing non-linearities in the model.
+Classical choices  for  activation functions  include the sigmoid-shaped logistic  function (or just sigmoid) $f(x) = 1/ (1  + \exp(-x))$ or the hyperbolic tangent function $f(x) = \tanh(x)$.
+However, much of the success of Deep Learning is due to the  introduction of activation functions that do not saturate, allowing for the  efficient training  of very deep architectures.
+The most common choice in modern deep learning models  is the simple ReLU activation (for rectified linear unit) \citep{Nair2010} defined as $f(x) = \max(x, 0 )$.
+A closely related  common alternative is the ELU activation (for Exponential Linear Unit) \citep{2015arXiv151107289C} defined as
+\begin{equation}
+	f(x ) = \begin{cases}
+    x & \text{if } x\geq 0\\
+    e^{x } - 1,              & \text{otherwise}
+\end{cases}\;,
+\end{equation}
+which often leads to better results in practice.
+
+Because the filters used in convolution layers are  typically  just a few pixels in size, to capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
 The most common downsampling schemes are the max-pooling and average pooling strategies, which downsample an input image by taking respectively the maximum or average values within a given region (e.g.
@@
 
-The network itself consists of three convolutional layers ($11\times 11 - 32$, $5\times 5 - 64$ and $3\times 3 - 64$), followed by two fully-connected layers ($256$ and $64$ neurons) and an output \blue{softmax layer}.
-The first five layers use the ELU (Exponential Linear Unit) \blue{activation function} \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
+%The network itself consists of three convolutional layers (11x11-32, 5x5-64 and 3x3-64), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer .
+The first five layers use the ELU (Exponential Linear Unit) activation function \citep{2015arXiv151107289C}, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
 Dropout regularization \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
+The network itself consists of three convolutional layers (11x11-32, 5x5-64 and 3x3-64), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer .
+The first five layers use the ELU activation function, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
+Dropout regularization is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
 

### 2017-09-08 paper.tex
Edit.

@@
 \end{align}
-where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002. \red{(reference)}
+where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002.
 
@@
 Figures~\ref{fig:roc_space} and \ref{fig:roc_ground} show the ROC curves for all the entries.  
+Note that ROC curves for the ground-based challenge (figure~\ref{fig:roc_ground}) are uniformly better than those for the space-based challenge (figure~\ref{fig:roc_space}).
+This is because of the importance of color information in discriminating lensed arcs from pieces of the foreground lens galaxy.
+
 In addition, figure~\ref{fig:roc_kids} shows the ROC curves for only the ground-based images where an actual KiDS image was used (see section~\ref{sec:sim-ground-based}).
@@
 This indicates that the simulated galaxy images are different from the real ones and that the classifiers are able to distinguish fake foreground galaxies from lenses more easily than from real galaxies.
+Some methods are more affected by this than others, but none seem to be immune, not even the human classification.
 This is perhaps not unexpected, but does show that the simulated lenses need to be improved before the raw numbers can be directly used to evaluate the performance of a classifier on real data.
@@
 CMU-DeepLens-ResNet in particular reaches a TPR$_0$ above 75\% for the brightest $\sim$ 10\% of the lenses.
+\red{(Find these numbers for the real KiDS sample)}
 
@@
 A large variety of lens finding methods were tested on simulated images that were developed separately.
-We found that some methods could recover more than 50\% of the lenses above a lens image brightness or size threshold without a single false positive.
+We found that some methods could recover more than 50\% of the lenses above a lensed image brightness or size threshold without a single false positive out of 100,000 candidates.
 If the data closely resembled the simulations we would already have reasonably good methods whose efficiency and biases can be quantitatively characterized.
@@
 It is the rare "abnormal" objects that pose the greatest challenge.
-When real KiDS data was used in the simulations the classifiers were all less accurate and it was only human inspection that found the one jackpot lens in the data.
+When real KiDS data was used in the simulations the classifiers were all less accurate and it was only human inspection that found the one jackpot lens (a double Einstein ring with two background sources) in the data.
 Things like ring galaxies, tidal tails in merging galaxies and irregular galaxies can be mistaken for lenses and were not well represented in the simulated data.
@@
 The distinguishing characteristics might only be a property of simulated data and not of real data.
-The confidence one will have in these methods is really the confidence one has in the realism of the simulations.
+In principle, SVM methods might potentially mitigate this somewhat because with them one can choose which features to used based on knowledge of the properties of irregular galaxies or ring galaxies for example.
+This has yet to be shown however.
+The confidence one will have in these machine learning methods is really based on the confidence one has in the realism of the simulations.
 
@@
 Another lesson is that color information is very important.
-Even with lower noise levels, higher resolution, a simpler PSF and no masking the lenses in the space-based set were harder to find than the lenses in the ground-based set.
-Having multiple bands clearly makes a big difference.
+Even with lower noise levels, higher resolution, a simpler PSF and no masking the lenses in the space-based set were harder to find than the lenses in the ground-based set (see figures~\ref{fig:roc_space} and \ref{fig:roc_ground}).
+Having multiple bands clearly makes a significant difference.
 Euclid will have several infrared bands with lower resolution than the visible images that were not included in the challenge.
 Even rather low resolution information from another instrument or telescope when combined with higher resolution data in one band might significantly improve the detection rates.
+Combining ground based data, such as LSST, with space based data, such as Euclid, would likely boost the detection rates by factors of several.
 

### 2017-09-08 paper.tex
Edit.
Update on Overleaf.

@@
 % List of institutions
+\vspace{0.5cm}\\
 $^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
@@
 Using the training set, an optimal boundaries are found according to a criterion that depends on the method.
-The machine learns which combinations of features are best for distinguishing between lenses and non-lenses.
-
-\red{Philippa, what do you think of this? }
+The machine learns how to weight the features best for distinguishing between lenses and non-lenses.
 

### 2017-09-12 paper.tex
Update on Overleaf.

@@
 \newauthor
-Gijs Verdoes Kleijn,$^{22}$ 
 Jean-Paul Kneib,$^6$
-Leon Koopmans,$^{22}$
+L\'{e}on V. E. Koopmans,$^{22}$
 \newauthor
@@
 Manuel B. Valent\'in,$^{19}$
-and Santiago Velasco-Forero,$^{10}$
+Santiago Velasco-Forero,$^{10}$
+and Gijs A. Verdoes Kleijn$^{22}$ 
 \\
@@
 \subsubsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
-\red{This is a bit ragged and another submission needs to be analysed.}
+\red{Another submission needs to be analysed.}
 
 Our lens-finder is based on a CNN, following the strategy adopted recently in \citep{2017arXiv170207675P}. 
-
 We decide to treat the problem as a three-class classification problem where the classes are \textit{non-lenses}, \textit{clear lenses} and \textit{dubious lenses}.
@@
 Given the rules of the challenge, we had to submit a prediction for each source in the test-set as a single number: a number in the interval [0,1] or either a 0 or a 1.
-Unfortunately, to satisfy this requirement we had to collapse one of the class into another: we provided a 0 when the source is classified as a \textit{non-lens} and 1 if it is classified as a \textit{clear lenses} or as a \textit{dubious lenses}.
-Moreover, this did not allow to build a continuous ROC curve but only a binary one.
+For satisfying this requirement we had to collapse one of the class into another: we provided a 0 when a source is classified as a \textit{non-lens} and a 1 when is classified as a \textit{clear lens} or as a \textit{dubious lenses}.
+This configuration did not allow to build a continuous ROC curve but only a binary one.
 \textbf{(We need to test if this was an improvement or not.
 I have the submission ready.)}
-
-Ihe final submission is made using the average values of the predictions from the same network trained three different times.
+The final submission was produced averaging the values of the predictions from three CNNs with the same architecture.
 
@@
 We used the CNN architecture called ResNet described in \citep{he2015deep} with three stacks of residual blocks of 5 layers. 
-
-The output layer is composed by three units. Each units gives in output a number between 0 and 1 that represents, respectively, the probability of being a non-lens, a small-lens, a big-lens.
+The output layer is composed by three units.
+Each units gives in output a number between 0 and 1 that represents, respectively, the probability of being a \textit{non-lens}, a \textit{dubious lens}, a \textit{certain lens}.
 
@@
 The training fits files are preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
-
 Due to memory limitations we down-sampled the images to 84 by 84 pixels. Most likely, this leads to a worse classification accuracy than using the original image resolution.
-
 We augmented the training images in the following way: i) random rotation of 90, 180 or 270 degrees; ii) random shift in both $x$ and $y$ direction between -2 and +2 pixels; iii) $50\%$ probability of horizontally flipping the image.
-
 Finally, the image border is cropped in order to have 80 by 80 pixel input images.
@@
 We started with a learning rate of $4 \times 10^{-4}$, decrease it to $4 \times 10^{-5}$ after 35000 updates and to $4 \times 10^{-6}$ after 43000 updates.
-The initial values of the biases are set to zero and the weights of each filter are initialized from a random normal distribution with variance ${2/n}$ where $n$ is the number of inputs of the unit (see \citep{he2015delving}).
+The initial values of the biases are set to zero and the weights of each filter are initialized from a random normal distribution with variance ${2/n}$ where $n$ is the number of inputs of the unit \citep{He2015a}.
 We use L2-norm regularization with $\lambda= 9 \times 10^{-3}$.

### 2017-09-14 paper.tex
Update on Overleaf.

@@
 %C.~E.~Petrillo$^{1}$,  C.~Tortora$^{1}$, L.~V.~E.~Koopmans$^{1}$, \and G.~Verdoes~Kleijn$^{1}$
-\author[R. B. Metcalf {\it et al.}]{
-R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
+\author[R. B. Metcalf {\it et al.}]{R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
 M. Meneghetti,$^4$ 
@@
 The Square Kilometer Array (SKA)\footnote{http://skatelescope.org/}, the Large Synoptic Survey Telescope (LSST)\footnote{https://www.lsst.org/} and the Euclid space telescope\footnote{https://www.euclid-ec.org/} are expected to increase the number of potential lenses by orders of magnitude \citep{collett_15,euclidSLWGwhitepaper,2015aska.confE..84M,2010MNRAS.405.2579O}.
-For example it is estimated that there will be approximately 200,000 observable galaxy-galaxy lenses in the Euclid data set among tens of billions of potential objects .
+For example it is estimated that there will be approximately 200,000 observable galaxy-galaxy lenses in the Euclid data set among tens of billions of potential objects.
 So far, less than a thousand lenses have been found in total across many heterogeneous data sets.
@@
 More recently, machine learning techniques that have become widely used in the fields of computer image processing and artificial intelligence have been applied to this problem and others in astronomy.
-In particular, artificial neural networks (ANNs) and support vector machines (SVM).
-SVMs and other logistic regression methods learn from a training set how to classify objects using predefined features which characterize each instance while ANNs (and a popular variant convolutional neural networks (CNNs) ) can learn directly from a training set which features are most important for distinguishing categories of objects.
+In particular, artificial neural networks (ANNs), support vector machines (SVM), and logistic regression.
+SVMs and logistic regression methods belong to the family of reproducing kernel Hilbert Space methods.
+They learn from a training set how to classify objects using features given by predefined kernel functions.
+In contrast ANNs (and a popular variant convolutional neural networks (CNNs) ) can learn directly from a training set which features are the most important for distinguishing categories of objects \red{Well, there are kernel learning methods for SVMs and logistic regressions as well as well...}.
 These have been used widely for such tasks as handwriting and facial recognition.
@@
 The participants were free to download these sets and train their algorithms on them.
-To enter the contest the participants needed to register with a team name at which point they would be given a unique key and the address of a test data set.
+To enter the contest, the participants needed to register with a team name at which point they would be given a unique key and the address of a test data set.
 These data sets contained 100,000 candidates.
 In the case of the multi-band ground-based set this was 400,000 images.
-The participant had 48 hours to upload a classification of all candidates consisting of a score between 0 and 1 -- 0 signifying the lowest confidence that it is a lens and 1 signifying the highest confidence that it is a lens.
+The participants had 48 hours to upload a classification of all candidates consisting of a score between 0 and 1 -- 0 signifying the lowest confidence that it is a lens and 1 signifying the highest confidence that it is a lens.
 This ranking could have been a simple binary (0 or 1) classification  or it could have been a continuous range of numbers representing the probability of being a lens or it could have been a finite number of confidence levels.
@@
 The halos are found with a friends-of-friends algorithm and characterized by a total mass, size and half mass radius.
-They includes subhalos of larger halos.
+They include subhalos of larger halos.
 The halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
@@
 There were 24 valid entries into the challenge.
-They are listed in table~\ref{table:entries}.
-There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries from people outside of the field.
+They are listed in Table~\ref{table:entries}.
+There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries from researchers outside of the field.
 
@@
 These are methods that classify the objects by making linear or nonlinear boundaries in a feature space.
-The features are properties of the image and are typically chosen by the user with a combination of knowledge, intuition and trial-and-error.
-Using the training set, an optimal boundaries are found according to a criterion that depends on the method.
-The machine learns how to weight the features best for distinguishing between lenses and non-lenses.
+The features are properties of the image and are typically chosen by the user with a combination of knowledge, intuition, and trial-and-error.
+Using the training set, the optimal boundaries are found according to a criterion that depends on the method.
+The machine learns how to use the features best for distinguishing between lenses and non-lenses.
 
@@
 A Support Vector Machine (SVM) is a supervised machine learning method which uses labeled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
-A preprocessing stage first extracts a set of useful features from input samples, before projecting each sample as a vector in multidimensional space.
+A preprocessing stage first extracts a set of useful features from input samples, before projecting each sample as a vector into a high-, possibly infinite-dimensional space.
 The model then separates classes of data by maximising the margin between a defining hyperplane and a set of so-called support-vectors at the inner edge of each class.
-The process of classification is computationally inexpensive since optimisation depends only on the dot products of the support vector subset.
+The process of classification is computationally inexpensive since the optimisation depends only on the dot products of the support vector subset.
 Feature extraction, however,  requires both an extensive exploration of the feature space during the development of a model, and potentially intensive computer resources in order to transform the original samples.
-Our full method is described in detail in \citet{hartley2017support}, and was developed using the Python scikit-learn and scikit-image packages \citep{scikit-learn,scikit-image}.
+Our full method is described in detail in \citet{hartley2017support} and was developed using the Python scikit-learn and scikit-image packages \citep{scikit-learn,scikit-image}.
 
@@
 
-Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later a brief general description of them will be useful.
-A CNN \citep{Fukushima1980,Lecun1998} is a multi-layer feed-forward neural network model particularly well suited for processing natural images.
+Since Convolutional Neural Networks (CNNs) are central to many of the methods that will be described later, here we provide a brief general description of them.
+A CNN \citep{Fukushima1980,Lecun1998} is a multi-layer feed-forward neural network model, which is particularly well-suited for processing natural images.
 With the very recent advances of the \textit{Deep Learning} framework \citep{Lecun2015}, models based on CNN architectures have reached or even surpassed human accuracy in image classification tasks \citep{He2015a}.
@@
 
-Similarly to conventional fully-connected neural networks, convolution layers are typically followed  by an element-wise activation function which allows for the modeling of complex functional forms  by introducing non-linearities in the model.
+Similarly to conventional fully-connected neural networks, convolution layers are typically followed  by an element-wise activation function, which allows for the modeling of complex functional forms  by introducing non-linearities in the model.
 Classical choices  for  activation functions  include the sigmoid-shaped logistic  function (or just sigmoid) $f(x) = 1/ (1  + \exp(-x))$ or the hyperbolic tangent function $f(x) = \tanh(x)$.
@@
 
-Because the filters used in convolution layers are  typically  just a few pixels in size, to capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers} which apply a downsampling operation to the feature maps.
+Because the filters used in convolution layers are  typically  just a few pixels in size, to capture features on larger scales, CNNs rely on a multi-resolution approach by interleaving convolutional layers with \textit{pooling layers}, which apply a downsampling operation to the feature maps.
 The most common downsampling schemes are the max-pooling and average pooling strategies, which downsample an input image by taking respectively the maximum or average values within a given region (e.g.
@@
 where $N$ is the number of training instances, $y \in \{0,1\}$ is the true class of the image and $\hat{y} \in [0,1]$ is the class probability predicted by the model.
-This optimization is usually performed by a Stochastic Gradient Descent (SGD) algorithm which updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
-All the CNN-based methods presented in this work rely on the ADAM \citep{Kingma_2014} algorithm, an accelerated variant of SGD algorithm.
-\red{True?}
-
-\fl{Missing components:
-\begin{itemize}
-	\item dropout \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} 
-	\item batch norm \citep{batch_norm}
-\end{itemize}}
+This optimization is usually performed by a Stochastic Gradient Descent (SGD) algorithm or its variants (e.g.
+ADAM \citep{Kingma_2014}, Adagrad \citep{duchi12adaptive}, RMSprop \citep{Tieleman12RMSProp}, or accelerated gradients \citep{nesterov83method}).
+SGD updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
+All the CNN-based methods presented in this work rely on the ADAM optimization algorithm, which also uses past gradients from previous iterations to adaptively estimate lower-order moments.
+Empirically it has been found that in many problems ADAM converges faster than SGD \citep{Ruder16overview}.
+
+To avoid overfitting in neural networks, we used the Dropout regularization technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}.
+During training, we randomly drop a certain percent of neurons and their connections from the neural
+network. This regularization technique reduces overfitting  by preventing complex co-adaptations of neurons on training data.
+
+Training multi-layer neural networks with gradient descent based approaches can be very challenging.
+One of the main reasons behind this is the effect of \textit{vanishing gradients}: it has been empirically observed that in many multi-layer neural networks the gradients in higher-level layers often become too small to be effective in gradient descent based optimization.
+Another difficulty is that the distribution of each layer’s inputs changes during training as the parameters of the previous layers change.
+These issues make difficult to find the best learning rates.
+
+To address these challenges, we use batch normalization layers \citep{batch_norm}: Let the activities of a given neuron in a mini-batch be denoted by $x_1,\ldots,x_m$.
+The batch normalization layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardize the neuron activities to make them zero mean with variance one, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
+Here $y_i$ denotes the output after applying the batch normalization layer on the neuron with activities $x_i$.
+It has been empirically demonstrated that batch normalization can often accelerate the training procedure and help mitigate the above described challenges.
+
+%\fl{Missing components:
+%\begin{itemize}
+%\item dropout
+%	\item batch norm 
+%\end{itemize}}
 
@@
 The predictions of the best 2 out of 3 models were then averaged to produce the final classification probability.
+
+\red{B: would be nice to have a figure about the resnet architecture}
 

### 2017-09-22 paper.tex
Update on Overleaf.

@@
 Santiago Velasco-Forero,$^{10}$
-and Gijs A. Verdoes Kleijn$^{22}$ 
+Gijs A. Verdoes Kleijn,$^{22}$
+\newauthor
+and Georgios Vernardos$^{22}$
 \\
@@
 $^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{6}$ \red{Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL)
-Observatoire de Sauverny CH - 1290 Versoix Switzerland} \\
+$^{6}$ Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, Switzerland \\
 $^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of \\ Manchester, Oxford Rd, Manchester M13 9PL, UK \\
@@
 $^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
-$^{16}$\red{ LAM - Laboratory of Astrophysics of Marseille P\^ole de l'\'Etoile Website of Ch\^ateau-Gombert 
-38,} \\ \red{rue Fr\'ed\'eric Joliot-Curie 13388 Marseille cedex 13 FRANCE} \\
+$^{16}$Aix Marseille Universit\'e, CNRS, LAM (Laboratoire d'Astrophysique de Marseille) UMR 7326, 13388, Marseille, France \\
 $^{17}$\red{Institut d'Astrophysique de Paris (IAP)- 98 bis boulevard Arago - 75014 Paris } \\
@@
 to satisfy the properties required by the normalization propagation.
-In our implementation of batch normalization, instead of using only the moments computed over the current batch, we used a low-pass filter ($\bar\mu_i \longleftarrow (1-\eta) \; \bar\mu_{i-1} + \eta \; \mu_i(\text{batch})$, $\eta$ set to $1$ at the beginning and decay with the iterations).
+Our batch normalization implementation computes the mean of the activation function $\bar\mu_i$ using the following equation 
+\begin{equation} \label{eq:batchnorm}
+    \bar\mu_i \longleftarrow (1-\eta) \; \bar\mu_{i-1} + \eta \; \mu_i(\text{batch}).
+\end{equation}
+$\bar\mu_i$ is computed using the mean value $\mu_i$ over the batch in combination with the previous mean $\bar\mu_{i-1}$ using an inertia value $\eta$ set to $1$ at the beginning and decaying with the iterations.
 For the training, the 20k provided images were split into two sets, 17k for training and 3k for validation.
@@
 where $p$ is the output of the neural network, computed over a batch of 30 images, 15 lenses and 15 nonlenses, picked from the training set.
-Making batches of 30 images adds noise to the gradient \red{which?} makes the iterations faster.
+The small batches with only 30 images were easier to handle computationally but add more noise to the gradient which we considered negligible due to there being only two classes to classify.
 
@@
 The architecture is implemented in Tensorflow\footnote{\url{http://tensorflow.org/}}.
-Our code is accessible on github\footnote{\url{https://github.com/antigol/lensfinder-euclid}}.
+Our code is accessible on github\footnote{\url{https://github.com/antigol/lensfinder-euclid}}. Additional details can be found in \citet{2017Schaefer}.
 
@@
 \red{We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}}
+JPK and CS acknowledge support from the ERC advanced grant LIDA and the ESA-NPI grant 491-2016.
 CA acknowledges support from the Enrico Fermi

### 2017-10-05 paper.tex
Update on Overleaf.

@@
 Fabio Bellagamba,$^1$
-Cl\'ecio R. Bom,$^{18,19}$
+Cl\'ecio R. Bom,$^{17,18}$
 Emmanuel Bertin,$^3$ 
@@
 \newauthor
-Raphael Gavazzi,$^{17}$ 
+Raphael Gavazzi,$^{3}$ 
 Mario Geiger,$^6$ 
@@
 Jean-Paul Kneib,$^6$
-L\'{e}on V. E. Koopmans,$^{22}$
+L\'{e}on V. E. Koopmans,$^{21}$
 \newauthor
-Fran\c{c}ois Lanusse,$^{20}$ 
-Chun-Liang Li,$^{21}$
-Quanbin Ma,$^{21}$ 
+Fran\c{c}ois Lanusse,$^{19}$ 
+Chun-Liang Li,$^{20}$
+Quanbin Ma,$^{20}$ 
 \newauthor
-Martin Makler,$^{19}$
+Martin Makler,$^{18}$
 Nan Li,$^{14}$
@@
 \newauthor
-Carlo Enrico Petrillo,$^{22}$
+Carlo Enrico Petrillo,$^{21}$
 Christoph Sch\"{a}fer,$^6$ 
@@
 Amit Tagore,$^7$
-Crescenzo Tortora,$^{22}$
+Crescenzo Tortora,$^{21}$
 Diego Tuccillo,$^{9,10}$
 \newauthor
-Manuel B. Valent\'in,$^{19}$
+Manuel B. Valent\'in,$^{18}$
 Santiago Velasco-Forero,$^{10}$
-Gijs A. Verdoes Kleijn,$^{22}$
+Gijs A. Verdoes Kleijn,$^{21}$
 \newauthor
-and Georgios Vernardos$^{22}$
+and Georgios Vernardos$^{21}$
 \\
@@
 $^{16}$Aix Marseille Universit\'e, CNRS, LAM (Laboratoire d'Astrophysique de Marseille) UMR 7326, 13388, Marseille, France \\
-$^{17}$\red{Institut d'Astrophysique de Paris (IAP)- 98 bis boulevard Arago - 75014 Paris } \\
-$^{18}${Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil}\\
-$^{19}${Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil}\\
-$^{20}${McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
-$^{21}${School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
-$^{22}${Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands}\\
+$^{17}${Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil}\\
+$^{18}${Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil}\\
+$^{19}${McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
+$^{20}${School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
+$^{21}${Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands}\\
 $^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
@@
 \section*{Acknowledgements}
-
-EB thanks Raphael Gavazzi for proposing him to participate to the challenge.
 AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.

### 2017-12-20 paper.tex
Update on Overleaf.
Edit.

@@
 % List of institutions
-\vspace{0.5cm}\\
+%\vspace{0.5cm}\\
 $^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
@@
 $^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{6}$ Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, Switzerland \\
+$^{6}$ Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), \\ Observatoire de Sauverny, 1290 Versoix, Switzerland \\
 $^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of \\ Manchester, Oxford Rd, Manchester M13 9PL, UK \\
@@
 \begin{abstract}
-\red{Preamble}
+Large scale imaging surveys will increase the number of galaxy-scale strong lensing candidates by maybe three orders of magnitudes beyond the number known today.
+Finding these rare objects will require picking them out of at least tens of millions of images and deriving scientific results from them will require quantifying the efficiency and bias of any search method.
+To achieve these objectives automated methods must be developed.
+Because gravitational lenses are rare objects reducing false positives will be particularly important.
 We present a description and results of an open gravitational lens finding challenge.
 Participants were asked to classify 100,000 candidate objects as to whether they were gravitational lenses or not with the goal of developing better automated methods for finding lenses in large data sets.
-\red{Mehtods used.} \red{Conclusions}
+A variety of methods were used including visual inspection, arc and ring finders, support vector machines (SVM) and convolutional neural networks (CNN).
+We find that many of the methods will be easily fast enough to analyze the anticipated data flow.
+In test data several methods are able to identify upwards of half the lenses after applying some thresholds on the lens characteristics such as lensed image brightness, size or contrast with the lens galaxy without making a single false-positive identification.
+This is significantly better than direct inspection by humans was able to do.
+Having multi-band, ground based data is found to be better for this purpose than single-band space based data with lower noise and higher resolution.
+The most difficult challenge for a lens finder is differentiating between rare irregular and ring galaxies and true gravitational lenses.
+The degree to which the efficiency and biases of lens finders can be quantified largely depends on the realism of the simulated data on which the finders are trained.
 \end{abstract}
@@
 Their magnification has been used as a natural telescope to observe otherwise undetectable objects \citep[e.g][]{2007ApJ...671.1196M,2017MNRAS.464.4823B,2016ApJ...833..264S}.
-They have put limits on the self interaction of dark matter and on the theory of gravitation.
-\red{Citation?} Through microlensing they have been used to study the structure of quasars \citep{2008ApJ...689..755M,2008ApJ...673...34P,2011ApJ...729...34B}.
+They have put limits on the self interaction of dark matter and on the theory of gravitation \citep{0004-637X-606-2-819}.
+Through microlensing they have been used to study the structure of quasars \citep{2008ApJ...689..755M,2008ApJ...673...34P,2011ApJ...729...34B}.
 To access this wealth of information the first step is to find the lenses.
@@
 Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of candidates that have been selected on the bases of luminosity and/or color.
-This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2014MNRAS.439.3392P} \red{(Maybe there are some others to cite here?)}.
+This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2014MNRAS.439.3392P}.
 A related method pioneered by the SPACE WARPS project \citep{2016MNRAS.455.1171M,2016MNRAS.455.1191M,2015MNRAS.452..502G} has been to crowd source the visual inspection through an online platform.
@@
 They learn from a training set how to classify objects using features given by predefined kernel functions.
-In contrast ANNs (and a popular variant convolutional neural networks (CNNs) ) can learn directly from a training set which features are the most important for distinguishing categories of objects \red{Well, there are kernel learning methods for SVMs and logistic regressions as well as well...}.
+ANNs (and a popular variant convolutional neural networks (CNNs) ) are even more flexible in learn directly from a training set which features are the most important for distinguishing categories of objects.
 These have been used widely for such tasks as handwriting and facial recognition.
@@
 An additional mass component that will be discussed later is added to each halo to represent the stellar ans gas mass.
-
-{\color{blue} RBM: I added some explanation in the above.}
 
@@
 
-{\color{blue}
 To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
@@
 These mass maps are added to the NFW dark matter halos discussed before to make the total lens mass distribution.
-The deflections caused by the mass maps are calculated by Fast Fourier Transform (FFT) and added to the halos'  deflections for the ray tracing is.}
+The deflections caused by the mass maps are calculated by Fast Fourier Transform (FFT) and added to the halos'  deflections for the ray tracing is.
 
@@
 
-\red{Blue terms in following need to be defined.}
-
 \subsubsection{AstrOmatic (Bertin)}
@@
 \mathrm{arcsinh} (10^{11} x)$, and bad pixels are simply set to 0.
-\blue{Data augmentation} is performed in the form of random up-down and left-right image flipping, plus $k\pi/2$ rotations, where $k$ is a random integer in the $[0,3]$ range.
+Data augmentation (increasing the amount of training data by modifying and reusing it) is performed in the form of random up-down and left-right image flipping, plus $k\pi/2$ rotations, where $k$ is a random integer in the $[0,3]$ range.
 Additionally, a small rotation with random angle $\theta$ is applied, involving bicubic image resampling.
@@
 We used a CNN \citep{Fukushima1980,Lecun1998} with a simple architecture of 12 layers (inspired by \citep{symmetry}), see table \ref{tab:architecture}.
-To avoid the problem of the data flow distribution getting out of the comfort zone of the activation functions (\blue{Internal Covariate Shift}), we used a mix of normalization propagation \citep{norm_prop} (without the constraint on the weights but a proper initialization) and batch normalization \citep{batch_norm} (slowly disabled over the iterations).
+To avoid the problem of the data flow distribution getting out of the comfort zone of the activation functions ("Internal Covariate Shift"), we used a mix of normalization propagation \citep{norm_prop} (without the constraint on the weights but a proper initialization) and batch normalization \citep{batch_norm} (slowly disabled over the iterations).
 As activation function, we used a scaled and shifted ReLU (Rectifier Linear Unit), 
@@
 Another two identical units follow, with a growing dimensionality of the output space (depth, i.e.output number of filters) in the convolution, for a total of 3 convolutional layers and 3 max pooling layers.
-Each of these convolutional layers is followed by a \blue{rectified linear unit (ReLU) step}.
+Each of these convolutional layers is followed by a rectified linear unit (ReLU) step.
 The output of these units is then processed through a single fully-connected layer follower by a dropout layer, and, finally, by a one-neuron fully connected layer with sigmoid activation function.
@@
 \begin{itemize}
-\item Random rotation of the image in the range [0, 180$\degree$], using a \blue{reflection fill mode} to keep constant the size of the images.
+\item Random rotation of the image in the range [0, 180$\degree$], using a reflection fill mode to keep constant the size of the images.
 \item The images were randomly shifted of 0.02 times the total width of the image.
@@
 However, resnet differ from CNNs by the introduction of so-called shortcut connections bypassing blocks of several convolutional layers.
-As a result, instead of learning the full mapping from their input to their output these residual blocks only have to {\color{blue} learn the difference to the identity}\red{(I don't know what you mean by this)}.
+As a result, instead of learning the full mapping from their input to their output these residual blocks only have to  learn the difference to the identity.
 In practice, this difference allows residual networks to be trained even for very deep models.
@@
 The model is topped by an average-pooling layer followed by a single fully-connected sigmoid layer with a single output.
-Apart from the final layer, we use the \blue{ELU} activation throughout.
+Apart from the final layer, we use the ELU (Exponential Linear Unit) activation throughout.
 The weights of the model are initialized using random normal values, following the strategy advocated in \citet{He2015a}.
@@
 
-\red{B: would be nice to have a figure about the resnet architecture}
+\red{Barnabas: would be nice to have a figure about the resnet architecture}
 
@@
 \subsubsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
-\red{Another submission needs to be analysed.}
 
@@
  \includegraphics[width=2\columnwidth]{figures/flux_contrast_space.pdf}
-  \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the ratio of the flux coming from the lensed source to the total flux in the image.  (\red{ check this.  Band?})}
+  \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the ratio of the flux coming from the lensed source to the total flux in the image in the index band.}
  \label{fig:flux_contrast_space}
@@
 CMU-DeepLens-ResNet in particular reaches a TPR$_0$ above 75\% for the brightest $\sim$ 10\% of the lenses.
-\red{(Find these numbers for the real KiDS sample)}
+%\red{(Find these numbers for the real KiDS sample)}
 
@@
 Interestingly some method's TPRs go up with this quantity and some go down.
-\red{explanation?}
-
-\red{surface brightness contrast}
-
-\red{breakups Manchester between Neal and Amit}
+We have not yet found any clear explanation for this variety of behaviors.
+%\red{explanation?}
+
+The two human inspector, NJ and AT, got significantly different scores on the ground based test set with individual AUROCs of 0.88 and 0.902 and TPR$_{10}$s of 0.01 and 0.06 respectively.
+They did not inspect the same images however so differences cannot be considered conclusive, but it does suggest that different inspectors will have different detection efficiencies and biases.
+
+%\red{surface brightness contrast}
 
@@
 Another lesson is that color information is very important.
-Even with lower noise levels, higher resolution, a simpler PSF and no masking the lenses in the space-based set were harder to find than the lenses in the ground-based set (see figures~\ref{fig:roc_space} and \ref{fig:roc_ground}).
+Even with lower noise levels, higher resolution, a simpler PSF and no masking, the lenses in the space-based set were harder to find than the lenses in the ground-based set (see figures~\ref{fig:roc_space} and \ref{fig:roc_ground}).
 Having multiple bands clearly makes a significant difference.
@@
 assistantship.
-\red{We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}}
+We thank the International Space Science Institute (ISSI) for hosting and funding our workshop.\footnote{http://www.issibern.ch/}
 JPK and CS acknowledge support from the ERC advanced grant LIDA and the ESA-NPI grant 491-2016.

### 2017-12-21 paper.tex
Update on Overleaf.

@@
   23 & YattaLensLite & Ground-Based & Sonnenfeld   \\ 
-  24 & Kapteyn Resnet & Space-Based & Petrillo, Koopmans, Kleijn, Tortora \& Vernardos \\ 
+  24 & Kapteyn Resnet & Space-Based & Petrillo, Tortora, Verdoes Kleijn, Koopmans \& Vernardos \\ 
    \hline
@@
 We define the \textit{dubious lenses} as the lenses with lensing features with less than 160 pixels and the \textit{clear lenses} those with more than 160 pixels belonging to the lensed source.
-This choice is motivated by the fact that specializing the network in recognizing different class could lead to a more robust classification.
+This choice is motivated by the fact that specializing the network in recognizing different classes could lead to a more robust classification.
 In addition, in a hypothetical application of the method to real data from a survey, this could be a way to select the most blatant lenses.
@@
 Given the rules of the challenge, we had to submit a prediction for each source in the test-set as a single number: a number in the interval [0,1] or either a 0 or a 1.
-For satisfying this requirement we had to collapse one of the class into another: we provided a 0 when a source is classified as a \textit{non-lens} and a 1 when is classified as a \textit{clear lens} or as a \textit{dubious lenses}.
-This configuration did not allow to build a continuous ROC curve but only a binary one.
-\textbf{(We need to test if this was an improvement or not.
-I have the submission ready.)}
+For satisfying this requirement we had to collapse one of the class into another: we provided a 0 when a source is classified as a \textit{non-lens} and a 1 when is classified as a \textit{clear lens} or as a \textit{dubious lens}.
+This choice did not allow to build a continuous ROC curve but only a binary one.
 The final submission was produced averaging the values of the predictions from three CNNs with the same architecture.

### 2018-01-27 paper.tex
Update on Overleaf.

@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-      \includegraphics[width=1\columnwidth]{figures/Fig1_gamoclass.pdf} 
+      \includegraphics[width=1\textwidth]{figures/Fig1_gamoclass.pdf} 
   \caption{GAMOCLASS schematic}
  \label{Fig1_gamoclass}
-\end{figure}
+\end{figure*}
 
@@
 AS was supported by World Premier International Research Center Initiative (WPI Initiative), MEXT, Japan.
-RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349.
-AT acknowledges receipt of an STFC postdoctoral research
+RBM's research was partly part of project GLENCO, funded under the European Seventh Framework Programme, Ideas, Grant Agreement n. 259349. AT acknowledges receipt of an STFC postdoctoral research
 assistantship.
@@
 through grant NSF PHY-1125897 and an endowment from the Kavli
-Foundation and its founder Fred Kavli.
+Foundation and its founder Fred Kavli. LVEK, CEP, CT and GV are supported through an NWO-VICI grant (project number 639.043.308). GVK acknowledges
+financial support from the Netherlands Research School for
+Astronomy (NOVA) and Target. Target is supported by
+Samenwerkingsverband Noord Nederland, European fund for regional
+development, Dutch Ministry of economic affairs, Pieken in de
+Delta, Provinces of Groningen and Drenthe.
 

### 2018-01-29 paper.tex
Edit.

@@
 $^{2}$ IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.\\
-$^{3}$ Sorbonne Universit\'{e}s, UPMC Univ. Paris 6 and CNRS, UMR 7095, Institut d'Astrophysique de Paris,  \\ 98bis Bd Arago, F-75014, Paris France.\\
+$^{3}$ Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS,  UMR 7095, 98 bis bd Arago, 75014 Paris, France.\\
 $^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
@@
 A variety of methods were used including visual inspection, arc and ring finders, support vector machines (SVM) and convolutional neural networks (CNN).
-We find that many of the methods will be easily fast enough to analyze the anticipated data flow.
-In test data several methods are able to identify upwards of half the lenses after applying some thresholds on the lens characteristics such as lensed image brightness, size or contrast with the lens galaxy without making a single false-positive identification.
+We find that many of the methods will be easily fast enough to analyse the anticipated data flow.
+In test data, several methods are able to identify upwards of half the lenses after applying some thresholds on the lens characteristics such as lensed image brightness, size or contrast with the lens galaxy without making a single false-positive identification.
 This is significantly better than direct inspection by humans was able to do.
-Having multi-band, ground based data is found to be better for this purpose than single-band space based data with lower noise and higher resolution.
-The most difficult challenge for a lens finder is differentiating between rare irregular and ring galaxies and true gravitational lenses.
+Having multi-band, ground based data is found to be better for this purpose than single-band space based data with lower noise and higher resolution, suggesting that colours bring a crucial additional information.
+The most difficult challenge for a lens finder is differentiating between rare irregular and ring-like face-on galaxies and true gravitational lenses.
 The degree to which the efficiency and biases of lens finders can be quantified largely depends on the realism of the simulated data on which the finders are trained.
@@
 
-Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of candidates that have been selected on the bases of luminosity and/or color.
-This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2014MNRAS.439.3392P}.
+Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of candidates that have been selected on the bases of luminosity and/or colour.
+This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2010A&A...517A..25S,2014MNRAS.439.3392P}.
 A related method pioneered by the SPACE WARPS project \citep{2016MNRAS.455.1171M,2016MNRAS.455.1191M,2015MNRAS.452..502G} has been to crowd source the visual inspection through an online platform.
@@
 Spectroscopic searches for galaxy scale lenses have also been done by looking for high redshift stellar lines in the spectra of lower redshift large galaxies.
-Notably this was done in the Sloan Lens ACS (SLACS) survey, producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006ApJ...638..703B}.
+Notably this was done in the Sloan Lens ACS (SLACS) survey, producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006MNRAS.369.1521W,2006ApJ...638..703B,2012ApJ...744...41B,2015MNRAS.449.3441S}.
 However, spectroscopy is telescope-time consuming and for the foreseeable future we are not likely to have spectroscopic surveys that cover anywhere near the number of objects as the planned imaging surveys.
@@
 They have been applied to survey data and found of order 200 lenses \citep{2007A&A...461..813C,2012ApJ...749...38M,2016A&A...592A..75P}.
-Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2010A&A...517A..25S,2017arXiv170401585S}.
+Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2017arXiv170401585S}.
 
@@
 
-The paper is organized as follows.
+The paper is organised as follows.
 The form of the challenge and its rules are described in the next section.
@@
 light cone extending out to redshift $z=6$.
-The halos are found with a friends-of-friends algorithm and characterized by a total mass, size and half mass radius.
+The halos are found with a friends-of-friends algorithm and characterised by a total mass, size and half mass radius.
 They include subhalos of larger halos.
@@
 In this way the halos have the mass, concentration and clustering properties from the N-body simulation, but within each strong lens the mass resolution is not limited by the original simulation, but follows the analytic mass profile.
-An additional mass component that will be discussed later is added to each halo to represent the stellar ans gas mass.
+An additional mass component that will be discussed later is added to each halo to represent the stellar and gas mass \red{I don't see any further reference to the gas component}.
 
@@
 This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the process inefficient because most of the sources are too far away from the caustic to produce clear lenses.
-If the source positions where taken completely at random the fraction of clear lenses would be very low.
+If the source positions were taken completely at random the fraction of clear lenses would be very low.
 
@@
 The magnitude and bulge-to-disk ratio are a function of the pass band.
-Each galaxy is given a random orientation and inclination angle.between 0 and $80\degree$.
+Each galaxy is given a random orientation and inclination angle between 0 and $80\degree$.
 The disk is exponential with no vertical height which is why the inclination is limited to $80\degree$.
-The bulge is represented by a S\'{e}rsic profile with a axis ratio randomly sampled between 0.5 and 1.
+The bulge is represented by a S\'{e}rsic profile with an axis ratio randomly sampled between 0.5 and 1.
 The S\'{e}rsic index, $n_s$, is given by
@@
 \end{align}
-where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.  This approximately reproduces the observed correlation between these quantities.
+where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.  This approximately reproduces the observed correlation between these quantities \red{REF?}.
 
@@
 To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
-The surface brightness map in converted into a mass map withing GLAMER by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
+The surface brightness map in converted into a mass map within GLAMER by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
 These mass maps are added to the NFW dark matter halos discussed before to make the total lens mass distribution.
-The deflections caused by the mass maps are calculated by Fast Fourier Transform (FFT) and added to the halos'  deflections for the ray tracing is.
+The deflections caused by the mass maps are calculated by Fast Fourier Transform (FFT) and added to the halos'  deflections for the ray tracing.
 
@@
 For the training set we provided an image of the total lens with noise, an image of the foreground galaxies with noise and image of the lensed background source without noise.
-For the test sets only the final images were provided to participants although all the information was stored for analyzing the entries.
+For the test sets only the final images were provided to participants although all the information was stored for analysing the entries.
 
@@
 
-By chance one of the original KiDS images appears to have been a lens.  When an additional lensed source was added this made a double lens or "jackpot" lens.
+By chance one of the original KiDS images appears to have been a lens.  When an additional lensed source was added this made a double lens or "jackpot" lens \citep{2008ApJ...677.1046G}.
 
@@
   3 & \red{CAS Swinburne Melb} & Ground-Based & Jacobs   \\ 
-  4 & ALL-star & Ground-Based & Avestruz, N.Li \& Lightman  \\ 
+  4 & ALL-star & Ground-Based & Avestruz, N. Li \& Lightman  \\ 
   5 & Manchester1 & Space-Based & Jackson \& Tagore  \\ 
@@
   13 & CMU-DeepLens-ResNet-ground3 & Ground-Based &  Lanusse, Ma, Ravanbakhsh \& C. Li \\ 
-  14 & GAMOCLASS & Space-Based & Marc Huertas-Company, Tuccillo, Velasco-Forero \& Decenci\~{a}re \\ 
+  14 & GAMOCLASS & Space-Based &  Huertas-Company, Tuccillo, Velasco-Forero \& Decenci\`{e}re \\ 
   15 & LASTRO EPFL (CNN) & Space-Based & Geiger, Sch\"{a}fer \& Kneib \\ 
@@
 For the current SL challenge, arcfinder was tuned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.
-A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code as a linux line command.
+A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code as a linux  command line.
 Arcfinder took a couple of hours to run on the entire dataset with some overheads due to the dataset format.
@@
 SGD updates the model iteratively by taking small gradient steps over randomly selected subsamples of the training set (so called \textit{mini-batches}).
-All the CNN-based methods presented in this work rely on the ADAM optimization algorithm, which also uses past gradients from previous iterations to adaptively estimate lower-order moments.
+All the CNN-based methods presented in this work rely on the ADAM optimisation algorithm, which also uses past gradients from previous iterations to adaptively estimate lower-order moments.
 Empirically it has been found that in many problems ADAM converges faster than SGD \citep{Ruder16overview}.
 
-To avoid overfitting in neural networks, we used the Dropout regularization technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}.
-During training, we randomly drop a certain percent of neurons and their connections from the neural
-network. This regularization technique reduces overfitting  by preventing complex co-adaptations of neurons on training data.
+To avoid overfitting in neural networks, we used the Dropout regularisation technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}.
+During training, we randomly drop a certain percent of neurones and their connections from the neural
+network. This regularisation technique reduces overfitting  by preventing complex co-adaptations of neurones on training data.
 
 Training multi-layer neural networks with gradient descent based approaches can be very challenging.
-One of the main reasons behind this is the effect of \textit{vanishing gradients}: it has been empirically observed that in many multi-layer neural networks the gradients in higher-level layers often become too small to be effective in gradient descent based optimization.
-Another difficulty is that the distribution of each layer’s inputs changes during training as the parameters of the previous layers change.
+One of the main reasons behind this is the effect of \textit{vanishing gradients}: it has been empirically observed that in many multi-layer neural networks the gradients in higher-level layers often become too small to be effective in gradient descent based optimisation.
+Another difficulty is that the distribution of each layers inputs changes during training as the parameters of the previous layers change.
 These issues make difficult to find the best learning rates.
 
-To address these challenges, we use batch normalization layers \citep{batch_norm}: Let the activities of a given neuron in a mini-batch be denoted by $x_1,\ldots,x_m$.
-The batch normalization layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardize the neuron activities to make them zero mean with variance one, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
-Here $y_i$ denotes the output after applying the batch normalization layer on the neuron with activities $x_i$.
-It has been empirically demonstrated that batch normalization can often accelerate the training procedure and help mitigate the above described challenges.
+To address these challenges, we use batch normalisation layers \citep{batch_norm}: Let the activities of a given neurone in a mini-batch be denoted by $x_1,\ldots,x_m$.
+The batch normalisation layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardise the neurone activities to make them zero mean with variance one, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
+Here $y_i$ denotes the output after applying the batch normalisation layer on the neurone with activities $x_i$.
+It has been empirically demonstrated that batch normalisation can often accelerate the training procedure and help mitigate the above described challenges.
 
@@
 The best architecture was trained over 220 epochs with a parameter of patience equal to 20.
-We implemented our code the Keras framework \citep{Chollet_2015} on top of Theano \citep{Bastien_2012}.
+We implemented our code in the Keras framework \citep{Chollet_2015} on top of Theano \citep{Bastien_2012}.
 Our architecture converges with a classification accuracy of 91\% on the validation sample.
@@
 This evaluates the overall ability of a classifier to distinguish between cases.
-This was the criterion on which the challenge participants were told to optimize.
+This was the criterion on which the challenge participants were told to optimise.
 However, in the case of gravitational lensing this is not the only thing, and not the most important thing, to consider.
-Gravitational lenses are rare events, but to improve the discrimination and training of the classifiers the fraction lenses in test and training sets are boosted to something around half.
-In these circumstances it is important to consider the absolute number of cases that will be missclassified when the fraction of true cases is closer to what is expected in the data.
+Gravitational lenses are rare events, but to improve the discrimination and training of the classifiers the fraction of lenses in test and training sets are boosted to something around half.
+In these circumstances it is important to consider the absolute number of cases that will be misclassified when the fraction of true cases is closer to what is expected in the data.
 
@@
 \begin{align}
-\frac{\rm FP}{\rm TP} \simeq \frac{\rm FPR}{\rm TPR} \left(\frac{\textrm{number of non-lenses in sample}}{\textrm{number of lenses is sample}} \right)
+\frac{\rm FP}{\rm TP} \simeq \frac{\rm FPR}{\rm TPR} \left(\frac{\textrm{number of non-lenses in sample}}{\textrm{number of lenses in sample}} \right)
 \end{align}
@@
 It might be that one classifier is good at finding systems with large Einstein radii and incomplete arcs, but not as good at finding small complete Einstein rings that are blended with the light of the lens galaxy.
-Also lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test dataset.
+Also lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test dataset \red{How could this latter happen?
+For a lens to be classified as a lens, it should exceed a minimum magnification threshold}.
 We want to include these objects because we want to test the limits of the classifiers.
@@
 For this reason we plot the AUROC, TPR$_0$ and TPR$_{10}$ as a function of several variables for all the entries.
-This is done by removing all the lenses that do not exceed the threshold and then recalculating the these quantities, the number of non-lenses remains the same.
+This is done by removing all the lenses that do not exceed the threshold and then recalculating  these quantities, the number of non-lenses remains the same.
 
@@
  \caption{The ROC curves for the ground-based entries.
-Notice that these are are generally better than in figure~\ref{fig:einstein_space} indicating that colour information is an important discriminant.
+Notice that these are generally better than in figure~\ref{fig:einstein_space} indicating that colour information is an important discriminant.
 }
@@
 
-We have done a fairly good jobs of determining that lenses can be identified in a population of fairly "normal" galaxies.
+We have done a fairly good job of determining that lenses can be identified in a population of fairly "normal" galaxies.
 It is the rare "abnormal" objects that pose the greatest challenge.
@@
 The distinguishing characteristics might only be a property of simulated data and not of real data.
-In principle, SVM methods might potentially mitigate this somewhat because with them one can choose which features to used based on knowledge of the properties of irregular galaxies or ring galaxies for example.
+In principle, SVM methods might potentially mitigate this somewhat because with them one can choose which features to use based on knowledge of the properties of irregular galaxies or ring galaxies for example.
 This has yet to be shown however.
@@
 
-Another lesson is that color information is very important.
+Another lesson is that colour information is very important.
 Even with lower noise levels, higher resolution, a simpler PSF and no masking, the lenses in the space-based set were harder to find than the lenses in the ground-based set (see figures~\ref{fig:roc_space} and \ref{fig:roc_ground}).

### 2018-01-29 paper.tex
Edit

@@
 It might be that one classifier is good at finding systems with large Einstein radii and incomplete arcs, but not as good at finding small complete Einstein rings that are blended with the light of the lens galaxy.
-Also lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test dataset \red{How could this latter happen?
+Also a lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test dataset \red{How could this latter happen?
 For a lens to be classified as a lens, it should exceed a minimum magnification threshold}.

### 2018-02-06 paper.tex
Edit.

--- 2018-01-29 paper.tex
@@
 %C.~E.~Petrillo$^{1}$,  C.~Tortora$^{1}$, L.~V.~E.~Koopmans$^{1}$, \and G.~Verdoes~Kleijn$^{1}$
-\author[R. B. Metcalf {\it et al.}]{R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
+\author[R. B. Metcalf {\it et al.}]{
+R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
 M. Meneghetti,$^4$ 
@@
 % List of institutions
-%\vspace{0.5cm}\\
 $^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
@@
 In this way the halos have the mass, concentration and clustering properties from the N-body simulation, but within each strong lens the mass resolution is not limited by the original simulation, but follows the analytic mass profile.
-An additional mass component that will be discussed later is added to each halo to represent the stellar and gas mass \red{I don't see any further reference to the gas component}.
+An additional mass component that will be discussed later is added to each halo to represent the stellar mass.
 
@@
 \label{sec:entries}
-
-There were 24 valid entries into the challenge.
-They are listed in Table~\ref{table:entries}.
-There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries from researchers outside of the field.
 
@@
 
-This section contains short descriptions of the lens finding methods that were used in 
+There were 24 valid entries into the challenge.
+They are listed in Table~\ref{table:entries}.
+There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries from researchers outside of the field.
+
+The following sections contain short descriptions of the lens finding methods that were used in 
 the challenge.  Each subsection refers to a team which gave a separate entry.  We have grouped the 
@@
 The coefficients of these filters are free parameters that are learned by the model.
-We will use the notation
-$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps.
+The notation
+$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps will be used.
 In typical architectures, the size of these convolution filters is kept small (i.e.
@@
 Classical choices  for  activation functions  include the sigmoid-shaped logistic  function (or just sigmoid) $f(x) = 1/ (1  + \exp(-x))$ or the hyperbolic tangent function $f(x) = \tanh(x)$.
-However, much of the success of Deep Learning is due to the  introduction of activation functions that do not saturate, allowing for the  efficient training  of very deep architectures.
+However, much of the success of Deep Learning is due to the  introduction of activation functions that do not saturate (become very close to one with very small derivatives), allowing for the  efficient training  of very deep architectures.
 The most common choice in modern deep learning models  is the simple ReLU activation (for rectified linear unit) \citep{Nair2010} defined as $f(x) = \max(x, 0 )$.
@@
 
-To avoid overfitting in neural networks, we used the Dropout regularisation technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}.
-During training, we randomly drop a certain percent of neurones and their connections from the neural
-network. This regularisation technique reduces overfitting  by preventing complex co-adaptations of neurones on training data.
+Neural networks often suffer from overfitting to the training set.
+A common way to mitigate this is to use a regularisation scheme.
+For example, the Dropout regularisation technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}, were a certain percentage of the neurones and their connections are  randomly drop  from the neural network.
+This regularisation techniques reduces overfitting  by preventing complex co-adaptations of neurones on training data.
 
@@
 Another difficulty is that the distribution of each layers inputs changes during training as the parameters of the previous layers change.
-These issues make difficult to find the best learning rates.
-
-To address these challenges, we use batch normalisation layers \citep{batch_norm}: Let the activities of a given neurone in a mini-batch be denoted by $x_1,\ldots,x_m$.
+These issues make it difficult to find the best learning rates.
+
+Batch normalisation layers \citep{batch_norm} are one way of addressing these challenges.
+Let the activities of a given neurone in a mini-batch be denoted by $x_1,\ldots,x_m$.
 The batch normalisation layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardise the neurone activities to make them zero mean with variance one, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
@@
 
+There are many variations on these techniques and concepts some of which are represented in the following descriptions of particular methods.  
 %\fl{Missing components:
@@
 It might be that one classifier is good at finding systems with large Einstein radii and incomplete arcs, but not as good at finding small complete Einstein rings that are blended with the light of the lens galaxy.
-Also lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test dataset \red{How could this latter happen?
-For a lens to be classified as a lens, it should exceed a minimum magnification threshold}.
-We want to include these objects because we want to test the limits of the classifiers.
+Also a lens may have a source that is too faint to be detected by any algorithm or is too far from the lens to be very distorted, but will be classified as a lens in the test dataset.
+We do not impose a definitive arc/ring magnification, brightness or surface brightness limit for a system to be considered a lens because we
+want to include these objects because we want to test the limits of the classifiers.
 As we will see, if you restrict your objectives to detecting only lensed images with surface brightness above threshold, for example, the "best" algorithm might change and the TPR will change.

### 2018-02-06 paper.tex
Edit.

@@
 \end{align}
-where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.  This approximately reproduces the observed correlation between these quantities \red{REF?}.
+where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.
+This very approximately reproduces the observed correlation between these quantities \citep{2001AJ....121..820G}.
 
@@
   2 & GAHEC IRAP & Space-Based & Cabanac  \\ 
-  3 & \red{CAS Swinburne Melb} & Ground-Based & Jacobs   \\ 
+  3 & CAS Swinburne Melb$^\dagger$& Ground-Based & Jacobs   \\ 
   4 & ALL-star & Ground-Based & Avestruz, N. Li \& Lightman  \\ 
@@
   10 & YattaLensLite & Space-Based &  Sonnenfeld  \\ 
-  11 & \red{NeuralNet2} & Space-Based &  Davies  \\ 
+  11 & NeuralNet2$^\dagger$ & Space-Based &  Davies  \\ 
   12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  \\ 
@@
    \hline
+   & & &$\dagger$ No description was submitted for this paper.
 \end{tabular}
@@
 
-\red{Barnabas: would be nice to have a figure about the resnet architecture}
+%\red{Barnabas: would be nice to have a figure about the resnet architecture}
 

### 2018-02-08 paper.tex
Converted to A&A format.

@@
-\documentclass[useAMS,usenatbib]{mnras}
+%\documentclass[useAMS,usenatbib]{mnras}
+%\documentclass[useAMS,usenatbib]{aa}
+\documentclass{aa}
 
@@
 \usepackage{amssymb}
-\usepackage{cite}
+%\usepackage{cite}
 \usepackage{natbib}
@@
 \usepackage{import}
+\usepackage[varg]{txfonts}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{etoolbox}
-\makeatletter
-\newcount\c@additionalboxlevel
-\setcounter{additionalboxlevel}{0}
-\newcount\c@maxboxlevel
-\setcounter{maxboxlevel}{1}
-\patchcmd\@combinedblfloats{\box\@outputbox}{%
-  \stepcounter{additionalboxlevel}%
-  \box\@outputbox
-}{}{\errmessage{\noexpand\@combinedblfloats could not be patched}}
-
-\AtBeginShipout{%
-  \ifnum\value{additionalboxlevel}>\value{maxboxlevel}%
-    \typeout{Warning: maxboxlevel might be too small, increase to %
-      \the\value{additionalboxlevel}%
-    }%
-  \fi 
-  \@whilenum\value{additionalboxlevel}<\value{maxboxlevel}\do{%
-    \typeout{* Additional boxing of page `\thepage'}%
-    \setbox\AtBeginShipoutBox=\hbox{\copy\AtBeginShipoutBox}%
-    \stepcounter{additionalboxlevel}%
-  }%
-  \setcounter{additionalboxlevel}{0}%
+%\usepackage{etoolbox}
+%\makeatletter
+%\newcount\c@additionalboxlevel
+%\setcounter{additionalboxlevel}{0}
+%\newcount\c@maxboxlevel
+%\setcounter{maxboxlevel}{1}
+%\patchcmd\@combinedblfloats{\box\@outputbox}{%
+%  \stepcounter{additionalboxlevel}%
+%  \box\@outputbox
+%}{}{\errmessage{\noexpand\@combinedblfloats could not be patched}}
+%
+%\AtBeginShipout{%
+%  \ifnum\value{additionalboxlevel}>\value{maxboxlevel}%
+%    \typeout{Warning: maxboxlevel might be too small, increase to %
+%      \the\value{additionalboxlevel}%
+%    }%
+%  \fi 
+%  \@whilenum\value{additionalboxlevel}<\value{maxboxlevel}\do{%
+%    \typeout{* Additional boxing of page `\thepage'}%
+%    \setbox\AtBeginShipoutBox=\hbox{\copy\AtBeginShipoutBox}%
+%    \stepcounter{additionalboxlevel}%
+%  }%
+%  \setcounter{additionalboxlevel}{0}%
+%}
+%\makeatother
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+\begin{document}
+
+\title{The Strong Gravitational  Lens Finding Challenge}
+
+\author{
+R. Benton Metcalf \inst{1,2}\thanks{E-mail: robertbenton.metcalf@unibo.it} 
+\and
+M. Meneghetti \inst{2}
+\and
+Camille Avestruz \inst{3,4,5}\fnmsep\thanks{Provost's Postdoctoral Scholar at the University of Chicago}
+\and
+Fabio Bellagamba\inst{1}
+\and
+Cl\'ecio R. Bom\inst{6,7}
+\and
+Emmanuel Bertin\inst{8}
+\and
+R\'emi Cabanac \inst{9}
+\and
+Etienne Decenci\`ere \inst{10}
+\and
+R\'emi Flamary \inst{11}
+\and
+Raphael Gavazzi \inst{8}
+\and
+Mario Geiger \inst{12} 
+\and
+Philippa Hartley \inst{13}
+\and
+Marc Huertas-Company \inst{14}
+\and
+Neal Jackson \inst{13}
+\and
+Eric Jullo \inst{15}
+\and
+Jean-Paul Kneib \inst{12}
+\and
+L\'{e}on V. E. Koopmans \inst{16}
+\and
+Fran\c{c}ois Lanusse \inst{17}
+\and
+Chun-Liang Li \inst{18}
+\and
+Quanbin Ma \inst{18}
+\and
+Martin Makler \inst{7}
+\and
+Nan Li \inst{19}
+\and
+Matthew Lightman \inst{15}
+\and
+Carlo Enrico Petrillo \inst{16}
+\and
+Christoph Sch\"{a}fer \inst{12}
+\and
+Alessandro Sonnenfeld \inst{21}
+\and
+Amit Tagore \inst{13}
+\and
+Crescenzo Tortora \inst{16}
+\and
+Diego Tuccillo \inst{10,14}
+\and
+Manuel B. Valent\'in \inst{7}
+\and
+Santiago Velasco-Forero \inst{10}
+\and
+Gijs A. Verdoes Kleijn \inst{16}
+\and
+Georgios Vernardos \inst{16}
 }
-\makeatother
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
-
-\title[SL Challenge]{The Strong Gravitational  Lens Finding Challenge}
-%C.~E.~Petrillo$^{1}$,  C.~Tortora$^{1}$, L.~V.~E.~Koopmans$^{1}$, \and G.~Verdoes~Kleijn$^{1}$
-\author[R. B. Metcalf {\it et al.}]{
-R. Benton Metcalf,$^{1,4}$\thanks{E-mail: robertbenton.metcalf@unibo.it} 
-M. Meneghetti,$^4$ 
-Camille Avestruz,$^{11,12,13,\dagger}$
-\newauthor
-Fabio Bellagamba,$^1$
-Cl\'ecio R. Bom,$^{17,18}$
-Emmanuel Bertin,$^3$ 
-\newauthor
-R\'emi Cabanac,$^2$ 
-Etienne Decenci\`ere,$^{10}$
-R\'emi Flamary,$^8$
-\newauthor
-Raphael Gavazzi,$^{3}$ 
-Mario Geiger,$^6$ 
-Philippa Hartley,$^7$
-\newauthor
-Marc Huertas-Company,$^9$
-Neal Jackson,$^7$ 
-Eric Jullo,$^{16}$
-\newauthor
-Jean-Paul Kneib,$^6$
-L\'{e}on V. E. Koopmans,$^{21}$
-\newauthor
-Fran\c{c}ois Lanusse,$^{19}$ 
-Chun-Liang Li,$^{20}$
-Quanbin Ma,$^{20}$ 
-\newauthor
-Martin Makler,$^{18}$
-Nan Li,$^{14}$
-Matthew Lightman,$^{15}$
-\newauthor
-Carlo Enrico Petrillo,$^{21}$
-Christoph Sch\"{a}fer,$^6$ 
-Alessandro Sonnenfeld,$^5$ 
-\newauthor
-Amit Tagore,$^7$
-Crescenzo Tortora,$^{21}$
-Diego Tuccillo,$^{9,10}$
-\newauthor
-Manuel B. Valent\'in,$^{18}$
-Santiago Velasco-Forero,$^{10}$
-Gijs A. Verdoes Kleijn,$^{21}$
-\newauthor
-and Georgios Vernardos$^{21}$
-\\
-% List of institutions
-$^{1}$ Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy \\
-$^{2}$ IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.\\
-$^{3}$ Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS,  UMR 7095, 98 bis bd Arago, 75014 Paris, France.\\
-$^{4}$ INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy \\
-$^{5}$ Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
-$^{6}$ Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL), \\ Observatoire de Sauverny, 1290 Versoix, Switzerland \\
-$^{7}$ Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of \\ Manchester, Oxford Rd, Manchester M13 9PL, UK \\
-$^{8}$ Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique,\\ Observatoire de la C\^{o}te d'Azur, Parc Valrose, 06108 Nice, France \\
-$^{9}$ LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France \\
-$^{10}$ MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue \\ Saint-Honore, Fontainebleau, France \\
-$^{11}${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
-$^{12}${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
-$^{13}${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
-$^{14}${School of Physics and Astronomy, Nottingham University, University Park, Nottingham, NG7 2RD, UK
-}\\
-$^{15}${JPMorgan Chase, Chicago, IL 60603 U.S.A.}\\
-$^{16}$Aix Marseille Universit\'e, CNRS, LAM (Laboratoire d'Astrophysique de Marseille) UMR 7326, 13388, Marseille, France \\
-$^{17}${Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil}\\
-$^{18}${Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil}\\
-$^{19}${McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
-$^{20}${School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA}\\
-$^{21}${Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands}\\
-$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
+
+\institute{
+Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy 
+\and
+INAF-Osservatorio Astronomico di Bologna, via Ranzani 1, 40127 Bologna, Italy 
+\and
+Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.
+\and
+Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.
+\and
+Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.
+\and
+Centro Federal de Educa\c{c}\~ao Tecnol\'ogica Celso Suckow da Fonseca, CEP 23810-000,  Itagua\'i, RJ, Brazil
+\and
+Centro Brasileiro de Pesquisas F\'isicas, CEP 22290-180, Rio de Janeiro, RJ, Brazil
+\and
+Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS,  UMR 7095, 98 bis bd Arago, 75014 Paris, France.
+\and
+IRAP, Universit\'e de Toulouse, CNRS, UPS, Toulouse, France.
+\and
+MINES Paristech, PSL Research University, Centre for Mathematical Morphology, 35 rue  Saint-Honore, Fontainebleau, France
+\and
+Laboratoire Lagrange, Universi\'{e} de Nice Sophia-Antipolis, Centre National de la Recherche Scientifique,
+\and
+Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique F\'ed\'erale de Lausanne (EPFL),  Observatoire de Sauverny, 1290 Versoix, Switzerland 
+\and
+Jodrell Bank Centre for Astrophysics, School of Physics \& Astronomy, University of  Manchester, Oxford Rd, Manchester M13 9PL, UK Observatoire de la C\^{o}te d'Azur, Parc Valrose, 06108 Nice, France 
+\and
+LERMA, Observatoire de Paris, CNRS, Universit\'e Paris Diderot, 61, Avenue de l'Observatoire F-75014, Paris, France
+\and
+Aix Marseille Universit\'e, CNRS, LAM (Laboratoire d'Astrophysique de Marseille) UMR 7326, 13388, Marseille, France
+\and
+Kapteyn Astronomical Institute, University of Groningen, Postbus 800, 9700 AV, Groningen, The Netherlands
+\and
+McWilliams Center for Cosmology, Department of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA
+\and
+School of Computer Science, Carnegie Mellon University, Pittsburgh, PA 15213, USA
+\and
+School of Physics and Astronomy, Nottingham University, University Park, Nottingham, NG7 2RD, UK
+\and
+JPMorgan Chase, Chicago, IL 60603 U.S.A.
+\and
+Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan
 }
 
-\begin{document}
-
-\date{Accepted . Received ; in original form }
-
-\maketitle
-
-\label{firstpage}
-
-% Abstract of the paper
-\begin{abstract}
+%\date{Accepted . Received ; in original form }
+%\maketitle
+%\label{firstpage}
+
+\abstract{
+%\begin{abstract}
 Large scale imaging surveys will increase the number of galaxy-scale strong lensing candidates by maybe three orders of magnitudes beyond the number known today.
@@
 The degree to which the efficiency and biases of lens finders can be quantified largely depends on the realism of the simulated data on which the finders are trained.
-\end{abstract}
-
-\begin{keywords}
-gravitational lensing -- cosmology 
-\end{keywords}
+}%\end{abstract}
+
+\keywords{gravitational lensing -- cosmology }
+
+\maketitle
 
@@
 These take the form of multiple images of a quasar and Einstein rings surrounding a galaxy and of highly distorted arcs seen through galaxy groups and clusters.
-The first strong lens was discovered in 1979 \citep{1979Natur.279..381W} and since then many valuable scientific uses have been found for them.
+The first strong lens was discovered in 1979 \citet{1979Natur.279..381W} and since then many valuable scientific uses have been found for them.
 They have been used to study how dark matter is distributed in galaxies and clusters \citep[e.g.][]{1991ApJ...373..354K,2001ApJ...554.1216C,2002ApJ...568L...5K,2003ApJ...587..143R,2003ApJ...583..606K,2005MNRAS.360.1333W,2005ApJ...623...31D,2009MNRAS.392..945V,2016MNRAS.463.3115T}.
-They have been used to measure the Hubble constant and other cosmological parameters \citep[e.g.][]{1964MNRAS.128..307R,1992ARA&A..30..311B,2000ApJ...544...98W,2013ApJ...766...70S,2016A&ARv..24...11T}.
+They have been used to measure the Hubble constant and other cosmological parameters
+\citep[e.g.][]{1964MNRAS.128..307R,1992ARAandA..30..311B,2000ApJ...544...98W,2013ApJ...766...70S,2016AandARv..24...11T}.  
 Their magnification has been used as a natural telescope to observe otherwise undetectable objects \citep[e.g][]{2007ApJ...671.1196M,2017MNRAS.464.4823B,2016ApJ...833..264S}.
@@
 Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of candidates that have been selected on the bases of luminosity and/or colour.
-This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2010A&A...517A..25S,2014MNRAS.439.3392P}.
+This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2010AandA...517A..25S,2014MNRAS.439.3392P}.
 A related method pioneered by the SPACE WARPS project \citep{2016MNRAS.455.1171M,2016MNRAS.455.1191M,2015MNRAS.452..502G} has been to crowd source the visual inspection through an online platform.
@@
 Some automated algorithms have been developed in the past to detect lenses in images.
-These have been designed to detect arc-like features \citep{2006astro.ph..6757A,2007A&A...472..341S, 2017A&A...597A.135B} and rings \citep{2014ApJ...785..144G,2014A&A...566A..63J}.
-They have been applied to survey data and found of order 200 lenses \citep{2007A&A...461..813C,2012ApJ...749...38M,2016A&A...592A..75P}.
+These have been designed to detect arc-like features \citep{2006astro.ph..6757A,2007AandA...472..341S, 2017AandA...597A.135B} and rings \citep{2014ApJ...785..144G,2014AandA...566A..63J}.
+They have been applied to survey data and found of order 200 lenses \citep{2007AandA...461..813C,2012ApJ...749...38M,2016AandA...592A..75P}.
 Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2017arXiv170401585S}.
@@
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy, these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017A&A...597A.135B,hartley2017support}.
+In astronomy, these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017AandA...597A.135B,hartley2017support}.
 
@@
 To model the background sources that are lensed we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.
-This is the same set of images as used in \citet{2008A&A...482..403M,2010A&A...514A..93M,2016arXiv160604548M}.
+This is the same set of images as used in \citet{2008AandA...482..403M,2010AandA...514A..93M,2016arXiv160604548M}.
 There are 9,350 such sources with redshifts and separate shapelet coefficients in 4 bands.
@@
 where $\frac{B}{T}$ is the bulge to total flux ratio and $x$ is a uniform random number between -1 and 1.
-This very approximately reproduces the observed correlation between these quantities \citep{2001AJ....121..820G}.
+This very approximately reproduces the observed correlation between these quantities \citep{2001AJ...121..820G}.
 
@@
 The reference band for background and foreground galaxies was SDSS $i$, which is overlapping with the broader Euclid VIS band.
-The realisation of the mock images followed the same procedure described in \citet{2004PASP..116..750G} and \citet{2008A&A...482..403M}.
+The realisation of the mock images followed the same procedure described in \citet{2004PASP..116..750G} and \citet{2008AandA...482..403M}.
 As a result, the noise follows a Gaussian distribution with a realistic width and is uncorrelated between pixels.
@@
 
-Arcfinder \citep{2006astro.ph..6757A,2007A&A...461..813C,2012ApJ...749...38M} illustrated in Figure \ref{fig:Cabanac}, is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
+Arcfinder \citep{2006astro.ph..6757A,2007AandA...461..813C,2012ApJ...749...38M} illustrated in Figure \ref{fig:Cabanac}, is a fast linear method that computes a pixel wise elongation parameter (ratio of first-order moments in a n-pix window oriented in proper reference frame) for all pixels of mexican-hat-smoothed FITS images.
 Arcfinder then extracts contiguous pixels above a given background and computes the candidate arc's length, width, area, radius of curvature and peak surface brightness.
@@
 
-During our development of an SVM classifier for lens finding, feature extraction initially involved the decomposition of each image into a set of objects, using SExtractor \citep{1996A&AS..117..393B} and GALFIT \citep{2002AJ....124..266P} to recover and subtract objects iteratively.
-This method had previously been used in a static algorithm approach which assigned points according to the morphological properties of each image \citep[see][]{2014A&A...566A..63J}.
+During our development of an SVM classifier for lens finding, feature extraction initially involved the decomposition of each image into a set of objects, using SExtractor \citep{1996AandAS..117..393B} and GALFIT \citep{2002AJ...124..266P} to recover and subtract objects iteratively.
+This method had previously been used in a static algorithm approach which assigned points according to the morphological properties of each image \citep[see][]{2014AandA...566A..63J}.
 Lensed-like objects displaying, for example, greater ellipticity and tangentiality were awarded more points.

### 2018-02-08 paper.tex
Update on Overleaf.

@@
 
-\usepackage{newtxtext,newtxmath}
+%\usepackage{newtxtext,newtxmath}
 \usepackage[T1]{fontenc}
@@
 \end{itemize}
-During the training we initialize the weights of our model with random normal values and we warm up the training \citet{Huang_2016} of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) and a staring learning rate of α = 0.001.
+During the training we initialize the weights of our model with random normal values and we warm up the training \citet{Huang_2016} of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) and a staring learning rate of  0.001.
 Then the network is trained using an early stopping method, and for a maximum number of 300 epochs.

### 2018-02-12 paper.tex
Update on Overleaf.
edit

@@
-%\documentclass[useAMS,usenatbib]{mnras}
-%\documentclass[useAMS,usenatbib]{aa}
+%\documentclass[onecolumn]{aa}
 \documentclass{aa}
@@
 
-\keywords{gravitational lensing -- cosmology }
-
 \maketitle
@@
 
-Some automated algorithms have been developed in the past to detect lenses in images.
-These have been designed to detect arc-like features \citep{2006astro.ph..6757A,2007AandA...472..341S, 2017AandA...597A.135B} and rings \citep{2014ApJ...785..144G,2014AandA...566A..63J}.
+Some automated algorithms have been developed in the past to detect lenses in images.  These have been designed to detect arc-like 
+features \citep{2006astro.ph..6757A,2007AnadA...472..341S, 2017AnadA...597A.135B} and rings 
+\citep{2014ApJ...785..144G,2014AandA...566A..63J}.
 They have been applied to survey data and found of order 200 lenses \citep{2007AandA...461..813C,2012ApJ...749...38M,2016AandA...592A..75P}.
@@
 Thus, for the Strong Lensing Challenge in the ground base sample, we used configuration VI.
-This final scheme is ilustraded in figure \ref{colorCASTCNN}.
+This final scheme is illustrated in figure \ref{colorCASTCNN}.
 

### 2018-02-16 paper.tex
Added authors.
Update on Overleaf.

@@
 \and
+Andrew Davies \inst{22}
+\and
 Etienne Decenci\`ere \inst{10}
@@
 Carlo Enrico Petrillo \inst{16}
+\and
+Stephen Serjeant \inst{22}
 \and
@@
 Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan
+\and
+School of Physical Sciences, The Open University, Walton Hall, Milton Keynes, MK7 6AA, UK
 }
-
-%\date{Accepted . Received ; in original form }
-%\maketitle
-%\label{firstpage}
 
@@
   10 & YattaLensLite & Space-Based &  Sonnenfeld  \\ 
-  11 & NeuralNet2$^\dagger$ & Space-Based &  Davies  \\ 
+  11 & NeuralNet2 & Space-Based &  Davies  \\ 
   12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  \\ 
@@
 We use L2-norm regularization with $\lambda= 9 \times 10^{-3}$.
+
+\subsubsection{NeuralNet2 (Davies, Serjeant) }
+
+Our lens finder included wavelet prefiltering.
+The image was convolved with the Mallat wavelet with a kernel size of 4 in both the horizontal and vertical directions, then combined and compared to the original image to make the final image; $final image = \sqrt[]{H^{2}+V^{2}}$.
+This prefiltering was performed the emphasise the edges in the images, improving the results from the Convolutional Neural Network (CNN).
+The CNN had 2 convolution layers each containing 32 $3\times3$ filters, incorporating dropout and max-pooling, and then 3 dense fully-connected layers to classify each image.
+The network was trained on 18000 of the 20000 training images; training took 15 epochs and was completed once the validation loss was minimised.
+The training was validated on the remaining 2000 images.
+Validation loss $\mathcal{L}(\theta)$ was calculated using binary cross entropy
+\begin{equation}
+\mathcal{L}(\theta) = \sum_{i=1}^{n} \big[ y_{i}$ $log(p_{i}) + (1 $ - $ y_{i})$ $log(1 $ - $ p_{i}) \big]
+\end{equation} where $\mathcal{L}(\theta)$ is the loss function, $n$ is the number of inputs, $y_{i}$ is the true value of the $i^{th}$ input , and $p_{i}$ is the predicted value for the $i^{th}$ input from the network.
+A perfect loss of $0$ was generated once every predicted value matched the true value for every input.
+The network was made and trained in Python 2.7 using the open-source libraries \textsc{theano} and \textsc{keras}\footnote{\href{https://github.com/keras-team/keras}{\tt https://github.com/keras-team/keras}}.
+A more developed version of our lens finder will appear in Davies, Bromley and Serjeant (in preparation).
 

### 2018-02-16 paper.tex
Update on Overleaf.
Edit.

@@
 \and
-Fabio Bellagamba\inst{1}
+Fabio Bellagamba\inst{1,2}
 \and
@@
 \institute{
-Departimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gabetti 93/2, 4012 Bologna, Italy 
+Dipartimento di Fisica \& Astronomia, Universit\`a di Bologna, via Gobetti 93/2, 40129 Bologna, Italy 
 \and
@@
 The image was convolved with the Mallat wavelet with a kernel size of 4 in both the horizontal and vertical directions, then combined and compared to the original image to make the final image; $final image = \sqrt[]{H^{2}+V^{2}}$.
-This prefiltering was performed the emphasise the edges in the images, improving the results from the Convolutional Neural Network (CNN).
+This prefiltering was performed to emphasise the edges in the images, improving the results from the Convolutional Neural Network (CNN).
 The CNN had 2 convolution layers each containing 32 $3\times3$ filters, incorporating dropout and max-pooling, and then 3 dense fully-connected layers to classify each image.
@@
 The training was validated on the remaining 2000 images.
-Validation loss $\mathcal{L}(\theta)$ was calculated using binary cross entropy
+Validation loss was calculated using binary cross entropy
 \begin{equation}

### 2018-02-16 paper.tex
Update on Overleaf.

@@
 Our lens finder included wavelet prefiltering.
-The image was convolved with the Mallat wavelet with a kernel size of 4 in both the horizontal and vertical directions, then combined and compared to the original image to make the final image; $final image = \sqrt[]{H^{2}+V^{2}}$.
+The image was convolved with the Mallat wavelet with a kernel size of 4 in both the horizontal and vertical directions, then combined and compared to the original image to make the input image; $input image = \sqrt[]{H^{2}+V^{2}}$.
 This prefiltering was performed to emphasise the edges in the images, improving the results from the Convolutional Neural Network (CNN).
@@
 \begin{equation}
-\mathcal{L}(\theta) = \sum_{i=1}^{n} \big[ y_{i}$ $log(p_{i}) + (1 $ - $ y_{i})$ $log(1 $ - $ p_{i}) \big]
-\end{equation} where $\mathcal{L}(\theta)$ is the loss function, $n$ is the number of inputs, $y_{i}$ is the true value of the $i^{th}$ input , and $p_{i}$ is the predicted value for the $i^{th}$ input from the network.
+\mathcal{L} = \sum_{i=1}^{n} \big[ y_{i}$ $log(p_{i}) + (1 $ - $ y_{i})$ $log(1 $ - $ p_{i}) \big]
+\end{equation} where $\mathcal{L}$ is the loss function, $n$ is the number of inputs, $y_{i}$ is the true value of the $i^{th}$ input , and $p_{i}$ is the predicted value for the $i^{th}$ input from the network.
 A perfect loss of $0$ was generated once every predicted value matched the true value for every input.

### 2018-11-27 paper.tex
Fixed problems with references.

@@
 
-\def\aap{Astronomy \& Astrophysics}
-\def\apj{The Astrophysical Journal}
-\def\mnras{Monthly Notices of the Royal Astronomical Society}
-\def\aj{Astronomical Journal}
+\def\aap{A\& A}
+\def\apj{ApJ}
+\def\mnras{MNRAS}
+\def\aj{AJ}
 \def\aaps{AAPS}
 \def\nat{Nature}
+\def\araa{ARA\& A}
+\def\aapr{A\& ARv}
 
@@
 Some automated algorithms have been developed in the past to detect lenses in images.  These have been designed to detect arc-like 
-features \citep{2006astro.ph..6757A,2007AnadA...472..341S, 2017AnadA...597A.135B} and rings 
+features \citep{2006astro.ph..6757A,2007AandA...472..341S, 2017AandA...597A.135B} and rings 
 \citep{2014ApJ...785..144G,2014AandA...566A..63J}.
@@
 To model the background sources that are lensed we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.
-This is the same set of images as used in \citet{2008AandA...482..403M,2010AandA...514A..93M,2016arXiv160604548M}.
+This is the same set of images as used in \citet{2008AandA...482..403M,2010AandA...514A..93M}.
 There are 9,350 such sources with redshifts and separate shapelet coefficients in 4 bands.
@@
 
-During our development of an SVM classifier for lens finding, feature extraction initially involved the decomposition of each image into a set of objects, using SExtractor \citep{1996AandAS..117..393B} and GALFIT \citep{2002AJ...124..266P} to recover and subtract objects iteratively.
+During our development of an SVM classifier for lens finding, feature extraction initially involved the decomposition of each image into a set of objects, using SExtractor \citep{1996AandAS..117..393B} and GALFIT \citep{2002AJ....124..266P} to recover and subtract objects iteratively.
 This method had previously been used in a static algorithm approach which assigned points according to the morphological properties of each image \citep[see][]{2014AandA...566A..63J}.

### 2018-12-03 paper.tex
Edit.

@@
 \usepackage[varg]{txfonts}
+
+\usepackage{enumitem}
 
@@
 To achieve these objectives automated methods must be developed.
-Because gravitational lenses are rare objects reducing false positives will be particularly important.
+Because gravitational lenses are rare, objects reducing false positives will be particularly important.
 We present a description and results of an open gravitational lens finding challenge.
@@
 This is significantly better than direct inspection by humans was able to do.
-Having multi-band, ground based data is found to be better for this purpose than single-band space based data with lower noise and higher resolution, suggesting that colours bring a crucial additional information.
+Having multi-band, ground based data is found to be better for this purpose than single-band space based data with lower noise and higher resolution, suggesting that multi colours data is crucial additional.
 The most difficult challenge for a lens finder is differentiating between rare irregular and ring-like face-on galaxies and true gravitational lenses.
@@
 These take the form of multiple images of a quasar and Einstein rings surrounding a galaxy and of highly distorted arcs seen through galaxy groups and clusters.
-The first strong lens was discovered in 1979 \citet{1979Natur.279..381W} and since then many valuable scientific uses have been found for them.
-They have been used to study how dark matter is distributed in galaxies and clusters \citep[e.g.][]{1991ApJ...373..354K,2001ApJ...554.1216C,2002ApJ...568L...5K,2003ApJ...587..143R,2003ApJ...583..606K,2005MNRAS.360.1333W,2005ApJ...623...31D,2009MNRAS.392..945V,2016MNRAS.463.3115T}.
-They have been used to measure the Hubble constant and other cosmological parameters
+The first strong lens was discovered in 1979 by \citet{1979Natur.279..381W} and since then many valuable scientific uses have been found for them.
+They have been used to study how dark matter is distributed in galaxies and clusters \citep[e.g.][]{1991ApJ...373..354K,2001ApJ...554.1216C,2002ApJ...568L...5K,2003ApJ...587..143R,2003ApJ...583..606K,2005MNRAS.360.1333W,2005ApJ...623...31D,2009MNRAS.392..945V,2016MNRAS.463.3115T} and  to measure the Hubble constant and other cosmological parameters
 \citep[e.g.][]{1964MNRAS.128..307R,1992ARAandA..30..311B,2000ApJ...544...98W,2013ApJ...766...70S,2016AandARv..24...11T}.  
-Their magnification has been used as a natural telescope to observe otherwise undetectable objects \citep[e.g][]{2007ApJ...671.1196M,2017MNRAS.464.4823B,2016ApJ...833..264S}.
+Their magnification has been used as a natural telescope to observe otherwise undetectable objects at high redshift \citep[e.g][]{2007ApJ...671.1196M,2017MNRAS.464.4823B,2016ApJ...833..264S}.
 They have put limits on the self interaction of dark matter and on the theory of gravitation \citep{0004-637X-606-2-819}.
@@
 
-Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of candidates that have been selected on the bases of luminosity and/or colour.
+Up to this point, the most widely used method for finding lenses in imaging surveys has been by visual inspection of candidates that have been selected on the basis of luminosity and/or colour.
 This has been done in the radio \citep{2003MNRAS.341...13B} and in the visible with space and ground based data \citep{2008MNRAS.389.1311J,2008ApJS..176...19F,2010AandA...517A..25S,2014MNRAS.439.3392P}.
@@
 
-More recently, machine learning techniques that have become widely used in the fields of computer image processing and artificial intelligence have been applied to this problem and others in astronomy.
-In particular, artificial neural networks (ANNs), support vector machines (SVM), and logistic regression.
-SVMs and logistic regression methods belong to the family of reproducing kernel Hilbert Space methods.
+More recently, machine learning techniques that have become widely used in the fields of computer image processing and artificial intelligence have been applied to this problem and others in astronomy; in particular, artificial neural networks (ANNs), support vector machines (SVM), and logistic regression.
+SVMs and some logistic regression methods belong to the family of reproducing kernel Hilbert Space methods.
 They learn from a training set how to classify objects using features given by predefined kernel functions.
@@
 We anticipate further challenges in the future in which the realism of the data simulations will become progressively better.
-Here we have chosen to concentrate on galaxy/small group scale lenses where the background source is a galaxy because we feel that this is where the most progress can be made and the scientific return is the highest, but QSO lenses and cluster/group lenses challenges may follow.
+Here we have chosen to concentrate on galaxy/small group scale lenses where the background source is a galaxy because we feel that this is where the most progress can be made and the scientific return is the highest, but QSO lens and cluster/group lens challenges may follow.
 
@@
 We discuss the metrics used to evaluate entries in section~\ref{sec:figure_of_merit}.
-The performance of each of the methods broken down in different ways is presented in section~\ref{sec:performance}.
+The performance of each of the methods is presented in section~\ref{sec:performance}.
 Finally,  in section~\ref{sec:conclusion}, we conclude with a discussion of what was learned and how methods can be improved in the future.
@@
 In the case of the multi-band ground-based set this was 400,000 images.
-The participants had 48 hours to upload a classification of all candidates consisting of a score between 0 and 1 -- 0 signifying the lowest confidence that it is a lens and 1 signifying the highest confidence that it is a lens.
+The participants had 48 hours to upload a classification of all candidates consisting of a score between 0 and 1 0 signifying the lowest confidence that it is a lens and 1 signifying the highest confidence that it is a lens.
 This ranking could have been a simple binary (0 or 1) classification  or it could have been a continuous range of numbers representing the probability of being a lens or it could have been a finite number of confidence levels.
@@
 
-Creating the mock images started with a cosmological N-body simulation.
-In this case it was the Millennium simulation \citep{2009MNRAS.398.1150B}.
-A catalog of dark matter halos within a light-cone is constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
+Creating the mock images started with a cosmological N-body simulation, in this case it was the Millennium simulation \citep{2009MNRAS.398.1150B}.
+A catalog of dark matter halos within a light-cone was constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
 The challenge sets were based on a 1.6 sq.deg.
@@
 The halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
-Within the code a Navarro, Frenk \& White (NFW) \citep{1996ApJ...462..563N} profile is fit to the three parameters given above.
-The halos are projected onto a series of lens planes, in this case 20,  and the deflection angle at any point in each plane can be calculated by summing the effects of all the halos with a hybrid tree method.
+Within this code a Navarro, Frenk \& White (NFW) \citep{1996ApJ...462..563N} profile is fit to the three parameters given above.
+The halos are projected onto a series of 20 lens planes  and the deflection angle at any point on each plane are calculated by summing the effects of all the halos with a hybrid tree method.
 In this way the halos have the mass, concentration and clustering properties from the N-body simulation, but within each strong lens the mass resolution is not limited by the original simulation, but follows the analytic mass profile.
@@
 
-To model the background sources that are lensed we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.
+To model the background objects that are lensed we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.
 This is the same set of images as used in \citet{2008AandA...482..403M,2010AandA...514A..93M}.
@@
 \begin{align}
-S(\theta,r) = e^{-r/R_h} \left( 1 + A \cos(N_a\theta + \phi_r \right) ~, \\
-\phi_r = \alpha\log(2 r/ R_h) + \phi_d \nonumber
+S(\theta,r) &= e^{-r/R_h} \left( 1 + A \cos(N_a\theta + \phi_r \right) ~, \\
+\phi_r &= \alpha\log(2 r/ R_h) + \phi_d \nonumber
 \end{align}
@@
 \end{align}
-where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002.
+where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002.   This is to create some deviation from a perfect S\'{e}rsic profile.
 
@@
 
-These images of the of foreground galaxies are not intended to reproduce the true population of galaxies, but only to be sufficiently irregular to make them difficult to fit to a simple analytic model that might make them very easy to distinguish from a foreground plus a lensed image.
+These images of the of foreground galaxies are not intended to reproduce the true population of galaxies, but only to be sufficiently irregular to make them difficult to fit to a simple analytic model that might make them unrealistically easy to distinguish from a foreground plus a lensed image.
 As will be discussed later, more realistic models will be needed in the future and are a subject of current investigation.
@@
 To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
-The surface brightness map in converted into a mass map within GLAMER by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
+The surface brightness map is converted into a mass map within GLAMER by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
 These mass maps are added to the NFW dark matter halos discussed before to make the total lens mass distribution.
@@
 The code is able to produce any combination of foreground galaxies, lensed image and noise that is desired.
-For the training set we provided an image of the total lens with noise, an image of the foreground galaxies with noise and image of the lensed background source without noise.
+For the training set,  an image of the total lens with noise, an image of the foreground galaxies with noise and image of the lensed background source without noise.
 For the test sets only the final images were provided to participants although all the information was stored for analysing the entries.
@@
 over a 48-hour period, at the rate of 5000/hr (NJ) and 2500/hr (AT). 
-The overall results, in terms of ROC curves, were very similar for 
+The overall results, in terms of ROC (see section \ref{sec:figure_of_merit}) curves, were very similar for 
 both observers. The space-based challenge produced areas of 0.800 and 
@@
 These methods seek to identify gravitationally lensed arcs and differentiate between them and 
-other objects such as spiral arms and edge on spirals using their width, color, curvature and other pre-selected criterion.
+other objects such as spiral arms and edge on spirals using their width, colour, curvature and other pre-selected criterion.
 
@@
 For the current SL challenge, arcfinder was tuned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.
-A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code as a linux  command line.
+A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code from the linux  command line.
 Arcfinder took a couple of hours to run on the entire dataset with some overheads due to the dataset format.
@@
 In the ground-based challenge, the model lens surface brightness profile is obtained by taking a rescaled version of the $i$-band image.
-The difference in color between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
-However, in order to avoid subtracting off the lensed images in systems with similar colors between lens source, we radially truncate the model lens surface brightness.
+The difference in colour between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
+However, in order to avoid subtracting off the lensed images in systems with similar colours between lens source, we radially truncate the model lens surface brightness.
 The model lens light is truncated at the smallest radius between the position where the surface brightness is comparable to the sky background level, or the position of a positive radial gradient in surface brightness, if detected.
 
-In the space-based challenge, it is not possible to separate lens and source based on color, because only data in one band is provided.
+In the space-based challenge, it is not possible to separate lens and source based on colour, because only data in one band is provided.
 The lens light model then is produced by taking a centrally-inverted image and then using the same truncation prescription used with ground-based data.
@@
 This method had previously been used in a static algorithm approach which assigned points according to the morphological properties of each image \citep[see][]{2014AandA...566A..63J}.
-Lensed-like objects displaying, for example, greater ellipticity and tangentiality were awarded more points.
+Lensed-like objects displaying, for example, greater ellipticity and tangential elongation were awarded more points.
 Since the SVM operates in a fixed dimensional space,  properties of individual objects were collapsed into a fixed set describing the mean and variance of morphological properties of all the objects within an image.
@@
 
-We detail the ALL team methodology in \citet{avestruz_etal17}. The
+The ALL team methodology is detailed in \citet{avestruz_etal17}. The
 pipeline was originally developed to automatically classify strong
-lenses in mock Hubble Space Telescope and Large Synoptic Sky Telescope
+lenses in mock HST and LSST
 data generated with code described in \citet{li_etal16} and
-\citet{collett_15}.  We apply the same exact steps for the single-band
+\citet{collett_15}.  We apply exactly the same steps for the single-band
 data for Euclid, but modify the feature extraction step for the
@@
 
-We use tools from {\em Scikit-learn} \citep{pedregosa_etal12} and
-perform minimal image preprocessing. First, we replace masked pixels
+Tools from {\em Scikit-learn} \citep{pedregosa_etal12} are used and
+some minimal image preprocessing is  performed. First, we replace masked pixels
 with the average of surrounding pixels, then enhance contrast in the
-image by taking the normalized log of pixel values.  The next step of
-our pipeline consists of a feature extraction stage, where our feature
+image by taking the normalized log of pixel values.  The next step 
+consists of a feature extraction stage, where our feature
 vector is a {\em histogram of oriented gradients} (HOG)
@@
 The notation
-$n \times n - n_c$ to denote a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps will be used.
+$n \times n - n_c$ will signify a convolutional layer using filters of size $n \times n$ pixels and outputting $n_c$ feature maps.
 In typical architectures, the size of these convolution filters is kept small (i.e.
@@
 
-For a binary classification problem such as the one involved in strong lens detection, the training is performed by optimizing the weights of the model as to minimize the \textit{binary cross-entropy} objective:
+For a binary classification problem such as the one involved in strong lens detection, the training is performed by optimizing the weights of the model so that it  minimizes the \textit{binary cross-entropy} :
 \begin{equation}
@@
 A common way to mitigate this is to use a regularisation scheme.
-For example, the Dropout regularisation technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}, were a certain percentage of the neurones and their connections are  randomly drop  from the neural network.
-This regularisation techniques reduces overfitting  by preventing complex co-adaptations of neurones on training data.
+For example, the Dropout regularisation technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}, were a certain percentage of the neurons and their connections are  randomly drop  from the neural network.
+This regularisation techniques reduces overfitting  by preventing complex co-adaptations of neurons on training data.
 
 Training multi-layer neural networks with gradient descent based approaches can be very challenging.
-One of the main reasons behind this is the effect of \textit{vanishing gradients}: it has been empirically observed that in many multi-layer neural networks the gradients in higher-level layers often become too small to be effective in gradient descent based optimisation.
+One of the main reasons behind this is the effect of \textit{vanishing gradients}: it has been empirically observed that in many multi-layer neural networks the gradients in higher-level (further from the image) layers often become too small to be effective in gradient descent based optimisation.
 Another difficulty is that the distribution of each layers inputs changes during training as the parameters of the previous layers change.
@@
 Batch normalisation layers \citep{batch_norm} are one way of addressing these challenges.
-Let the activities of a given neurone in a mini-batch be denoted by $x_1,\ldots,x_m$.
-The batch normalisation layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardise the neurone activities to make them zero mean with variance one, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
-Here $y_i$ denotes the output after applying the batch normalisation layer on the neurone with activities $x_i$.
+Let the activities of a given neuron in a mini-batch be denoted by $x_1,\ldots,x_m$.
+The batch normalisation layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardise the neuron activities to make them zero mean with variance one, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
+Here $y_i$ denotes the output after applying the batch normalisation layer on the neuron with activities $x_i$.
 It has been empirically demonstrated that batch normalisation can often accelerate the training procedure and help mitigate the above described challenges.
@@
 
-Prior to entering the first convolutional layer, input image data are rescaled and dynamic-range compressed with function $f(x) =
+Prior to entering the first convolutional layer, input image data are rescaled and the dynamic-range compressed with the function $f(x) =
 \mathrm{arcsinh} (10^{11} x)$, and bad pixels are simply set to 0.
@@
 Additionally, a small rotation with random angle $\theta$ is applied, involving bicubic image resampling.
-$\theta$ follows a Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma_{\theta}=5^{\circ}$.
+the angle $\theta$ is drawn from a Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma_{\theta}=5^{\circ}$.
 No attempt was made to generate and randomize bad pixel masks in the data augmentation process.
@@
 Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.
+
 The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$.
-The network is trained on a Titan-X ``Pascal'' nVidia GPU using the \textit{Adam} gradient-based optimizer during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
+The network is trained on a Titan-X ``Pascal'' nVidia GPU using the ADAM gradient-based optimizer during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
 Because of a lack of time, tests were limited to assessing the basic classification performance on a subset of the of 1,000 images/datacubes, using the 19,000 others for training.
@@
 For the training, the 20k provided images were split into two sets, 17k for training and 3k for validation.
-Each iteration of the gradient descent (more precisely \textit{Adam} \citep{adam}) minimizes the cross entropy, 
+Each iteration of the gradient descent (more precisely ADAM \citep{adam}) minimizes the cross entropy, 
 \begin{equation} \label{eq:xent}
@@
 
-Our algorithm for classification of strong lensed galaxies was developed as a CNN used for binary classification task.
-Our code was trained and tested on the space-based dataset (dataset 0) provided for the Ssrong lensing challenge, comprising 20,000 stamps of single band simulated galaxies.
-We used the full dataset in the proportion of 4/5 for training and 1/5 for validation.
+GAMOCLASS is a CNN based classifier.
+We used the full training data set in the proportion of 4/5 for training and 1/5 for validation.
 The training images were labelled with 1 if showing strong lensing and 0 otherwise.
@@
 The input image (101x101 pixels) is first processed by a 2D convolution layer with a 3x3 filter size, then subsampled by a 3x3 max pooling layer.
-Another two identical units follow, with a growing dimensionality of the output space (depth, i.e.output number of filters) in the convolution, for a total of 3 convolutional layers and 3 max pooling layers.
+Another two identical units follow, with a growing dimensionality of the output space %%(depth, i.e.
+output number of filters)
+ in the convolution, for a total of 3 convolutional layers and 3 max pooling layers.
 Each of these convolutional layers is followed by a rectified linear unit (ReLU) step.
-The output of these units is then processed through a single fully-connected layer follower by a dropout layer, and, finally, by a one-neuron fully connected layer with sigmoid activation function.
-For the classification problem we used the binary cross-entropy cost function and for weights updates we used an adaptive moment estimation (ADAM, \citealt{Kingma_2014}) optimization method.
-The use of the ADAM optimizer improves the learning rate, and previous tests with stochastic gradient descent (SGD) lead to worse results on the classification of the validation sample.
-In order to increase the size of the training set and make the model invariant to specific transformations, we perform several data augmentation steps:
-\begin{itemize}
-\item Random rotation of the image in the range [0, 180$\degree$], using a reflection fill mode to keep constant the size of the images.
-\item The images were randomly shifted of 0.02 times the total width of the image.
-\item Random horizontal and vertical flips of the images
-\end{itemize}
-During the training we initialize the weights of our model with random normal values and we warm up the training \citet{Huang_2016} of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) and a staring learning rate of  0.001.
-Then the network is trained using an early stopping method, and for a maximum number of 300 epochs.
-The early stopping method is an effective method to prevent overfitting and consists in stopping the training if a monitored quantity does not improve for a fixed number (called \textit{patience}) of training epochs.
+The output of these units is then processed through a single fully-connected layer follower by a dropout layer, and, finally, by a one-neuron fully connected layer with sigmoid activation functions.
+For the classification problem we used the binary cross-entropy cost function and found the weights  using ADAM \citep{Kingma_2014}) optimization method.
+The use of the ADAM optimizer improved the learning rate compared to tests with stochastic gradient descent (SGD).
+In order to increase the size of the training set and make the model invariant to specific transformations, we perform these data augmentation steps:
+1) Random rotation of the image in the range [0, 180$\degree$], using a reflection fill mode to keep constant the size of the images,
+2) The images were randomly shifted of 0.02 times the total width of the image,
+3) Random horizontal and vertical flips of the images.
+
+During the training we initialize the weights of our model with random normal values and we "warm up" the training of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) \citep{Huang_2016}  and then a staring learning rate of  0.001.
+When the network was trained using an early stopping method, and for a maximum number of 300 epochs.
+The early stopping method is an effective method of preventing overfitting and consists in stopping the training if a monitored quantity does not improve for a fixed number (called \textit{patience}) of training epochs.
 The quantity that we monitored was the \textit{accuracy} of the classification of the validation sample.
@@
 Our architecture converges with a classification accuracy of 91\% on the validation sample.
-We further evaluated the performance of our classifier calculating the ROC curve of the classifier, i.e.
+We further evaluated the performance of our classifier calculating the ROC (see section \ref{sec:figure_of_merit})  curve of the classifier, i.e.
 the True Positive Rate (TPR) against the False Positive Rate.
 As shown in Fig.
-\ref{Fig2_gamoclass}, we reach a TPR higher than the 90\% with a FPR < 8\%.
+\ref{Fig2_gamoclass}, we reached a TPR higher than the 90\% with a FPR < 8\%.
 
@@
       \includegraphics[width=1\columnwidth]{figures/Fig2_gamoclass.pdf} 
-  \caption{GAMOCLASS ROC on training data.}
+  \caption{GAMOCLASS ROC (see section \ref{sec:figure_of_merit})  on training data.}
  \label{Fig2_gamoclass}
@@
 
-The CBPF Arc Search Team (CAST) tested several arcfinding schemes using as core a CNN.
-For both the space-based and ground-based samples we carried out a simple preprocessing phase to enhance the objects in the images in order to check if they improve the automated arc detection with CNN.
+The CBPF Arc Search Team (CAST) tested several arcfinding schemes with CNNs at their core.  
+For both the space-based and ground-based samples we used a simple preprocessing phase to enhance the objects in the images to check to 
+see if this improved the automated arc detection with the CNN.
 We chose a contrast adjustment with $0.1\%$ pixel saturation and apply a low pass band Wiener filter \citep{wiener1964extrapolation} to reduce the effect of the noise.
@@
 This CNN can work either with one or three input images, representing greyscale and colour images.
-Therefore, we employed different strategies for the two samples available for the challenge, which involve combinations of the available bands running in one or more CNN, using or not the preprocessing, and combining the output with the aid of other machine learning methods.
-In each case we used the simulations made available for the challenge both to train and to validate the results and we used the area under the ROC to determine which combination of methods gives the best result.
+We employed different strategies for the two samples available for the challenge, which involve combinations of the available bands running in one or more CNN, using or not the preprocessing, and combining the output with the aid of other machine learning methods.
+In each case we used the simulations made available for the challenge both to train and to validate the results and we used the area under the ROC (see section \ref{sec:figure_of_merit}) to determine which combination of methods gives the best result.
 We selected 
@@
 $90\%$ of the images, chosen randomly, for the training and $10\%$ to validate.
-We repeated the process $10$ times to avoid bias due a specific choice of training/validation set and to define an uncertainty in our ROC.
-
-For the space-based data set we tested only two configurations: i) using the CNN straightforwardly for classification and ii) with the preprocessing described above. 
+We repeated the process $10$ times to avoid bias due a specific choice of training/validation set and to define an uncertainty in our ROC (see section \ref{sec:figure_of_merit}) .
+
+For the space-based data set we tested only two configurations: i) using the CNN straightforwardly for classification and ii) 
+with the preprocessing described above. 
 We found that the results, accounting for the uncertainties,  
-were clearly superior for the area under the ROC in the case 
-including the preprocessing. Therefore, this is the configuration we have used for the challenge.
-
-As mentioned above, the CNN used can take 3 color images as input.
-Thus, if we want to use the information on the $4$ available bands, we will have to either combine $2$ of the $4$ bands to end up with $3$ bands for a single RGB CNN (configuration I below) or we use multiple CNNs to use the information available (configuration II to VI below).
+were clearly superior in term of the area under the ROC with the preprocessing. Therefore, this is the configuration we used for the challenge entry.
+
+As mentioned above, the CNN we used can take 3 colour images as input.
+To use the information on the $4$ available bands, we needed to either combine $2$ of the $4$ bands to end up with $3$ bands for a single RGB CNN (configuration I below) or we use multiple CNNs (configuration II to VI below).
 To combine the outputs of several CNNs we use a Support Vector Machine \citep[hereafter SVM; see e.g., ][]{rebentrost2014quantum} also implemented in Matlab.
@@
 A more detailed description of each configuration tested is presented below:
-\begin{enumerate}
+\begin{enumerate}[label=\Roman*.]
 \item Combination of bands r and i with the average between bands u and g. Use one CNN for classification.
@@
 \item Use of CNN-activations (CNN feature maps) as inputs to a SVM classifier, using same combinations of bands of III. The output of each CNN is used as input to a SVM classifier.
-\item Use of wiener filter and contrast adjustment on each band, then using the resulting images in the same architecture as in (iii). 
+\item Use of wiener filter and contrast adjustment on each band, then using the resulting images in the same architecture as in (III). 
 \end{enumerate}
 
-For the ground based cases three configurations with highest area under ROC were III,IV and VI.
+For the ground based cases three configurations with highest area under ROC were III, IV and VI.
 Although the areas are very similar between IV and VI the last one is superior in the low fake positives end.
@@
 
-The area under ROC, in both space based configurations were, in general, smaller than in the multi-band case, which suggests how the CNNs are sensitive to color information to find Strong Lensing.
-Particularly,  ground base configuration II used one CNN per band thus not considering color information and has the similar area under ROC as our best single band configuration.
+The area under ROC, in both space based configurations were, in general, smaller than in the multi-band case, which suggests how the CNNs are sensitive to colour information to find strong lensing.
+Particularly,  ground base configuration II used one CNN per band and has the similar area under ROC as our best single band configuration.
 
@@
 However, resnet differ from CNNs by the introduction of so-called shortcut connections bypassing blocks of several convolutional layers.
-As a result, instead of learning the full mapping from their input to their output these residual blocks only have to  learn the difference to the identity.
+As a result, instead of learning the full mapping from their input to their output these residual blocks only have to  learn the difference to the identity transformation.
 In practice, this difference allows residual networks to be trained even for very deep models.
@@
 Training was performed using the ADAM optimizer with mini-batches of size 128 over 120 epochs, with an initial learning rate of $\alpha=0.001$, subsequently decreased by a factor 10 every 40 epochs.
-This multi-step training procedure is important to progressively refine the model parameters of the model and achieve our final accuracy.
-
-We adopt a minimal pre-processing strategy for the input images, removing the mean image and normalising by the noise standard deviation $\sigma$ in each band, these statistic being evaluated over the whole training set.
+This multi-step training procedure is important to progressively refine the model parameters and achieve our final accuracy.
+
+We adopt a minimal pre-processing strategy for the input images, removing the mean image and normalising by the noise standard deviation $\sigma$ in each band, this statistic being evaluated over the whole training set.
 In addition, we clip extreme values above $250 \,\sigma$ to limit the dynamic range of the input.
@@
 
-Given the rules of the challenge, we had to submit a prediction for each source in the test-set as a single number: a number in the interval [0,1] or either a 0 or a 1.
-For satisfying this requirement we had to collapse one of the class into another: we provided a 0 when a source is classified as a \textit{non-lens} and a 1 when is classified as a \textit{clear lens} or as a \textit{dubious lens}.
-This choice did not allow to build a continuous ROC curve but only a binary one.
-The final submission was produced averaging the values of the predictions from three CNNs with the same architecture.
+%Given the rules of the challenge, we had to submit a prediction for each source in the test-set as a single number: a number in the interval [0,1] or either a 0 or a 1.
+For satisfying this requirement we had to
 
@@
 The output layer is composed by three units.
-Each units gives in output a number between 0 and 1 that represents, respectively, the probability of being a \textit{non-lens}, a \textit{dubious lens}, a \textit{certain lens}.
+Each units gives is output a number between 0 and 1 that represents, respectively, the probability of being a \textit{non-lens}, a \textit{dubious lens}, a \textit{certain lens}.
+We then collapsed one of the classes into another to give a binary classification : 0 when a source is classified as a \textit{non-lens} and a 1 when is classified as a \textit{clear lens} or as a \textit{dubious lens}.
+This choice did not allow for building  a continuous ROC (see section \ref{sec:figure_of_merit})  curve but only a binary one.
+The final submission was produced by averaging the values of the predictions from three CNNs with the same architecture.
 
 {\bf Preprocessing}
-The training fits files are preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
-Due to memory limitations we down-sampled the images to 84 by 84 pixels. Most likely, this leads to a worse classification accuracy than using the original image resolution.
+The training image files were preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
+Due to memory limitations we down-sampled the images to 84 by 84 pixels. 
+%Most likely, this leads to a worse classification accuracy than using the original image resolution.
 We augmented the training images in the following way: i) random rotation of 90, 180 or 270 degrees; ii) random shift in both $x$ and $y$ direction between -2 and +2 pixels; iii) $50\%$ probability of horizontally flipping the image.
@@
 where the $t_j$ and $p_j$ are respectively the label and the prediction for the class $j$. 
-The minimization is done via mini-batch stochastic gradient descent with \textit{Adam} updates \citep{Kingma_2014}.
+The minimization is done via mini-batch stochastic gradient descent with ADAM updates \citep{Kingma_2014}.
 We used a batch size of 56 and performed  46000 gradient updates.
 We started with a learning rate of $4 \times 10^{-4}$, decrease it to $4 \times 10^{-5}$ after 35000 updates and to $4 \times 10^{-6}$ after 43000 updates.
-The initial values of the biases are set to zero and the weights of each filter are initialized from a random normal distribution with variance ${2/n}$ where $n$ is the number of inputs of the unit \citep{He2015a}.
+%The initial values of the biases are set to zero and 
+The weights of each filter are initialized from a random normal distribution with variance ${2/n}$ where $n$ is the number of inputs of the unit  and a mean of zero \citep{He2015a}.  
 We use L2-norm regularization with $\lambda= 9 \times 10^{-3}$.
@@
 Our lens finder included wavelet prefiltering.
-The image was convolved with the Mallat wavelet with a kernel size of 4 in both the horizontal and vertical directions, then combined and compared to the original image to make the input image; $input image = \sqrt[]{H^{2}+V^{2}}$.
-This prefiltering was performed to emphasise the edges in the images, improving the results from the Convolutional Neural Network (CNN).
-The CNN had 2 convolution layers each containing 32 $3\times3$ filters, incorporating dropout and max-pooling, and then 3 dense fully-connected layers to classify each image.
+The image was convolved with the Mallat wavelet with a kernel size of 4 in both the horizontal and vertical directions, then combined and compared to the original image to make the input image;  input image $= \sqrt[]{H^{2}+V^{2}}$.
+This prefiltering was performed to emphasise the edges in the images.
+It as found to improve the results compared to the CNN without this pre-filter.
+The CNN had 2 convolution layers each containing  $3\times3 - 32$ filters, incorporating dropout and max-pooling, and then 3 dense fully-connected layers to classify each image.
 The network was trained on 18000 of the 20000 training images; training took 15 epochs and was completed once the validation loss was minimised.
@@
 In deriving a good figure of merit for evaluating lens finding algorithms one needs to take into account the particular nature of this problem.
-The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or {\bf ROC} curve.
+The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or  ROC (see section \ref{sec:figure_of_merit}) curve.
 This is a plot of the true positive rate (TPR) and the false positive rate (FPR).
@@
 We do not impose a definitive arc/ring magnification, brightness or surface brightness limit for a system to be considered a lens because we
-want to include these objects because we want to test the limits of the classifiers.
-As we will see, if you restrict your objectives to detecting only lensed images with surface brightness above threshold, for example, the "best" algorithm might change and the TPR will change.
+want to include these "barely lensed" objects because we want to test the limits of the classifiers.
+As we will see, if you restrict your objectives to detecting only lensed images with surface brightness above some threshold, for example, the "best" algorithm might change and the TPR will change.
 For this reason we plot the AUROC, TPR$_0$ and TPR$_{10}$ as a function of several variables for all the entries.
@@
 
-\subsection{Performance of methods}
+\subsection{Performance of the methods}
 \label{sec:performance}
@@
 Note that ROC curves for the ground-based challenge (figure~\ref{fig:roc_ground}) are uniformly better than those for the space-based challenge (figure~\ref{fig:roc_space}).
-This is because of the importance of color information in discriminating lensed arcs from pieces of the foreground lens galaxy.
+This is because of the importance of colour information in discriminating lensed arcs from pieces of the foreground lens galaxy.
 
@@
 When deriving the distribution of Einstein radii from data these curves would need to be used to correct for detection bias.
-It can be seen the CMU-DeepLens-ResNet, Manchester1, Manchester SVM and GAMOCLASS obtain significantly higher TPR$_0$ and  TPR$_{10}$ for larger Einstein radii.
+It can be seen that CMU-DeepLens-ResNet, Manchester1, Manchester SVM and GAMOCLASS obtain significantly higher TPR$_0$ and  TPR$_{10}$ for larger Einstein radii.
 Manchester1 is the human inspection method.
 In some cases the TPR$_0$'s are above 50\% of the lenses that meet this criterion.
-Remember that many of the so called lenses are very dim or there is no significant arc because of the source position is well outside the caustic.
-If an additional require was placed on the definition of a lens, such as the brightness of the arc being above a threshold, the TPRs would go up.
-
-Figures~\ref{fig:flux_space} and \ref{fig:flux_ground} are the same except that the flux in the lensed image is used as the threshold.
+Remember that many of the so called lenses are very dim or there is no significant arc because the source position is well outside the caustic.
+If an additional requirement was placed on the definition of a lens, such as the brightness of the arc being above a threshold, the TPRs would go up.
+
+Figures~\ref{fig:flux_space} and \ref{fig:flux_ground} are the same except that the fluxes in the lensed image is used as the threshold.
 We count only the flux in pixels with flux over one $\sigma$ of the background.
@@
 
-The two human inspector, NJ and AT, got significantly different scores on the ground based test set with individual AUROCs of 0.88 and 0.902 and TPR$_{10}$s of 0.01 and 0.06 respectively.
+The two human inspectors, NJ and AT, got significantly different scores on the ground based test set with individual AUROCs of 0.88 and 0.902 and TPR$_{10}$s of 0.01 and 0.06 respectively.
 They did not inspect the same images however so differences cannot be considered conclusive, but it does suggest that different inspectors will have different detection efficiencies and biases.

### 2018-12-04 response.tex
Edit.

\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{R.B. Metcalf}
\begin{document}
Referee Report

{\bf 
Overall, this work is an important milestone towards exploring the usefulness of strong gravitational lenses in many applications in astrophysics, and after significant copy-editing and clarifications should be published.  I particularly agree that the emphasis on attempting to understand the most successful lens-candidate identification approaches and on the role of false positives is important.

The submitted manuscript is full of incorrectly assigned or compiled references.  The Sections’ organizational structure is incomplete and mis-referenced. Furthermore, the paper seems not to have been proof-read carefully as there are many minor grammatical and typesetting errors that are avoidable and distracting.  This includes typos within equations.  All of these must be corrected and scrupulously proof-read for re-submission.

The long-term goal of this collaboration of maturing algorithms for delivering automated gravitational lens detection across datasets as diverse as Euclid, LSST, and SKA, is timely and an important effort for the community.  Developing such flexible infrastructure is going to be challenging, and as the authors themselves point out, the realism of the simulated datasets will be an essential element. To that end, it makes sense that the present work gives a taste of what this may look like, by considering two parallel efforts in tandem, focusing on the single-band space-based Euclid and the multiple-band ground-based Kilo-Degree Survey (KiDS) datasets. 
}

{\bf
The paper seems to have been written towards an audience that is already closely familiar with gravitational lensing topics, which misses an opportunity to have a broader impact. For example, in stating “These take the form of multiple images of a quasar and Einstein rings surrounding a galaxy and of highly distorted arcs seen through galaxy groups and clusters.” conflates several lens geometries and situations in a way that e.g. a student would need to disentangle. 
}

The paper is generally targeted toward astronomers, but the point is taken.  The first paragraph of the introduction has been expanded to better describe gravitational lensing.  We do not wish to take up to much space describing the whole field when this can be read about elsewhere.

{\bf
In the abstract (but nowhere else it seems) there is a summary result that “several methods are able to identify upwards of half the lenses”.  It seems that this is a statement of significance or interpretation and so it seems incomplete.  Or is it simply a statement of fact? 
}

This is referred to in paragraph 4 of section 6.2.  It is a conclusion drawn from figures 9 and 10.  We are not sure what the referee is asking here.

{\bf
What was the rationale for the 20.000 size of the training sets and the choice of the 101x101 pixels? 
}

No particularly rational reason.  The 101x101 pixels originally was the size of some early stage cutouts from KIDS.  20,000 was a convenient number for processing time and storage reasons.  We have added a comment on this.

{\bf
The challenge dataset is stated as having 100.000 objects, and in one place only there is a reference that in “the case of the multi-band ground-based set this was 400,000 images.”  There’s never another reference to the 400.000, however, so this setup description is confusing or incomplete. 
}

It is clearly stated several times that there were 4 bands in the ground based set which makes 400,000 images for 100,000 objects.

{\bf
Understanding how the simulation set was prepared is significant for understanding the entire project and its results.  The Millennium simulation was used to identify galaxies.  The generally available Millennium catalog is at redshift zero, rather than at the various lens-plane redshifts given.  If some epoch-matching was made, please explain this, or justify the use of redshift-zero galaxy properties.  I do note a description of the adopted catalog being projected to a series of twenty lens planes with the total deflection calculated through a sum, but remain unclear about the process.  I also do not follow what “A NFW profile is fit to the [total mass, size, and half mass radius] parameters” actually means for this application.  As galaxies identified within Millennium were used, these are generally sub-critical to strong lensing, unless an additional central baryonic steepening has been applied. Please clarify.  
}

We did not use just the zero redshift galaxies.  The details of the light-cone construction is given in Overzier, et al. 2013 MNRAS 428, 778.  They used a semi-analytic model to populate the halos with galaxies.  The galaxies are accounted for in both light (section 3 paragraph 8 through 11, formerly 7 through 10) and mass 
(section 3 paragraphs 12 and 13, formerly 11-12).  We have tried to make this clearer  by changing the first paragraph of the section.

{\bf
In the Introduction’s description of imaging searches for lenses, references to past work is quite incomplete, and it would be appreciated to have these developed further.  For example, while there is a passing reference to the Marshall et al HAGGLeS work, this is arguably a significant precursor to the present paper so it is surprising that it is not discussed at all.  I think that giving depth of context to readers is critical for this paper. 
}

We have added a little more discussion of this paper in the introduction and conclusion.

{\bf
The dismissal of spectroscopic surveys for lenses seems flippant in addition to being incomplete. There are several spectroscopic lens projects after SLACS, and if the spectroscopic approach does return “well defined and pure” samples, it seems that at least some reference to the potential of DESI and PFS is expected to be in comparison to imaging surveys. 
}

We added a reference to these instruments in the introduction.

{\bf
It is good to see arc finders included in this challenge, though there is scant quantitative information about how the analysis was set up with these techniques to be able to judge or comment on them. In a comment related to the CNNs’ below, what are development or advancement areas that the Arc Finder community already knew, or learned based on this work, that will be addressed in the future?  
}

?????

{\bf
The Machine Learning / Support Vector Machine approaches seem clear enough, though these sections also include spare or undefined information.  I happen to know that AUC means area under a curve and how it pertains to the ROC exercise at hand, but this is quite mysterious and incomplete as presented. This can and must be improved significantly in the re-editing of the manuscript.}

Yes, unfortunately the ROC is not defined until section 6.1.  We have put in a reference to this section so that the reader knows where to find the definition if they don't know it.

{\bf Incidentally, the “AUC of 0.88 for the space set and 0.95 for the ground set” stated in section 5.3.1 are different numbers from what are given in Tables 3 \& 4, further casting doubt on the validation of all results here.  
}

That is the AUC on the training set not the challenge set.

{\bf
The Convolutional Neural Networks general description is well done.  This is a complex and rich topic that is certainly still developing within astrophysics, and this section gives enough sense of the uncertainty and nuance behind exactly how the network methodologies may be set up for particular analyses.  Note that “neurones” are “neurons”, suggesting that additional care is needed in verifying the presentation in this section.   
}

"neurones" is the British spelling.  The spelling has been standardized to "neurons" and "neuron".

{\bf
How the training sets are handled by each CNN approach is very interesting reading, and there is a great deal to digest about the choices for convolution layers, neuron numbers, and classification metrics.  The variety of how rotation/reflection/spatial transformations of the training sets are treated is interesting, as is the varied use of multiple bands’ images or not.  Given the focus on CNN methods, the reader may expect some greater discussion after the lens-finding conclusions on what areas of advancement or improvement emerged from this exercise, even at high level.   This is offered as an observation.  
}

?????

{\bf
In fact, some of the algorithm descriptions are rather spare in their details, and so difficult to judge or intercompare.  The reader (and this referee) is forced to take much at face value, which perhaps is acceptable for the scope of an “overview” report such as this.  It is a little disappointing, all the same.  A uniform template in the structure of each contributor’s report could have helped mitigate that, so that similar context or informational questions would at least have a chance of being reported.  The additional descriptive detail given by some of the contributors, in particular LASTRO, GAMOCLASS, and CAST are appreciated. 
}

??????

{\bf
The receiver operating characteristic (ROC) curve technique is referred to via its acronym in many places in the manuscript without explanation or definition, and even in the Results Section the description is 
}

Added this.

{\bf
There is a brief discussion about rare “abnormal” objects including merging and irregular galaxies potentially being “the greatest challenge” for a full realistic application. 
An accurate representation of these objects is promised for future work. Can the authors elaborate how this may be done? 
}

We are working on this.  There are several approaches we are considering.  They would 
involve randomizing existing images.

{\bf
This referee agrees forcefully with the statement in the Conclusions \& Discussion section that application of SVM and CNN methods have “some danger of over-fitting to the training set”, and that there is enormous weight on how realistic the simulations are.  This discussion draws no conclusions, however, about how confident the community may reasonable expect to become with this or future work, and how to get there.  A brief discussion of this should be included.  
}

This is a good question and one I don't think was fully answered by the challenge.  You might have 
thought that visual inspection is the gold standard, but it seems that you can do better.  But maybe 
that is just over-fitting.  It might be that unsupervised learning techniques have a part to play.

A little discussion has been added to the conclusion, but any more would be pure speculation.

{\bf
The overall conclusion or claim that ground-based multi-band data are more successful than low SNR single-band space-based data is a quite strong and even disturbing statement.  The way it is cast here, it seems to imply that we should not bother with space-based (Euclid) data at all for detecting strong lenses.  Is that the ultimate message the authors wish to convey to their audience?  Are there factors of solid angle, depth, or data stability and robustness that may be factors in the near future if not just at present?  The final statement on the importance of colour information for Euclid, whether from the infrared bands that were not presently included or by the combination with other ground-based data, is well done. Is future work planned that will include these dimensions? 
}

It is true that mono-band space based data might not be a big step up for this purpose, but 
multi-band data exists and even if it is of lower resolution, as it will be for Euclid, it should 
make space based searches more successful than ground based ones.  Yes, we are fallowing 
up with Euclid UV simulations.  We have tried to change this impression by adding a note to the abstract.

\end{document}

### 2018-12-04 paper.tex
Edit.

@@
 This is significantly better than direct inspection by humans was able to do.
-Having multi-band, ground based data is found to be better for this purpose than single-band space based data with lower noise and higher resolution, suggesting that multi colours data is crucial additional.
+Having multi-band, ground based data is found to be better for this purpose than single-band space based data with lower noise and higher resolution, suggesting that multi colour data is crucial.
+Multi-band space based data will be superior to ground based data.
 The most difficult challenge for a lens finder is differentiating between rare irregular and ring-like face-on galaxies and true gravitational lenses.
@@
 Strong gravitational lenses are rare cases where a distant galaxy or quasar is aligned so closely with a foreground galaxy or cluster of galaxies  that the gravitational field of the foreground object creates multiple, highly distorted images of the background object.
-These take the form of multiple images of a quasar and Einstein rings surrounding a galaxy and of highly distorted arcs seen through galaxy groups and clusters.
-The first strong lens was discovered in 1979 by \citet{1979Natur.279..381W} and since then many valuable scientific uses have been found for them.
+The first strong lens was discovered in 1979 by \citet{1979Natur.279..381W} and since then several hundred of them have been found.
+When the lens is an individual galaxy and the source a quasar, there are two, four or five distinct images of the source.
+The time-delay between images,  the magnification ratios between images and the image positions can all be used to model the mass distribution of the lens and measure cosmological parameters.
+When the lens is a cluster of galaxies the images of background galaxies are multiplied and distorted into many thin arcs.
+When the lens is an individual galaxy and the background source also a galaxy, the lensed images can take the form of a partial or complete ring seen around or through the lens galaxy, an {\it Einstein ring}.
+
+Strong lenses have to date provided very valuable scientific information.
 They have been used to study how dark matter is distributed in galaxies and clusters \citep[e.g.][]{1991ApJ...373..354K,2001ApJ...554.1216C,2002ApJ...568L...5K,2003ApJ...587..143R,2003ApJ...583..606K,2005MNRAS.360.1333W,2005ApJ...623...31D,2009MNRAS.392..945V,2016MNRAS.463.3115T} and  to measure the Hubble constant and other cosmological parameters
@@
 Through microlensing they have been used to study the structure of quasars \citep{2008ApJ...689..755M,2008ApJ...673...34P,2011ApJ...729...34B}.
-To access this wealth of information the first step is to find the lenses.
+To expand on this wealth of information we must study more lenses.
+The first step in doing this is to find more of these rare objects.
 
@@
 Notably this was done in the Sloan Lens ACS (SLACS) survey, producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006MNRAS.369.1521W,2006ApJ...638..703B,2012ApJ...744...41B,2015MNRAS.449.3441S}.
+New spectrographs such as the Dark Energy Spectroscopic Instrument  (DESI) \citep{2016arXiv161100036D} and Subaru Prime Focus Spectrograph (PFS) \citep{2016SPIE.9908E..1MT} have the potential to expanding spectroscopic lens searches greatly.
 However, spectroscopy is telescope-time consuming and for the foreseeable future we are not likely to have spectroscopic surveys that cover anywhere near the number of objects as the planned imaging surveys.
@@
 features \citep{2006astro.ph..6757A,2007AandA...472..341S, 2017AandA...597A.135B} and rings 
-\citep{2014ApJ...785..144G,2014AandA...566A..63J}.
-They have been applied to survey data and found of order 200 lenses \citep{2007AandA...461..813C,2012ApJ...749...38M,2016AandA...592A..75P}.
-Another approach has been to use a lens modeling code to fit a model to all the candidates and pick out the ones that fit the model well \citep{2009ApJ...694..924M,2017arXiv170401585S}.
+\citep{2014ApJ...785..144G,2014AandA...566A..63J}.  They have been applied to survey data and found of order 200 lenses \citep{2007AandA...461..813C,2012ApJ...749...38M,2016AandA...592A..75P}.
+
+\cite{2009ApJ...694..924M} pioneered an automated technique for finding Einstein ring type lenses that uses a lens modeling code to fit a model to all candidates and picks out the ones that fit the model well \citep[see also][]{2017arXiv170401585S}.
+This approach has the attractive feature that it distinguishes lenses from non-lenses by their similarity to what we expect a lens to look like and priors can be put on the model parameters that are physically motivated, unlike the next category of finders below.
+Challenges arise in making the modeling fast enough and automatic enough to handle large
+data sets while allowing it to be flexible enough to find unusual lens configurations.  The YattaLens entrant to this challenge was of this type.
 
@@
 Each image was $101\times101$ pixels.
+These specifications were not of particular significance except that the image size would encompass almost all galaxy-galaxy lenses and that the number of images (including ones with and without noise, lens and source) was not too large.
 The participants were free to download these sets and train their algorithms on them.
@@
 
-Creating the mock images started with a cosmological N-body simulation, in this case it was the Millennium simulation \citep{2009MNRAS.398.1150B}.
-A catalog of dark matter halos within a light-cone was constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
+Creating the mock images started with a cosmological N-body simulation, in this case the Millennium simulation \citep{2009MNRAS.398.1150B}.
+A catalog of dark matter halos and galaxies  within a light-cone was constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
 The challenge sets were based on a 1.6 sq.deg.
-light cone extending out to redshift $z=6$.
+light cone extending out to redshift $z=6$ using all the simulation snapshots.
 The halos are found with a friends-of-friends algorithm and characterised by a total mass, size and half mass radius.
 They include subhalos of larger halos.
-The halo catalog is read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
-Within this code a Navarro, Frenk \& White (NFW) \citep{1996ApJ...462..563N} profile is fit to the three parameters given above.
+The halos where populated with galaxies based on their merger history using the semi-analytic model  (SAM) of \cite{2011MNRAS.413..101G}.
+
+The halo catalog were read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
+Within this code a Navarro, Frenk \& White (NFW) \citep{1996ApJ...462..563N} profile is fit to the three parameters given above to represent the dark matter component of the lens.
 The halos are projected onto a series of 20 lens planes  and the deflection angle at any point on each plane are calculated by summing the effects of all the halos with a hybrid tree method.
@@
 We used brute-force optimisation methods to select a non-linear SVM containing radial basis function (RBF) kernel and tuned a small set of regularisation hyperparameters to achieve good generalisation performance.
-During training and testing, our final and best scores achieved when testing on the lens finding challenge training data were an AUC of 0.88 for the space set and 0.95 for the ground set.
+During training and testing, our final and best scores achieved when testing on the  training data were an area under the ROC curve of 0.88 for the space set and 0.95 for the ground set.
 Classification was performed using a modest desktop PC.
@@
 In deriving a good figure of merit for evaluating lens finding algorithms one needs to take into account the particular nature of this problem.
-The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or  ROC (see section \ref{sec:figure_of_merit}) curve.
+The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or  ROC (receiver operating characteristic) curve.
 This is a plot of the true positive rate (TPR) and the false positive rate (FPR).
@@
 Accurately reproducing these objects will be an objective of future work.
+This might be done by including more real images in the challenge or images based on real images with some random elements added.
 
@@
 This has yet to be shown however.
-The confidence one will have in these machine learning methods is really based on the confidence one has in the realism of the simulations.
+Methods based on fitting with a lens modeling code \citep{2009ApJ...694..924M,2017arXiv170401585S} might also help to mitigate this problem.
+The confidence one will have in the machine learning methods is really limited by the confidence one has in the realism of the simulations.
+It might be useful in the future to have a challenge without a training set.
+This might more clearly reveal the presence of over-fitting.
+It would also be useful to include more real images or images more closely based on real images.
 

### 2019-01-14 response.tex
Update on Overleaf.
Edit

@@
 All of these must be corrected and scrupulously proof-read for re-submission.
+}
 
+We acknowledge the poor proof reading of the draft.
+There was some miscommunication about responsibilities between the authors.
+We have edited the text more carefully and made many small corrections corrections.
+
+{\bf
 The long-term goal of this collaboration of maturing algorithms for delivering automated gravitational lens detection across datasets as diverse as Euclid, LSST, and SKA, is timely and an important effort for the community.
@@
 
-This is referred to in paragraph 4 of section 6.2.  It is a conclusion drawn from figures 9 and 10.  We are not sure what the referee is asking here.
+This is referred to in paragraph 4 of section 6.2.
+It is a conclusion drawn from figures 9 and 10.
+It is also mentioned in the first paragraph of the conclusion where we added a reference to the figures it is based on.
 
@@
 The galaxies are accounted for in both light (section 3 paragraph 8 through 11, formerly 7 through 10) and mass
-(section 3 paragraphs 12 and 13, formerly 11-12).  We have tried to make this clearer  by changing the first paragraph of the section.
+(section 3 paragraphs 12 and 13, formerly 11-12).
+We have tried to make this clearer  by changing the first paragraph of the section 3.
+The NFW profile has three free parameters which can be taken to be the mass, radius and concentration.
+Since many of the halos are substructures the size is not always the virial radius.
+This parameters are fit so that the mass, size and half mass radius are the same as the ones given in the halo catalog.
 
@@
 This is offered as an observation.
-}
 
-?????
-
-{\bf
 In fact, some of the algorithm descriptions are rather spare in their details, and so difficult to judge or intercompare.
@@
 
-??????
+Yes, this was difficult to pinpoint.
+The very large number of possible CNN configurations and the lack of overlaps between the methods tested makes it hard to conclude what specifically about architecture of one CNN makes it better than another.
+The performance of a CNN will also depend critically on the nature of the data.
+The best CNN for one data set might not be the best one for another data set so they will need to be developed for specific surveys using real data in the training process.
+This study can be
+viewed as an exploration of how properties of the data (noise, pixel size, psf, etc.) and the data simulations affect lens finding rather than a systematic study of how to build the best lens finder.
 

### 2019-01-14 paper.tex
Update on Overleaf.
Edit

@@
 \and
+F. Courbin \inst{12}
+\and
 Andrew Davies \inst{22}
@@
 To achieve these objectives automated methods must be developed.
-Because gravitational lenses are rare, objects reducing false positives will be particularly important.
+Because gravitational lenses are rare objects, reducing false positives will be particularly important.
 We present a description and results of an open gravitational lens finding challenge.
@@
 Multi-band space based data will be superior to ground based data.
-The most difficult challenge for a lens finder is differentiating between rare irregular and ring-like face-on galaxies and true gravitational lenses.
+The most difficult challenge for a lens finder is differentiating between rare, irregular and ring-like face-on galaxies and true gravitational lenses.
 The degree to which the efficiency and biases of lens finders can be quantified largely depends on the realism of the simulated data on which the finders are trained.
@@
 
-The Square Kilometer Array (SKA)\footnote{http://skatelescope.org/}, the Large Synoptic Survey Telescope (LSST)\footnote{https://www.lsst.org/} and the Euclid space telescope\footnote{https://www.euclid-ec.org/} are expected to increase the number of potential lenses by orders of magnitude \citep{collett_15,euclidSLWGwhitepaper,2015aska.confE..84M,2010MNRAS.405.2579O}.
+So far, less than a thousand lenses have been found in total across many heterogeneous data sets.
+The Square Kilometer Array (SKA)\footnote{http://skatelescope.org/}, the Large Synoptic Survey Telescope (LSST)\footnote{https://www.lsst.org/} and the Euclid space telescope\footnote{https://www.euclid-ec.org/} are expected to increase the number of potential lenses by orders of magnitude \citep{2010MNRAS.405.2579O,collett_15,euclidSLWGwhitepaper,2015aska.confE..84M}.
 For example it is estimated that there will be approximately 200,000 observable galaxy-galaxy lenses in the Euclid data set among tens of billions of potential objects.
-So far, less than a thousand lenses have been found in total across many heterogeneous data sets.
 These surveys will bring a new era for strong lensing where large relatively well defined samples of lenses will be possible.
@@
 Notably this was done in the Sloan Lens ACS (SLACS) survey, producing a relatively well defined and pure sample of Einstein ring lenses \citep{2006MNRAS.369.1521W,2006ApJ...638..703B,2012ApJ...744...41B,2015MNRAS.449.3441S}.
-New spectrographs such as the Dark Energy Spectroscopic Instrument  (DESI) \citep{2016arXiv161100036D} and Subaru Prime Focus Spectrograph (PFS) \citep{2016SPIE.9908E..1MT} have the potential to expanding spectroscopic lens searches greatly.
+New spectrographs such as the Dark Energy Spectroscopic Instrument  (DESI) \citep{2016arXiv161100036D} and Subaru Prime Focus Spectrograph (PFS) \citep{2016SPIE.9908E..1MT} have the potential to greatly expand spectroscopic lens searches.
 However, spectroscopy is telescope-time consuming and for the foreseeable future we are not likely to have spectroscopic surveys that cover anywhere near the number of objects as the planned imaging surveys.
 
-Some automated algorithms have been developed in the past to detect lenses in images.  These have been designed to detect arc-like 
+Some automated algorithms have been developed in the past to detect lenses by their morphology in images.  These have been designed to detect arc-like 
 features \citep{2006astro.ph..6757A,2007AandA...472..341S, 2017AandA...597A.135B} and rings 
@@
 This approach has the attractive feature that it distinguishes lenses from non-lenses by their similarity to what we expect a lens to look like and priors can be put on the model parameters that are physically motivated, unlike the next category of finders below.
-Challenges arise in making the modeling fast enough and automatic enough to handle large
+Challenges arise in making the modeling fast and automatic enough to handle large
 data sets while allowing it to be flexible enough to find unusual lens configurations.  The YattaLens entrant to this challenge was of this type.
 
-More recently, machine learning techniques that have become widely used in the fields of computer image processing and artificial intelligence have been applied to this problem and others in astronomy; in particular, artificial neural networks (ANNs), support vector machines (SVM), and logistic regression.
+More recently, machine learning techniques that have become widely used in the fields of computer image processing and artificial intelligence have been applied to this  and other problems in astronomy; in particular, artificial neural networks (ANNs), support vector machines (SVM), and logistic regression.
 SVMs and some logistic regression methods belong to the family of reproducing kernel Hilbert Space methods.
 They learn from a training set how to classify objects using features given by predefined kernel functions.
-ANNs (and a popular variant convolutional neural networks (CNNs) ) are even more flexible in learn directly from a training set which features are the most important for distinguishing categories of objects.
+ANNs , and a popular variant convolutional neural networks (CNNs),  are even more flexible in learning directly from a training set which features are the most important for distinguishing categories of objects.
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy, these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017MNRAS.471..167J,2017arXiv170207675P,2017MNRAS.465.4325O,2017AandA...597A.135B,hartley2017support}.
-
-Given the future of this field with large amounts of data coming soon and many new ideas emerging, it is timely to stage a series of challenges to stimulate new work, determine what can realistically be done in lens finding and get a better idea of the strengths and weaknesses to different methods.
+In astronomy, these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017arXiv170207675P,2017MNRAS.471..167J,2017MNRAS.465.4325O,2017AandA...597A.135B,hartley2017support}.
+
+Given the future of this field, with large amounts of data coming soon and many new ideas emerging, it is timely to stage a series of challenges to stimulate new work, determine what can realistically be done in lens finding and get a better idea of the strengths and weaknesses of different methods.
 The long term goal is to get a set of algorithms that can handle Euclid, LSST or SKA data sets and produce high purity and high completeness lens samples with well defined efficiency or selection.
@@
 Each image was $101\times101$ pixels.
-These specifications were not of particular significance except that the image size would encompass almost all galaxy-galaxy lenses and that the number of images (including ones with and without noise, lens and source) was not too large.
+These specifications were not of particular significance except that the image size would encompass almost all galaxy-galaxy lenses and that the number of images (including ones with and without noise, lens and source which were needed for later analysis) was not too large.
 The participants were free to download these sets and train their algorithms on them.
@@
 In the case of the multi-band ground-based set this was 400,000 images.
-The participants had 48 hours to upload a classification of all candidates consisting of a score between 0 and 1 0 signifying the lowest confidence that it is a lens and 1 signifying the highest confidence that it is a lens.
+The participants had 48 hours to upload a classification of all candidates consisting of a score between 0 and 1, 0 signifying the lowest confidence that it is a lens and 1 signifying the highest.
 This ranking could have been a simple binary (0 or 1) classification  or it could have been a continuous range of numbers representing the probability of being a lens or it could have been a finite number of confidence levels.
@@
 light cone extending out to redshift $z=6$ using all the simulation snapshots.
-The halos are found with a friends-of-friends algorithm and characterised by a total mass, size and half mass radius.
-They include subhalos of larger halos.
+The halos were found with a friends-of-friends algorithm and characterised by a total mass, size and half mass radius.
+They included subhalos of larger halos.
 The halos where populated with galaxies based on their merger history using the semi-analytic model  (SAM) of \cite{2011MNRAS.413..101G}.
 
-The halo catalog were read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
+The halo catalog was read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
 Within this code a Navarro, Frenk \& White (NFW) \citep{1996ApJ...462..563N} profile is fit to the three parameters given above to represent the dark matter component of the lens.
@@
 The furthest point in the caustic is found from its own center and the source is placed randomly within 3 times this distance.
-This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses because all the sources are right in the center of the caustic and making the process inefficient because most of the sources are too far away from the caustic to produce clear lenses.
+This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses, because all the sources are right in the center of the caustic, and making the process inefficient because most of the sources are too far away from the caustic to produce clear lenses.
 If the source positions were taken completely at random the fraction of clear lenses would be very low.
@@
 The disk is exponential with no vertical height which is why the inclination is limited to $80\degree$.
-The bulge is represented by a S\'{e}rsic profile with an axis ratio randomly sampled between 0.5 and 1.
+The bulge is represented by an elliptical S\'{e}rsic profile with an axis ratio randomly sampled between 0.5 and 1.
 The S\'{e}rsic index, $n_s$, is given by
@@
 \end{align}
-where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002.   This is to create some deviation from a perfect S\'{e}rsic profile.
+where $\phi_n$ is a random phase.  The coefficients are picked randomly from between -0.002 and 0.002.
 
@@
 
-These images of the of foreground galaxies are not intended to reproduce the true population of galaxies, but only to be sufficiently irregular to make them difficult to fit to a simple analytic model that might make them unrealistically easy to distinguish from a foreground plus a lensed image.
+These images of the foreground galaxies are not intended to reproduce the true population of galaxies, but only to be sufficiently irregular to make them difficult to fit to a simple analytic model that might make them unrealistically easy to distinguish from a foreground plus a lensed image.
 As will be discussed later, more realistic models will be needed in the future and are a subject of current investigation.
@@
 To represent the mass of the galaxies we make a gridded map of the surface brightness at 3 times the resolution of the final image.
-The surface brightness map is converted into a mass map within GLAMER by assuming a uniform mass-to-light ratio of 1.5 solar in the reference band.
+The surface brightness map is converted into a mass map within GLAMER by assuming a uniform mass-to-light ratio of 1.5 times solar in the reference band.
 These mass maps are added to the NFW dark matter halos discussed before to make the total lens mass distribution.
@@
 The code is able to produce any combination of foreground galaxies, lensed image and noise that is desired.
-For the training set,  an image of the total lens with noise, an image of the foreground galaxies with noise and image of the lensed background source without noise.
-For the test sets only the final images were provided to participants although all the information was stored for analysing the entries.
+For the training set,  an image of the total lens with noise, an image of the foreground galaxies with noise and image of the lensed background source without noise were provided.
+For the test sets only the final images were provided to participants although all the information was stored for analysing the challenge entries.
 
@@
 
- In the challenge set the limiting magnitude for background sources to 28 in $i$.   60\% of the cases had no background source and were thus labeled as non-lenses.
+ In the challenge set the limiting magnitude for background sources was 28 in $i$.   60\% of the cases had no background source and were thus labeled as non-lenses.
 
@@
 The reference band was $r$.
-For the challenge set 85\% of the images where made with purely simulated images as outlined above and the other 15\% used actual images taken from a preliminary sample of bright galaxies directly from the KiDS survey.
+For the challenge set, 85\% of the images where made with purely simulated images as outlined above and the other 15\% used actual images taken from a preliminary sample of bright galaxies directly from the KiDS survey.
 Lensed source images where added to these real images at the same rate as for the mock images,  in this case 50\%.
@@
 By chance one of the original KiDS images appears to have been a lens.  When an additional lensed source was added this made a double lens or "jackpot" lens \citep{2008ApJ...677.1046G}.
-
-\section{The Entries}
-\label{sec:entries}
 
@@
    \hline
-   & & &$\dagger$ No description was submitted for this paper.
+   & & &$\dagger$ No description was submitted for this entry.
 \end{tabular}
@@
 \section{lens finding methods}
-\label{sec:methods}
-
-There were 24 valid entries into the challenge.
-They are listed in Table~\ref{table:entries}.
-There were a variety of different methods used and participants come from a variety of different backgrounds, most were professional astronomers, but there were also entries from researchers outside of the field.
+\label{sec:entries}
+
+There were 24 valid entries into the challenge which are listed in Table~\ref{table:entries}.
+There were a variety of different methods used and participants came from a variety of different backgrounds, most were professional astronomers, but there were also entries from researchers outside of the field.
 
@@
 methods into four categories according to the type of method used.
+The Receiver Operating Characteristic (ROC) curve and the area under this curve are referred to in these sections.
+The ROC is defined in section~\ref{sec:figure_of_merit} where methods for evaluating the entries is discussed.
+A reader unfamiliar with the ROC might want to refer to that section.
 
@@
 over a 48-hour period, at the rate of 5000/hr (NJ) and 2500/hr (AT). 
-The overall results, in terms of ROC (see section \ref{sec:figure_of_merit}) curves, were very similar for 
+The overall results, in terms of area under the ROC (see section \ref{sec:figure_of_merit}) curves, were very similar for 
 both observers. The space-based challenge produced areas of 0.800 and 
@@
  \includegraphics[width=\columnwidth]{figures/arcmethod.pdf}
- \caption{ (GAHEC IRAP) From top-left to bottom right, 1) a simulated arc extracted from SL challenge in which an tuned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixel wise elongation is computed, 3) the resulting elongated pixels after threshold, 4) the set of pixels selected for the computation of arc candidate properties.
+ \caption{ (GAHEC IRAP) From top-left to bottom right, 1) a simulated arc extracted from the strong lensing challenge in which an tuned Arcfinder selects 3 candidates (green circles), 2) the smoothed image on which pixel wise elongation is computed, 3) the resulting elongated pixels after threshold, 4) the set of pixels selected for the computation of arc candidate properties.
 }
@@
 A final thresholding is set to maximize purity over completeness on a few typical arcs of the dataset.
-For the current SL challenge, arcfinder was tuned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.
+For the current strong lensing challenge, arcfinder was tuned to detect long and narrow arcs, and was optimized on a subset of 1000 simulated images with a grid covering a range of elongation windows and arc areas.
 A python wrapper allows users to change parameters in a flexible way and run the arcfinder C code from the linux  command line.
@@
 The difference in colour between lens and source usually allows the lensed images to still be detectable after the lens subtraction process.
-However, in order to avoid subtracting off the lensed images in systems with similar colours between lens source, we radially truncate the model lens surface brightness.
+However, in order to avoid subtracting off the lensed images in systems with similar colours between lens and source, we radially truncate the model lens surface brightness.
 The model lens light is truncated at the smallest radius between the position where the surface brightness is comparable to the sky background level, or the position of a positive radial gradient in surface brightness, if detected.
@@
 \begin{equation}
-G_c[i,j]=Be^{-\frac{(i^2+j^2)}{2\sigma^2}} \mathrm{cos}\left(\frac{2\pi}{\lambda} (i\, \mathrm{cos} \, \theta + j\, \mathrm{sin} \,\theta)\right),
+G_c[i,j]=Be^{-\frac{(i^2+j^2)}{2\sigma^2}} \mathrm{cos}\left[\frac{2\pi}{\lambda} (i\, \mathrm{cos} \, \theta + j\, \mathrm{sin} \,\theta)\right],
 \end{equation}
 where harmonic wavelength $\lambda$, Gaussian spread  $\sigma$ and orientation $\theta$ define the operation performed on each point $i,j$ in an image.
-Such a kernel is a popular image processing choice for edge detection and texture classification \citep[e.g.][]{Feichtinger98a,Springer-verlag97computationalmodels} and is thought to mimic some image processing functions of the mammalian brain \citep{Jones1233}.
+Such a kernel is a popular image processing choice for edge detection and texture classification \citep[e.g.][]{Springer-verlag97computationalmodels,Feichtinger98a} and is thought to mimic some image processing functions of the mammalian brain \citep{Jones1233}.
 
@@
 \begin{equation}
-	- \sum_{n=1}^{N} y[n] \log \hat{y}[n] + (1 - y[n])\log(1 - \hat{y}[n]) \;,
+S =	- \sum_{n=1}^{N} y[n] \log \hat{y}[n] + (1 - y[n])\log(1 - \hat{y}[n]) \;,
 \end{equation}
@@
 A common way to mitigate this is to use a regularisation scheme.
-For example, the Dropout regularisation technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}, were a certain percentage of the neurons and their connections are  randomly drop  from the neural network.
+For example, the Dropout regularisation technique \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a}, were a certain percentage of the neurons and their connections are  randomly dropped  from the neural network.
 This regularisation techniques reduces overfitting  by preventing complex co-adaptations of neurons on training data.
@@
 One of the main reasons behind this is the effect of \textit{vanishing gradients}: it has been empirically observed that in many multi-layer neural networks the gradients in higher-level (further from the image) layers often become too small to be effective in gradient descent based optimisation.
-Another difficulty is that the distribution of each layers inputs changes during training as the parameters of the previous layers change.
+Another difficulty is that the distribution of each layer's inputs changes during training as the parameters of the previous layers change.
 These issues make it difficult to find the best learning rates.
@@
 Let the activities of a given neuron in a mini-batch be denoted by $x_1,\ldots,x_m$.
-The batch normalisation layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardise the neuron activities to make them zero mean with variance one, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
+The batch normalisation layers i) calculate the empirical mean ($\mu = \frac{1}{m}\sum_{i=1}^m x_i $) and variance ($\sigma^2 = \frac{1}{m}\sum_{i=1}^m (x_i-\mu)^2 $) of the neural activities using the mini-batch data, ii) standardise the neuron activities to make them zero mean with unit variance, that is $\hat x_i = (x_i-\mu)/\sigma$, iii) linearly transform these activities with adjustable parameters $\beta, \gamma \in \mathbb{R}$: $y_i=\gamma\hat x_i +\beta$.
 Here $y_i$ denotes the output after applying the batch normalisation layer on the neuron with activities $x_i$.
@@
 Dropout regularization \citep{2012arXiv1207.0580H,JMLR:v15:srivastava14a} is applied to both convolutional and fully connected layers, with ``keep'' probabilities $p=2/3$ and $p=1/2$, respectively.
-The network itself consists of three convolutional layers (11x11-32, 5x5-64 and 3x3-64), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer .
+The network itself consists of three convolutional layers (11x11-32, 5x5-64 and 3x3-64), followed by two fully-connected layers ($256$ and $64$ neurons) and an output softmax layer.
 The first five layers use the ELU activation function, which in our tests led to significantly faster convergence compared to ReLU and even SoftPlus activation.
@@
 
-The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=5.10^{-2}$.
+The CNN weights are initialized to random values using a truncated Gaussian distribution with mean $\mu=0$ and standard deviation $\sigma=0.05$.
 The network is trained on a Titan-X ``Pascal'' nVidia GPU using the ADAM gradient-based optimizer during 800 epochs, with an initial learning rate $\eta(t=0)=10^{-3}$ and a learning rate decay $\eta(t+1)/\eta(t)=0.99$, where $t$ is the epoch.
@@
 $\bar\mu_i$ is computed using the mean value $\mu_i$ over the batch in combination with the previous mean $\bar\mu_{i-1}$ using an inertia value $\eta$ set to $1$ at the beginning and decaying with the iterations.
-For the training, the 20k provided images were split into two sets, 17k for training and 3k for validation.
+For the training, the 20,000 provided images were split into two sets, 17,000 for training and 3k for validation.
 Each iteration of the gradient descent (more precisely ADAM \citep{adam}) minimizes the cross entropy, 
@@
 where $p$ is the output of the neural network, computed over a batch of 30 images, 15 lenses and 15 nonlenses, picked from the training set.
-The small batches with only 30 images were easier to handle computationally but add more noise to the gradient which we considered negligible due to there being only two classes to classify.
+The small batches with only 30 images were easier to handle computationally but added more noise to the gradient which we considered negligible due to there being only two classes to classify.
 
@@
 To prevent the overfitting, we used some dropout \citep{dropout} (with a keeping probability decreasing with the iterations).
-The masked region of the ground based images are handled by simply setting them to zero.
+The masked regions of the ground based images are handled by simply setting them to zero.
 Each final prediction is made of the product of the predictions of the 8 transformations of the image by the dihedral group.
@@
 During the training we initialize the weights of our model with random normal values and we "warm up" the training of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) \citep{Huang_2016}  and then a staring learning rate of  0.001.
-When the network was trained using an early stopping method, and for a maximum number of 300 epochs.
+Then the network was trained using an early stopping method, and for a maximum number of 300 epochs.
 The early stopping method is an effective method of preventing overfitting and consists in stopping the training if a monitored quantity does not improve for a fixed number (called \textit{patience}) of training epochs.
@@
 $90\%$ of the images, chosen randomly, for the training and $10\%$ to validate.
-We repeated the process $10$ times to avoid bias due a specific choice of training/validation set and to define an uncertainty in our ROC (see section \ref{sec:figure_of_merit}) .
+We repeated the process $10$ times to avoid bias due to a specific choice of training/validation set and to define an uncertainty in our ROC (see section \ref{sec:figure_of_merit}) .
 
@@
 We found that the results, accounting for the uncertainties,  
-were clearly superior in term of the area under the ROC with the preprocessing. Therefore, this is the configuration we used for the challenge entry.
+were clearly superior in terms of the area under the ROC with the preprocessing. Therefore, this is the configuration we used for the challenge entry.
 
@@
 
-For the ground based cases three configurations with highest area under ROC were III, IV and VI.
+For the ground based cases, the three configurations with highest area under ROC were III, IV and VI.
 Although the areas are very similar between IV and VI the last one is superior in the low fake positives end.
@@
 
-\subsubsection{Kapteyn Resnet (Petrillo, Tortora, Verdoes Kleijn, Koopmans) }
+\subsubsection{Kapteyn Resnet (Petrillo, Tortora, Vernardos, Kleijn, Koopmans) }
 
@@
 
-{\bf Implementation}
+{\bf Implementation}:
 The CNN is implemented in Python 2.7 using the open-source libraries \textsc{Lasagne}\footnote{\href{http://github.com/Lasagne/Lasagne/}{\tt http://github.com/Lasagne/Lasagne/}} 
@@
 
-{\bf Architecture}
+{\bf Architecture}:
 We used the CNN architecture called ResNet described in \citep{he2015deep} with three stacks of residual blocks of 5 layers. 
 The output layer is composed by three units.
-Each units gives is output a number between 0 and 1 that represents, respectively, the probability of being a \textit{non-lens}, a \textit{dubious lens}, a \textit{certain lens}.
+Each unit gives as an output a number between 0 and 1 that represents, respectively, the probability of being a \textit{non-lens}, a \textit{dubious lens}, a \textit{certain lens}.
 We then collapsed one of the classes into another to give a binary classification : 0 when a source is classified as a \textit{non-lens} and a 1 when is classified as a \textit{clear lens} or as a \textit{dubious lens}.
@@
 
-{\bf Preprocessing}
+{\bf Preprocessing}:
 The training image files were preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
@@
 
-{\bf Training}
+{\bf Training}:
 The network is trained by minimizing the categorical cross-entropy loss function
@@
 This prefiltering was performed to emphasise the edges in the images.
-It as found to improve the results compared to the CNN without this pre-filter.
+It was found to improve the results compared to the CNN without this pre-filter.
 The CNN had 2 convolution layers each containing  $3\times3 - 32$ filters, incorporating dropout and max-pooling, and then 3 dense fully-connected layers to classify each image.
@@
 
-In this section we summarize some of our analysis of the submissions.
+In this section we summarize the analysis of the submissions.
 In section~\ref{sec:figure_of_merit} we discuss how to judge a classifier in this particular case and define some metrics of success.
+The results for all the submissions are given in section~\ref{sec:performance}.
 
@@
 In deriving a good figure of merit for evaluating lens finding algorithms one needs to take into account the particular nature of this problem.
-The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or  ROC (receiver operating characteristic) curve.
-This is a plot of the true positive rate (TPR) and the false positive rate (FPR).
+The traditional method for evaluating a classification algorithm is with the receiver operating characteristic curve, or  ROC  curve.
+This is a plot of the true positive rate (TPR) versus the false positive rate (FPR).
 In this case these are defined as
@@
 \end{align}
-The classifier generally gives a probability of a case being a lens, $p$, in which case a threshold is set and everything with $p$ greater is classified as a lens and everything smaller is classified as not a lens.
+The classifier generally gives a probability of a candidate being a lens, $p$, in which case a threshold is set and everything with $p$ greater is classified as a lens and everything smaller is classified as not a lens.
 The TPR and FPR are then plotted as a curve parametrised by this threshold.
@@
 \begin{align}
-\frac{\rm FP}{\rm TP} \simeq \frac{\rm FPR}{\rm TPR} \left(\frac{\textrm{number of non-lenses in sample}}{\textrm{number of lenses in sample}} \right)
+\frac{\rm FP}{\rm TP} \simeq \frac{\rm FPR}{\rm TPR} \left(\frac{\textrm{number of non-lenses in sample}}{\textrm{number of lenses in sample}} \right).
 \end{align}
-Since only about one in a thousand objects will be lenses (perhaps somewhat more depending on pre-selection) the contamination will be high unless the FPR is much less than the TPR.
+Since only about one in a thousand objects will be a lens (perhaps somewhat more depending on pre-selection) the contamination will be high unless the FPR is much less than the TPR.
 For this reason we consider some additional figures of merit.
@@
 We do not impose a definitive arc/ring magnification, brightness or surface brightness limit for a system to be considered a lens because we
-want to include these "barely lensed" objects because we want to test the limits of the classifiers.
+want to include these "barely lensed" objects to test the limits of the classifiers.
 As we will see, if you restrict your objectives to detecting only lensed images with surface brightness above some threshold, for example, the "best" algorithm might change and the TPR will change.
 For this reason we plot the AUROC, TPR$_0$ and TPR$_{10}$ as a function of several variables for all the entries.
-This is done by removing all the lenses that do not exceed the threshold and then recalculating  these quantities, the number of non-lenses remains the same.
+This is done by removing all the lenses that do not exceed the threshold and then recalculating  these quantities, while the number of non-lenses remains the same.
 
@@
 
-Figures~\ref{fig:einstein_space} and \ref{fig:einstein_ground} shows the AUROC, TPR$_0$, TPR$_{10}$ and fraction of lenses as a function of a lower cutoff on the Einstein radius (area).
-There is also a vertical dotted line that indicates where no more than 100 lenses in the test sample had Einstein radii larger than this mark.
+Figures~\ref{fig:einstein_space} and \ref{fig:einstein_ground} show the AUROC, TPR$_0$, TPR$_{10}$ and fraction of lenses as a function of a lower cutoff on the Einstein radius (area).
+There is also a vertical dotted line that indicates
+where no more than 100 lenses in the test sample had larger Einstein radii.
 Beyond this point one should be suspicious of small number statistics.
@@
 
-Figures~\ref{fig:flux_space} and \ref{fig:flux_ground} are the same except that the fluxes in the lensed image is used as the threshold.
+Figures~\ref{fig:flux_space} and \ref{fig:flux_ground} are the same except that the flux in the lensed images is used as the threshold.
 We count only the flux in pixels with flux over one $\sigma$ of the background.
@@
 
-A lensed image can be bright without being visibly distorted as in the case of a unresolved images.
+A lensed image can be bright without being visibly distorted as in the case of unresolved images.
 Figures~\ref{fig:npixel_space} and \ref{fig:npixel_ground} use the number of pixels in the lensed image(s) that are over  one $\sigma$ of the background.
@@
 Figures~\ref{fig:flux_contrast_space} and \ref{fig:flux_contrast_ground} investigate how the flux contrast between the foreground objects and the lensed source affects the classifiers.
-Interestingly some method's TPRs go up with this quantity and some go down.
+Interestingly some methods' TPRs go up with this quantity and some go down.
 We have not yet found any clear explanation for this variety of behaviors.

### 2019-01-14 response.tex
Edit.

@@
 \begin{document}
-Referee Report
+Response to Referee Report
+
+We thank the referee for his/her comments.  Below are these comments in bold face and our 
+responses to each one in non-bold.
 
@@
 There was some miscommunication about responsibilities between the authors.
-We have edited the text more carefully and made many small corrections corrections.
+We have edited the text more carefully and made many small corrections corrections to the grammar, style and formatting.
+We think that it is much improved now.
 
@@
 The first paragraph of the introduction has been expanded to better describe gravitational lensing.
-We do not wish to take up to much space describing the whole field when this can be read about elsewhere.
+We do not wish to take up to much space describing the whole field when this can be read about elsewhere though.
 
@@
 It is also mentioned in the first paragraph of the conclusion where we added a reference to the figures it is based on.
+It is a statement of fact, but the fraction of identified lenses is a function of the threshold that defines what is and is not a lens so it is not a simply stated fact.
+The information is contained in the plots however.
 
@@
 
-It is clearly stated several times that there were 4 bands in the ground based set which makes 400,000 images for 100,000 objects.
+It is stated several times that there were 4 bands in the ground based set which makes 400,000 images for 100,000 objects.  We have tried to make this clearer.
 
@@
 
-We have added a little more discussion of this paper in the introduction and conclusion.
+We have added more discussion of this paper in the introduction and conclusion.
 
@@
 
-?????
+Details of these methods are in the cited papers.  The arc finders where not able to match the performance 
+of the CNNs here, but in this challenge supervised learning is used to train the CNNs while the arc finders were not developed to take full advantage of this particular data set.
+The real data will not come with labels so the arc finders might be more competitive in reality.
+The creators of the arc finders did not think they should invest large amounts of time to optimize their codes to fit these particular data sets when they
+realized that the CNNs were likely to out perform them in this situation.  The performance of the arc finders  should really be considered separately from the other methods.
 
@@
 
-That is the AUC on the training set not the challenge set.
+That is the AUC on the training set not the challenge set.  We have made this clearer.
 
@@
 Yes, this was difficult to pinpoint.
-The very large number of possible CNN configurations and the lack of overlaps between the methods tested makes it hard to conclude what specifically about architecture of one CNN makes it better than another.
+The very large number of possible CNN configurations and the lack of overlaps between the methods tested make it hard to conclude what specifically about architecture of one CNN makes it better than another.
 The performance of a CNN will also depend critically on the nature of the data.
@@
 We are working on this.  There are several approaches we are considering.  They would 
-involve randomizing existing images.
+involve randomizing existing images.  This is beyond the scope of this paper.
 
@@
 multi-band data exists and even if it is of lower resolution, as it will be for Euclid, it should 
-make space based searches more successful than ground based ones.  Yes, we are fallowing 
+make space based searches more successful than ground based ones.  Yes, we are following 
 up with Euclid UV simulations.  We have tried to change this impression by adding a note to the abstract.

### 2019-01-14 paper.tex
Edit.

@@
 \documentclass{aa}
+%\documentclass[referee]{aa}
 
@@
 
-\section{the simulations}
+\section{The simulations}
 \label{sec:simulation}
@@
 
-\section{lens finding methods}
+\section{Lens finding methods}
 \label{sec:entries}
@@
 
-\section{results}
+\section{Results}
 \label{sec:results}
@@
 A large variety of lens finding methods were tested on simulated images that were developed separately.
-We found that some methods could recover more than 50\% of the lenses above a lensed image brightness or size threshold without a single false positive out of 100,000 candidates.
+Based on figures~\ref{fig:einstein_space} and \ref{fig:einstein_ground}, we found that some methods could recover more than 50\% of the lenses above a lensed image brightness or size threshold without a single false positive out of 100,000 candidates.
 If the data closely resembled the simulations we would already have reasonably good methods whose efficiency and biases can be quantitatively characterized.

### 2019-02-05 paper.tex
Added Jacobs' contribution.

@@
 \and
+Colin Jacobs\inst{23}
+\and
 Eric Jullo \inst{15}
@@
 School of Physical Sciences, The Open University, Walton Hall, Milton Keynes, MK7 6AA, UK
+\and
+Centre for Astrophysics and Supercomputing, Swinburne University of Technology, P.O. Box 218, Hawthorn, VIC 3122, Australia
 }
@@
 
+\subsubsection{CAS Swinburne (Jacobs)}
+
+Our model is a CNN-based classifier.
+The architecture of our network was simple, similar to that of AlexNet \citep{krizhevsky_imagenet_2012}, with three 2D convolutional layers (with kernel sizes 11, 5, and 3), and two fully-connected layers of 1024 neurons each.
+The activation function after each convolutional layer was a ReLU.
+After each convolution we employed a 3x3 max pooling layer.
+To avoid over-fitting, we included a dropout layer of 0.5 after each of the two fully-connected layers.
+We implemented our network using the Keras python framework \citep{Chollet_2015} and Theano \citep{Bastien_2012}.
+
+The training set was augmented with three rotations, and 20\% of the images were reserved for validation.
+The training set consisted of 4-band FITS files of simulated lenses and non-lenses.
+We imported the training set into HDF5 database files.
+The data was normalised on import, such that the mean value of the data cube, across all bands, is zero and the standard deviation is one, i.e.
+\(X' = (X - \mu)/\sigma\); the dynamic range was not altered.
+We also include batch normalisation step after the first convolution, which normalises the outputs of this layer to the same range (\(\mu = 0\), \(\sigma = 1\)).
+This has been shown empirically to aid in more rapid convergence of the training process.
+
+The training process using a categorical cross-entropy loss function, and a stochastic gradient descent optimizer with an initial learning rate of 0.01, learning rate decay of \(10^{-6}\), and Nesterov momentum \citep{nesterov83method} of 0.9.
+Training converged (validation loss stopped decreasing) after approximately 30 epochs.
+
+We note that experiments indicated that training on 4-band FITS data, as opposed to RGB images produced from the fits files, resulted in improved validation accuracy, of order a few percent.
+
 \section{Results}

### 2019-02-05 paper.tex
Edit

@@
 \begin{align}
-S(\theta,r) &= e^{-r/R_h} \left( 1 + A \cos(N_a\theta + \phi_r \right) ~, \\
+S(\theta,r) &= e^{-r/R_h} \left[ 1 + A \cos(N_a\theta + \phi_r ) \right]~, \\
 \phi_r &= \alpha\log(2 r/ R_h) + \phi_d \nonumber
@@
 \centering
-\begin{tabular}{rlll}
+\begin{tabular}{rllll}
   \hline
- & Name & type & authors \\ 
+ & Name & type & authors & section \\ 
   \hline
-  1 & AstrOmatic & Space-Based & Bertin   \\ 
-  2 & GAHEC IRAP & Space-Based & Cabanac  \\ 
-  3 & CAS Swinburne Melb$^\dagger$& Ground-Based & Jacobs   \\ 
-  4 & ALL-star & Ground-Based & Avestruz, N. Li \& Lightman  \\ 
-  5 & Manchester1 & Space-Based & Jackson \& Tagore  \\ 
-  6 & CMU-DeepLens-Resnet-Voting & Space-Based & Ma, Lanusse \& C. Li  \\ 
-  7 & Manchester SVM & Ground-Based & Hartley \& Flamary  \\ 
-  8 & CMU-DeepLens-ResNet & Space-Based & Francois Lanusse, Ma, C. Li \& Ravanbakhsh \\ 
-  9 & CMU-DeepLens-Resnet-Voting & Ground-Based & Ma, Lanusse \& C. Li   \\ 
-  10 & YattaLensLite & Space-Based &  Sonnenfeld  \\ 
-  11 & NeuralNet2 & Space-Based &  Davies  \\ 
-  12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  \\ 
-  13 & CMU-DeepLens-ResNet-ground3 & Ground-Based &  Lanusse, Ma, Ravanbakhsh \& C. Li \\ 
-  14 & GAMOCLASS & Space-Based &  Huertas-Company, Tuccillo, Velasco-Forero \& Decenci\`{e}re \\ 
-  15 & LASTRO EPFL (CNN) & Space-Based & Geiger, Sch\"{a}fer \& Kneib \\ 
-  16 & Manchester SVM & Space-Based &  Hartley  \& Flamary\\ 
-  17 & CMU-DeepLens-ResNet-aug & Space-Based & Ma,  Lanusse, Ravanbakhsh \& C. Li \\ 
-  18 & LASTRO EPFL & Ground-Based & Geiger, Sch\"{a}fer \& Kneib   \\ 
-  19 & CAST & Space-Based & Bom, Valent\'{\i}n \& Makler  \\ 
-  20 & AstrOmatic & Ground-Based & Bertin  \\ 
-  21 & All-now & Space-Based & Avestruz, N. Li \& Lightman   \\ 
-  22 & Manchester-NA2 & Ground-Based & Jackson \& Tagore  \\ 
-  23 & YattaLensLite & Ground-Based & Sonnenfeld   \\ 
-  24 & Kapteyn Resnet & Space-Based & Petrillo, Tortora, Verdoes Kleijn, Koopmans \& Vernardos \\ 
+  1 & AstrOmatic & Space-Based & Bertin  & \ref{sec:AstrOmatic}  \\ 
+  2 & GAHEC IRAP & Space-Based & Cabanac & \ref{sec:IRAP} \\ 
+  3 & CAS Swinburne Melb & Ground-Based & Jacobs   & \ref{sec:CASSwinburne} \\ 
+  4 & ALL-star & Ground-Based & Avestruz, N. Li \& Lightman  & \ref{sec:ALL} \\ 
+  5 & Manchester1 & Space-Based & Jackson \& Tagore  & \ref{sec:manchester} \\ 
+  6 & CMU-DeepLens-Resnet-Voting & Space-Based & Ma, Lanusse \& C. Li  & \ref{sec:CMU_DeepLens} \\ 
+  7 & Manchester SVM & Ground-Based & Hartley \& Flamary  & \ref{sec:Gabor-SVM} \\ 
+  8 & CMU-DeepLens-Resnet & Space-Based & Francois Lanusse, Ma, C. Li \& Ravanbakhsh  & \ref{sec:CMU_DeepLens} \\ 
+  9 & CMU-DeepLens-Resnet-Voting & Ground-Based & Ma, Lanusse \& C. Li  & \ref{sec:CMU_DeepLens} \\ 
+  10 & YattaLensLite & Space-Based &  Sonnenfeld  & \ref{sec:YettaLens} \\ 
+  11 & NeuralNet2 & Space-Based &  Davies \& Serjeant & \ref{sec:NeuralNet2} \\ 
+  12 & CAST & Ground-Based &  Roque De Bom, Valent\'{\i}n \&  Makler  & \ref{sec:CAST} \\ 
+  13 & CMU-DeepLens-Resnet-ground3 & Ground-Based &  Lanusse, Ma, Ravanbakhsh \& C. Li  & \ref{sec:CMU_DeepLens} \\ 
+  14 & GAMOCLASS & Space-Based &  Huertas-Company, Tuccillo, Velasco-Forero \& Decenci\`{e}re & \ref{sec:GAMOCLASS} \\ 
+  15 & LASTRO EPFL (CNN) & Space-Based & Geiger, Sch\"{a}fer \& Kneib  & \ref{sec:LASTRO} \\ 
+  16 & Manchester SVM & Space-Based &  Hartley  \& Flamary & \ref{sec:Gabor-SVM} \\ 
+  17 & CMU-DeepLens-Resnet-aug & Space-Based & Ma,  Lanusse, Ravanbakhsh \& C. Li  & \ref{sec:CMU_DeepLens} \\ 
+  18 & LASTRO EPFL & Ground-Based & Geiger, Sch\"{a}fer \& Kneib  & \ref{sec:LASTRO} \\ 
+  19 & CAST & Space-Based & Bom, Valent\'{\i}n \& Makler  & \ref{sec:LASTRO} \\ 
+  20 & AstrOmatic & Ground-Based & Bertin  & \ref{sec:AstrOmatic} \\ 
+  21 & ALL-now & Space-Based & Avestruz, N. Li \& Lightman  & \ref{sec:ALL} \\ 
+  22 & Manchester2 & Ground-Based & Jackson \& Tagore  & \ref{sec:manchester} \\ 
+  23 & YattaLensLite & Ground-Based & Sonnenfeld  & \ref{sec:YettaLens} \\ 
+  24 & Kapteyn Resnet & Space-Based & Petrillo, Tortora, Kleijn, Koopmans \& Vernardos & \ref{sec:KapteynResnet} \\ 
    \hline
-   & & &$\dagger$ No description was submitted for this entry.
 \end{tabular}
-\caption{Entries to the challenges.}
+\caption{Entries to the challenges.  Descriptions of the methods are in the sections listed on the right.}
 \label{table:entries}
@@
 \subsection{Visual Inspection}
-\subsubsection{Manchester/Manchester1 (Jackson,Tagore)}
+\subsubsection{Manchester1/Manchester2 (Jackson,Tagore)}
+\label{sec:manchester}
 
@@
 
-\subsubsection{ IRAP (Cabanac)}
+\subsubsection{ GAHEC IRAP (Cabanac)}
+\label{sec:IRAP}
 
@@
 \subsubsection{YattaLens Lite (Sonnenfeld)}
+\label{sec:YettaLens}
 
@@
 
-\subsubsection{Gabor-SVM (Hartley, Flamary)}
+\subsubsection{Manchester-SVM (Hartley, Flamary)}
+\label{sec:Gabor-SVM}
 
@@
 \subsubsection{ALL (Avestruz, Li, Lightman)}
+\label{sec:ALL}
 %-------------------------------------------------%
@@
 \subsubsection{AstrOmatic (Bertin)}
+\label{sec:AstrOmatic}
 
@@
 \subsubsection{LASTRO EPFL (Geiger, Sch\"{a}fer)}
+\label{sec:LASTRO}
 
@@
 \subsubsection{GAMOCLASS (Tuccillo, Huertas-Company, Velasco-Forero, Decenci\`ere)}
+\label{sec:GAMOCLASS}
 
@@
 \subsubsection{CAST (Bom, Valent\'in, Makler)}
+\label{sec:CAST}
 %-------------------------------------------------%
@@
 \subsubsection{CMU DeepLens (Lanusse, Ma, Li, Ravanbakhsh)}
+\label{sec:CMU_DeepLens}
 
@@
 \subsubsection{Kapteyn Resnet (Petrillo, Tortora, Vernardos, Kleijn, Koopmans) }
+\label{sec:KapteynResnet}
 
@@
 {\bf Architecture}:
-We used the CNN architecture called ResNet described in \citep{he2015deep} with three stacks of residual blocks of 5 layers. 
+We used the CNN architecture called Resnet described in \citep{he2015deep} with three stacks of residual blocks of 5 layers. 
 The output layer is composed by three units.
@@
 \subsubsection{NeuralNet2 (Davies, Serjeant) }
+\label{sec:NeuralNet2}
 
@@
 \subsubsection{CAS Swinburne (Jacobs)}
+\label{sec:CASSwinburne}
 
@@
   \hline
- CMU-DeepLens-ResNet-ground3 & Ground-Based & 0.98 & 0.09 & 0.45 & CNN \\ 
+ CMU-DeepLens-Resnet-ground3 & Ground-Based & 0.98 & 0.09 & 0.45 & CNN \\ 
   CMU-DeepLens-Resnet-Voting & Ground-Based & 0.98 & 0.02 & 0.10 & CNN \\ 
@@
   Manchester SVM & Ground-Based & 0.93 & 0.22 & 0.35 & SVM / Gabor \\ 
-  Manchester-NA2 & Ground-Based & 0.89 & 0.00 & 0.01 & Human Inspection \\ 
+  Manchester2 & Ground-Based & 0.89 & 0.00 & 0.01 & Human Inspection \\ 
    ALL-star & Ground-Based & 0.84 & 0.01 & 0.02 & edges/gradiants and Logistic Reg. \\ 
@@
    LASTRO EPFL & Space-Based & 0.93 & 0.00 & 0.08 & CNN \\ 
-  CMU-DeepLens-ResNet & Space-Based & 0.92 & 0.22 & 0.29 & CNN \\ 
+  CMU-DeepLens-Resnet & Space-Based & 0.92 & 0.22 & 0.29 & CNN \\ 
    GAMOCLASS & Space-Based & 0.92 & 0.07 & 0.36 & CNN \\ 
@@
   AstrOmatic & Space-Based & 0.91 & 0.00 & 0.01 & CNN \\ 
-   CMU-DeepLens-ResNet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 
+   CMU-DeepLens-Resnet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 
    Kapteyn Resnet & Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
@@
 Table~\ref{table:AUROC} shows the AUROC, TPR$_0$ and TPR$_{10}$ for the entries in order of AUROC and dataset type.
-It can be seen that CMU-DeepLens-ResNet-ground3 had the best AUROC for the ground-based set and LASTRO EPFL the best for the space-based set.
+It can be seen that CMU-DeepLens-Resnet-ground3 had the best AUROC for the ground-based set and LASTRO EPFL the best for the space-based set.
 The order is different if TPR$_0$ is used to rank the entries as seen in table~\ref{table:TPR0}.
 Here Manchester SVM and
-CMU-DeepLens-ResNet get the best scores.
+CMU-DeepLens-Resnet get the best scores.
 
@@
  Manchester SVM & Ground-Based & 0.93 & 0.22 & 0.35 & SVM / Gabor \\ 
-  CMU-DeepLens-ResNet-ground3 & Ground-Based & 0.98 & 0.09 & 0.45 & CNN \\ 
+  CMU-DeepLens-Resnet-ground3 & Ground-Based & 0.98 & 0.09 & 0.45 & CNN \\ 
   LASTRO EPFL & Ground-Based & 0.97 & 0.07 & 0.11 & CNN \\ 
@@
    ALL-star & Ground-Based & 0.84 & 0.01 & 0.02 & edges/gradiants and Logistic Reg. \\ 
-   Manchester-NA2 & Ground-Based & 0.89 & 0.00 & 0.01 & Human Inspection \\ 
+   Manchester2 & Ground-Based & 0.89 & 0.00 & 0.01 & Human Inspection \\ 
    YattaLensLite & Ground-Based & 0.82 & 0.00 & 0.00 & SExtractor \\ 
@@
    AstrOmatic & Ground-Based & 0.96 & 0.00 & 0.01 & CNN \\ 
-   CMU-DeepLens-ResNet & Space-Based & 0.92 & 0.22 & 0.29 & CNN \\ 
+   CMU-DeepLens-Resnet & Space-Based & 0.92 & 0.22 & 0.29 & CNN \\ 
    GAMOCLASS & Space-Based & 0.92 & 0.07 & 0.36 & CNN \\ 
@@
    Kapteyn Resnet& Space-Based & 0.82 & 0.00 & 0.00 & CNN \\ 
-   CMU-DeepLens-ResNet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 
+   CMU-DeepLens-Resnet-aug & Space-Based & 0.91 & 0.00 & 0.00 & CNN \\ 
    CMU-DeepLens-Resnet-Voting & Space-Based & 0.91 & 0.00 & 0.01 & CNN \\ 
@@
 When deriving the distribution of Einstein radii from data these curves would need to be used to correct for detection bias.
-It can be seen that CMU-DeepLens-ResNet, Manchester1, Manchester SVM and GAMOCLASS obtain significantly higher TPR$_0$ and  TPR$_{10}$ for larger Einstein radii.
+It can be seen that CMU-DeepLens-Resnet, Manchester1, Manchester SVM and GAMOCLASS obtain significantly higher TPR$_0$ and  TPR$_{10}$ for larger Einstein radii.
 Manchester1 is the human inspection method.
@@
 In some cases one can see an abrupt rise in the TPRs at some flux threshold.
-CMU-DeepLens-ResNet in particular reaches a TPR$_0$ above 75\% for the brightest $\sim$ 10\% of the lenses.
+CMU-DeepLens-Resnet in particular reaches a TPR$_0$ above 75\% for the brightest $\sim$ 10\% of the lenses.
 %\red{(Find these numbers for the real KiDS sample)}

### 2019-02-17 paper.tex
Edit

@@
 The TPR and FPR are then plotted as a curve parametrised by this threshold.
-At $p=1$ all of the cases are classified as non-lenses and so TPR=FPR=1 and at $p=0$ all of the cases are classified as lenses so TPR=FPR=0.
+At $p=1$ all of the cases are classified as non-lenses and so TPR=FPR=0 and at $p=0$ all of the cases are classified as lenses so TPR=FPR=1.
 These points are always added to the ROC curve.
@@
  \includegraphics[width=2\columnwidth]{figures/einstein_space.pdf}
- \caption{The AUROC, TPR$_0$, TPR$_{10}$ and the fraction of lenses in the test sample after discarding the lenses with Einstein radii larger than the number indicated on the x-axis. }
+ \caption{The AUROC, TPR$_0$, TPR$_{10}$ and the fraction of lenses in the test sample after discarding the lenses with Einstein radii larger than the number indicated on the x-axis.
+The vertical dotted lines indicate where no more than 100 lenses in the test sample had larger Einstein radii.
+Beyond this point one should be suspicious of small number statistics.
+}
  \label{fig:einstein_space}
@@
  \includegraphics[width=2\columnwidth]{figures/einstein_ground.pdf}
- \caption{Same as figure~\ref{fig:einstein_space}, but for space-based entries.}
+ \caption{Same as figure~\ref{fig:einstein_space}, but for ground-based entries.
+The AUROC, TPR$_0$, TPR$_{10}$ and the fraction of lenses in the test sample after discarding the lenses with Einstein radii larger than the number indicated on the x-axis.
+The vertical dotted lines indicate where no more than 100 lenses in the test sample had larger Einstein radii.
+}
  \label{fig:einstein_ground}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_space.pdf}
- \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the flux within the pixels that are above 1 $\sigma$ in the lensed source only image.}
+ \caption{ The AUROC, TPR$_0$, TPR$_{10}$ and the fraction of lenses in the space-based test sample after discarding the lenses with fluxes within the pixels that are above 1 $\sigma$ in the lensed source as indicated on the x-axis.
+The vertical dotted lines indicate where no more than 100 lenses in the test sample had larger Einstein radii.
+}
  \label{fig:flux_space}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_ground.pdf}
- \caption{Same as figure~\ref{fig:flux_space}, but for space-based entries.}
+ \caption{Same as figure~\ref{fig:flux_space}, but for ground-based entries.}
  \label{fig:flux_ground}
@@
 \includegraphics[width=2\columnwidth]{figures/npixel_space.pdf}
- \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the number of pixels that are above 1 $\sigma$ in the lensed source only image.
-This is an indication of the lensed arcs' size.}
+ \caption{The AUROC, TPR$_0$, TPR$_{10}$ and the fraction of lenses as a function of the lens image size for the space-based test set.
+The x-axis is the number of pixels that are above 1 $\sigma$ in the lensed source only image.
+This is an indication of the lensed arcs' size.
+The vertical dotted lines indicate where no more than 100 lenses in the test sample had larger Einstein radii.
+ }
  \label{fig:npixel_space}
@@
  \includegraphics[width=2\columnwidth]{figures/npixel_ground.pdf}
- \caption{Same as figure~\ref{fig:npixel_space}, but for space-based entries.}
+ \caption{Same as figure~\ref{fig:npixel_space}, but for ground-based entries.}
  \label{fig:npixel_ground}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_contrast_space.pdf}
-  \caption{Same as figure~\ref{fig:einstein_space}, but here the x-axis is the ratio of the flux coming from the lensed source to the total flux in the image in the index band.}
+  \caption{Same as figure~\ref{fig:flux_contrast_space}, but here the x-axis is the ratio of the flux coming from the lensed source to the total flux in the image in the index band.
+This is for the space-based test set.}
  \label{fig:flux_contrast_space}
@@
  \includegraphics[width=2\columnwidth]{figures/flux_contrast_ground.pdf}
- \caption{Same as figure~\ref{fig:flux_contrast_space}, but for space-based entries.}
+ \caption{Same as figure~\ref{fig:flux_contrast_space}, but for ground-based entries.}
  \label{fig:flux_contrast_ground}

### 2019-02-22 paper.tex
few changes by MM

@@
 
-To model the background objects that are lensed we use sources from the Hubble Ultra Deep Field (UDF) that have been decomposed into shapelet functions to remove noise.
-This is the same set of images as used in \citet{2008AandA...482..403M,2010AandA...514A..93M}.
-There are 9,350 such sources with redshifts and separate shapelet coefficients in 4 bands.
+To model the background objects that are lensed we use sources from
+the Hubble Ultra Deep Field (UDF) that have been decomposed into
+shapelet functions to remove noise.  This is the same set of images as
+used in \citet{2008AandA...482..403M,2010AandA...514A..93M} \citep[see
+also][]{2019MNRAS.482.2823P}.   There are 9,350 such sources with redshifts and separate shapelet coefficients in 4 bands.
 
@@
 
-We use {\em Logistic Regression} (LR), a machine learning algorithm,
+We use {\em Logistic Regression} (LR) 
 to train a classifier model.  LR requires a parameter search over the
@@
 To avoid the problem of the data flow distribution getting out of the comfort zone of the activation functions ("Internal Covariate Shift"), we used a mix of normalization propagation \citep{norm_prop} (without the constraint on the weights but a proper initialization) and batch normalization \citep{batch_norm} (slowly disabled over the iterations).
-As activation function, we used a scaled and shifted ReLU (Rectifier Linear Unit), 
+As activation function, we used a scaled and shifted ReLU, defined as
 \begin{equation} \label{eq:relu}
@@
 output number of filters)
- in the convolution, for a total of 3 convolutional layers and 3 max pooling layers.
-Each of these convolutional layers is followed by a rectified linear unit (ReLU) step.
+ in the convolution, for a total of 3 convolutional layers and 3 max
+ pooling layers.
+Each of these convolutional layers is followed by a ReLU step.
 The output of these units is then processed through a single fully-connected layer follower by a dropout layer, and, finally, by a one-neuron fully connected layer with sigmoid activation functions.
@@
 In order to increase the size of the training set and make the model invariant to specific transformations, we perform these data augmentation steps:
-1) Random rotation of the image in the range [0, 180$\degree$], using a reflection fill mode to keep constant the size of the images,
-2) The images were randomly shifted of 0.02 times the total width of the image,
-3) Random horizontal and vertical flips of the images.
-
-During the training we initialize the weights of our model with random normal values and we "warm up" the training of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) \citep{Huang_2016}  and then a staring learning rate of  0.001.
+1) we introduce random rotations of the image in the range [0, 180$\degree$], using a reflection fill mode to keep constant the size of the images;
+2) the images are randomly shifted of 0.02 times the total width of the image;
+3) the images are randomly flipped horizontally and vertically.
+
+During the training we initialize the weights of our model with random normal values and we ``warm up" the training of the CNN for 25 epochs, using an exponential decay rate ($10^{-6}$) \citep{Huang_2016}  and then a staring learning rate of  0.001.
 Then the network was trained using an early stopping method, and for a maximum number of 300 epochs.
@@
 $90\%$ of the images, chosen randomly, for the training and $10\%$ to validate.
-We repeated the process $10$ times to avoid bias due to a specific choice of training/validation set and to define an uncertainty in our ROC (see section \ref{sec:figure_of_merit}) .
+We repeated the process $10$ times to avoid bias due to a specific choice of training/validation set and to define an uncertainty in our ROC.
 
@@
 \begin{enumerate}[label=\Roman*.]
-\item Combination of bands r and i with the average between bands u and g. Use one CNN for classification.
+\item Combination of bands $r$ and $i$ with the average between bands $u$ and $g$. Use one CNN for classification.
 \item Creation of $1$ CNN for each band (total of $4$). The $4$ outputs are used as input to a SVM classifier which returns the final classification $p$. 
@@
 
-\subsection{figures of merit}
+\subsection{Figures of merit}
 \label{sec:figure_of_merit}
@@
 We do not impose a definitive arc/ring magnification, brightness or surface brightness limit for a system to be considered a lens because we
-want to include these "barely lensed" objects to test the limits of the classifiers.
-As we will see, if you restrict your objectives to detecting only lensed images with surface brightness above some threshold, for example, the "best" algorithm might change and the TPR will change.
+want to include these ``barely lensed" objects to test the limits of the classifiers.
+As we will see, if one restricts the objectives to detecting only lensed images with surface brightness above some threshold, for example, the "best" algorithm might change and the TPR will change.
 For this reason we plot the AUROC, TPR$_0$ and TPR$_{10}$ as a function of several variables for all the entries.

### 2019-02-24 paper.tex
Removed one figure and some editing.

@@
 the True Positive Rate (TPR) against the False Positive Rate.
-As shown in Fig.
-\ref{Fig2_gamoclass}, we reached a TPR higher than the 90\% with a FPR < 8\%.
-
-\begin{figure}
-  \centering
-      \includegraphics[width=1\columnwidth]{figures/Fig2_gamoclass.pdf} 
-  \caption{GAMOCLASS ROC (see section \ref{sec:figure_of_merit})  on training data.}
- \label{Fig2_gamoclass}
-\end{figure}
+We reached a TPR higher than the 90\% with a FPR < 8\%.
 
@@
 
-{\bf Implementation}:
+%{\bf Implementation}:
 The CNN is implemented in Python 2.7 using the open-source libraries \textsc{Lasagne}\footnote{\href{http://github.com/Lasagne/Lasagne/}{\tt http://github.com/Lasagne/Lasagne/}} 
@@
 
-{\bf Architecture}:
+%{\bf Architecture}:
 We used the CNN architecture called Resnet described in \citep{he2015deep} with three stacks of residual blocks of 5 layers. 
@@
 
-{\bf Preprocessing}:
+%{\bf Preprocessing}:
 The training image files were preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
@@
 
-{\bf Training}:
+%{\bf Training}:
 The network is trained by minimizing the categorical cross-entropy loss function

### 2019-03-19 paper.tex
modified:   paper.tex
corrections

@@
-%\documentclass[onecolumn]{aa}
 \documentclass{aa}
@@
 %\begin{abstract}
-Large scale imaging surveys will increase the number of galaxy-scale strong lensing candidates by maybe three orders of magnitudes beyond the number known today.
-Finding these rare objects will require picking them out of at least tens of millions of images and deriving scientific results from them will require quantifying the efficiency and bias of any search method.
+Large-scale imaging surveys will increase the number of galaxy-scale strong lensing candidates by maybe three orders of magnitudes beyond the number known today.
+Finding these rare objects will require picking them out of at least tens of millions of images, and deriving scientific results from them will require quantifying the efficiency and bias of any search method.
 To achieve these objectives automated methods must be developed.
@@
 
-Strong gravitational lenses are rare cases where a distant galaxy or quasar is aligned so closely with a foreground galaxy or cluster of galaxies  that the gravitational field of the foreground object creates multiple, highly distorted images of the background object.
+Strong gravitational lenses are rare cases in which a distant galaxy or quasar is aligned so closely with a foreground galaxy or cluster of galaxies  that the gravitational field of the foreground object creates multiple, highly distorted images of the background object.
 The first strong lens was discovered in 1979 by \citet{1979Natur.279..381W} and since then several hundred of them have been found.
@@
 
-\cite{2009ApJ...694..924M} pioneered an automated technique for finding Einstein ring type lenses that uses a lens modeling code to fit a model to all candidates and picks out the ones that fit the model well \citep[see also][]{2017arXiv170401585S}.
+\cite{2009ApJ...694..924M} pioneered an automated technique for finding Einstein ring type lenses that uses a lens modelling code to fit a model to all candidates and picks out the ones that fit the model well \citep[see also][]{2017arXiv170401585S}.
 This approach has the attractive feature that it distinguishes lenses from non-lenses by their similarity to what we expect a lens to look like and priors can be put on the model parameters that are physically motivated, unlike the next category of finders below.
-Challenges arise in making the modeling fast and automatic enough to handle large
+Challenges arise in making the modelling fast and automatic enough to handle large
 data sets while allowing it to be flexible enough to find unusual lens configurations.  The YattaLens entrant to this challenge was of this type.
@@
 These have been used widely for such tasks as handwriting and facial recognition.
-In astronomy, these families of algorithms are beginning to be used for categorizing galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017arXiv170207675P,2017MNRAS.471..167J,2017MNRAS.465.4325O,2017AandA...597A.135B,hartley2017support}.
+In astronomy, these families of algorithms are beginning to be used for categorising galaxy morphologies \citep{2015MNRAS.450.1441D}, photometric redshifts \citep{2017MNRAS.465.1959C,2016PASP..128j4502S,2017NewA...51..169S}, supernova classification \citep{2016ApJS..225...31L} and the lens finding problem \citep{2017arXiv170207675P,2017MNRAS.471..167J,2017MNRAS.465.4325O,2017AandA...597A.135B,hartley2017support}.
 
@@
 This ranking could have been a simple binary (0 or 1) classification  or it could have been a continuous range of numbers representing the probability of being a lens or it could have been a finite number of confidence levels.
-
 The challenge was opened on November 25, 2016 and closed on February 5, 2017.
@@
 Creating the mock images started with a cosmological N-body simulation, in this case the Millennium simulation \citep{2009MNRAS.398.1150B}.
-A catalog of dark matter halos and galaxies  within a light-cone was constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
+A catalogue of dark matter halos and galaxies  within a light-cone was constructed within the Millennium Observatory project \citep{2013MNRAS.428..778O}.
 The challenge sets were based on a 1.6 sq.deg.
@@
 
-The halo catalog was read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
+The halo catalogue was read into the GLAMER lensing code \citep{2014MNRAS.445.1942M,2014MNRAS.445.1954P} to do all the ray-tracing.
 Within this code a Navarro, Frenk \& White (NFW) \citep{1996ApJ...462..563N} profile is fit to the three parameters given above to represent the dark matter component of the lens.
@@
 The lens is extracted as explained above and rotated randomly in three dimensions.
-A source is selected at random from the shapelet catalog subject to a magnitude limit in a reference band.
+A source is selected at random from the shapelet catalogue subject to a magnitude limit in a reference band.
 The redshift of the UDF source is used as the source redshift.
@@
 The visible galaxies associated with the lens must also be simulated.
-There  are too few bright galaxies in the UDF catalog  to make enough mock lens galaxies for this purpose.
+There  are too few bright galaxies in the UDF catalogue  to make enough mock lens galaxies for this purpose.
 Instead, for most of the lenses, we used an analytic model for the surface brightness of these galaxies.
@@
 
-In the full version of YattaLens, a lens modeling step is performed to improve the purity of the sample. However, such a procedure is too time consuming and was not performed in this challenge.
+In the full version of YattaLens, a lens modelilng step is performed to improve the purity of the sample. However, such a procedure is too time consuming and was not performed in this challenge.
 
@@
 
-Similarly to conventional fully-connected neural networks, convolution layers are typically followed  by an element-wise activation function, which allows for the modeling of complex functional forms  by introducing non-linearities in the model.
+Similarly to conventional fully-connected neural networks, convolution layers are typically followed  by an element-wise activation function, which allows for the modelling of complex functional forms  by introducing non-linearities in the model.
 Classical choices  for  activation functions  include the sigmoid-shaped logistic  function (or just sigmoid) $f(x) = 1/ (1  + \exp(-x))$ or the hyperbolic tangent function $f(x) = \tanh(x)$.
@@
 This has yet to be shown however.
-Methods based on fitting with a lens modeling code \citep{2009ApJ...694..924M,2017arXiv170401585S} might also help to mitigate this problem.
+Methods based on fitting with a lens modelling code \citep{2009ApJ...694..924M,2017arXiv170401585S} might also help to mitigate this problem.
 The confidence one will have in the machine learning methods is really limited by the confidence one has in the realism of the simulations.

### 2019-03-20 paper.tex
Corrections.

@@
 \citep[e.g.][]{1964MNRAS.128..307R,1992ARAandA..30..311B,2000ApJ...544...98W,2013ApJ...766...70S,2016AandARv..24...11T}.  
-Their magnification has been used as a natural telescope to observe otherwise undetectable objects at high redshift \citep[e.g][]{2007ApJ...671.1196M,2017MNRAS.464.4823B,2016ApJ...833..264S}.
+Their magnification has been used as a natural telescope to observe otherwise undetectable objects at high redshift \citep[e.g.][]{2007ApJ...671.1196M,2017MNRAS.464.4823B,2016ApJ...833..264S}.
 They have put limits on the self interaction of dark matter and on the theory of gravitation \citep{0004-637X-606-2-819}.
@@
 The form of the challenge and its rules are described in the next section.
-The methods used to simulate mock images of galaxies and gravitational lenses are described in section~\ref{sec:simulation}.
-In section~\ref{sec:entries}, each of the methods that were used to solve the challenge are briefly described.
-We discuss the metrics used to evaluate entries in section~\ref{sec:figure_of_merit}.
-The performance of each of the methods is presented in section~\ref{sec:performance}.
-Finally,  in section~\ref{sec:conclusion}, we conclude with a discussion of what was learned and how methods can be improved in the future.
+The methods used to simulate mock images of galaxies and gravitational lenses are described in Section~\ref{sec:simulation}.
+In Section~\ref{sec:entries}, each of the methods that were used to solve the challenge are briefly described.
+We discuss the metrics used to evaluate entries in Section~\ref{sec:figure_of_merit}.
+The performance of each of the methods is presented in Section~\ref{sec:performance}.
+Finally,  in Section~\ref{sec:conclusion}, we conclude with a discussion of what was learned and how methods can be improved in the future.
 
@@
 These lenses could be used as is, but we wanted to produce a much larger number with more randomness.
-For each caustic we identify the lens plane with the highest convergence and identify all the halos within a three dimensional distance of 0.5 Mpc from the center of the critical curve and on this and its neighboring lens planes.
+For each caustic we identify the lens plane with the highest convergence and identify all the halos within a three dimensional distance of 0.5 Mpc from the centre of the critical curve and on this and its neighbouring lens planes.
 This collection of halos is then used as the lens and rotated to produce more random lenses.
@@
 
-The furthest point in the caustic is found from its own center and the source is placed randomly within 3 times this distance.
-This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses, because all the sources are right in the center of the caustic, and making the process inefficient because most of the sources are too far away from the caustic to produce clear lenses.
+The furthest point in the caustic is found from its own centre and the source is placed randomly within 3 times this distance.
+This is a somewhat arbitrary length designed to be a compromise between producing only very clear strong lenses, because all the sources are right in the centre of the caustic, and making the process inefficient because most of the sources are too far away from the caustic to produce clear lenses.
 If the source positions were taken completely at random the fraction of clear lenses would be very low.
@@
 The Millennium Observatory provides parameters for the galaxies that inhabit the dark matter halos using the semi-analytic galaxy formation models of \citet{2011MNRAS.413..101G}.
-The parameters used here were the total magnitude, the bulge-to-disk ratio, the disk scale height and the bulge effective radius.
-The magnitude and bulge-to-disk ratio are a function of the pass band.
+The parameters used here were the total magnitude, the bulge-to-disc ratio, the disc scale height and the bulge effective radius.
+The magnitude and bulge-to-disc ratio are a function of the pass band.
 Each galaxy is given a random orientation and inclination angle between 0 and $80\degree$.
-The disk is exponential with no vertical height which is why the inclination is limited to $80\degree$.
+The disc is exponential with no vertical height which is why the inclination is limited to $80\degree$.
 The bulge is represented by an elliptical S\'{e}rsic profile with an axis ratio randomly sampled between 0.5 and 1.
@@
 
-In addition to the basic disk and bulge models we introduce some spiral arms.  The surface brightness of 
-the disks are given by
+In addition to the basic disc and bulge models we introduce some spiral arms.  The surface brightness of 
+the discs are given by
 \begin{align}
@@
 \end{align}
-where $R_h$ is the scale height of the disk.
+where $R_h$ is the scale height of the disc.
 The phase angle of the arms, $\phi_d$, is chosen at random.
@@
 These foreground galaxies are rotated in three dimensions with the halos of the lens each time a random lens is produced so that they remain in the same positions relative to the mass.
-All the random parameters are also reassigned with every realization of the lens.
+All the random parameters are also reassigned with every realisation of the lens.
 
@@
 
- In the challenge set the limiting magnitude for background sources was 28 in $i$.   60\% of the cases had no background source and were thus labeled as non-lenses.
+ In the challenge set the limiting magnitude for background sources was 28 in $i$.   60\% of the cases had no background source and were thus labelled as non-lenses.
 
@@
 The following sections contain short descriptions of the lens finding methods that were used in 
-the challenge.  Each subsection refers to a team which gave a separate entry.  We have grouped the 
+the challenge.  Each sub-section refers to a team which gave a separate entry.  We have grouped the 
 methods into four categories according to the type of method used.
 The Receiver Operating Characteristic (ROC) curve and the area under this curve are referred to in these sections.
-The ROC is defined in section~\ref{sec:figure_of_merit} where methods for evaluating the entries is discussed.
+The ROC is defined in Section~\ref{sec:figure_of_merit} where methods for evaluating the entries is discussed.
 A reader unfamiliar with the ROC might want to refer to that section.
 
-\subsection{Visual Inspection}
+\subsection{Visual inspection}
 \subsubsection{Manchester1/Manchester2 (Jackson,Tagore)}
@@
 over a 48-hour period, at the rate of 5000/hr (NJ) and 2500/hr (AT). 
-The overall results, in terms of area under the ROC (see section \ref{sec:figure_of_merit}) curves, were very similar for 
+The overall results, in terms of area under the ROC (see Section \ref{sec:figure_of_merit}) curves, were very similar for 
 both observers. The space-based challenge produced areas of 0.800 and 
@@
 
-A Support Vector Machine (SVM) is a supervised machine learning method which uses labeled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
+A Support Vector Machine (SVM) is a supervised machine learning method which uses labelled training data to determine a classification model (see e.g., \citet{vapnik79estimation}, \citet{Cortes1995} and \citet{Burges1998}).
 A preprocessing stage first extracts a set of useful features from input samples, before projecting each sample as a vector into a high-, possibly infinite-dimensional space.
@@
 Our architecture converges with a classification accuracy of 91\% on the validation sample.
-We further evaluated the performance of our classifier calculating the ROC (see section \ref{sec:figure_of_merit})  curve of the classifier, i.e.
+We further evaluated the performance of our classifier calculating the ROC (see Section \ref{sec:figure_of_merit})  curve of the classifier, i.e.
 the True Positive Rate (TPR) against the False Positive Rate.
@@
 We employed different strategies for the two samples available for the challenge, which involve combinations of the available bands running in one or more CNN, using or not the preprocessing, and combining the output with the aid of other machine learning methods.
-In each case we used the simulations made available for the challenge both to train and to validate the results and we used the area under the ROC (see section \ref{sec:figure_of_merit}) to determine which combination of methods gives the best result.
+In each case we used the simulations made available for the challenge both to train and to validate the results and we used the area under the ROC (see Section \ref{sec:figure_of_merit}) to determine which combination of methods gives the best result.
 We selected 
@@
 To use the information on the $4$ available bands, we needed to either combine $2$ of the $4$ bands to end up with $3$ bands for a single RGB CNN (configuration I below) or we use multiple CNNs (configuration II to VI below).
-To combine the outputs of several CNNs we use a Support Vector Machine \citep[hereafter SVM; see e.g., ][]{rebentrost2014quantum} also implemented in Matlab.
+To combine the outputs of several CNNs we use a Support Vector Machine \citep[ SVM; see e.g.
+][]{rebentrost2014quantum} also implemented in Matlab.
 The SVM is used to combine the outputs $p_i$ of the several CNNs (configurations II, III, IV and VI).
@@
 We then collapsed one of the classes into another to give a binary classification : 0 when a source is classified as a \textit{non-lens} and a 1 when is classified as a \textit{clear lens} or as a \textit{dubious lens}.
-This choice did not allow for building  a continuous ROC (see section \ref{sec:figure_of_merit})  curve but only a binary one.
+This choice did not allow for building  a continuous ROC (see Section \ref{sec:figure_of_merit})  curve but only a binary one.
 The final submission was produced by averaging the values of the predictions from three CNNs with the same architecture.
@@
 %{\bf Preprocessing}:
-The training image files were preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to gray-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
+The training image files were preprocessed with the software \textsc{STIFF}\footnote{\href{http://www.astromatic.net/software/stiff}{\tt http://www.astromatic.net/software/stiff}} which automatically converts the fits files to grey-scale TIFF images operating a non-linear intensity transformations to enhance the low-brightness features of the image.
 Due to memory limitations we down-sampled the images to 84 by 84 pixels. 
@@
 \begin{equation}
-\mathcal{L} = \sum_{i=1}^{n} \big[ y_{i}$ $log(p_{i}) + (1 $ - $ y_{i})$ $log(1 $ - $ p_{i}) \big]
-\end{equation} where $\mathcal{L}$ is the loss function, $n$ is the number of inputs, $y_{i}$ is the true value of the $i^{th}$ input , and $p_{i}$ is the predicted value for the $i^{th}$ input from the network.
+\mathcal{L} = \sum_{i=1}^{n} \big[ y_{i} \log(p_{i}) + (1  -  y_{i}) \log(1  -  p_{i}) \big]
+\end{equation} 
+where $\mathcal{L}$ is the loss function, $n$ is the number of inputs, $y_{i}$ is the true value of the $i^{th}$ input , and $p_{i}$ is the predicted value for the $i^{th}$ input from the network.
 A perfect loss of $0$ was generated once every predicted value matched the true value for every input.
@@
 In this section we summarize the analysis of the submissions.
-In section~\ref{sec:figure_of_merit} we discuss how to judge a classifier in this particular case and define some metrics of success.
-The results for all the submissions are given in section~\ref{sec:performance}.
+In Section~\ref{sec:figure_of_merit} we discuss how to judge a classifier in this particular case and define some metrics of success.
+The results for all the submissions are given in Section~\ref{sec:performance}.
 
@@
  \includegraphics[width=2\columnwidth]{figures/roc_space.pdf}
- \caption{The ROC curves for the space-based entries.}
+ \caption{ROC curves for the space-based entries.}
  \label{fig:roc_space}
@@
  \includegraphics[width=2\columnwidth]{figures/roc_ground.pdf}
- \caption{The ROC curves for the ground-based entries.
-Notice that these are generally better than in figure~\ref{fig:einstein_space} indicating that colour information is an important discriminant.
-}
+ \caption{ROC curves for the ground-based entries.  Notice that these are generally better than in figure~\ref{fig:einstein_space} indicating that colour information is an important discriminant. }
  \label{fig:roc_ground}
@@
  \includegraphics[width=2\columnwidth]{figures/roc_kids.pdf}
- \caption{The ROC curves for the ground-based entries including only the cases with authentic images taken from the KiDS survey.
+ \caption{ROC curves for the ground-based entries including only the cases with authentic images taken from the KiDS survey.
 It can be seen that in all cases these are lower than in figure~\ref{fig:roc_ground}.}
@@
 Figures~\ref{fig:roc_space} and \ref{fig:roc_ground} show the ROC curves for all the entries.  
-Note that ROC curves for the ground-based challenge (figure~\ref{fig:roc_ground}) are uniformly better than those for the space-based challenge (figure~\ref{fig:roc_space}).
+We note that ROC curves for the ground-based challenge (figure~\ref{fig:roc_ground}) are uniformly better than those for the space-based challenge (figure~\ref{fig:roc_space}).
 This is because of the importance of colour information in discriminating lensed arcs from pieces of the foreground lens galaxy.
 
-In addition, figure~\ref{fig:roc_kids} shows the ROC curves for only the ground-based images where an actual KiDS image was used (see section~\ref{sec:sim-ground-based}).
+In addition, figure~\ref{fig:roc_kids} shows the ROC curves for only the ground-based images where an actual KiDS image was used (see Section~\ref{sec:sim-ground-based}).
 It can be seen that the classifiers do uniformly less well on this subset.
@@
 Interestingly some methods' TPRs go up with this quantity and some go down.
-We have not yet found any clear explanation for this variety of behaviors.
+We have not yet found any clear explanation for this variety of behaviours.
 %\red{explanation?}
@@
 
-\section{Conclusions \& discussion}
+\section{Conclusions and discussion}
 \label{sec:conclusion}
